### 2015-09-09 ms.tex
some edits/suggestions for the title and abstract

\documentclass[iop,numberedappendix,apj]{emulateapj}

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color,xcolor}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
%\usepackage[dvipdfmx]{color}
%\usepackage[dvipdfmx]{graphicx}

% trivial change as a test

\bibliographystyle{apj}

\def\memoYF#1{\color{red}$[${\bf #1}$]$ \color{black}}

\def\memoDS#1{\color{blue}$[${\bf #1}$]$ \color{black}}

\def\memoNZ#1{\color{green}$[${\bf #1}$]$ \color{black}}

\definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
\def\memoTM#1{\color{DarkGreen}$[${\bf #1}$]$ \color{black}}

\def\plotonesc#1{\centering \leavevmode
\includegraphics[clip=, width=1.70\columnwidth]{#1}}
\def\plotoneh#1{\centering \leavevmode
\includegraphics[clip=, width=.95\columnwidth]{#1}}
\def\plotone#1{\centering \leavevmode
\includegraphics[clip=, width=.85\columnwidth]{#1}}
\def\plotoneShrinkSmall#1{\centering \leavevmode
\includegraphics[clip=, width=.49\columnwidth]{#1}}
\def\plotoneShrinkMed#1{\centering \leavevmode
\includegraphics[clip=, width=.55\columnwidth]{#1}}
\def\plotoneShrinkBig#1{\centering \leavevmode
\includegraphics[clip=, width=.65\columnwidth]{#1}}
\def\plottwo#1#2{\centering \leavevmode
\includegraphics[width=.45\columnwidth]{#1} \hfil
\includegraphics[width=.45\columnwidth]{#2}}
\def\plottwob#1#2{\centering \leavevmode
\includegraphics[width=.49\columnwidth]{#1} \hfil
\includegraphics[width=.49\columnwidth]{#2}}
\def\plottwor#1#2{\centering \leavevmode
\includegraphics[width=.55\columnwidth,angle=90]{#1} \hfil
\includegraphics[width=.55\columnwidth,angle=90]{#2}}
\def\plotthree#1#2#3{\centering \leavevmode
\includegraphics[width=.3\columnwidth]{#1} \hfil
\includegraphics[width=.3\columnwidth]{#2} \hfil
\includegraphics[width=.3\columnwidth]{#3}}

\newcommand{\cN}[1]{\mathcal{N}}
\newcommand{\pn}[1]{\mbox{$(#1)$}}
\newcommand{\spa}{\mbox{ }}
\def\gsim{\;\rlap{\lower 2.5pt
 \hbox{$\sim$}}\raise 1.5pt\hbox{$>$}\;}
\def\lsim{\;\rlap{\lower 2.5pt
   \hbox{$\sim$}}\raise 1.5pt\hbox{$<$}\;}

\newcommand{\Tcmb}{\mbox{$T_{\mbox{\tiny CMB}}$}}
\newcommand{\Tsky}{\mbox{$T_{\mbox{\tiny sky}}$}}
\newcommand{\Tsys}{\mbox{$T_{\mbox{\tiny sys}}$}}
\newcommand{\Trx}{\mbox{$T_{\mbox{\tiny rx}}$}}
\newcommand{\sigRMS}{\mbox{$\sigma_{\mbox{\tiny RMS}}$}}

% set formatting properties
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.8in}
\setlength{\hoffset}{0.0in}
\setlength{\voffset}{-0.4in}
%\setlength{\voffset}{0.3in}
\parindent 0.2in
\parskip 0.1in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE DOCUMENT BEGINS HERE                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\slugcomment{Submitted to ApJ, XX September 2015}

\begin{document}

%%% Begin front material
%\twocolumn[%%% Begin front material

\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?
\memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' 
or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}}

\author{
%
Yuka Fujii\altaffilmark{1} 
%
David S. Spiegel\altaffilmark{2,3}
%
Tony Mroczkowski\altaffilmark{4,5}
%
Jason Nordhaus\altaffilmark{6,7}\\
%
Neil T. Zimmerman\altaffilmark{8}
%
Aaron Parsons\altaffilmark{9}
%
Nikku Madhusudhan\altaffilmark{10}
%
Mehrdad Mirbabayi\altaffilmark{2}
}

\affil{$^1$Earth-Life Science Institute, Tokyo Institute of Technology, 
  Tokyo, JAPAN, 152-8550}

\affil{$^2$Astrophysics Department, Institute for Advanced Study,
  Princeton, NJ 08540}

\affil{$^3$Research \& Development, Sum Labs,
  New York, NY  10001}

\affil{$^4$National Research Council Fellow}

\affil{$^5$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^6$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^7$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}

\affil{$^8$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}

\affil{$^9$Astronomy Department, University of California Berkeley}

\affil{$^{10}$Astronomy Department, University of Cambridge, UK}

\vspace{0.5\baselineskip}

\email{
yuka.fujii@elsi.jp
}

\begin{abstract}
%%%
When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a massive stellar wind.
Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields.
We predict that RGHJs might be as bright as canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances less than a few hundred parsecs with current/future instruments such as LOFAR and SKA.

%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars. 
%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars.
%Post-main-sequence stars lose mass at much higher rates than main-sequence stars.
%A jovian planet passing through the dense winds of its RGB or AGB host can capture stellar wind in its magnetosphere, leading to radio emission from electrons spiraling in the magnetic field.
%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
%Counterintuitively, a plausible toy model suggests that a stronger planetary magnetic field leads to lower spectral flux density, and might therefore make objects more challenging to observe.
%Still, for a range of planetary and stellar parameters, a RGHJ might generate a radio luminosity that would be visible from kiloparsec distances.
\end{abstract}

\keywords{planets and satellites: Jupiter --- Sun: evolution ---
  planetary systems --- stars: evolution ---
  stars: AGB and post-AGB}
%]%%% End front material

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g. stellar wind particles and particles from Io-like moons. 
Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}. 
Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
\citet{farrell1999,zarka2001,lazio2004} pointed out that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass. 
%\citet{griesmeier2004} modeled in detail the evolution of atmosphere and magnetic field of the tidally-locked close-in stars and found that 
\citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
\citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed model of stellar wind property in the proximity of the stars. They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME). 
Note that in these papers, the scaling relation of planetary magnetic fields  differ from paper to paper.    
In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission.  
Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.

When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
they evolve through the red-giant branch (RGB) and the
asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}. 
Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr. 
On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.

Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission, probably below the detection limit.

In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit strong X-rays, thereby ionizing the hydrogen atoms around the planet.
The ionized stellar wind would then interact with the planetary magnetic field in the same way as Solar System planets do.
Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to the previous result.
Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
Instead, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.

In \S2, we describe our assumptions for the stellar wind, planetary magnetosphere, frequency of radio emission, and scaling of planetary radio emission.
\S3 presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
\S4 gives predictions for the signals from evolved systems within 400 pc, taking account of the intrinsic radio emission from the host evolved stars. Considering the sensitivity of the current and future radio instruments, we argue that SKA, and perhaps LOFAR-HBA as well, would be capable of detecting these signals within a reasonable integration time. 
%In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
In \S5, we mention the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.  
Finally, \S6 concludes the paper with a brief summary.

%Roughly 20\% of the more than 700 \memoYF{check!} currently known exoplanets around main-sequence stars \footnote{See online catalogs such as http://www.openexoplanetcatalogue.com/ \citep{rein2012}, http://exoplanet.eu \citep{schneider_et_al2011}, or http://exoplanets.org \citep{wright_et_al2011} for up-to-date lists.} have masses greater than half of Jupiter's, orbital radii greater than 1~AU, and will become hot Jupiters (i.e., for the present purposes, this means they will receive at least as much irradiation as the currently known hot Jupiters/Neptunes \citep{spiegel+madhusudhan2012}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
\label{s:assumptions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{In the end the number of significant decimal digits is set to 1 or 2.}

Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.  
Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Planetary Magnetic Field}
\label{ss:magneticfield}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We estimate the planetary magnetic field of general planets  
simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.

So far, several scaling relations for the planetary magnetic field strength  
have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
which are summarized and compared with numerical simulations in \citet{christensen2010}. 
We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars: 
%\memoYF{describe in more detail}:
%%%%%%%%%% 
%\begin{equation}
%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
%\end{equation}
\begin{equation}
B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
\end{equation}
%%%%%%%%%%
%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is an efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}. 
Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
Dipole magnetic field strength at the planetary surface, denoted by $B$, is then scaled by
%%%%%%%%%%
\begin{equation}
B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
\end{equation}
%%%%%%%%%%
where $r_{\rm dynamo}$ is the radius of the outer boundary of the dynamo region.

Note that the scaling law, Equation (\ref{eq:Bscaling}), would be reasonable only for rapidly rotating objects.
Indeed, unlike canonical hot Jupiters, RGHJs are not tidal locked to their host stars, so we do not have to assume slow spin rotation rates \citep{spiegel+madhusudhan2012}.
Therefore, we implicitly assume that the RGHJs we consider in this paper are rapidly rotating so that they generate planetary magnetic fields through the same mechanism as Jupiter.

In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need models of the internal planetary structure. 
We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
\end{equation}
%%%%%%%%%%
We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core. 
In the case of Jupiter, $r_{\rm dynamo, J} = 0.85 R_{\rm J}$ and $\rho_{\rm dynamo, J} = 1.899~{\rm g/cm}^3$.

The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$. 
The time-dependence luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
Ignoring the relatively weak dependence on average atmospheric Rosseland mean opacity leads to:
%%%%%%%%%%
\begin{equation}
L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
Therefore, we have
%%%%%%%%%%
\begin{equation}
q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
\label{eq:burrowsHeatFlux}
\end{equation}
%%%%%%%%%%

Substituting Equation~\ref{eq:burrowsHeatFlux} into Equation~\ref{eq:Bscaling2} and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
%%%%%%%%%% 
\begin{equation}
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
\end{equation}
%%%%%%%%%%
under this model.

%We note that the scaling relation based on \citet{christensen_et_al2009}, or equation (\ref{eq:Bscaling}), has also been adopted in \citet{reiners2010}. While the detailed treatment of $\rho _c$ and $q_o$ are different, two estimates of planetary magnetic field strength are fairly close, as shown in \S3 below.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Stellar Wind}
\label{ss:stellarwind}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Another ingredient needed for modeling the radio emission from the interaction between the planetary magnetic field and the stellar wind is the density and velocity of the stellar wind. 
The number density of electrons in the stellar wind, $n$, can be expressed as
%%%%%%%%%% 
\begin{equation}
n = \frac{\dot M_\star}{4\pi a^2 m_p v}
\label{eq:n}
\end{equation}
%%%%%%%%%% 
where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.

While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
Therefore, we have
%%%%%%%%%% 
\begin{equation}
\frac{\dot M_\star}{\dot M_{\odot}} \sim 10^6 - 10^9 \, . \label{eq:scale_Mdot}
\end{equation}
%%%%%%%%%%

On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to the expanded stellar radius).
%\footnote{Escape velocity is $\sqrt{2GM/r}$.}
Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
Therefore, 
%%%%%%%%%% 
\begin{equation}
\frac{v}{v_{\odot}} \sim 10^{-1} \, . \label{eq:scale_v}
\end{equation}
%%%%%%%%%% 
%where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.

Based on equations (\ref{eq:scale_Mdot}) and (\ref{eq:scale_v}), the number density of the stellar wind (equation (\ref{eq:n})) are normalized as follows:
%%%%%%%%%% 
\begin{eqnarray}
n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2}. \label{eq:n_normalized}
\end{eqnarray}
%%%%%%%%%% 
\memoYF{check the values above}

As discussed in \citet{ignace2010}, the ionization fraction of the stellar wind of evolved stars are supposedly as low as $\sim 10^{-3}$\memoYF{cite something}. Since only charged particles interact with planetary magnetic field, this suggests the inefficient interaction with planetary magnetosphere and hence low input energy for radio emission. 
However, at this stage, the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
\citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are: 
%%%%%%%%%
\begin{eqnarray}
L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
%
T_{\rm acc} \sim && 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
\sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). 
\end{eqnarray}
%%%%%%%%%
The accretion disks around planets therefore emit X-ray radiation. 
We estimate the scale of the ionized region by computing Stromgren radius of the accretion disk \citep{stromgren1939}: 
%%%%%%%%%
\begin{equation}
R_{\rm stromgren} = \frac{3}{4\pi} \left( \frac{S}{n^2 \beta } \right)^{1/3}
\end{equation}
%%%%%%%%%
where $S$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
% http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
% T \propto 4.3e-13 ( T /10^4 K )^-0.7
%%%%%%%%%
\begin{eqnarray}
%\beta &=& 4.3? \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
\beta &=& 2.6 \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
&\sim& 2.74 \times 10^{-14} \; \left( \frac{M_p}{M_J} \right)^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} 
\end{eqnarray}
%%%%%%%%%
The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV ($\lambda = $), the energy needed to ionize hydrogen atoms.
As a result, 
%%%%%%%%%
\begin{eqnarray}
S_* \sim  
  \left\{
    \begin{array}{ll}
      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
    \end{array}. 
  \right.
\end{eqnarray}
%%%%%%%%%
Using the number density of hydrogen atoms given by equation (\ref{eq:n_normalized}), 
%%%%%%%%%
\begin{eqnarray}
R_{\rm stromgren} \sim  
  \left\{
    \begin{array}{ll}
      40 ~R_J & \;\;\;(M_p = M_J) \\
      400 ~R_J & \;\;\;(M_p = 10 M_J)
    \end{array}
  \right.
\end{eqnarray}
%%%%%%%%%
for a planet around a red giants at 5~AU.

We therefore expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.
This implies that the stellar wind particles represented by (equation~\ref{eq:n}) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.

%\citet{drake1983}
%\citet{}
%\color{black}

%The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}. 
%\begin{equation}
%\frac{T}{T_{\odot}} \sim 10^{-2}
%\end{equation}
%where $T_{\odot } \sim 10^6$ K.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Frequency of Radio Emission}
\label{ss:model_frequency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $f_{\rm cyc}$: 
%%%%%%%%%% 
\begin{equation}
f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
\end{equation}
%%%%%%%%%%
where $e$ and $m_e$ are the charge and mass of the electron, respectively.

Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
The plasma frequency may be expressed as
\begin{eqnarray}
f_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
 & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
\label{eq:fplasma}
\end{eqnarray}
In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $f_{\rm plasma}^\oplus \lsim 10$~MHz.
At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
Therefore, combining Eq.~(\ref{eq:n}) and Eq.~(\ref{eq:fplasma}), we have
%%%
\begin{eqnarray}
\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
\label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
 & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
\end{eqnarray}
\memoYF{check numbers in above equation}
%%%
%where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flux of Radio Emission}
\label{ss:model_intensity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$, can be expressed by:
%%%
\begin{equation}
F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta \nu}
\label{eq:Fnu}
\end{equation}
%%%
where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.

We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
%%%
\begin{eqnarray}
P_{\rm radio} &\propto & P_{\rm inp} \\
P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag} \, ,
\end{eqnarray}
%%%
where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.

On the other hand, in the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}. 
In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.

In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}. 
Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.

The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about a half of actual radius of magnetosphere \citep[][]{griesmeier2005}. 
By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
%We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
\nonumber r_s 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
\nonumber &=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

%Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field. 
%In the following, we describe our assumptions for these properties.

We assume that the solid angle of the emission is same as the Jupiter's one for all of the exoplanets.
In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission. 
The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following \citet{griesmeier2007b}.

%We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{s:result}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
\label{ss:Bplanet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s

Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age. 
%Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
Reasonably, the resultant values are in a good agreement with \citet{reiners2010}, which adopted the same scaling law for planetary magnetic field; we show this figure just for self-completeness.

%%%%%%%%%% 
%\begin{eqnarray}
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
%\end{eqnarray}
%%%%%%%%%%
%under this model. 
Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
LOFAR, Hera, SKA, and upgrades to the VLA.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{fig1_linear.pdf}
   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
  \label{fig:planetaryB_pre}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{fig2_Christensen.pdf}
   \caption{Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
  \label{fig:planetaryB}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
\label{ss:brightness}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows:
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
\end{eqnarray}
%%%

We may compare radio emission power of canonical hot Jupiters set at 0.05 AU  and that of RGHJs at 5 AU.
%Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%%
Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker. 
%\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[htp]
%\caption{Canonical Parameters of 2 types of hot jupiters.}
%\begin{center}
%\begin{tabular}{c|cccc} \hline \hline
%& mass & magnetic field & orbit &  spin period \\ 
%& $M_p$ & B & $a$ &  \\ \hline
%canonical HJ & $M_J$ & $B_J$ & 0.05 AU & 4 days \\
%RGHJ & $M_J$ & $B_J$ & 5 AU &  0.4 days \\ \hline
%\end{tabular}
%\end{center}
%\label{tab:comp_HJ}
%\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
%   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
%   \plotonesc{radio_emission_Mdot1e-5_constRp_christesnsen.pdf}
	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom). The systems are located at 100 pc away. The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $f_{\rm cyc}$) is below the plasma frequency cut-off, $f_{\rm plasma}^{\rm los}$. The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1f_{\rm cyc}$, is below $f_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system. }
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Combining the expressions above, we find that the radio spectral flux density observed at the Earth is:
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
&\approx & 5.22\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
%%%
&\approx & 1.12 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
%%%
&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
%%%
&\approx & 2.42 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
\end{eqnarray}
%%% 
%\memoYF{cite original paper!}. 
Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them. 
Note that, within this framework, the {\it spectral} radio flux has necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}. 
Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$. This originates from the different scaling laws for the planetary magnetic field and that their paper didn't incorporate the compression of the planetary magnetosphere due to massive stellar wind.

Using the model for planetary magnetic field strength, we may consider the  radio spectral intensity and maximum frequency of given planetary mass and age. 
Figure \ref{fig:radio} shows the contours of spectral radio flux of planetary companions at 4.5~Gyr with varying masses and orbital distances. 
The target system is located at a distance of 10~pc from the Earth; the flux can be scaled by the distance as a quadratic function. 
The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.

Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}).
We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency:
%%%
\begin{equation}
\label{eq:fcyc>fplasma} f_{\rm cyc} > f_{\rm plasma}^{\rm los}
\end{equation} 
%%%
The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where this criteria is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
In reality, the peak of the auroral radio emission does not always occur at the maximum frequency. Instead, it usually exits at lower frequencies. Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission. In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 
It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. For a red-giant system, the most promising target if massive companion with $M_p \gtrsim 5M_J$. On the other hand, for a AGB-star system, it is very difficult to detect a signal from the planetary-mass companions within 100 AU.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[bp]
 %\begin{minipage}{0.5\hsize}
  %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
%   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
  %\end{center}
 %\end{minipage}
 %\begin{minipage}{0.5\hsize}
   %\begin{center}
   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
%   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
  %\end{center} 
 %\end{minipage}
%   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc. The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion. Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
%  \label{fig:radio}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observability}
\label{s:observability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we discuss the observability of the estimated radio emission. 
An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planets.
We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
Then, we estimate the radio emission of Jupiter-twin around known M giants in \S\ref{ss:actualMgiants}. 
In \S\ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
radio instruments at relevant frequencies.
Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a mean to discern the signals from the background noise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Intrinsic radio emission of red giants stars}
\label{ss:RGradio}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
Almost all observations have been carried out 
%at wavelengths of 6 cm and below, 
at frequency of 5 GHz or above, 
probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.

Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars 
%at wavelengths above 20 cm 
at frequencies below 1 GHz ($L$ band); both yielded null results.
First, a program that observed a sample of nine M-type giants at 430 MHz with the Arecibo Telescope failed to detect any of the sources down to flux density 10 mJy~\citep{Fix1976}.
Later, with the Molonglo Observatory Synthesis Telescope (MOST), a sample of eight K- and M-type giants were observed at 843 MHz; the upper limits of their flux densities were placed at approximately 1 mJy~\citep{Beasley1992}.
Current facilities could achieve far deeper sensitivity on similar targets.
For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a sensitivity better than 0.5~mJy in under an hour.
However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.

The only red giants that have been detected at meter wavelengths are those in interacting binary systems like those of the RS CVn type.
For example, van den Oord and de Bruyn detected plasma maser emission from II Pegasi at 360 MHz and 609 MHz with the WSRT~\citep{vandenOord1994}.
Although single dwarf-type main sequence stars are also known to exhibit bright, coherent radio flares~\citep{Bastian1990}, no analog to this non-thermal emission process has been proposed to exist for evolved stars.

Altogether, we lack firm observational constraints on the brightnesses of M giants near %1-m wavelengths.
30-300 MHz frequencies.

However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index when available. 
%In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz. 
% YF: This is consistent with the following equation, so I removed it to avoid redundancy. 
%
\citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy. 
Using these data, we extrapolate the radio flux from the host star to the lower frequency range with a simple power law as follows:
%%%
\begin{eqnarray}
\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
&& \times \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 ~R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
\end{eqnarray}
%%%
where the power index $\alpha $ is order of unity.

Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
Note that the thermal contribution from accretion disk is negligible in this figure. 
The spectral shape is modeled by simply scaling the Jovian radio spectra e.g. Figure 8 of \citet{zarka_et_al2004}. 
The continuum from the star in the case of $\alpha =0.6$ is shown as an extreme case; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}. 
As Figure \ref{fig:cartoon} indicates, with the reasonable range of spectral index, radio emission from the stars is by order of magnitude smaller than the expected radio flux from RGHJs at frequencies below 300~MHz. 
For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies is smaller.

Therefore, in the following, we ignore the radio emission from the red giant as a noise source.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tbp]
   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
  \label{fig:cartoon}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radio Flux from Nearby M giants}
\label{ss:actualMgiants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbhp]
   \plotoneh{radio_1Mp.pdf}
   \plotoneh{radio_10Mp.pdf}
%   \plotoneh{radio_1Mp_5AU.pdf}
%   \plotoneh{radio_5Mp_5AU.pdf}
%   \plotoneh{radio_2Mp_4-5Gyr.pdf}
%   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 10$M_J$ at 1 AU and 5AU.
Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
  \label{fig:observability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions. 
For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
%%%
\begin{equation}
\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
\end{equation}
%%%
where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
The factor $\eta $ is $\sim 0.3-3$, and we assume $\eta =1$ here. 
The velocity of stellar wind is assumed to scale with the escape velocity, hence
%%%
\begin{equation}
v \propto \sqrt{\frac{2GM_\star}{R_{\star }}}
\end{equation}
%%%
The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass.
We assume \memoYF{validation}:
%%%
\begin{equation}
t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
\end{equation}
%%%
In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.

Using these data, we can now calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\sim 300$~MHz (equations (\ref{eq:scalingB}) and (\ref{eq:fcyc})).

Figure \ref{fig:observability} displays the estimated radio intensity (i.e., cyclotron frequency) of Jupiters [A] and [B] around M-type red giants within 100~pc. 
Jupiters are placed at 1 AU and at 5 AU for reference. 
The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross).

%\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
%I wondered this because if planets at 1 AU would be engulfed anyway it would not be worth discussing here. According to e.g. Nordhaus and Spiegel (2013) it is the case--however, some planets may migrate inward within 1 AU after evolution. So it should be ok. In any case this is not the main point of this paper and I would leave it out.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Detectability with Current and Near Future Low Frequency Radio Instrumentation}
\label{ss:detectability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tablecaption{Detectability of Hot Jupiters with Current 
and Future Radio Telescopes.\label{tab:sens}}
\tablehead{
Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
           & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
\startdata
LOFAR-LBA  &  30-80  & 700   & 120000             & 8.3  & 42 \\ 
LOFAR-HBA  & 110-200 &  35   &    310             & 3.3  & 1.1 \\  
HERA       &  30-80  & 870   & 160000             & 1030 & 4.2$\times10^5$\\ 
GMRT       & 130-190 & 430   &  46000             & 16.5 & 56.9 \\ 
%LWA       &  30-80  & 58000 &  702127141         & 10.3 & 42.2 \\
%MWA       &  30-80  & 29000 &  176223211         & 1030 & 4.2$\times10^5$ \\
SKA-Low (part) & 50-200 & 7.8 &  12.6             & 7.6  & 9.7 \\
SKA-Low (full) & 50-350 & 2.2 &  1.0              & 4.8  & 1.5 \\
%VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
VLA-LOBO   &  50-350 &  92   &  1800              & 8.6  & 10.4
\enddata
%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
in this table (Equation~\ref{eq:rms_sens}).}
\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
\tablenotetext{c}{Source confusion RMS contribution.}
\end{deluxetable*}
%
% HERA
% http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
%
% LOFAR
% https://www.astron.nl/~heald/test/sens.php; 
% 24 core stations, 16 remote, 8 international, 488 subbands
%
% GMRT
% http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We consider in this section several current and near future radio observatories that operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum sensitivities less than 1~mJy in a few hours.
The results are summarized in Table~\ref{tab:sens}.

The primary limitation to detectability is a telescope's sensitivity, characterized by the root mean square (RMS) noise fluctuations in the sky and receiver.
The RMS noise \sigRMS\ in an interferometric observation with integration time $\tau$, bandwidth $\Delta \nu$, effective area $A_{\rm eff}$ ($\approx0.7 \pi (D/2)^2$ for interferometers comprising antennas with dish size $D$), and $N$ antennas is \citep[see e.g.][]{condon+ransom2016}
%%%
\begin{equation}
\sigRMS = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
\label{eq:rms_sens}
\end{equation}
%%%
Here, \Tsys\ is the blackbody temperature equivalent of the total system noise, which is the sum of the instrument or receiver noise temperature \Trx\ and the noise contribution from the sky \Tsky.
We estimate \Tsky\ using the low frequency sky noise temperature fit from \cite{Rogers+Bowman2008}:
%%%
\begin{equation}
\Tsky = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + \Tcmb 
\end{equation}
%%%
where $T_{150} = 283.2~\rm K$ is the \Tsky\ at 150~MHz, $\beta=2.47$, and $\Tcmb = 2.73~\rm K$ is the contribution from the cosmic microwave background (CMB).
While this relation was fit to data taken in the 100-200~MHz range, the authors found it to be consistent with published measurements from 10-408~MHz. 
%The \Trx\ is the receiver noise temperature, which depends on the instruments and is described below.

An additional contribution to the noise is due to source confusion, the imaging noise associated with unresolved interloping radio sources in an observation.
Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
To estimate $\sigma_c$, reported in Table~\ref{tab:sens}, we use the relations provided by \cite{condon+ransom2016}, reproduced below:
%%%
\begin{eqnarray}
\sigma_c & \approx & 0.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^2\!\!\!\!,~(\theta > 10\arcsec) \\
\sigma_c & \approx & 2.2 \left( \frac{\nu}{1 \rm~GHz} \right)^{-0.7} \left( \frac{\theta}{1\arcmin} \right)^{10/3}\!\!\!\!\!\!\!\!\!\!,~(\theta < 10\arcsec).
\end{eqnarray}
%%%
The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time.
Therefore both the circularly polarized nature of the emission from hot Jupiters and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing hot jupiters, like other time-variable sources, to be detected below the imaging confusion limit.
We therefore expect confusion not to be a strong limitation to detectability of hot Jupiters.

% LOFAR
The LOw-Frequency ARray (LOFAR) operates as two separate arrays defined by their high and low bands, differing configurations, and antenna designs, which are called respectively the Low Band Antennas (LBA) and High Band Antennas (HBA).
LOFAR-LBA operates in the 10-90~MHz range, and LOFAR-HBA operates in the 100-240~MHz range \citep{vanHaarlem2013}.
We consider it as two separate instruments here.
LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz.
Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the reciever noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.

% HERA
The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) \ldots \memoYF{write here (Aaron?)}

% GMRT
The Giant Metre-wave Radio Telescope (GMRT) is an array comprising thirty 25-meter antennas, operating at frequencies 130-2000~MHz.
The lowest band (130-190~MHz) exhibits receiver noise $T_{\rm rx}$ comparable to the sky noise.
To be conservative, we use the GMRT online calculator.\footnote{\url{http://gmrt.ncra.tifr.res.in/~astrosupp/obs\_setup/sensitivity.html}}

% SKA
The low frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used to detect $\sim 30 M_J$ hot Jupiters.
We adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ as above, and assume $\Trx \approx 60~\rm K$.
We caution that these assumptions are optimistic, and the time estimates could in reality be a factor of a few worse.

% VLA
For the low frequency receivers (28-80~MHz; 4-Band) in the \memoDS{Long Wavelength Array (LWA) and the?}\memoTM{No need to mention LWA here.  The receivers are the same in the VLA 4-band and the LWA, but the LWA is far too insensitive to consider here, as is VLA 4-band alone, so the reference just serves to place an upper limit on what \Trx\ will be for LOBO.} Very Large Array (VLA), the receiver noise temperature $\Trx \approx 260~\rm K$ \citep{Hicks2012} and is subdominant to \Tsky\ by at least -6~dB.
Future upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU} are being considered, and would cover the full 30-470~MHz band.
We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly from $\Trx \approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to $\Trx \approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion of the full 30-470~MHz band.

The estimates of the noises shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequency relevant to the radio emission from Jupiter-size planets, current instrument sensitivities are too low for detection.
On the other hand, for more massive exoplanets ($M_p\sim 10 M_J$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
LOFAR-HBA has reasonable sensitivity to $M_p =10~M_J$ planets at 5 AU around a few closest systems as well as those around further stars but orbiting closer to the stars. 
More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_J$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discriminating from Background}
\label{ss:timevariability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Since the confusion limit is on the same order as the signal (Table \ref{tab:sens}), it is crucial to consider the ways to discriminate the signal from the confusion sources. In this section, we discuss time variability and polarization as keys to identify the auroral radio emission from the planets.

One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}.
...\memoYF{write here (YF)}

Another key is that auroral radio emission from planets is not a static source but it significantly varies in time. 
The potential factors that cause time variability of the auroral radio emission are  listed below.

\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis. 
%
\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because the presence of Io inputs plasmas into the system. 
Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.

\paragraph{Variability of stellar wind (months $\sim $)?}
Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
\memoYF{To Jason: time variability?}
%
\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
If the planetary orbit is close to the edge-on configuration, the radio emission disappears synchronously to the orbital period, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
The probability of the latter one, secondary eclipse, is $\sim a/R_\star \sim 9$\% (in the case that $a=5~\mathrm{AU}$ and $R_{\star}=100R_{\odot }$). 
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{s:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implication for discovery and characterization of exoplanets}
\label{ss:implication}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{Need to elaborate. References are needed. }

So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
Therefore, one possible strategy is to target at the know planetary systems.  
One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox[m/s]$. 
Therefore, there are some parameter spaces where current radial velocity observations cannot survey. For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.

%For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means. 
%The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants). If the orbital period is long enough compared to the period of pulsation, it is possible to average out the pulsation and detect radial velocity of planetary component, but this requires long period monitoring. For transit observation Pulsation also contributes to the noise in detecting transit signals \memoYF{?} and besides the transit signals would be as low as 1ppm. Due to the great luminosity of the host star, direct imaging is also difficult \memoYF{?}. Thus, for the time being, one would have to aim at discovering planetary companions around evolved stars, rather than targeting at known planetary systems.

Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes. In turn, we could utilize the time variability to characterize the system. For example, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets. 
If the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).

If the spectra are obtained, the upper cut-off frequency of the radio spectra will imply us the magnetic field strengths of the planetary surface. Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because once both magnetic field strength and the planetary mass is constrained, the proposed scaling law of planetary dynamo may be contested. 
On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the density of the stellar wind at the planetary orbit.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Luminosity function of planetary radio emission}
\label{ss:Lfunc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known one could estimate the likelihood of detecting RGHJs in radio surveys. For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume. Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $f_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$. Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection. For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.

Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy. In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars. As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$. Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where, $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}. 
Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} [(R_\star/M_\star)(1+A/g_\star)]^{1/2}$. Therefore, the LF of giant host stars is an essential ingredient for determining the LF for RGHJs which future surveys would need to consider.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Back-reaction of a plasma flowing into a magnetic field}
\label{ss:offset}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

One might expect that plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field. 
To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field. 
A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
%%%
\begin{equation}
r=\frac{mv_\bot }{eB}.
\end{equation}
%%%
which creates a magnetic dipole
%%%
\begin{equation}
\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B}.
\end{equation}
%%%
The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
%%%
\begin{equation}
\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
\end{equation}
%%%

Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
%%%
\begin{equation}
\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B},
\end{equation}
%%%
where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively. 
%If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.

Just inside the stand-off point, 
%%%
\begin{equation}
m_p n[r_s] v^2 < \frac{B[r_s]^2}{2\pi }
\end{equation}
%%%
and thus $\rho_K/\rho _B < 1$. 
When the particle spirals into the planet, 
the magnetic pressures increases (by beaming?) by 
%%%
\begin{equation}
\frac{B^2}{8\pi } \propto \frac{1}{r^6}
\end{equation}
%%%
On the other hand, the kinetic energy of the moment increases
%%%
\begin{equation}
\frac{mv^2}{2} \propto \frac{1}{r}
%\rho _K \propto \frac{1}{r}
\end{equation}
%%%
Therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.

%It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind. 
Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
Based on such a picture, massive stellar wind of red giants and AGB stars would interact with planetary magnetic field and inputs kinetic energy into magnetospheres of RGHJs. 
We found that the intrinsic brightness of radio emission from RGHJs would be comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.

A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind. Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 15 MHz$ for typical red giants and $\sim 464 MHz$ for typical AGB stars. 
The most promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).

The radio flux from a system with an exoplanet at 5 AU at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy. 
Such signals would be detectable with SKA within a day or so. 
For a few nearest systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time. 
In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confusion sources.

Once the planetary radio emission is detected, ...\memoYF{write here}.

%Admittedly, uncertainties exist in the relation between radio emission of Jovian planets and the input energy from stellar wind, as well as in the scaling of planetary magnetic field. 
%Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.
%The viability of these scaling relations will be examined in the future.

%The planetary magnetic moment is computed based on the simple scaling relationship given by \citep{christensen2010}. 
%-about detectability
%-number of evolved stars within 100pc $\sim 1000$.

\vspace{0.5in}

\acknowledgements

{\sc Acknowledgments}

YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
DSS gratefully acknowledges support from a fellowship from the AMIAS group.
We thank David Hogg for encouraging us to pursue calculations of explanetary radio emission.
NM acknowledges support from [???]. 
YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
The portion of this research for which TM is responsible was performed while he held a National Research Council Research Associateship Award at the Naval Research Laboratory (NRL).
Basic research in radio astronomy at NRL is supported by 6.1 Base funding.

\bibliography{biblio.bib}

\newpage

\appendix

\section{Comparison with previous work}

There are rather wide variety of estimation for radio emission of Jovian exoplanets and it is worth noting how the different models return different answers.

A common part is the scaling relationship between the planetary magnetic field strength and the input kinetic energy.
Combining equation (\ref{eq:Pinp_kin}), i.e.,
%%%
\begin{equation}
P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2 s
\end{equation}
%%%
and the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (see equation (\ref{eq:stand-off-radius})):
%%%
\begin{equation}
r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} \dot v^{-1/6}
\end{equation}
%%%
under the constant stellar wind, we obtain:
%%%
\begin{equation}
P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} \dot v^{5/3}
\end{equation}
%%%

%equation (\ref{eq:stand-off-radius})
%%%
%\begin{equation}
%r_s = 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
%\end{equation}
%%%
Aside from this common part, the differences originate mainly from:
\renewcommand{\theenumi}{\roman{enumi}}
%%%
\begin{enumerate}
\item Assumptions for the scaling law of radio power in terms of input energy. 
\item Assumptions for the scaling law of planetary magnetic field strength. 
\item Different normalization (assumptions for Jovian radio emission). 
\item Assumptions for band width (either $f_{\rm cyc}$ or $0.5f_{\rm cyc}$). 
\item Modeling of stellar wind
\end{enumerate}
%%%

As for i., ii. and iii., the scaling laws are summarized in Table \ref{tab:comp}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htp]
\caption{Comparison for assumed scaling relationships.}
\begin{center}
\begin{tabular}{c|l|llcc} \hline \hline
%
& Paper & Radio power & Magnetic moment  & norm [W] & band width \\\hline
%
\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 f_{\rm cyc}$ \\ \hline
%
\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
& \citet{lazio2004} & & $\mathcal{M} \propto \omega M_p^{2}$?? & & \\
& \citet{ignace2010} & & & & \\ \hline
\#3 & \citet{stevens2005} & $P_{\rm radio} \propto P_{\rm sw} $ & $\mathcal{M} \propto M_p$ & - & - \\ \hline
\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
\#5 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{1/2} r_c^3 \sigma ^{-1/2} $ & & \\
\#6 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{3/4} r_c^{7/2} \sigma ^{-1/4} $ & \\
\#7 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^{7/2}$ & & \\ \hline
%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ f_{\rm cyc}$ \\ \hline
\#8 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
 & this work & & \\ \hline
\end{tabular}
\end{center}
\label{tab:comp}
\tablecomments{}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

If we use the assumptions that $R_p \sim R_J\;\;(const.)$, $\rho _c\sim R_p\sim const.$, and $\sigma = const.$, then the assumptions are reduced to:
%%%%%%%%%
\begin{eqnarray}
\mbox{[\#1]} \; P_{\rm rad} &\sim & 4 \times 10^9 \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{0.58} \left( \frac{M_p}{M_J} \right)^{0.98} \left( \frac{a}{a_J} \right)^{-1.17} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.586} \left( \frac{v}{v_{\odot}} \right)^{1.46} \\
%
\mbox{[\#2]} \; P_{\rm rad} &\sim & 4 \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{0.79} \left( \frac{M_p}{M_J} \right)^{1.33} \left( \frac{a}{a_J} \right)^{-1.60} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.8} \left( \frac{v}{v_{\odot}} \right)^{2.0} \\
%
\mbox{[\#3]} \; P_{\rm rad} &\sim & ? \times 10^{11} \,{\rm W}\,\left( \frac{M_p}{M_J} \right)^{2/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
%
\mbox{[\#4]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
%
\mbox{[\#5]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
%
\mbox{[\#6]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/2} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
%
\mbox{[\#7]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
%
\mbox{[\#8]} \; P_{\rm rad} &\sim & ? \times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_J} \right)^{0.69}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.288}  \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
\end{eqnarray}
%%%%%%%%%
For the last equation, we used the scaling of the luminosity $L$, equation (\ref{eq:burrowsLum}):
%%%
\begin{equation}
L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \tag{\ref{eq:burrowsLum}}
\end{equation} 
%%%
\memoYF{Note that in \citet{ignace2010} the dependence on mass-loss rate and stellar wind velocity is not taken account consistently; in that paper, $P_{\rm rad} \propto \dot M_{\star } v^2$.}

In summary, we write down the scaling of the radio emission as below, 
%%%
\begin{equation}
P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{\alpha } \left( \frac{M_p}{M_J} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_J} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
\end{equation} 
%%%
with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$.

\end{document}

\clearpage

\section{Memo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brighter Implies Harder to See:\\
Greater $B$ Produces Lower $F_\nu$}
\label{ss:counterintuitive}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The cyclotron frequency at radius $r$ is:
%%%
\begin{equation}
f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
\end{equation}
%%
Therefore, 
%%%
\begin{equation}
\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
\end{equation}
%%%
Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
%%%
\begin{equation}
\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
\end{equation}
%%%
where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.

We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
%%%
\begin{equation}
N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
\end{equation}
%%%
Due the the mass flux conservation,
%%%
\begin{equation}
4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
\end{equation}
%%%
Combining with equation (\ref{eq:N0_plasma}),
%%%
\begin{equation}
N_{\rm plasma}(r) \propto  \frac{r_s^2 }{v_{\|}(r) r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
\end{equation}
%%%

Because the magnetic dipole moment
%%%
\begin{equation}
\mu = \frac{mv_{\bot}(r)}{eB(r)}
\end{equation}
%%%
is approximately to be constant while the plasma falls down along the magnetic field, 
%%%
\begin{eqnarray}
v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
B(r) \propto \frac{B_p}{r^3} 
\end{eqnarray}
%%%
On the other hand, conservation of energy ensures that
%%%
\begin{equation}
\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
\end{equation}
%%%
Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
%%%
\begin{equation}
v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
\end{equation}
%%%

Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
\end{equation}
%%%
The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
At $r>>\tilde r$, 
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
\end{equation}
%%%
and
%%%
\begin{equation}
\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
\end{equation}
%%%

At $r<<\tilde r$, 
%%%
\begin{equation}
\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
\end{equation}
%%%
and
%%%
\begin{equation}
\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
\end{equation}
%%%

\newpage

\memoDS{Is this section needed anymore, since this is already in the Griesmeier paper?
Does the Griesmeier paper make the point explicit enough, or is this still somewhat valuable?
Also, are we 100\% sure that this section is right?
A planet with larger surface field achieves an equivalent field to a planet with a smaller surface field at a larger radius, and captures a larger wind flux.
Should we think more about the spectrum?}

According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!
\memoDS{Is this pointed out elsewhere in the literature?}

\section{Dave's sketch}

\citep{spiegel2008}

\citep{lecavelier_et_al2013}

\citep{janhunen_et_al2003}

\citep{zarka1992, zarka1998}

\citep{farrell_et_al2004}

\citep{lazio+farrell2007}: likelihood function, tau Boo search

\citep{lecavelier_et_al2009}

\citep{spiegel2012}

\citep{nordhaus+spiegel2013}

\citep{jiang+jin1996}: 12cm radio of Jupiter during Shoemake-Levy-9

\citep{morin2012, morin_et_al2013}

\citep{christensen_et_al2009, christensen2010}

\citep{saar2001}: Inverse rossby number scaling of magnetic field: $B
\sim 60 {\rm~G} \times Ro^{-1.2}$.  Here, he takes $Ro = \tau_c/P_{\rm
  rot}$, where $\tau_c$ is the convective turnover time = ?
\citep{gilliland1986}.  Well, $F \sim \rho v_c^3 \sim \rho
(H/\tau_c)^3$, so $\tau_c \sim H (\rho / F)^{1/3} = H / (\sigma T_{\rm
  eff}^4 / \rho)^{1/3}$.  Alternatively, $\tau_{\rm conv} \sim (M R^2
/ L)^{1/3}$.

On dimensional grounds, the convective turnover time goes as
$\tau_{\rm conv} \sim (M R^2 / L)^{1/3}$.  According to
\citet{burrows_et_al2001}, radius $R$ and luminosity scale with time
as $R \sim R_J$, where $R_J$ is the radius of Jupiter, and
\begin{equation}
\frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
\label{eq:burrowsLum_2}
\end{equation}
So,
%\begin{eqnarray}
%\nonumber \tau_{\rm conv} & \sim & 3 {\rm~days} \times \left( \frac{M}{M_J} \right)^{1/3} \left( \frac{R}{R_J} \right)^{2/3} \left( \frac{L}{L_\odot} \right)^{-1/3} \\
% & = & 
%\end{eqnarray}
\begin{eqnarray}
\nonumber \tau_c & \sim & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{L}{10^{-9} L_\odot} \right)^{1/3}} \\
 & = & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}} \\
\end{eqnarray}
So the Rossby number $Ro = \tau_c/P_{\rm rot}$ is
\begin{eqnarray}
Ro & = & \frac{\tau_c}{P_{\rm rot}} \\
 & = & \left( \frac{P_{\rm rot}}{3 \rm~hrs} \right)^{-1} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}}
\end{eqnarray}

\citep{hallinan_et_al2013}

\citep{desch+kaiser1984} radiometric Bode's law

Noting that
\begin{equation}
\dot{M}_* = 4\pi r^2 \rho[r] v \, ,
\label{eq:mdot}
\end{equation}
so $\rho[r] = \dot{M}_*/(4\pi r^2 v)$,
\begin{eqnarray}
\frac{\rho v^2}{2} = \frac{B^2}{8\pi} \sim \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-3} \, ,
\end{eqnarray}
where $B_0$ is the field strength at a distance $d_0$ from the planet.
\begin{eqnarray}
\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
  & \sim & 4 R_J \left( \frac{d_0}{R_J}\right) \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
\label{eq:Chapman-Ferraro}
\end{eqnarray}
In the above, $d_A$ is the distance from the planet to the Alfven
point, where the magnetic energy density $u_B = B^2 / 8\pi$ equals the
kinetic energy density in the stellar wind $u_w = \rho v^2/2$, and
$B_0$ is the magnetic field strength at distance $d_0$.

The escape speed is
\begin{equation}
v_{\rm esc}^* = \sqrt{\frac{2 G M_*}{R_*}} \, ,
\end{equation}
so if the stellar wind speed is a factor $C$ times the escape speed, then ...

The power incident on the planet within $d_A$ is
\begin{eqnarray}
P_{\rm inc} & = & \frac{\rho v^3}{2} \times \pi d_A^2 \\
\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
d_A^6 & = & d_0^6 \frac{B_0^2}{4\pi \rho v^2} \\
d_A^2 & = & d_0^2 \left( \frac{B_0^2}{4\pi \rho v^2}\right)^{1/3} \\
\pi d_A^2 \frac{\rho v^3}{2} & = & \frac{d_0^2}{2} \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{4} \right)^{1/3} \\
P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} 
%\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
%\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
%d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
%d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
%  & \sim & 4 d_0 \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
\end{eqnarray}
Note that $\rho v = \dot{M}_*/4\pi r^2$.  Therefore,
\begin{eqnarray}
P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} \\
 & = & d_0^2 \left( \frac{\dot{M}_*^2 v^5 B_0^2}{512 r^4} \right)^{1/3} \\
 & = & \frac{d_0^2}{8} \left( \frac{\dot{M}_*^2 v^5 B_0^2}{r^4} \right)^{1/3} \\
\nonumber  & \sim & 2 \times 10^{18} {\rm~W} \left( \frac{d_0}{R_J} \right)^2 \left( \frac{\dot{M}_*}{10^{-5} M_\odot / {\rm yr}} \right)^2 \\
 & & \times \left( \frac{v}{20 \rm~km/s} \right)^5 \left( \frac{B_0}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^{-4}
\end{eqnarray}

The power incident on the planet is

%\citep{lunine_et_al1989} -- error?

% http://kiss.caltech.edu/workshops/magnetic2013/presentations/winterhalter.pdf

%ftp://ftp.iwf.oeaw.ac.at/pub/Scherf/PRE-CD%20V2/pre6/nigl.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Assumptions for Planetary Magnetic Field}
%\label{ss:magneticfield}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{It may be better to consider Cristensen's scaling, taking account of the age. But I have not followed the theory yet.}

Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griesmeier2004}:
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}

Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants. Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 
\memoYF{Would their spin rate become higher or lower??}

In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
First, we assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}. 
For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
%%%%%%%%%% 
\begin{equation}
\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r_2}
\end{equation}
%%%%%%%%%%
We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$. The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core. 
We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

Equation (\ref{eq:fcyc>fplasma}) can also be rewritten as: 
%%%
\begin{eqnarray}
 \left( \frac{B}{10~\mbox{G}} \right) &>& 0.526 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
 && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
\end{eqnarray}
%%%
or, 
%%%
\begin{eqnarray}
 \left( \frac{M_p}{M_{p,J}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
 && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
\end{eqnarray}
%%%
In other words, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system. 
Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
%%%
\begin{eqnarray}
F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right)^{-2} \\
&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
\end{eqnarray}
%%%

\end{document}

### 2015-09-09 ms.tex
Added Stitch Fix affiliation.

@@
 %
-David S. Spiegel\altaffilmark{2,3}
-%
-Tony Mroczkowski\altaffilmark{4,5}
-%
-Jason Nordhaus\altaffilmark{6,7}\\
-%
-Neil T. Zimmerman\altaffilmark{8}
-%
-Aaron Parsons\altaffilmark{9}
-%
-Nikku Madhusudhan\altaffilmark{10}
-%
-Mehrdad Mirbabayi\altaffilmark{2}
+David S. Spiegel\altaffilmark{2,3,4}
+%
+Tony Mroczkowski\altaffilmark{5,6}
+%
+Jason Nordhaus\altaffilmark{7,8}\\
+%
+Neil T. Zimmerman\altaffilmark{9}
+%
+Aaron Parsons\altaffilmark{10}
+%
+Nikku Madhusudhan\altaffilmark{11}
+%
+Mehrdad Mirbabayi\altaffilmark{13}
 }
@@
 
-\affil{$^4$National Research Council Fellow}
-
-\affil{$^5$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^6$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^7$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^8$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
-
-\affil{$^9$Astronomy Department, University of California Berkeley}
-
-\affil{$^{10}$Astronomy Department, University of Cambridge, UK}
+\affil{$^4$Analytics \& Algorithms, Stitch Fix,
+  San Francisco, CA  94103}
+
+\affil{$^5$National Research Council Fellow}
+
+\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^7$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^8$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+
+\affil{$^{10}$Astronomy Department, University of California Berkeley}
+
+\affil{$^{11}$Astronomy Department, University of Cambridge, UK}
 

### 2015-09-09 ms.tex
changed frequency f to nu

--- 2015-09-09 ms.tex
@@
 In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
-\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission.  
+\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
@@
 asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}.
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
 Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr.
@@
 We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
-This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
 %\memoYF{describe in more detail}:
@@
 \begin{equation}
-B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
+B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
 \end{equation}
@@
 Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
-The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $f_{\rm cyc}$: 
-%%%%%%%%%% 
-\begin{equation}
-f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
+The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc}$: 
+%%%%%%%%%% 
+\begin{equation}
+\nu_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
 \end{equation}
@@
 
-Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
+Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$.
 The plasma frequency may be expressed as
 \begin{eqnarray}
-f_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
+\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
  & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
@@
 \end{eqnarray}
-In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $f_{\rm plasma}^\oplus \lsim 10$~MHz.
+In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz.
 At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
@@
 \begin{eqnarray}
-\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
+\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
 \label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
@@
 
-Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
+Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($\nu_{\rm cyc}$), as functions of planetary mass and the age.
 %Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
 %B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
-%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
-%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
+%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
+%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
 %\end{eqnarray}
@@
 The systems are located at 100 pc away.
-The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $f_{\rm cyc}$) is below the plasma frequency cut-off, $f_{\rm plasma}^{\rm los}$.
-The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1f_{\rm cyc}$, is below $f_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
+The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
+The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
 }
@@
 \begin{eqnarray}
-F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
+F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 \nu_{\rm cyc}} \\
 &\approx & 5.22\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
@@
 \begin{equation}
-\label{eq:fcyc>fplasma} f_{\rm cyc} > f_{\rm plasma}^{\rm los}
+\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
 \end{equation} 
@@
 Instead, it usually exits at lower frequencies.
-Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
+Here, we also consider a more conservative criteria, $0.1 \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
 In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
@@
 \citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
-Using these data, we extrapolate the radio flux from the host star to the lower frequency range with a simple power law as follows:
-%%%
-\begin{eqnarray}
-\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
+Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
+%%%
+\begin{eqnarray}
+\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
 && \times \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 ~R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
@@
 For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $f_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
+Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $F_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
 Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection.
@@
 \item Different normalization (assumptions for Jovian radio emission). 
-\item Assumptions for band width (either $f_{\rm cyc}$ or $0.5f_{\rm cyc}$). 
+\item Assumptions for band width (either $\nu_{\rm cyc}$ or $0.5\nu_{\rm cyc}$). 
 \item Modeling of stellar wind
@@
 %
-\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 f_{\rm cyc}$ \\ \hline
-%
-\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
+\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 \nu_{\rm cyc}$ \\ \hline
+%
+\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 \nu_{\rm cyc}$ \\
 & \citet{lazio2004} & & $\mathcal{M} \propto \omega M_p^{2}$?? & & \\
@@
 \#3 & \citet{stevens2005} & $P_{\rm radio} \propto P_{\rm sw} $ & $\mathcal{M} \propto M_p$ & - & - \\ \hline
-\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
+\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 \nu_{\rm cyc}$ \\
 \#5 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{1/2} r_c^3 \sigma ^{-1/2} $ & & \\
@@
 \#7 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^{7/2}$ & & \\ \hline
-%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ f_{\rm cyc}$ \\ \hline
+%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ \nu_{\rm cyc}$ \\ \hline
 \#8 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
@@
 \begin{equation}
-f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
+\nu_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
 \end{equation}
@@
 \begin{equation}
-\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
+\frac{dP}{d\nu_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
 \end{equation}
@@
 Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
+In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $\nu_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
 This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
-Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
+Since $\nu_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
 Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!

### 2015-09-09 ms.tex
Switched affiliation order.

@@
 
-\affil{$^2$Astrophysics Department, Institute for Advanced Study,
-  Princeton, NJ 08540}
+\affil{$^2$Analytics \& Algorithms, Stitch Fix,
+  San Francisco, CA  94103}
 
@@
 
-\affil{$^4$Analytics \& Algorithms, Stitch Fix,
-  San Francisco, CA  94103}
+\affil{$^4$Astrophysics Department, Institute for Advanced Study,
+  Princeton, NJ 08540}
 

### 2015-09-10 ms.tex
some small edits from tony

@@
 \S4 gives predictions for the signals from evolved systems within 400 pc, taking account of the intrinsic radio emission from the host evolved stars.
-Considering the sensitivity of the current and future radio instruments, we argue that SKA, and perhaps LOFAR-HBA as well, would be capable of detecting these signals within a reasonable integration time.
+Considering the sensitivity of the current and future radio instruments, we argue that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
 %In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
@@
 
-Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
+Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
 Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
@@
 The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
-The time-dependence luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
+The time-dependent luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
 Ignoring the relatively weak dependence on average atmospheric Rosseland mean opacity leads to:
@@
 
-Another ingredient needed for modeling the radio emission from the interaction between the planetary magnetic field and the stellar wind is the density and velocity of the stellar wind. 
+To model the radio emission from the interaction between the planetary magnetic field and the stellar wind,
+we need the density and velocity of the stellar wind. 
 The number density of electrons in the stellar wind, $n$, can be expressed as
@@
 \begin{eqnarray}
-n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2}. \label{eq:n_normalized}
+n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
 \end{eqnarray}
@@
 L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
+&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
 %
@@
 %%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV ($\lambda = $), the energy needed to ionize hydrogen atoms.
+The source rate is obtained by counting the number of photons whose energy is greater than 13.6~eV ($\lambda < 91~\rm nm$), the energy needed to ionize hydrogen atoms.
 As a result, 

### 2015-09-10 ms.tex
some small edits from tony

@@
 We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
-This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
 %\memoYF{describe in more detail}:
@@
 %Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
-Reasonably, the resultant values are in a good agreement with \citet{reiners2010}, which adopted the same scaling law for planetary magnetic field; we show this figure just for self-completeness.
+Reasonably, the resultant values are in good agreement with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure for completeness.
 
@@
 In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
-LOFAR, Hera, SKA, and upgrades to the VLA.
+LOFAR, Hera, SKA, and potential upgrades to the VLA.
 
@@
 Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
-Depending on the modeling of magnetic field strength, there is also a speculation that the tidally-locked planets may have weaker magnetic field due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker.
+Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker.
 %\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
@@
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupier-twin)} \notag \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupiter-twin)} \notag \\
 %%%
@@
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars.
-For a red-giant system, the most promising target if massive companion with $M_p \gtrsim 5M_J$.
-On the other hand, for a AGB-star system, it is very difficult to detect a signal from the planetary-mass companions within 100 AU.
+For a red-giant system, the most promising target is a massive companion with $M_p \gtrsim 5M_J$.
+On the other hand, for a AGB-star system, it is very difficult to detect a signal from any planetary-mass companions within 100 AU.
 

### 2015-09-10 ms.tex
1 sentence per line
more edits for section 4 -- tony

@@
 \citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
-Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
-though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
-
-When stars less than $\sim$8~$M_\sun$ evolve off the main sequence,
-they evolve through the red-giant branch (RGB) and the
-asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
+Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
+
+When stars less than $\sim$8~$M_\sun$ evolve off the main sequence, they evolve through the red-giant branch (RGB) and the asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude.
 Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
@@
 radio instruments at relevant frequencies.
-Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a mean to discern the signals from the background noise.
+Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a means to discern the signals from the background noise.
 
@@
 %at wavelengths of 6 cm and below, 
-at frequency of 5 GHz or above, 
+at frequencies $\geq 5~\rm GHz$, 
 probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
@@
 %
-\citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+\citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
 Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
@@
 \begin{eqnarray}
-\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
-&& \times \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 ~R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
+\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
+&& \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
 \end{eqnarray}
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from accretion disk is negligible in this figure. 
-The spectral shape is modeled by simply scaling the Jovian radio spectra e.g. Figure 8 of \citet{zarka_et_al2004}. 
+Note that the thermal contribution from the accretion disk is negligible in this figure. 
+The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
 The continuum from the star in the case of $\alpha =0.6$ is shown as an extreme case; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}. 
-As Figure \ref{fig:cartoon} indicates, with the reasonable range of spectral index, radio emission from the stars is by order of magnitude smaller than the expected radio flux from RGHJs at frequencies below 300~MHz.
-For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies is smaller.
+As Figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
+For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies are smaller.
 
@@
 
-In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
-For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
+In order to examine the potential to detect radio emission of RGHJs with current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+%For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
+\memoTM{For this purpose, we obtained the masses, radii, and effective temperatures for a catalog of M-type red giants \citet{dumm1998} (in their Table 4).}
 For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
@@
 %%%
-where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are radius, luminosity, and mass of the star. 
+where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are the radius, luminosity, and mass of the star. 
 The factor $\eta $ is $\sim 0.3-3$, and we assume $\eta =1$ here. 
-The velocity of stellar wind is assumed to scale with the escape velocity, hence
+The velocity of the stellar wind is assumed to scale with the escape velocity, hence
 %%%
@@
 %%%
-The age of the system is assumed to roughly same as the lifetime of their main-sequence stage, which depends on the stellar mass.
+The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass.
 We assume \memoYF{validation}:
@@
 %%%
-In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.
+In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets.\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}
 
@@
 \begin{equation}
-\sigRMS = \frac{2 k T_{\rm sys}}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
+\sigRMS = \frac{2 k \Tsys}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
 \left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
@@
 \Tsky = T_{150} \left( \frac{\nu}{150~\rm MHz}\right)^{-\beta} + \Tcmb
+\label{eq:Tsky}
 \end{equation}
@@
 The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time.
-Therefore both the circularly polarized nature of the emission from hot Jupiters and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing hot jupiters, like other time-variable sources, to be detected below the imaging confusion limit.
-We therefore expect confusion not to be a strong limitation to detectability of hot Jupiters.
+Therefore both the circularly polarized nature of the cyclotron emission from hot jupiters and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing hot jupiters, like other time-variable sources, to be detected below the imaging confusion limit.
+We therefore expect confusion not to be a strong limitation to the detectability of hot jupiters.
 
@@
 LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz.
-Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the reciever noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, for our fiducial sensitivity and imaging parameters in Table~\ref{tab:sens}.
+Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the reciever noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, to obtain the sensitivity and imaging parameters in Table~\ref{tab:sens}.
 
@@
 We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used to detect $\sim 30 M_J$ hot Jupiters.
-We adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ as above, and assume $\Trx \approx 60~\rm K$.
+We again adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ (Equation~\ref{eq:Tsky}), and assume $\Trx \approx 60~\rm K$.
 We caution that these assumptions are optimistic, and the time estimates could in reality be a factor of a few worse.
@@
 % VLA
-For the low frequency receivers (28-80~MHz; 4-Band) in the \memoDS{Long Wavelength Array (LWA) and the?}\memoTM{No need to mention LWA here.
-The receivers are the same in the VLA 4-band and the LWA, but the LWA is far too insensitive to consider here, as is VLA 4-band alone, so the reference just serves to place an upper limit on what \Trx\ will be for LOBO.} Very Large Array (VLA), the receiver noise temperature $\Trx \approx 260~\rm K$ \citep{Hicks2012} and is subdominant to \Tsky\ by at least -6~dB.
-Future upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU} are being considered, and would cover the full 30-470~MHz band.
+For the low frequency receivers (28-80~MHz; 4-Band) in the Very Large Array (VLA) have $\Trx \sim 260~\rm K$, similar to the receiver noise temperatures for the Long Wavelength Array (LWA) \citep{Hicks2012}.
+As noted in \citep{Hicks2012}, this noise level is subdominant to \Tsky\ by at least -6~dB.
+Future upgrades to the VLA such as the LOw Band Observatory \citep[LOBO][]{Kassim2015IAU} are being considered, and could potentially cover the full 30-470~MHz band.
 We estimate the sensitivity of LOBO assuming the receiver noise extrapolates linearly from $\Trx \approx 60~\rm K$ (internal VLA memo) in P-Band (230-470~MHz) to $\Trx \approx 260~\rm K$ in 4-band, and consider just the 50-350~MHz portion of the full 30-470~MHz band.
 
-The estimates of the noises shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequency relevant to the radio emission from Jupiter-size planets, current instrument sensitivities are too low for detection.
+The noise estimates shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
 On the other hand, for more massive exoplanets ($M_p\sim 10 M_J$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
-LOFAR-HBA has reasonable sensitivity to $M_p =10~M_J$ planets at 5 AU around a few closest systems as well as those around further stars but orbiting closer to the stars. 
+LOFAR-HBA has reasonable sensitivity to $M_p =10~M_J$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
 More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_J$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Discriminating from Background}
+\subsection{Discriminating the Signal from the Background}
 \label{ss:timevariability}
@@
 
-Since the confusion limit is on the same order as the signal (Table \ref{tab:sens}), it is crucial to consider the ways to discriminate the signal from the confusion sources.
+Since the confusion limit is on the same order as the signal (Table \ref{tab:sens}), it is crucial to consider the ways to discriminate the signal from these sources.
 In this section, we discuss time variability and polarization as keys to identify the auroral radio emission from the planets.
 
-One of the key features that make planetary radio emission distinct is the almost complete polarization \citep[e.g.][]{dulk1994}.
+One of the key features that makes planetary radio emission distinct is the almost complete circular polarization \citep[e.g.][]{dulk1994}.
 ...\memoYF{write here (YF)}

### 2015-09-10 ms.tex
minor edit

--- 2015-09-10 ms.tex
@@
 
-\slugcomment{Submitted to ApJ, XX September 2015}
+%\slugcomment{Submitted to ApJ, 20 October 2011}
 
@@
 
-\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?
-\memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' 
-or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}}
+\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?}
 
@@
 %
-David S. Spiegel\altaffilmark{2,3,4}
-%
-Tony Mroczkowski\altaffilmark{5,6}
-%
-Jason Nordhaus\altaffilmark{7,8}\\
-%
-Neil T. Zimmerman\altaffilmark{9}
-%
-Aaron Parsons\altaffilmark{10}
-%
-Nikku Madhusudhan\altaffilmark{11}
-%
-Mehrdad Mirbabayi\altaffilmark{13}
+David S. Spiegel\altaffilmark{2,3}
+%
+Tony Mroczkowski\altaffilmark{4,5}
+%
+Jason Nordhaus\altaffilmark{6,7}\\
+%
+Neil T. Zimmerman\altaffilmark{8}
+%
+Aaron Parsons\altaffilmark{9}
+%
+Nikku Madhusudhan\altaffilmark{10}
+%
+Mehrdad Mirbabayi\altaffilmark{2}
 }
@@
 
-\affil{$^2$Analytics \& Algorithms, Stitch Fix,
-  San Francisco, CA  94103}
+\affil{$^2$Astrophysics Department, Institute for Advanced Study,
+  Princeton, NJ 08540}
 
@@
 
-\affil{$^4$Astrophysics Department, Institute for Advanced Study,
-  Princeton, NJ 08540}
-
-\affil{$^5$National Research Council Fellow}
-
-\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^7$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^8$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
-
-\affil{$^{10}$Astronomy Department, University of California Berkeley}
-
-\affil{$^{11}$Astronomy Department, University of Cambridge, UK}
+\affil{$^4$National Research Council Fellow}
+
+\affil{$^5$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^6$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^7$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^8$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+
+\affil{$^9$Astronomy Department, University of California Berkeley}
+
+\affil{$^10$Astronomy Department, University of Cambridge, UK}
 
@@
 %%%
-When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
-Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a massive stellar wind.
-Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
-We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields.
-We predict that RGHJs might be as bright as canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances less than a few hundred parsecs with current/future instruments such as LOFAR and SKA.
+When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders-of-magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
+Accordingly, planetary companions around them at a few AU orbits, if exist, are heated up to the level of canonical hot Jupiters and also subjected to the massive stellar wind.
+Given that magnetized planets emit radio waves in the interaction with stellar winds, such ``Red-Giant Hot Jupiters'' (RGHJs) may be candidates of bright radio emitters.
+We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and proposed scaling of planetary magnetic fields.
+We find that RGHJs might be as bright as canonical hot Jupiters as predicted so far, and thus radio emission from a RGHJ would be visible from a hundred parsec distances with current/future detectors such as LOFAR-HBA and SKA.
 
@@
 Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}.
-Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
+Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems have been examined. 
 \citet{farrell1999,zarka2001,lazio2004} pointed out that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
@@
 They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME).
-Note that in these papers, the scaling relation of planetary magnetic fields  differ from paper to paper.    
+Note that in these paperes, the scaling relation of planetary magnetic fields  differ from paper to paper.    
 In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
-\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
+\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission.  
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, 
@@
 asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude. 
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
+Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\sim$1000~K or more) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs) but refer to planets orbiting RGB and AGB stars \citep{spiegel+madhusudhan2012}.
 Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim  10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr.
@@
 \S4 gives predictions for the signals from evolved systems within 400 pc, taking account of the intrinsic radio emission from the host evolved stars.
-Considering the sensitivity of the current and future radio instruments, we argue that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
+Considering the sensitivity of the current and future radio instruments, we argue that SKA, and perhaps LOFAR-HBA as well, would be capable of detecting these signals within a reasonable integration time.
 %In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
@@
 
-Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
+Before estimating the frequency of planetary radio emission and the spectral radio intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
 Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
@@
 We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
-This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of available convected energy and was found to be in a good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
 %\memoYF{describe in more detail}:
@@
 \begin{equation}
-B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
+B_{\rm dynamo} ^2 \propto f_{\rm ohm}\;\rho_{\rm dynamo}  ^{1/3} \;  (Fq_o)^{2/3} \label{eq:Bscaling} 
 \end{equation}
@@
 The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
-The time-dependent luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
+The time-dependence luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
 Ignoring the relatively weak dependence on average atmospheric Rosseland mean opacity leads to:
@@
 
-To model the radio emission from the interaction between the planetary magnetic field and the stellar wind,
-we need the density and velocity of the stellar wind. 
+Another ingredient needed for modeling the radio emission from the interaction between the planetary magnetic field and the stellar wind is the density and velocity of the stellar wind. 
 The number density of electrons in the stellar wind, $n$, can be expressed as
@@
 \begin{eqnarray}
-n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
+n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \\
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1} \left( \frac{a}{5 \; {\rm AU}} \right)^{-2}. \label{eq:n_normalized}
 \end{eqnarray}
@@
 L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
+&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \\
 %
@@
 %%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy is greater than 13.6~eV ($\lambda < 91~\rm nm$), the energy needed to ionize hydrogen atoms.
+The source rate is obtained by counting the number of photons whose energy is higher than 13.6~eV ($\lambda = $), the energy needed to ionize hydrogen atoms.
 As a result, 
@@
 Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
-The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc}$: 
-%%%%%%%%%% 
-\begin{equation}
-\nu_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
+The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $f_{\rm cyc}$: 
+%%%%%%%%%% 
+\begin{equation}
+f_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
 \end{equation}
@@
 
-Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$.
+Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $f_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $f_{\rm plasma}^{\rm los}$.
 The plasma frequency may be expressed as
 \begin{eqnarray}
-\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
+f_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
  & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
@@
 \end{eqnarray}
-In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz.
+In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $f_{\rm plasma}^\oplus \lsim 10$~MHz.
 At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
@@
 \begin{eqnarray}
-\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
+\label{eq:fplasmalos} f_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
 \label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
@@
 
-Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($\nu_{\rm cyc}$), as functions of planetary mass and the age.
+Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($f_{\rm cyc}$), as functions of planetary mass and the age.
 %Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
 %B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
-%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
-%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
+%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
+%f_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
 %\end{eqnarray}
@@
 The systems are located at 100 pc away.
-The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
-The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
+The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $f_{\rm cyc}$) is below the plasma frequency cut-off, $f_{\rm plasma}^{\rm los}$.
+The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1f_{\rm cyc}$, is below $f_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
 }
@@
 \begin{eqnarray}
-F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 \nu_{\rm cyc}} \\
+F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyc}} \\
 &\approx & 5.22\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
@@
 %%%
+%Note that, within this framework, the {\it spectral} radio flux has necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}. 
 %\memoYF{cite original paper!}. 
-Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters, and Jupiter-like planets around AGB stars are potentially orders-of-magnitude brighter than them. 
-Note that, within this framework, the {\it spectral} radio flux has necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}. 
+Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
+Compared with the distant Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than 2 orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
+This compensates the small population of evolved stars at least partially.
+
 Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$.
@@
 \begin{equation}
-\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
+\label{eq:fcyc>fplasma} f_{\rm cyc} > f_{\rm plasma}^{\rm los}
 \end{equation} 
@@
 Instead, it usually exits at lower frequencies.
-Here, we also consider a more conservative criteria, $0.1 \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
+Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
 In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
-For a red-giant system, the most promising target if massive companion with $M_p \gtrsim 5M_J$.
-On the other hand, for a AGB-star system, it is very difficult to detect a signal from the planetary-mass companions within 100 AU.
+For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_J$. 
+On the other hand, for a AGB-star system, only massive planets at distant orbits are marginally detectable.
 
@@
 \citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3,910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
-Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
-%%%
-\begin{eqnarray}
-\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
+Using these data, we extrapolate the radio flux from the host star to the lower frequency range with a simple power law as follows:
+%%%
+\begin{eqnarray}
+\nonumber f_{\star }(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \\
 && \times \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2}  \left( \frac{R_{\star }}{100 ~R_{\odot }} \right)^2 \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
-For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
+For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975} \memoYF{should be replaced by the updated Reimer's equation}:
 %%%
@@
 For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $F_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
+Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $f_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
 Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection.
@@
 \item Different normalization (assumptions for Jovian radio emission). 
-\item Assumptions for band width (either $\nu_{\rm cyc}$ or $0.5\nu_{\rm cyc}$). 
+\item Assumptions for band width (either $f_{\rm cyc}$ or $0.5f_{\rm cyc}$). 
 \item Modeling of stellar wind
@@
 %
-\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 \nu_{\rm cyc}$ \\ \hline
-%
-\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 \nu_{\rm cyc}$ \\
+\#1 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{0.88} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^9$ & $ 0.5 f_{\rm cyc}$ \\ \hline
+%
+\#2 & \citet{farrell1999} & $P_{\rm radio} \propto P_{\rm sw}^{1.2} $ & $\mathcal{M} \propto \omega M_p^{5/3}$ & $4 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
 & \citet{lazio2004} & & $\mathcal{M} \propto \omega M_p^{2}$?? & & \\
@@
 \#3 & \citet{stevens2005} & $P_{\rm radio} \propto P_{\rm sw} $ & $\mathcal{M} \propto M_p$ & - & - \\ \hline
-\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 \nu_{\rm cyc}$ \\
+\#4 & \citet{griesmeier2005,griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^4 $ & $2.1 \times 10^{11}$ & $ 0.5 f_{\rm cyc}$ \\
 \#5 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega^{1/2} r_c^3 \sigma ^{-1/2} $ & & \\
@@
 \#7 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^{7/2}$ & & \\ \hline
-%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ \nu_{\rm cyc}$ \\ \hline
+%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ f_{\rm cyc}$ \\ \hline
 \#8 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
@@
 \begin{equation}
-\nu_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
+f_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
 \end{equation}
@@
 \begin{equation}
-\frac{dP}{d\nu_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
+\frac{dP}{df_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
 \end{equation}
@@
 Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $\nu_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
+In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $f_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
 This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
-Since $\nu_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
+Since $f_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
 Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!

### 2015-09-10 ms.tex

--- 2015-09-10 ms.tex
@@
 Instead, it usually exits at lower frequencies.
-Here, we also consider a more conservative criteria, $0.1 \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
+Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
 In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
-For a red-giant system, the most promising target is a massive companion with $M_p \gtrsim 5M_J$.
-On the other hand, for a AGB-star system, it is very difficult to detect a signal from any planetary-mass companions within 100 AU.
+For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_J$. 
+On the other hand, for a AGB-star system, only massive planets at distant orbits are marginally detectable.
 
@@
 
-In order to examine the potential to detect radio emission of RGHJs with current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
-%For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
-\memoTM{For this purpose, we obtained the masses, radii, and effective temperatures for a catalog of M-type red giants \citet{dumm1998} (in their Table 4).}
-For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975}:
+In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
+For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975} \memoYF{should be replaced by the updated Reimer's equation}:
 %%%

### 2015-09-10 ms.tex
Variability text/refs added

@@
 When stars less than $\sim$8~$M_\sun$ evolve off the main sequence, they evolve through the red-giant branch (RGB) and the asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude.
-Jovian planets in orbit around such stars can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
+Jovian planets in orbit around such stars can migrate inward or outward due to the interplay between tidal torques and mass-loss process on the post-main sequence \citep{nordhaus_et_al2010,nordhaus+spiegel2013}.
+During this time, such planets can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
 Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr.
@@
 
-\paragraph{Variability of stellar wind (months $\sim $)?}
-Based on the correlation between the planetary radio emission and the solar wind plasma density also suggest that the radio emission from the planet around the evolved stars, which typically oscillate, are time variable.
-\memoYF{To Jason: time variability?}
+\paragraph{Variability of stellar wind (a few months $\sim $)?}
+If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time-variabililty of planetary radio emission.
+Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.
+
 %

### 2015-09-10 ms.tex
more edits -- TM.

@@
 So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
-Therefore, one possible strategy is to target at the know planetary systems.  
+Therefore, one possible strategy is to target known planetary systems.  
 One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox[m/s]$.
@@
 As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$.
-Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where, $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
+Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
 Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} [(R_\star/M_\star)(1+A/g_\star)]^{1/2}$.
@@
 Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
-Based on such a picture, massive stellar wind of red giants and AGB stars would interact with planetary magnetic field and inputs kinetic energy into magnetospheres of RGHJs. 
+Based on such a picture, the massive stellar wind of a red giant or AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
 We found that the intrinsic brightness of radio emission from RGHJs would be comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.
@@
 Such signals would be detectable with SKA within a day or so. 
-For a few nearest systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time. 
-In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confusion sources.
+For a few nearby systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time. 
+In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confused sources in the same resolution element.
 
@@
 DSS gratefully acknowledges support from a fellowship from the AMIAS group.
-We thank David Hogg for encouraging us to pursue calculations of explanetary radio emission.
+We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.
 NM acknowledges support from [???]. 
 YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
-The portion of this research for which TM is responsible was performed while he held a National Research Council Research Associateship Award at the Naval Research Laboratory (NRL).
+The portion of this research for which TM is responsible was performed under a National Research 
+Council Research Associateship Award at the Naval Research Laboratory (NRL).
 Basic research in radio astronomy at NRL is supported by 6.1 Base funding.
@@
 
-There are rather wide variety of estimation for radio emission of Jovian exoplanets and it is worth noting how the different models return different answers.
+There is a rather wide range in estimates of the radio emission from Jovian exoplanets and it is worth noting how the different models yield different answers.
 
 A common part is the scaling relationship between the planetary magnetic field strength and the input kinetic energy.
-Combining equation (\ref{eq:Pinp_kin}), i.e.,
-%%%
-\begin{equation}
-P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2 s
-\end{equation}
-%%%
-and the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (see equation (\ref{eq:stand-off-radius})):
-%%%
-\begin{equation}
-r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} \dot v^{-1/6}
-\end{equation}
-%%%
-under the constant stellar wind, we obtain:
-%%%
-\begin{equation}
-P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} \dot v^{5/3}
+From equations \ref{eq:Pinp_kin} and \ref{eq:n}, the input kinetic energy scales as
+%%%
+\begin{equation}
+P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2 s.
+\end{equation}
+%%%
+Combining the above equation with the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (equation \ref{eq:stand-off-radius}), i.e.\
+%%%
+\begin{equation}
+r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} \dot v^{-1/6}, 
+\end{equation}
+%%%
+and assuming a constant stellar wind, we obtain:
+%%%
+\begin{equation}
+P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} \dot v^{5/3}.
 \end{equation}

### 2015-09-11 ms.tex
confused by A1--A3 -- TM
minor edits

@@
 
-Planets with strong magnetic fields may generate radio or X-ray emission when interacting with energetic charged particles. 
-It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep{zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
+Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
+It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
 Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
@@
 \citet{griesmeier2005} took account of the high stellar activity in the early stage of the planetary system and proposed that the young system would be good candidates to search for radio emission. 
-\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed model of stellar wind property in the proximity of the stars.
+\citet{griesmeier2007a, griesmeier2007b} discussed the effects of the detailed properties of stellar wind in the proximity of the stars.
 They considered not only the kinetic energy of the stellar wind but also the magnetic energy of the stellar wind and coronal mass ejection (CME).
 Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
-In \citet{reiners2010}, the authors adopted new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
+In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}.
 \citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
@@
 Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to the previous result.
+We also consider the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
 Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
@@
 Indeed, unlike canonical hot Jupiters, RGHJs are not tidal locked to their host stars, so we do not have to assume slow spin rotation rates \citep{spiegel+madhusudhan2012}.
-Therefore, we implicitly assume that the RGHJs we consider in this paper are rapidly rotating so that they generate planetary magnetic fields through the same mechanism as Jupiter.
+Therefore, we implicitly assume that the RGHJs considered in this paper are rapidly rotating so that they generate planetary magnetic fields through the same mechanism as Jupiter.
 
 In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need models of the internal planetary structure. 
-We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) converge to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
 For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
@@
 The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
-The time-dependent luminosity is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
+The time-dependent luminosity is taken from equation (1) of \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
 Ignoring the relatively weak dependence on average atmospheric Rosseland mean opacity leads to:
@@
 \begin{equation}
-q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
+q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_{\rm dynamo}}{r_{\rm dynamo\,J}} \right)^{-2}\, .
 \label{eq:burrowsHeatFlux}
@@
 
-Substituting Equation~\ref{eq:burrowsHeatFlux} into Equation~\ref{eq:Bscaling2} and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is roughly, we find that:
+Substituting Equation~\ref{eq:burrowsHeatFlux} into Equation~\ref{eq:Bscaling2} and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
 %%%%%%%%%% 
@@
 we need the density and velocity of the stellar wind. 
-The number density of electrons in the stellar wind, $n$, can be expressed as
+The number density of particles in the stellar wind, $n$, can be expressed as
 %%%%%%%%%% 
@@
 However, at this stage, the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
-\citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are: 
+\citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ as follows: 
 %%%%%%%%%
@@
 At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
-Therefore, combining Eq.~(\ref{eq:n}) and Eq.~(\ref{eq:fplasma}), we have
+Therefore, combining Eq.~(\ref{eq:n_normalized}) and Eq.~(\ref{eq:fplasma}), we have
 %%%
@@
 
-On the other hand, in the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
+In the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
 In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
@@
 
-We assume that the solid angle of the emission is same as the Jupiter's one for all of the exoplanets.
+We assume that the solid angle of the emission, $\Omega $, is same as the Jupiter's one for all of the exoplanets.
 In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
@@
 %Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
-Reasonably, the resultant values are in good agreement with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure for completeness.
+Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness.
 
@@
 %under this model. 
-Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz, the plasma cut-off frequency of Earth's ionosphere, and less than 1~GHz. 
+Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz ($\sim $ the plasma cut-off frequency of Earth's ionosphere) and 1~GHz. 
 In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
-LOFAR, Hera, SKA, and potential upgrades to the VLA.
+LOFAR, HERA, SKA, and potential upgrades to the VLA.
 
@@
    \plotoneh{fig1_linear.pdf}
-   \caption{Planetary magnetic field as a function of age and planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of internal heat of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
+   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
   \label{fig:planetaryB_pre}
@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
+P_{\rm k,\,inp} &=& nv^3 r_s^2 %= n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
 &=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
@@
 Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
-Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be even weaker.
+Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
 %\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
@@
 Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$.
-This originates from the different scaling laws for the planetary magnetic field and that their paper didn't incorporate the compression of the planetary magnetosphere due to massive stellar wind.
+This originates from the different scaling laws for the planetary magnetic field and that their formulation didn't incorporate the compression of the planetary magnetosphere due to massive stellar wind.
 
@@
 Figure \ref{fig:radio} shows the contours of spectral radio flux of planetary companions at 4.5~Gyr with varying masses and orbital distances. 
-The target system is located at a distance of 10~pc from the Earth; the flux can be scaled by the distance as a quadratic function. 
+The target system is located at a distance of 100~pc from the Earth; the flux is scaled by the distance as a quadratic function. 
 The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.
@@
 Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}).
-We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency:
+We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
 %%%
@@
 In this section, we discuss the observability of the estimated radio emission. 
-An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planets.
+An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planetary contribution.
 We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
@@
 radio instruments at relevant frequencies.
-Finally, \S\ref{ss:timevariability} discusses the expected time variability of the radio emission as a means to discern the signals from the background noise.
+Finally, \S\ref{ss:timevariability} discusses the polarization and the expected time variability of the radio emission as means to discern the signals from the background noise.
 
@@
 
-However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index when available.
+However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index.
 %In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
@@
 %
-\citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+For example, \citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
 Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from the accretion disk is negligible in this figure. 
+Note that the thermal contribution from the accretion disk is negligible in this figure. \memoYF{check} 
 The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
-The continuum from the star in the case of $\alpha =0.6$ is shown as an extreme case; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}. 
+The continuum lines from the star in the cases of $\alpha =0.8$ and $2.0$ are shown as an extreme case.
+%; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
 As Figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
@@
 
-Another key is that auroral radio emission from planets is not a static source but it significantly varies in time. 
-The potential factors that cause time variability of the auroral radio emission are  listed below.
+Another key is the significant time variability of the planetary radio emission. 
+The potential factors that cause time variability are  listed below.
 
@@
 The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis.
+If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation.
 %
@@
 Therefore, one possible strategy is to target known planetary systems.  
-One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox[m/s]$.
+One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox{m/s}$.
 Therefore, there are some parameter spaces where current radial velocity observations cannot survey.
@@
 If the spectra are obtained, the upper cut-off frequency of the radio spectra will imply us the magnetic field strengths of the planetary surface.
-Such information would be most useful if we could follow up the system by radial velocity to get constraints on the planetary mass, because once both magnetic field strength and the planetary mass is constrained, the proposed scaling law of planetary dynamo may be contested.
+Such information would be most useful if we could obtain constraints on planetary mass via e.g.
+radial velocity observations, because once both magnetic field strength and the planetary mass is constrained, the proposed scaling law of planetary dynamo may be contested.
 On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the density of the stellar wind at the planetary orbit.
@@
 \begin{equation}
-P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2 s.
-\end{equation}
-%%%
-Combining the above equation with the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (equation \ref{eq:stand-off-radius}), i.e.\
+P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2.
+\end{equation}
+%%%
+Combining the above equation with the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (equation (\ref{eq:stand-off-radius})), i.e.\
 %%%
@@
 \end{equation}
+\memoTM{I don't see how $\dot v \neq 0$ here, if we're assuming a constant stellar wind.}
 %%%

### 2015-09-11 ms.tex
commented out end of line in an equation

@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_s^2 %= n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
+P_{\rm k,\,inp} &=& nv^3 r_s^2 \\ %= n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
  &=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\

### 2015-09-12 ms.tex
more of minor edits

--- 2015-09-11 ms.tex
@@
 
-\memoYF{In the end the number of significant decimal digits is set to 1 or 2.}
-
 Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
@@
 \begin{equation}
-L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
+%L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
+L \sim 6.3\times10^{23} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 
 \label{eq:burrowsLum}
@@
 \begin{eqnarray}
-n &=& 1.80 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
+n &=& 1.8 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
 &&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
@@
 %%%%%%%%%%
-\memoYF{check the values above}
 
@@
 \begin{equation}
-\nu_{\rm cyc} = \frac{eB}{2\pi m_e} \approx 27.9 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
+\nu_{\rm cyc} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
 \end{equation}
@@
 \begin{eqnarray}
-\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 8.98 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
-\label{eq:fplasmalos_scaled} & = & 14.7{\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
+\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 
+8979 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
+\label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
  & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
 \end{eqnarray}
-\memoYF{check numbers in above equation}
 %%%
@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_s^2 %= n v^3 \left( \frac{B^2}{2\pi m_{\rm p}nv^2} \right)^{1/3}  \\
-&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.20~\mbox{AU}} \right)^{-4/3}  \notag \\
+P_{\rm k,\,inp} &=& nv^3 r_s^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
+\\
+&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
-For each red giant, the mass-loss rate is estimated by Reimers' equation \citep{reimers1975} \memoYF{should be replaced by the updated Reimer's equation}:
-%%%
-\begin{equation}
-\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
-\end{equation}
-%%%
-where $R_{\star }$, $L_{\star } (=4\pi R_{\star }^2 T_{\star }^4)$, and $M_{\star}$ are the radius, luminosity, and mass of the star. 
-The factor $\eta $ is $\sim 0.3-3$, and we assume $\eta =1$ here. 
+For each red giant, the mass-loss rate is estimated by the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
+%%%
+\begin{equation}
+%\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) 
+\end{equation}
+%%%
+where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
 The velocity of the stellar wind is assumed to scale with the escape velocity, hence
@@
 %%%
-The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass.
-We assume \memoYF{validation}:
+The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
 %%%

### 2015-09-12 ms.tex
Updates ionizing source rate description.

@@
 %%%%%%%%%
-where $S$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
+where $\dot{N}_x$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
 % http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
@@
 %%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy is greater than 13.6~eV ($\lambda < 91~\rm nm$), the energy needed to ionize hydrogen atoms.
+The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($1{\rm~Ry} = 13.6$~eV where Ry is the Rydberg constant, or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
+\begin{equation}
+\dot{N}_x \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
+\end{equation}
+where $k_B$ is Boltzmann's constant.
 As a result, 
@@
 \begin{eqnarray}
-S_* \sim  
+\dot{N}_x \sim  
   \left\{

### 2015-09-13 ms.tex
normalized to 1e-8 Msolar/yr...not sure this is better, plus minor edit

@@
 && \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
-\nonumber &=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
+\nonumber &=& 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
 && \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
@@
 P_{\rm k,\,inp} 
-&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
+%&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+%&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
+&\approx &  140 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}{\rm /yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+%&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+%&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
+&\approx & 14000 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&& \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}{\rm /yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
-&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+%&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+%&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
@@
 F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 \nu_{\rm cyc}} \\
-&\approx & 5.22\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 5.2\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 %%%
-&\approx & 1.12 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+%&\approx & 1.12 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+%&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+%&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+&\approx & 0.70 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
+&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
 %%%
-&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+%&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+%&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+%&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+&\approx & 0.70 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
+&& \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
 %%%
-&\approx & 2.42 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
+&\approx & 2.4 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
 &&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
@@
 \begin{equation}
-r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} \dot v^{-1/6}, 
+r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} v^{-1/6}, 
 \end{equation}
@@
 \begin{equation}
-P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} \dot v^{5/3}.
+P_{\rm inp, k} \propto B^{2/3} a^{-4/3} \dot M_{\star }^{2/3} v^{5/3}.
 \end{equation}

### 2015-09-13 ms.tex
updating ionized region (halfway)

@@
 \begin{equation}
-R_{\rm stromgren} = \frac{3}{4\pi} \left( \frac{S}{n^2 \beta } \right)^{1/3}
-\end{equation}
-%%%%%%%%%
-where $\dot{N}_x$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
+R_{\rm stromgren} = \frac{3}{4\pi} \left( \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
+\end{equation}
+%%%%%%%%%
+where $\dot{N}_X$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
 % http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
@@
 \begin{equation}
-\dot{N}_x \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
+\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
 \end{equation}
@@
 for a planet around a red giants at 5~AU.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\memoYF{how about the following}
+
+The accretion disks around planets therefore emit X-ray radiation. 
+The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
+or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
+%%%%%%%%%
+\begin{equation}
+\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
+\end{equation}
+%%%%%%%%%
+where $k_B$ is Boltzmann's constant.
+As a result, 
+%%%%%%%%%
+\begin{eqnarray}
+\dot{N}_x \sim  
+  \left\{
+    \begin{array}{ll}
+      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
+      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+    \end{array}. 
+  \right.
+\end{eqnarray}
+%%%%%%%%%
+
+Let us consider the ionization state around the planet. 
+We suppose a state where the ionization and recombination rates are in equilibrium. 
+The cross section of H atoms for X-ray, $\sigma _H [E_{\rm photon}] $ is
+%%%%%%%%%
+\begin{equation}
+\sigma _H [E_{\rm photon}] = 6.3 \times 10^{-18} \;{\rm cm}^2 \cdot \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} \right)^{-3} 
+\end{equation}
+%%%%%%%%%
+where $E_{\rm photon} = k_B T_{\rm acc} $ is energy per photon, 
+while the recombination rate $\beta [T_e]$ is 
+%%%%%%%%%
+\begin{equation}
+\beta [T_e] = 2.6 \times 10^{-13}\;{\rm cm^3/sec}\cdot\left(\frac{T_e}{10^{4}} \right)^{-3/4}
+\end{equation}
+%%%%%%%%%
+where $T _e$ is electron temperature $\sim 10^4$ K \memoYF{cite something}.
+
+Denoting the ionization fraction by $\alpha $, the equilibrium state at a distance $r$ from the planet is represented by 
+%%%%%%%%%
+\begin{equation}
+\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-\alpha ) \sigma _H [E_{\rm photon}] = (n \alpha )^2 \beta [T_e] \label{eq:equilibrium}
+\end{equation}
+%%%%%%%%%
+Here, we ignored the attenuation of X-ray because the optical depth $\tau \sim n \sigma r$ is much smaller than unity.  
+The ionization fraction $\alpha $ that satisfies \ref{eq:equilibrium} is shown in Figure \ref{fig:ionizationfraction}.  
+Although the photon number is large for larger planets, the strong dependence of cross section on the photon energy decreases the radius of ionized region. 
+However, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius. 
+\memoYF{Secondary ionization by energetic electrons needs to be incorporated. }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{ionizationfraction.pdf}
+   \caption{Ionization fraction due to X-ray from the planetary accretion disk.}
+  \label{fig:ionizationfraction}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{until here}
 

### 2015-09-14 ms.tex
Minor comment about additions to ionization fraction figure.

@@
 However, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius. 
-\memoYF{Secondary ionization by energetic electrons needs to be incorporated. }
+\memoYF{Secondary ionization by energetic electrons needs to be incorporated.}
 
@@
    \caption{Ionization fraction due to X-ray from the planetary accretion disk.}
+   \memoDS{This looks great.
+Might be good to also show the locations of the magnetic standoff point and the ``stromgren sphere radius'' on this figure (say, with vertical dashed and dotted lines?), and to move the legend to the lower left corner?
+{\tt plt.legend(loc=3)}}
   \label{fig:ionizationfraction}

### 2015-09-14 ms.tex
removed appendix comment --TM
removed dot over the velocity in equations 35 and 36.  must be a typo, looking at 7 and 34.

@@
 %%%
-The radius obtained for Jupiter from this equality is about a half of actual radius of magnetosphere \citep[][]{griesmeier2005}. 
+The radius obtained for Jupiter from this equality is about a half of the actual radius of magnetosphere \citep[][]{griesmeier2005}. 
 By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
@@
 &=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
-&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
+&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \\
 \nonumber &=& 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
-&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
+&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{v}{10^{-1}v_{\odot }} \right)^{-1/6}
  \label{eq:stand-off-radius}
@@
 \end{equation}
-\memoTM{I don't see how $\dot v \neq 0$ here, if we're assuming a constant stellar wind.}
 %%%

### 2015-09-14 ms.tex
minor edits

--- 2015-09-14 ms.tex
@@
 
-\title{Red-Giant Hot Jupiters: Brilliant Radio Beacons?
-\memoTM{Since they are not that bright, maybe ``The Radio Emission from Red-Giant Hot Jupiters'' 
-or ``A Novel Method for Detecting Red-Giant Hot Jupiters'' would be a better title?}}
+\title{Radio Emission from Red-Giant Hot Jupiters}
 
@@
 
-One of the key features that makes planetary radio emission distinct is the almost complete circular polarization \citep[e.g.][]{dulk1994}.
-...\memoYF{write here (YF)}
+One of the key features that makes planetary radio emission distinct is the nearly  complete circular polarization \citep[e.g.][and reference therein]{dessler1983}. 
+On the other hand, active galactic nuclei, which are the major confusion sources, are known to have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014}.
 
 Another key is the significant time variability of the planetary radio emission. 
-The potential factors that cause time variability are  listed below.
+The factors that influence time variability are listed below.
 
@@
 \paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
-The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because the presence of Io inputs plasmas into the system. 
+The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because Io disturbs the surrounding electromagnetic field. 
 Likewise, if the exoplanets have moons that emit plasmas, then the radio flux is  modulated by the orbital motion of the moon \citep[see e.g.,][]{noyola2014}.
@@
 \paragraph{Variability of stellar wind (a few months $\sim $)?}
-If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time-variabililty of planetary radio emission.
+If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variabililty of planetary radio emission.
 Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.
@@
 
-\memoYF{Need to elaborate. References are needed. }
-
 So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
 Therefore, one possible strategy is to target known planetary systems.  
-One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30 \mbox{m/s}$.
-Therefore, there are some parameter spaces where current radial velocity observations cannot survey.
+One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30$ [m/s].
+Therefore, there are some parameter spaces where current radial velocity observations have not been able to survey.
 For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
@@
 In turn, we could utilize the time variability to characterize the system.
-For example, if the system is near edge-on, we will observe the time variability corresponding to orbital period, which can tell us the orbital distance of the planets.
-If the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable (This is an advantage of searching for RGHJs rather than canonical hot Jupiters, because the latter is likely to be tidally locked to the stars).
+For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable.
+Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply presence of satellites.
 
@@
 Based on such a picture, the massive stellar wind of a red giant or AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
-We found that the intrinsic brightness of radio emission from RGHJs would be comparable to or greater than canonical hot Jupiters in close-in orbits around main-sequence stars.
+We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars.
 
 A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind.
-Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 15 MHz$ for typical red giants and $\sim 464 MHz$ for typical AGB stars.
-The most promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
+Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
+The promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 
@@
 
-Once the planetary radio emission is detected, ...\memoYF{write here}.
+The radio intensity of the RGHJs are intrinsically $>100$ times brighter than the main-sequence counterparts.
+This indicates that they can be observed 10 times further away, or in 1000 times larger volume.
+This can compensate the rareness of the evolved stars at least partly. Thus, RGHJs will be reasonable targets for future search for radio lighthouse from planetary systems.
+
+Radio emission can be follow-up observations of known RGHJs or may also be used as probe to discover them, given the lowered sensitivity of  radial velocity methods in detecting planetary companions. 
+Once the planetary radio emission is detected, it will provide a unique approach to  planetary spin, magnetic field, and presence of satellite, and potentially stellar wind properties.
 

### 2015-09-15 ms.tex
minor wordsmithing of magnetosphere sentence
discussion about inoized region is improved

@@
 
-As discussed in \citet{ignace2010}, the ionization fraction of the stellar wind of evolved stars are supposedly as low as $\sim 10^{-3}$\memoYF{cite something}.
+As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind are lowered down to order of $\sim 10^{-3}$ \citep{drake1987}.
 Since only charged particles interact with planetary magnetic field, this suggests the inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
@@
 T_{\rm acc} \sim && 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
-\sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). 
-\end{eqnarray}
-%%%%%%%%%
-The accretion disks around planets therefore emit X-ray radiation. 
-We estimate the scale of the ionized region by computing Stromgren radius of the accretion disk \citep{stromgren1939}: 
-%%%%%%%%%
-\begin{equation}
-R_{\rm stromgren} = \frac{3}{4\pi} \left( \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
-\end{equation}
-%%%%%%%%%
-where $\dot{N}_X$ is the source rate of ionizing photons, $n$ is the density of hydrogen, and $\beta $ is the coefficient for recombination \memoYF{cite something}:
-% http://www.tapir.caltech.edu/~chirata/ay102/Photoionized.pdf
-% T \propto 4.3e-13 ( T /10^4 K )^-0.7
-%%%%%%%%%
-\begin{eqnarray}
-%\beta &=& 4.3? \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
-\beta &=& 2.6 \times 10^{-13} \; \left( \frac{T}{10^4 \;{\rm K}} \right) ^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} \\
-&\sim& 2.74 \times 10^{-14} \; \left( \frac{M_p}{M_J} \right)^{-3/4} \;\; {\rm cm^3 \; sec^{-1}} 
-\end{eqnarray}
-%%%%%%%%%
-The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($1{\rm~Ry} = 13.6$~eV where Ry is the Rydberg constant, or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
+\sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). \label{eq:Tacc}
+\end{eqnarray}
+%%%%%%%%%
+Therefore, the accretion disks around planets therefore emit UV/X-ray radiation 
+whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$.
+
+Let us consider the ionization profile around the planet. 
+We suppose a state where the ionization and recombination rates are in equilibrium. 
+Denoting the ionization fraction by $\alpha $, the equilibrium state at a distance $r$ from the planet may be approximately represented by 
+%%%%%%%%%
+\begin{equation}
+\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-\alpha ) \sigma _H [E_{\rm photon}] = (n \alpha )^2 \beta [T_e] \label{eq:equilibrium}
+\end{equation}
+%%%%%%%%%
+where $\dot N_X$ is the source rate of the photons that can ionize the hydrogen, 
+$\sigma _H$ is the cross section of H atoms for X-ray \citep{verner1996}: 
+%%%%%%%%%
+\begin{equation}
+\sigma _H [E_{\rm photon}] \sim 6.3 \times 10^{-18} \;{\rm cm}^2 \cdot \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} \right)^{-3} \label{eq:sigma_H}
+\end{equation}
+%%%%%%%%%
+where $E_{\rm photon}$ is the energy per photon, 
+and $\beta [T_e]$ is the ``class B'' recombination coefficient which is 
+$ \beta \sim 2.6 \times 10^{-13}\;{\rm cm^3/sec} $ \citep{pequignot1991} 
+at electron temperature of stellar wind of evolved stars, $T_e \sim 10^4 $K \citep{suzuki2007}. 
+In equation (\ref{eq:equilibrium}), we ignored the attenuation of X-ray because the optical depth $\tau \sim n \sigma _H r$ is much smaller than unity.
+
+The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
+or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
+%%%%%%%%%
 \begin{equation}
@@
 \end{equation}
+%%%%%%%%%
 where $k_B$ is Boltzmann's constant.
@@
 %%%%%%%%%
-Using the number density of hydrogen atoms given by equation (\ref{eq:n_normalized}), 
+For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$.
+In theory, photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
+To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
+%%%%%%%%%
+\begin{equation}
+\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + f \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
+\end{equation}
+%%%%%%%%%
+where the $f$ is a fudge factor to represent the efficiency of this reaction.
+
+The ionization fraction $\alpha $ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
+The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$.
+In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
+\memoYF{need to replace the order?}
+While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region. 
+Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
+
+The extent of ionized region can also be roughly estimated by Stromgren radius of the accretion disk \citep{stromgren1939}: 
+%%%%%%%%%
+\begin{equation}
+R_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
+\end{equation}
+%%%%%%%%%
+which gives
 %%%%%%%%%
@@
     \begin{array}{ll}
-      40 ~R_J & \;\;\;(M_p = M_J) \\
-      400 ~R_J & \;\;\;(M_p = 10 M_J)
+      67 ~R_J & \;\;\;(M_p = M_J) \\
+      310 ~R_J & \;\;\;(M_p = 10 M_J)
     \end{array}
-  \right.
+  \right. \label{eq:stromgren}
 \end{eqnarray}
@@
 for a planet around a red giants at 5~AU. 
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\memoYF{how about the following}
-
-The accretion disks around planets therefore emit X-ray radiation. 
-The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
-or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
-%%%%%%%%%
-\begin{equation}
-\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
-\end{equation}
-%%%%%%%%%
-where $k_B$ is Boltzmann's constant.
-As a result, 
-%%%%%%%%%
-\begin{eqnarray}
-\dot{N}_x \sim  
-  \left\{
-    \begin{array}{ll}
-      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
-      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
-    \end{array}. 
-  \right.
-\end{eqnarray}
-%%%%%%%%%
-
-Let us consider the ionization state around the planet. 
-We suppose a state where the ionization and recombination rates are in equilibrium. 
-The cross section of H atoms for X-ray, $\sigma _H [E_{\rm photon}] $ is
-%%%%%%%%%
-\begin{equation}
-\sigma _H [E_{\rm photon}] = 6.3 \times 10^{-18} \;{\rm cm}^2 \cdot \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} \right)^{-3} 
-\end{equation}
-%%%%%%%%%
-where $E_{\rm photon} = k_B T_{\rm acc} $ is energy per photon, 
-while the recombination rate $\beta [T_e]$ is 
-%%%%%%%%%
-\begin{equation}
-\beta [T_e] = 2.6 \times 10^{-13}\;{\rm cm^3/sec}\cdot\left(\frac{T_e}{10^{4}} \right)^{-3/4}
-\end{equation}
-%%%%%%%%%
-where $T _e$ is electron temperature $\sim 10^4$ K \memoYF{cite something}.
-
-Denoting the ionization fraction by $\alpha $, the equilibrium state at a distance $r$ from the planet is represented by 
-%%%%%%%%%
-\begin{equation}
-\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-\alpha ) \sigma _H [E_{\rm photon}] = (n \alpha )^2 \beta [T_e] \label{eq:equilibrium}
-\end{equation}
-%%%%%%%%%
-Here, we ignored the attenuation of X-ray because the optical depth $\tau \sim n \sigma r$ is much smaller than unity.  
-The ionization fraction $\alpha $ that satisfies \ref{eq:equilibrium} is shown in Figure \ref{fig:ionizationfraction}.  
-Although the photon number is large for larger planets, the strong dependence of cross section on the photon energy decreases the radius of ionized region. 
-However, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius. 
-\memoYF{Secondary ionization by energetic electrons needs to be incorporated.}
+The Stromgren radius for $1M_J $ and for $10M_J$ are also indicated in Figure \ref{fig:ionizationfraction}.
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Stromgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
+The Stromgren radius are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
 
@@
    \plotoneh{ionizationfraction.pdf}
-   \caption{Ionization fraction due to X-ray from the planetary accretion disk.}
-   \memoDS{This looks great.
+   \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
+Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with the fudge factor $f=0.5$.
+The vertical arrows show the Stromgren radius estimated simply  by equation (\ref{eq:stromgren}).
+The dotted vertical lines indicate the location of the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
+}
+   %\memoDS{This looks great.
 Might be good to also show the locations of the magnetic standoff point and the ``stromgren sphere radius'' on this figure (say, with vertical dashed and dotted lines?), and to move the legend to the lower left corner?
@@
 
-\memoYF{until here}
-
 We therefore expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.

### 2015-09-16 ms.tex
Change ionization fraction from \alpha to x

@@
 We suppose a state where the ionization and recombination rates are in equilibrium. 
-Denoting the ionization fraction by $\alpha $, the equilibrium state at a distance $r$ from the planet may be approximately represented by 
-%%%%%%%%%
-\begin{equation}
-\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-\alpha ) \sigma _H [E_{\rm photon}] = (n \alpha )^2 \beta [T_e] \label{eq:equilibrium}
+Denoting the ionization fraction by $x$, the equilibrium state at a distance $r$ from the planet may be approximately represented by 
+%%%%%%%%%
+\begin{equation}
+\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-x ) \sigma _H [E_{\rm photon}] = (n x )^2 \beta [T_e] \label{eq:equilibrium}
 \end{equation}
@@
 \begin{eqnarray}
-\dot{N}_x \sim  
+\dot{N}_X \sim  
   \left\{
@@
 
-The ionization fraction $\alpha $ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
+The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
 The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$.
@@
 %%%
-The radius obtained for Jupiter from this equality is about a half of the actual radius of magnetosphere \citep[][]{griesmeier2005}. 
+The radius obtained for Jupiter from this equality is about half of the actual magnetospheric radius \citep[][]{griesmeier2005}. 
 By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
@@
 %
-For example, \citet{OGorman2013} reported $\alpha $ Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha $ Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+For example, \citet{OGorman2013} reported $\alpha$~Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha$~Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
 Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
@@
 \nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
-&& \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha } 
-\end{eqnarray}
-%%%
-where the power index $\alpha $ is order of unity.
+&& \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha_* } 
+\end{eqnarray}
+%%%
+where the power index $\alpha_* $ is order of unity.
 
@@
 The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
-The continuum lines from the star in the cases of $\alpha =0.8$ and $2.0$ are shown as an extreme case.
+The continuum lines from the star in the cases of $\alpha_* =0.8$ and $2.0$ are shown as an extreme case.
 %; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
@@
 In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known one could estimate the likelihood of detecting RGHJs in radio surveys.
-For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $F_{\rm max} \propto d^{\frac{3}{\alpha} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha < 3/2$.
+For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha_L}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
+Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $F_{\rm max} \propto d^{\frac{3}{\alpha_L} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha_L < 3/2$.
 Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection.
@@
 
-Unlike usual hot jupiters, RGHJs are not subject to tidal lock, as the gravitational effects of their host star does not change even if the star evolves into red giants.
+Unlike usual hot jupiters, RGHJs are not tidally locked to their host stars, as the stellar tidal field does not change significantly even if the star evolves into a giant.
 Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 

### 2015-09-16 ms.tex
Note on number of electrons ... See the memo below eq. 18

@@
 For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$.
-In theory, photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
+Photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
 To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
@@
 \begin{equation}
-\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + f \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
-\end{equation}
-%%%%%%%%%
-where the $f$ is a fudge factor to represent the efficiency of this reaction.
+\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + \xi \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
+\end{equation}
+%%%%%%%%%
+where the $\xi$ is a fudge factor to represent the efficiency of this reaction.
+\memoDS{Does the above argument imply that $\xi \sim 0.6$?
+Should we think of it as an $N$-Rydberg photon, if absorbed, leads to 1 $N-1$-Rydberg electron, which produces 0.6 $N-2$-Rydberg electrons, $0.6^2$ $N-3$-Rydberg electrons, ...
+and $0.6^{N-1}$ 0-Rydberg electrons, so in the end we have $1 + 0.6 + 0.6^2 + ...
++ 0.6^{N-1} \sim 2.5$ electrons?}
+% N - power - 1 = energy of electrons
+% N - (N-1) - 1 = 0-Rydberg electron
 
 The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}.
+\memoDS{We should write the expression ...
+it's just the quadratic formula, but it would be useful to write.}
 The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$.

### 2015-09-18 ms.tex
sub photon
Added grant info
Fixed affiliation error

@@
 
-\affil{$^8$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}
+\affil{$^8$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}
 
@@
 For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$.
-Photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
+Photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
 To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
@@
 YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
-DSS gratefully acknowledges support from a fellowship from the AMIAS group.
+DSS gratefully acknowledges support from a fellowship from the AMIAS group. JN acknowledges support from NASA grant HST AR-12146.04-A and NSF grant AST-1102738.
 We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.

### 2015-09-18 ms.tex
f -> \xi

--- 2015-09-16 ms.tex
@@
 it's just the quadratic formula, but it would be useful to write.}
-The solid lines show the ionization fraction of $f=0$ (no additional ionization by electrons) and dashed lines show that of $f=0.5$.
+The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$.
 In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
@@
    \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
-Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with the fudge factor $f=0.5$.
+Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with the fudge factor $\xi=0.5$.
 The vertical arrows show the Stromgren radius estimated simply  by equation (\ref{eq:stromgren}).

### 2015-09-21 ms.tex
Minor edits to the abstract; adds a comment to the abstract.

@@
 We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields.
-We predict that RGHJs might be as bright as canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances less than a few hundred parsecs with current/future instruments such as LOFAR and SKA.
+\memoDS{I recommend nixing ``radiometric Bode's law'' from the abstract, but wanted to get others' opinions before doing so.}
+We predict that RGHJs might be intrinsically brighter than canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array.
 

### 2015-09-21 ms.tex
discussion for ionized region is revised

@@
 \begin{equation}
-\frac{\dot N_X}{ 4 \pi r^2 } n ( 1-x ) \sigma _H [E_{\rm photon}] = (n x )^2 \beta [T_e] \label{eq:equilibrium}
+\frac{\dot N_X}{ 4 \pi r^2 } e^{- \tau } n ( 1-x ) \sigma _H [E_{\rm photon}] = (n x )^2 \beta [T_e] \label{eq:equilibrium} 
+\end{equation}
+%%%%%%%%%
+\begin{equation}
+\tau = \int _{R_J}^r n(1-x) \sigma_H dr 
 \end{equation}
@@
 at electron temperature of stellar wind of evolved stars, $T_e \sim 10^4 $K \citep{suzuki2007}.
-In equation (\ref{eq:equilibrium}), we ignored the attenuation of X-ray because the optical depth $\tau \sim n \sigma _H r$ is much smaller than unity.
 
@@
 %%%%%%%%%
-For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$.
-Photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
-To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
-%%%%%%%%%
-\begin{equation}
-\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + \xi \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
-\end{equation}
-%%%%%%%%%
-where the $\xi$ is a fudge factor to represent the efficiency of this reaction.
-\memoDS{Does the above argument imply that $\xi \sim 0.6$?
-Should we think of it as an $N$-Rydberg photon, if absorbed, leads to 1 $N-1$-Rydberg electron, which produces 0.6 $N-2$-Rydberg electrons, $0.6^2$ $N-3$-Rydberg electrons, ...
-and $0.6^{N-1}$ 0-Rydberg electrons, so in the end we have $1 + 0.6 + 0.6^2 + ...
-+ 0.6^{N-1} \sim 2.5$ electrons?}
-% N - power - 1 = energy of electrons
-% N - (N-1) - 1 = 0-Rydberg electron
+
+For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and the mean free path of the electrons is $\sim 2R_J$.
+In practice, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
+To take this into account, we consider the cascade where an electron with energy $E _{\rm in}$ ionize an atom releasing two electrons  (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each.
+Note that the proton will not acquire much energy due to the conservation of momentum and conservation of energy. \memoYF{in more detail?}
+For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce a photon with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum.
+In reality, not all released electrons may be able to proceed the next ionization.
+Letting $\xi $ represent the fraction of released electrons that proceed to the next ionization, the number of ionized atoms through this cascade, $\alpha $, is
+%%%%%%%%%
+\begin{equation}
+\alpha = (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3. 
+\end{equation}
+%%%%%%%%%
+With $\xi = 0.8 $, this gives $\alpha \sim 5$. 
+Then, $\dot{N}_X $ in equation (\ref{eq:equilibrium}) is replaced by 
+%%%%%%%%%
+\begin{equation}
+\dot{N}_X \rightarrow \alpha \dot{N}_X. 
+\end{equation}
+%%%%%%%%%
 
 The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
-\memoDS{We should write the expression ...
-it's just the quadratic formula, but it would be useful to write.}
+%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
+When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
+%%%%%%%%%
+\begin{eqnarray}
+x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
+C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
+%%%%%%%%%
 The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$.
 In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
-\memoYF{need to replace the order?}
-While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region. 
+While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region. 
 Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
@@
 Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Stromgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
-The Stromgren radius are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
+The Stromgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
 
@@
    \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
-Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with the fudge factor $\xi=0.5$.
+Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $\xi=0.8$.
 The vertical arrows show the Stromgren radius estimated simply  by equation (\ref{eq:stromgren}).
-The dotted vertical lines indicate the location of the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
+The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius}) below.
 }
@@
 
-We therefore expect that the X-ray emission from the accretion disk is enough to ionize the stellar wind.
-This implies that the stellar wind particles represented by (equation~\ref{eq:n}) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
+We therefore expect for the X-ray emission from the accretion disk to ionize the stellar wind.
+This implies that the stellar wind particles represented by (equation~(\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
 
@@
 P_{\rm radio} &\propto & P_{\rm inp} \\
-P_{\rm inp,\,k} &=& n v^3 r_s ^2 \label{eq:Pinp_kin}, \\
-P_{\rm inp,\,m} &=& v B_{\bot }^2 r_s ^2 \label{eq:Pinp_mag} \, ,
-\end{eqnarray}
-%%%
-where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_s$ is the radius of the magnetic stand-off point. 
+P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
+P_{\rm inp,\,m} &=& v B_{\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
+\end{eqnarray}
+%%%
+where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point. 
 %In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
@@
 
-The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
-%%%
-\begin{equation}
-m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
+The radius of the magnetic stand-off point, $r_{\rm mag}$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
+%%%
+\begin{equation}
+m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_{\rm mag}}{R_p} \right)^{-6}  \label{eq:stand-off}
 \end{equation}
@@
 %If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
-%We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
-%%%
-\begin{eqnarray}
-\nonumber r_s 
+%We estimate $r_{\rm mag}$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
+%%%
+\begin{eqnarray}
+\nonumber r_{\rm mag} 
 %&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_s^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
+P_{\rm k,\,inp} &=& nv^3 r_{\rm mag}^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
 \\
@@
 As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$.
-Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} (R_\star/M_\star)(1+A/g_\star)$, where $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
-Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} [(R_\star/M_\star)(1+A/g_\star)]^{1/2}$.
+Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$, where $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
+Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} R_\star ^{-0.375} M_\star^{-1/2} (1+A/g_\star)^{1/2}$.
 Therefore, the LF of giant host stars is an essential ingredient for determining the LF for RGHJs which future surveys would need to consider.
@@
 \begin{equation}
-m_p n[r_s] v^2 < \frac{B[r_s]^2}{2\pi }
+m_p n[r_{\rm mag}] v^2 < \frac{B[r_{\rm mag}]^2}{2\pi }
 \end{equation}
@@
 
+\end{document}
+
 \newpage
@@
 \begin{equation}
-P_{\rm inp,k}=nv^3 r_s^2 \propto \dot M_{\star} v^2 a^{-2} r_s^2.
-\end{equation}
-%%%
-Combining the above equation with the scaling between the radius of the magnetic stand-off point, $r_s$, and the planetary magnetic field $B$ (equation (\ref{eq:stand-off-radius})), i.e.\
-%%%
-\begin{equation}
-r_s \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} v^{-1/6}, 
+P_{\rm inp,k}=nv^3 r_{\rm mag}^2 \propto \dot M_{\star} v^2 a^{-2} r_{\rm mag}^2.
+\end{equation}
+%%%
+Combining the above equation with the scaling between the radius of the magnetic stand-off point, $r_{\rm mag}$, and the planetary magnetic field $B$ (equation (\ref{eq:stand-off-radius})), i.e.\
+%%%
+\begin{equation}
+r_{\rm mag} \propto B^{1/3} a^{1/3} \dot M_{\star }^{-1/6} v^{-1/6}, 
 \end{equation}
@@
 %\begin{equation}
-%r_s = 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
+%r_{\rm mag} = 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 %\end{equation}
@@
 
-We assume that $N_{\rm plasma}(r_s) $  is proportional to the squared radius of the magnetic stand-off point:
-%%%
-\begin{equation}
-N_{\rm plasma}(r_s) \propto \pi r_s^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
+We assume that $N_{\rm plasma}(r_{\rm mag}) $  is proportional to the squared radius of the magnetic stand-off point:
+%%%
+\begin{equation}
+N_{\rm plasma}(r_{\rm mag}) \propto \pi r_{\rm mag}^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
 \end{equation}
@@
 \begin{equation}
-N_{\rm plasma}(r) \propto  \frac{r_s^2 }{v_{\|}(r) r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
+N_{\rm plasma}(r) \propto  \frac{r_{\rm mag}^2 }{v_{\|}(r) r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
 \end{equation}
@@
 %%%
-Assuming that the initial energy (at $r=r_s$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
-%%%
-\begin{equation}
-v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \label{eq:v_||}
+Assuming that the initial energy (at $r=r_{\rm mag}$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
+%%%
+\begin{equation}
+v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_{\rm mag}} \right)^{-6} \label{eq:v_||}
 \end{equation}
@@
 \begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_s} \right)^{-6} \right)^{1/2}  
+\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_{\rm mag}} \right)^{-6} \right)^{1/2}  
 \end{equation}

### 2015-09-21 ms.tex
photon -> electron

@@
 Note that the proton will not acquire much energy due to the conservation of momentum and conservation of energy. \memoYF{in more detail?}
-For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce a photon with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum.
+For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce an electron with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum.
 In reality, not all released electrons may be able to proceed the next ionization.

### 2015-09-22 ms.tex
Edited ionization cascade section and added Mehrdad's work as an appendix section

--- 2015-09-21 ms.tex
@@
 %%%%%%%%%
-Therefore, the accretion disks around planets therefore emit UV/X-ray radiation 
+The accretion onto planets, therefore, leads to emission of UV/X-ray radiation 
 whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$.
@@
 
-For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and the mean free path of the electrons is $\sim 2R_J$.
-In practice, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
-To take this into account, we consider the cascade where an electron with energy $E _{\rm in}$ ionize an atom releasing two electrons  (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each.
-Note that the proton will not acquire much energy due to the conservation of momentum and conservation of energy. \memoYF{in more detail?}
-For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization produce a photon with energy of $(12-1) = 11 E_{\rm Rydberg} $, then second ionization by that electron produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$; the cascade can proceed to the forth  order at the maximum.
+For the accretion onto large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity.
+The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$ (\citep{fite1958}), which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
+As a result, nearly 2/3 of released energetic electrons will ionize a hydrogen atom within $\sim$2$R_J$, and more than 99\% will ionize a hydrogen atom within $\sim$10$R_J$.
+
+In principle, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times.
+To take this into account, we consider two limiting possibilities:
+After an ionizing collision, the energy can (\emph{i}) be split evenly between the two electrons, or it can (\emph{ii}) go entirely into the kinetic energy of one electron and not at all into that of the other (of course, any split in between these extremes is possible, too).
+Note that conservation of momentum and energy imply that the proton will not acquire a significant fraction of the energy of the collision.\footnote{Were it otherwise, we'd have to take into account what fraction of a rubber ball's kinetic energy is imparted to the kinetic energy of the Earth when bouncing a ball.}  \memoYF{in more detail?} \memoDS{I think it's fine.}
+
+Scenario (\emph{i}) implies a cascade where an electron with energy $E_{\rm in}$ ionizes an atom producing two electrons (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each.
+For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization could produce an electron with energy of $(12-1) = 11 E_{\rm Rydberg} $, then a second ionization by that electron would produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons would produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$, etc.
+The cascade can proceed to the fourth order at the maximum.
+
+Under scenario (\emph{ii}), the cascade proceeds with the initial $E_{\rm in}$ electron leading to an electron with kinetic energy $E_{\rm in} - E_{\rm Rydberg}$ and another electron with 0 kinetic energy.
+Clearly, this cascade can produce a maximum total of $E_{\rm in} / E_{\rm Rydberg}$ free electrons.
+
 In reality, not all released electrons may be able to proceed the next ionization.
-Letting $\xi $ represent the fraction of released electrons that proceed to the next ionization, the number of ionized atoms through this cascade, $\alpha $, is
-%%%%%%%%%
-\begin{equation}
-\alpha = (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3. 
-\end{equation}
-%%%%%%%%%
-With $\xi = 0.8 $, this gives $\alpha \sim 5$. 
-Then, $\dot{N}_X $ in equation (\ref{eq:equilibrium}) is replaced by 
-%%%%%%%%%
-\begin{equation}
-\dot{N}_X \rightarrow \alpha \dot{N}_X. 
-\end{equation}
-%%%%%%%%%
+If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
+%%%%%%%%%
+\begin{eqnarray}
+  \nonumber N_i & = & (1-\xi) + 2\xi (1-\xi) + 4 \xi^2 (1-\xi) + 8 \xi^3 \\
+  \label{eq:N_i1} & = & 1 + \xi + 2 \xi^2 + 4 \xi ^3 \, .
+\end{eqnarray}
+%%%%%%%%%
+With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
+Alternatively, cascade (\emph{ii}) leads to
+%%%%%%%%%
+\begin{eqnarray}
+  \nonumber N_i & = & \frac{1 - \xi^\nu}{1 - \xi} \\
+  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
+\end{eqnarray}
+%%%%%%%%%
+where $\nu \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
+This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
+In Appendix \ref{sec:AppendixB}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) is probably more realistic.
+
+Ultimately, $\dot{N}_X $ in equation (\ref{eq:equilibrium}) is replaced by 
+%%%%%%%%%
+\begin{equation}
+\dot{N}_X \rightarrow N_i \dot{N}_X \, .
+\end{equation}
+%%%%%%%%%
+For a $10 M_J$ planet, $N_i$ is probably approximately in the range 5---10.
 
@@
 
-\end{document}
-
 \newpage
@@
 \section{Comparison with previous work}
+\label{sec:AppendixA}
 
@@
 
+\section{Ionization Cascade}
+\label{sec:AppendixB}
+
+For an electron-hydrogen ionizing collision, we estimate the differential cross section $\sigma$ as a function of recoil energy $d\sigma / dE_{\rm recoil}$.
+We approximate the bound electron as a free one at rest and use the differential cross section for scattering of two electrons (Bhabha scattering) in the non-relativistic limit:
+\begin{equation}
+\label{eq:dsig/dOmeg} \frac{d\sigma}{d\Omega_{\rm CM}} \sim \frac{\alpha^2}{m_e^2 v_{\rm rel}^2 \sin^4 \theta} \, ,
+\end{equation}
+where $\alpha$ is the fine structure constant, $v_{\rm rel}$ is the relative velocity, $\theta$ is the scattering angle in the center of mass (CM) frame, and $m_e$ is the electron mass.
+The recoil energy (that is, the energy transferred to the electron at rest) is related to the scattering angle via
+\begin{equation}
+  \label{eq:Erec} = \frac{1}{4} m_e v_{\rm rel}^2 \left( 1 - \cos \theta \right) \, ,
+\end{equation}
+and hence
+\begin{equation}
+  \label{eq:dErec/dOmeg} \frac{dE_{\rm recoil}}{d\Omega_{\rm CM}} = -\frac{1}{4} m_e v_{\rm rel}^2 \, .
+\end{equation}
+We therefore have
+\begin{equation}
+  \label{eq:dsig/dErec} \frac{d\sigma}{dE_{\rm recoil}} \sim \frac{\alpha^2}{m_e v_{\rm rel}^2 E_{\rm recoil}^2} \, ,
+\end{equation}
+which is largest for small recoil energies.
+Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful.
+%This suggests that if the energetic electron ends up ionizing other atoms, it is more likely to put them right at the threshold of
+
 \end{document}

### 2015-09-22 ms.tex
I forgot where I have changed... but they must be minor
attempting to revise discussions on luminosity function

@@
 %\usepackage[dvipdfmx]{graphicx}
-
-% trivial change as a test
 
@@
 After an ionizing collision, the energy can (\emph{i}) be split evenly between the two electrons, or it can (\emph{ii}) go entirely into the kinetic energy of one electron and not at all into that of the other (of course, any split in between these extremes is possible, too).
-Note that conservation of momentum and energy imply that the proton will not acquire a significant fraction of the energy of the collision.\footnote{Were it otherwise, we'd have to take into account what fraction of a rubber ball's kinetic energy is imparted to the kinetic energy of the Earth when bouncing a ball.}  \memoYF{in more detail?} \memoDS{I think it's fine.}
+Note that conservation of momentum and energy imply that the proton will not acquire a significant fraction of the energy of the collision.\footnote{Were it otherwise, we'd have to take into account what fraction of a rubber ball's kinetic energy is imparted to the kinetic energy of the Earth when bouncing a ball.}
 
@@
 \begin{equation}
-R_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
+r_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
 \end{equation}
@@
 \begin{eqnarray}
-R_{\rm stromgren} \sim  
+r_{\rm stromgren} \sim  
   \left\{
@@
 %&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
-&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
+&=& r_{mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
 && \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \\
@@
 %\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
-\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) 
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
 \end{equation}
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross). 
+For a hypothetical Jupiter-mass planet at 5 AU, a reasonable number of systems have potential to emit radio wave at the level of $\sim 10 \mu {\rm Jy}$  out to $\sim 100-150$ pc.
 
@@
 In any case this is not the main point of this paper and I would leave it out.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Luminosity function of planetary radio: 
+nearby faint object v.s. far luminous object}
+\label{ss:Lfunc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
+For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume.
+Under these assumptions, the largest luminosity in a volume limited sample (volume $V$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
+The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$.
+Therefore,the likelihood of finding the brighter source increases with distance for $\alpha_L < 3/2$. 
+Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
+For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
+Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.
+
+Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy. 
+In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars. 
+As discussed in Section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
+Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity due to planets are roughly $L \propto L_{\star }^{2/3}$.
+Thus,  the criteria $\alpha _L < 3/2$ is satisfied if the slope of the luminosity function of the stars are not steeper than $-1$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Luminosity function of planetary radio emission}
-\label{ss:Lfunc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known one could estimate the likelihood of detecting RGHJs in radio surveys.
-For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N(L) \propto L^{-\alpha_L}$, where, $N(L)$ is the number of objects per unit volume with a luminosity of L, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the observed flux from the brightest source in a volume limited sample will scale with distance as $F_{\rm max} \propto d^{\frac{3}{\alpha_L} - 2}$, implying that the likelihood of finding the brightest source increases with distance for $\alpha_L < 3/2$.
-Such a scenario would indeed be favorable to detect RGHJs given that AGB stars, which are good sources for bright RGHJs due to their high mass loss rates, are rare and would require probing out to larger distances for detection.
-For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects.
-Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.
-
-Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy.
-In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars.
-As discussed in section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate as $\dot{M}_\star^{1/2}$.
-Recent empirical studies of stellar mass-loss rates, including those for evolved giant stars, suggest $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$, where $L_\star$,  $R_\star$, $M_\star$, and $g_\star$ are the stellar luminosity, radius, mass, and gravity, respectively, and $A  = g_\odot/4300$ is a constant \citep{schroder2005,schroder2007}.
-Therefore, the luminosity of a RGHJ varies nearly linearly as the luminosity of the host star, and is given by $L \propto L_\star^{7.5/8} R_\star ^{-0.375} M_\star^{-1/2} (1+A/g_\star)^{1/2}$.
-Therefore, the LF of giant host stars is an essential ingredient for determining the LF for RGHJs which future surveys would need to consider.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Back-reaction of a plasma flowing into a magnetic field}

### 2015-09-22 ms.tex
description for velocity term is improved

@@
 \begin{equation}
-n = \frac{\dot M_\star}{4\pi a^2 m_p v}
+n = \frac{\dot M_\star}{4\pi a^2 m_p v_{\rm sw}}
 \label{eq:n}
@@
 %%%%%%%%%% 
-where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v$ is the velocity of the stellar wind.
-
-While the solar mass loss rate, $\dot M_\odot$, is $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr \citep[e.g.,][]{hundhausen1997}, the mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
+where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v_{\rm sw}$ is the velocity of the stellar wind.
+For the solar wind, $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr and $v_{\rm sw} \sim 400 {\rm km/s}$ \citep[e.g.,][]{hundhausen1997}.
+
+The mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 Therefore, we have
@@
 
-On the other hand, the stellar wind velocity becomes smaller because of the small escape velocity (due to the expanded stellar radius).
-%\footnote{Escape velocity is $\sqrt{2GM/r}$.}
-Assuming that the stellar wind scales as the escape velocity, i.e., $\propto \sqrt{2GM_{\star}/R_{\star}}$ ($G$ is the gravitational constant, $M_{\star}$ is the stellar mass, and $R_{\star}$ is the stellar radius), a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
-Therefore, 
+On the other hand, the stellar wind velocity, $v_{\rm sw}$, becomes smaller as the star evolves.
+The wind velocity is typically the escape velocity at the distance of the several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star }$.
+For a planet with radius $R_{\star }=100~R_{\odot }$, this results in $v_{\rm sw}\sim 30~{\rm km/s}$. 
+Therefore, a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters at least 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
+
+Based on equations (\ref{eq:scale_Mdot}), the number density of the stellar wind (equation (\ref{eq:n})) are normalized as follows:
+%%%%%%%%%% 
+\begin{eqnarray}
+n &=& 1.8 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v_{\rm sw}}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
+\end{eqnarray}
+%%%%%%%%%%
+
+The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the infall velocity (i.e., acceleration by planetary gravity), and the planetary orbital velocity.
+While $v_{\rm sw}$ is $\sim 30~{\rm km/s}$, the infall velocity at the planetary to be added is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$), and the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$).
+Here, we simply consider
 %%%%%%%%%% 
@@
 %%%%%%%%%%
+as a fiducial values for the normalization. 
 %where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
-
-Based on equations (\ref{eq:scale_Mdot}) and (\ref{eq:scale_v}), the number density of the stellar wind (equation (\ref{eq:n})) are normalized as follows:
-%%%%%%%%%% 
-\begin{eqnarray}
-n &=& 1.8 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
-\end{eqnarray}
-%%%%%%%%%%
 

### 2015-09-22 ms.tex
independent section for inoization fraction

@@
 
-Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify the property of the planetary magnetic field in \S\ref{ss:magneticfield}, and that of the stellar wind of the evolved stars in \S\ref{ss:stellarwind}.
-Then, we discuss the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
+Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify some ingredients. 
+The property of the planetary magnetic field is described in \S\ref{ss:magneticfield}, and the stellar wind of the evolved stars is discussed in \S\ref{ss:stellarwind}.  
+In \S\ref{ss:ionization}, we consider the ionization around the planets because it is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind. 
+Then, we proceed to the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Ionization around the planet}
+\label{ss:ionization}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind are lowered down to order of $\sim 10^{-3}$ \citep{drake1987}.
@@
 %%%%%%%%%
-With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
+%With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
 Alternatively, cascade (\emph{ii}) leads to

### 2015-09-22 ms.tex
changed the order of appendix

@@
 
-In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
+In principle, if the expected luminosity function and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
 For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume.
@@
 Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
-For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
-Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.
-
-Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy. 
-In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars. 
-As discussed in Section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+For example, for an $N[L] \propto L^{-1}$ the apparently brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
+Therefore, if we can estimate the luminosity function of RGHJ emitters, we may estimate their detectability.
+
+Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy.
+In order to estimate the true luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
+As discussed in Section~3.2,\memoDS{Replace ``3.2'' with the section label.} for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$.
 Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity due to planets are roughly $L \propto L_{\star }^{2/3}$.
-Thus,  the criteria $\alpha _L < 3/2$ is satisfied if the slope of the luminosity function of the stars are not steeper than $-1$.
+Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
+Thus, the criterion $\alpha_L < 3/2$ is satisfied if the slope of the luminosity function of the host stars is shallower than $-1$.
 
@@
 
+\section{Ionization Cascade}
+\label{sec:AppendixB}
+
+For an electron-hydrogen ionizing collision, we estimate the differential cross section $\sigma$ as a function of recoil energy $d\sigma / dE_{\rm recoil}$.
+We approximate the bound electron as a free one at rest and use the differential cross section for scattering of two electrons (Bhabha scattering) in the non-relativistic limit:
+\begin{equation}
+\label{eq:dsig/dOmeg} \frac{d\sigma}{d\Omega_{\rm CM}} \sim \frac{\alpha^2}{m_e^2 v_{\rm rel}^2 \sin^4 \theta} \, ,
+\end{equation}
+where $\alpha$ is the fine structure constant, $v_{\rm rel}$ is the relative velocity, $\theta$ is the scattering angle in the center of mass (CM) frame, and $m_e$ is the electron mass.
+The recoil energy (that is, the energy transferred to the electron at rest) is related to the scattering angle via
+\begin{equation}
+  \label{eq:Erec} = \frac{1}{4} m_e v_{\rm rel}^2 \left( 1 - \cos \theta \right) \, ,
+\end{equation}
+and hence
+\begin{equation}
+  \label{eq:dErec/dOmeg} \frac{dE_{\rm recoil}}{d\Omega_{\rm CM}} = -\frac{1}{4} m_e v_{\rm rel}^2 \, .
+\end{equation}
+We therefore have
+\begin{equation}
+  \label{eq:dsig/dErec} \frac{d\sigma}{dE_{\rm recoil}} \sim \frac{\alpha^2}{m_e v_{\rm rel}^2 E_{\rm recoil}^2} \, ,
+\end{equation}
+which is largest for small recoil energies.
+Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful.
+%This suggests that if the energetic electron ends up ionizing other atoms, it is more likely to put them right at the threshold of
+
 \section{Comparison with previous work}
@@
 with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$. 
-
-\section{Ionization Cascade}
-\label{sec:AppendixB}
-
-For an electron-hydrogen ionizing collision, we estimate the differential cross section $\sigma$ as a function of recoil energy $d\sigma / dE_{\rm recoil}$.
-We approximate the bound electron as a free one at rest and use the differential cross section for scattering of two electrons (Bhabha scattering) in the non-relativistic limit:
-\begin{equation}
-\label{eq:dsig/dOmeg} \frac{d\sigma}{d\Omega_{\rm CM}} \sim \frac{\alpha^2}{m_e^2 v_{\rm rel}^2 \sin^4 \theta} \, ,
-\end{equation}
-where $\alpha$ is the fine structure constant, $v_{\rm rel}$ is the relative velocity, $\theta$ is the scattering angle in the center of mass (CM) frame, and $m_e$ is the electron mass.
-The recoil energy (that is, the energy transferred to the electron at rest) is related to the scattering angle via
-\begin{equation}
-  \label{eq:Erec} = \frac{1}{4} m_e v_{\rm rel}^2 \left( 1 - \cos \theta \right) \, ,
-\end{equation}
-and hence
-\begin{equation}
-  \label{eq:dErec/dOmeg} \frac{dE_{\rm recoil}}{d\Omega_{\rm CM}} = -\frac{1}{4} m_e v_{\rm rel}^2 \, .
-\end{equation}
-We therefore have
-\begin{equation}
-  \label{eq:dsig/dErec} \frac{d\sigma}{dE_{\rm recoil}} \sim \frac{\alpha^2}{m_e v_{\rm rel}^2 E_{\rm recoil}^2} \, ,
-\end{equation}
-which is largest for small recoil energies.
-Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful.
-%This suggests that if the energetic electron ends up ionizing other atoms, it is more likely to put them right at the threshold of
-
 \end{document}

### 2015-09-22 ms.tex
Minor edits to velocity section, and adds question in memo about relevant infall velocity

@@
 
-The mass loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
+The mass-loss rate of red giants is typically $\dot M_\star \sim 10^{-8}-10^{-7} M_{\odot}$/yr \citep{reimers1975}, and the rate can be as high as $10^{-5} M_\odot{\rm /yr}$ during the AGB phase \citep{schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 Therefore, we have
@@
 
-On the other hand, the stellar wind velocity, $v_{\rm sw}$, becomes smaller as the star evolves.
-The wind velocity is typically the escape velocity at the distance of the several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star }$.
-For a planet with radius $R_{\star }=100~R_{\odot }$, this results in $v_{\rm sw}\sim 30~{\rm km/s}$. 
-Therefore, a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters at least 10 times as slow stellar wind as that at the Sun, $v_{\odot}$.
-
-Based on equations (\ref{eq:scale_Mdot}), the number density of the stellar wind (equation (\ref{eq:n})) are normalized as follows:
+The stellar wind velocity, $v_{\rm sw}$, becomes smaller as the star evolves.
+The wind velocity is typically of order the escape velocity at the distance of the several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star}$.
+For a star with radius $R_{\star }=100~R_{\odot }$, this results in $v_{\rm sw}\sim 30~{\rm km/s}$.
+Therefore, a Solar-mass red giant with radius $R_{\star}=100R_{\odot}$ encounters a stellar wind that is slower by at least an order of magnitude than that of the Sun, $v_{\odot}$.
+
+Based on equations (\ref{eq:scale_Mdot}), the number density of the stellar wind (equation (\ref{eq:n})) is normalized as follows:
 %%%%%%%%%% 
@@
 
-The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the infall velocity (i.e., acceleration by planetary gravity), and the planetary orbital velocity.
-While $v_{\rm sw}$ is $\sim 30~{\rm km/s}$, the infall velocity at the planetary to be added is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$), and the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$).
+The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the planetary orbital velocity, and the infall velocity (i.e., the velocity due to falling in the planet's gravitional field).
+While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$).
+\memoDS{Where is the relevant velocity?
+Is it at the magnetic standoff point, or at the planetary surface, or somewhere in between?
+At the planet's surface, the infall velocity is 150 km/s for a 10$M_J$ planet, no?}
 Here, we simply consider
@@
 %where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
+%, and  (and should be something like the sum in quadrature of these velocities)
 

### 2015-09-22 ms.tex
minor revisions after proofreading abstract and section 1

--- 2015-09-22 ms.tex
@@
 Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.
-We estimate the spectral auroral radio intensity of RGHJs employing the ``radiometric Bode's law'' and a proposed scaling for planetary magnetic fields.
-\memoDS{I recommend nixing ``radiometric Bode's law'' from the abstract, but wanted to get others' opinions before doing so.}
-We predict that RGHJs might be intrinsically brighter than canonical hot Jupiters, and thus the low frequency radio emission from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array.
+We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
+We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and 100 times brighter than equivalent objects around main-sequence stars, which allow us to search them in 1000 times larger volume.
+The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array.
 
@@
 Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
-\citet{farrell1999,zarka2001,lazio2004} pointed out that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
+\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
 %\citet{griesmeier2004} modeled in detail the evolution of atmosphere and magnetic field of the tidally-locked close-in stars and found that 
@@
 In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
-\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
+%\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
+% I leave this out because this is not based on radiometric bode's law. 
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
@@
 During this time, such planets can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
-Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}, thus higher than that of the Sun, $\sim 10^{-14}M_\odot$/yr.
+Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit strong X-rays, thereby ionizing the hydrogen atoms around the planet.
-The ionized stellar wind would then interact with the planetary magnetic field in the same way as Solar System planets do.
-Thus, by extrapolating the radiometric Bode's law, we provide more optimistic estimates for highly evolved stars compared to the previous result.
+The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
+Thus, by extrapolating the ``radiometric Bode's law'', we provide more optimistic estimates for highly evolved stars compared to the previous result.
 We also consider the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
@@
 
-In \S2, we describe our assumptions for the stellar wind, planetary magnetosphere, frequency of radio emission, and scaling of planetary radio emission.
-\S3 presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
-\S4 gives predictions for the signals from evolved systems within 400 pc, taking account of the intrinsic radio emission from the host evolved stars.
-Considering the sensitivity of the current and future radio instruments, we argue that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
+In Section \ref{s:assumptions}, we introduce the framework to obtain the frequency of radio emission and the planetary radio emission, and describe our models for the stellar wind and planetary magnetosphere.
+Section \ref{s:result} presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
+Section \ref{s:observability} gives the prospects for the signal detection with the current/future instruments. 
+Estimates for the actual late-type (M type) evolved stars are also included. 
+We find that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
 %In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
-In \S5, we mention the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.  
-Finally, \S6 concludes the paper with a brief summary.
+Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission for characterizing the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.
+Finally, Section \ref{s:conc} concludes the paper with a brief summary.
 
@@
 We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
-The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radio Bode's law''; ][]{desch+kaiser1984}, i.e.,
+The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
 %Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
@@
 \section{Conclusions}
-\label{sec:conc}
+\label{s:conc}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-09-22 ms.tex
cleaned abstract and section 1

@@
 The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array. 
-
-%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars. 
-%Red-giant hot Jupiters (RGHJs) are jovian planets orbiting red-giant-branch (RGB) or asymptotic-giant-branch (AGB) stars.
-%Post-main-sequence stars lose mass at much higher rates than main-sequence stars.
-%A jovian planet passing through the dense winds of its RGB or AGB host can capture stellar wind in its magnetosphere, leading to radio emission from electrons spiraling in the magnetic field.
-%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
-%The cyclotron frequency of electrons from the stellar wind accreting onto the planet scales as 100~MHz~$(B/30 {\rm~Gauss})$.
-%Counterintuitively, a plausible toy model suggests that a stronger planetary magnetic field leads to lower spectral flux density, and might therefore make objects more challenging to observe.
-%Still, for a range of planetary and stellar parameters, a RGHJ might generate a radio luminosity that would be visible from kiloparsec distances.
 \end{abstract}
@@
 Planets with strong magnetic fields may generate radio and/or X-ray emission when interacting with energetic charged particles. 
-It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.  % due to the acceleration of the plasmas. \memoYF{?}.
+It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
 Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
@@
 \citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
-%\citet{griesmeier2004} modeled in detail the evolution of atmosphere and magnetic field of the tidally-locked close-in stars and found that 
 \citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
@@
 We find that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
-%In \S5, we discuss the usefulness of radio emission in exploring Jupiter-like planets around evolved stars. 
-Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission for characterizing the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.
+Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission to characterize the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.
 Finally, Section \ref{s:conc} concludes the paper with a brief summary.
-
-%Roughly 20\% of the more than 700 \memoYF{check!} currently known exoplanets around main-sequence stars \footnote{See online catalogs such as http://www.openexoplanetcatalogue.com/ \citep{rein2012}, http://exoplanet.eu \citep{schneider_et_al2011}, or http://exoplanets.org \citep{wright_et_al2011} for up-to-date lists.} have masses greater than half of Jupiter's, orbital radii greater than 1~AU, and will become hot Jupiters (i.e., for the present purposes, this means they will receive at least as much irradiation as the currently known hot Jupiters/Neptunes \citep{spiegel+madhusudhan2012}.
 
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from the accretion disk is negligible in this figure. \memoYF{check} 
+Note that the thermal contribution from the accretion disk is negligible in this figure. 
 The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
@@
 %%%
-\memoYF{Note that in \citet{ignace2010} the dependence on mass-loss rate and stellar wind velocity is not taken account consistently; in that paper, $P_{\rm rad} \propto \dot M_{\star } v^2$.}
 

### 2015-09-22 ms.tex
proofread through the end

@@
 
-The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net-planetary luminosity by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
+The scaling of convected heat flux at the outer boundary, $q_o$, is obtained by dividing the age-dependent net planetary luminosity, $L_p$, by the surface area of the core region, i.e., $4\pi r_{\rm dynamo}^2$.
 The time-dependent luminosity is taken from equation (1) of \citet{burrows_et_al2001} \citep[see also][]{marley2007}. 
@@
 %L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
-L \sim 6.3\times10^{23} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 
+L_p \sim 6.3\times10^{23} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 
 \label{eq:burrowsLum}
@@
 \begin{equation}
-q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_{\rm dynamo}}{r_{\rm dynamo\,J}} \right)^{-2}\, .
+q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_{\rm dynamo}}{r_{\rm dynamo,\,J}} \right)^{-2}\, .
 \label{eq:burrowsHeatFlux}
@@
 
-Substituting Equation~\ref{eq:burrowsHeatFlux} into Equation~\ref{eq:Bscaling2} and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
+Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
 %%%%%%%%%% 
@@
 
-To model the radio emission from the interaction between the planetary magnetic field and the stellar wind,
-we need the density and velocity of the stellar wind. 
+Another ingredient for radio emission is the property of the stellar wind.  
 The number density of particles in the stellar wind, $n$, can be expressed as
@@
 where $\dot M_\star$ is the stellar mass loss rate, $a$ is the orbital distance from the star and $m_p$ is proton mass, and $v_{\rm sw}$ is the velocity of the stellar wind.
-For the solar wind, $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr and $v_{\rm sw} \sim 400 {\rm km/s}$ \citep[e.g.,][]{hundhausen1997}.
+For the solar wind, $\dot M_\odot \sim 2\times 10^{-14} M_{\odot}$/yr and $v_{\rm sw} \sim 400~{\rm km/s}$ \citep[e.g.,][]{hundhausen1997}.
 
@@
 The stellar wind velocity, $v_{\rm sw}$, becomes smaller as the star evolves.
-The wind velocity is typically of order the escape velocity at the distance of the several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star}$.
+The wind velocity is typically of order the escape velocity at a distance of several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star}$.
 For a star with radius $R_{\star }=100~R_{\odot }$, this results in $v_{\rm sw}\sim 30~{\rm km/s}$.
@@
 %%%%%%%%%%
-as a fiducial values for the normalization. 
+as a fiducial value for normalization. 
 %where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
@@
 \begin{eqnarray}
-L_{\rm acc} \sim &&  10^{28} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{10 M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
-%
-T_{\rm acc} \sim && 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
-\sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). \label{eq:Tacc}
+L_{\rm acc} \sim &&  10^{25} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
+&& \times \left( \frac{M_p}{M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
+%
+T_{\rm acc} \sim %&& 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
+%\sim 
+&& 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). \label{eq:Tacc}
 \end{eqnarray}
@@
 whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
+Therefore, UV/X-ray radiation ffom accretion disk will create local ionized region around the planet.
 
@@
 \begin{equation}
-\tau = \int _{R_J}^r n(1-x) \sigma_H dr 
+\tau = \int _{R_J}^r n(1-x) \sigma_H [E_{\rm photon}] dr 
 \end{equation}
@@
 For the accretion onto large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity.
-The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$ (\citep{fite1958}), which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
+The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$ \citep{fite1958}, which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
 As a result, nearly 2/3 of released energetic electrons will ionize a hydrogen atom within $\sim$2$R_J$, and more than 99\% will ionize a hydrogen atom within $\sim$10$R_J$.
@@
 \begin{eqnarray}
-  \nonumber N_i & = & \frac{1 - \xi^\nu}{1 - \xi} \\
+  \nonumber N_i & = & \frac{1 - \xi^k}{1 - \xi} \\
   \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
@@
 %%%%%%%%%
-where $\nu \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
+where $k \equiv E_{\rm in} / E_{\rm Rydberg}$ is the maximum number of ionizations for the given initial electron energy.
 This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
@@
 Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
-
-The extent of ionized region can also be roughly estimated by Stromgren radius of the accretion disk \citep{stromgren1939}: 
-%%%%%%%%%
-\begin{equation}
-r_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
-\end{equation}
-%%%%%%%%%
-which gives
-%%%%%%%%%
-\begin{eqnarray}
-r_{\rm stromgren} \sim  
-  \left\{
-    \begin{array}{ll}
-      67 ~R_J & \;\;\;(M_p = M_J) \\
-      310 ~R_J & \;\;\;(M_p = 10 M_J)
-    \end{array}
-  \right. \label{eq:stromgren}
-\end{eqnarray}
-%%%%%%%%%
-for a planet around a red giants at 5~AU. 
-The Stromgren radius for $1M_J $ and for $10M_J$ are also indicated in Figure \ref{fig:ionizationfraction}.
-Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Stromgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
-The Stromgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
 
@@
 Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $\xi=0.8$.
-The vertical arrows show the Stromgren radius estimated simply  by equation (\ref{eq:stromgren}).
+The vertical arrows show the Str\"omgren radius estimated simply  by equation (\ref{eq:stromgren}).
 The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius}) below.
@@
 
-We therefore expect for the X-ray emission from the accretion disk to ionize the stellar wind.
+The extent of ionized region may also be roughly estimated by Str\"omgren radius of the accretion disk \citep{stromgren1939}: 
+%%%%%%%%%
+\begin{equation}
+r_{\rm stromgren} = \left( \frac{3}{4\pi} \frac{\dot N_X}{n^2 \beta } \right)^{1/3}
+\end{equation}
+%%%%%%%%%
+which gives
+%%%%%%%%%
+\begin{eqnarray}
+r_{\rm stromgren} \sim  
+  \left\{
+    \begin{array}{ll}
+      67 ~R_J & \;\;\;(M_p = M_J) \\
+      310 ~R_J & \;\;\;(M_p = 10 M_J)
+    \end{array}
+  \right. \label{eq:stromgren}
+\end{eqnarray}
+%%%%%%%%%
+for a planet around a red giants at 5~AU. 
+The Str\"omgren radius for $1M_J $ and for $10M_J$ are also indicated in Figure \ref{fig:ionizationfraction}.
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
+The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.
+
+As a whole, we expect for the X-ray emission from the accretion disk to ionize the incoming stellar wind.
 This implies that the stellar wind particles represented by (equation~(\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
@@
 
-Figure \ref{fig:planetaryB_pre} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region, and Figure \ref{fig:planetaryB} displays the estimates of the strength of planetary magnetic field $B$ based on the scaling relation in \S\ref{ss:magneticfield} and the corresponding cyclotron frequency ($\nu_{\rm cyc}$), as functions of planetary mass and the age.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{fig1_linear.pdf}
+%   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
+   \plotoneh{fig2_Christensen.pdf}
+   \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass.
+Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
+  \label{fig:planetaryB}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age.
 %Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
@@
 LOFAR, HERA, SKA, and potential upgrades to the VLA.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{fig1_linear.pdf}
-   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
-  \label{fig:planetaryB_pre}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{fig2_Christensen.pdf}
-   \caption{Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
-  \label{fig:planetaryB}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$.
-This originates from the different scaling laws for the planetary magnetic field and that their formulation didn't incorporate the compression of the planetary magnetosphere due to massive stellar wind.
+This originates from the different scaling laws for the planetary magnetic field and that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind.
 
@@
 The target system is located at a distance of 100~pc from the Earth; the flux is scaled by the distance as a quadratic function. 
-The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.
+%The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.
 
@@
 An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planetary contribution.
-We will see in \S\ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
-Then, we estimate the radio emission of Jupiter-twin around known M giants in \S\ref{ss:actualMgiants}. 
-In \S\ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
+We will see in Section \ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
+Then, we estimate the radio emission of Jupiter-twin around known M giants in Section \ref{ss:actualMgiants}. 
+A general discussion about the luminosity function of planetary radio emission is given in Section \ref{ss:Lfunc}. 
+In Section \ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
 radio instruments at relevant frequencies.
-Finally, \S\ref{ss:timevariability} discusses the polarization and the expected time variability of the radio emission as means to discern the signals from the background noise.
+Finally, Section \ref{ss:timevariability} points out the polarization and the time variability of the radio emission as keys to discern the signals from the background noise.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
-Almost all observations have been carried out 
-%at wavelengths of 6 cm and below, 
-at frequencies $\geq 5~\rm GHz$, 
-probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
-The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.
-
-Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars 
-%at wavelengths above 20 cm 
-at frequencies below 1 GHz ($L$ band); both yielded null results.
-First, a program that observed a sample of nine M-type giants at 430 MHz with the Arecibo Telescope failed to detect any of the sources down to flux density 10 mJy~\citep{Fix1976}.
-Later, with the Molonglo Observatory Synthesis Telescope (MOST), a sample of eight K- and M-type giants were observed at 843 MHz; the upper limits of their flux densities were placed at approximately 1 mJy~\citep{Beasley1992}.
-Current facilities could achieve far deeper sensitivity on similar targets.
-For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a sensitivity better than 0.5~mJy in under an hour.
-However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.
-
-The only red giants that have been detected at meter wavelengths are those in interacting binary systems like those of the RS CVn type.
-For example, van den Oord and de Bruyn detected plasma maser emission from II Pegasi at 360 MHz and 609 MHz with the WSRT~\citep{vandenOord1994}.
-Although single dwarf-type main sequence stars are also known to exhibit bright, coherent radio flares~\citep{Bastian1990}, no analog to this non-thermal emission process has been proposed to exist for evolved stars.
-
-Altogether, we lack firm observational constraints on the brightnesses of M giants near %1-m wavelengths.
-30-300 MHz frequencies.
-
-However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index.
-%In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
-% YF: This is consistent with the following equation, so I removed it to avoid redundancy. 
-%
-For example, \citet{OGorman2013} reported $\alpha$~Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha$~Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
-Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
-%%%
-\begin{eqnarray}
-\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
-&& \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha_* } 
-\end{eqnarray}
-%%%
-where the power index $\alpha_* $ is order of unity.
-
-Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from the accretion disk is negligible in this figure. 
-The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
-The continuum lines from the star in the cases of $\alpha_* =0.8$ and $2.0$ are shown as an extreme case.
-%; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
-As Figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
-For less massive planets (with weaker magnetic fields), the distinction is even clearer, as the peak flux is larger and the peak frequencies are smaller.
-
-Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
 
@@
 
+Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
+Almost all observations have been carried out 
+%at wavelengths of 6 cm and below, 
+at frequencies $\geq 5~\rm GHz$, 
+probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
+The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.
+
+Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars 
+%at wavelengths above 20 cm 
+at frequencies below 1 GHz ($L$ band); both yielded null results.
+First, a program that observed a sample of nine M-type giants at 430 MHz with the Arecibo Telescope failed to detect any of the sources down to flux density 10 mJy~\citep{Fix1976}.
+Later, with the Molonglo Observatory Synthesis Telescope (MOST), a sample of eight K- and M-type giants were observed at 843 MHz; the upper limits of their flux densities were placed at approximately 1 mJy~\citep{Beasley1992}.
+Current facilities could achieve far deeper sensitivity on similar targets.
+For example, as listed in Table~\ref{tab:sens}, the Giant Metrewave Radio Telescope (GMRT) at 150 MHz reaches a sensitivity better than 0.5~mJy in under an hour.
+However, any re-attempts to detect single red giants at wavelengths near 1 meter remain to be presented in the literature.
+
+The only red giants that have been detected at meter wavelengths are those in interacting binary systems like those of the RS CVn type.
+For example, van den Oord and de Bruyn detected plasma maser emission from II Pegasi at 360 MHz and 609 MHz with the WSRT~\citep{vandenOord1994}.
+Although single dwarf-type main sequence stars are also known to exhibit bright, coherent radio flares~\citep{Bastian1990}, no analog to this non-thermal emission process has been proposed to exist for evolved stars.
+
+Altogether, we lack firm observational constraints on the brightnesses of M giants near %1-m wavelengths.
+30-300 MHz frequencies.
+
+However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index.
+%In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
+% YF: This is consistent with the following equation, so I removed it to avoid redundancy. 
+%
+For example, \citet{OGorman2013} reported $\alpha$~Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha$~Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
+Using these data, we extrapolate the radio flux from the host star $F_{\star}$ to the lower frequency range with a simple power law as follows:
+%%%
+\begin{eqnarray}
+\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
+&& \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha_* } 
+\end{eqnarray}
+%%%
+where the power index $\alpha_* $ is order of unity.
+
+Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
+Note that the thermal contribution from the accretion disk is negligible in this figure. 
+The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
+The continuum lines from the star in the cases of $\alpha_* =0.8$ and $2.0$ are shown as an extreme case.
+%; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
+As figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
+For less massive planets (with weaker magnetic fields), the distinction is even clearer, because the peak flux is larger and the peak frequencies are smaller.
+
+Therefore, in the following, we ignore the radio emission from the red giant as a noise source.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
+For each red giant, the mass-loss rate is estimated by the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
+%%%
+\begin{equation}
+%\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
+\end{equation}
+%%%
+where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
+The velocity of the stellar wind is assumed to scale with the escape velocity, hence
+%%%
+\begin{equation}
+v \propto \sqrt{\frac{2GM_\star}{R_{\star }}}
+\end{equation}
+%%%
+The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
+%%%
+\begin{equation}
+t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
+\end{equation}
+%%%
+In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets.\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}
+
+Using these data, we calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
+We consider [A] a Jupiter-twin whose maximum cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 300$~MHz (equations (\ref{eq:scalingB}) and (\ref{eq:fcyc})).
+
+Figure \ref{fig:observability} displays the estimated radio intensity (i.e., cyclotron frequency) of Jupiters [A] and [B] around M-type red giants within 300~pc. 
+Jupiters are placed at 1 AU and at 5 AU for reference. 
+The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$.  
+For a hypothetical Jupiter-mass planet at 5 AU, a reasonable number of systems have potential to emit radio wave at the level of $\sim 10 \mu {\rm Jy}$  out to $\sim 100-150$ pc.
+
+%\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
+%I wondered this because if planets at 1 AU would be engulfed anyway it would not be worth discussing here.
+According to e.g.
+Nordhaus and Spiegel (2013) it is the case--however, some planets may migrate inward within 1 AU after evolution.
+So it should be ok.
+In any case this is not the main point of this paper and I would leave it out.
 
@@
 
-In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
-For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
-For each red giant, the mass-loss rate is estimated by the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
-%%%
-\begin{equation}
-%\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
-\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
-\end{equation}
-%%%
-where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
-The velocity of the stellar wind is assumed to scale with the escape velocity, hence
-%%%
-\begin{equation}
-v \propto \sqrt{\frac{2GM_\star}{R_{\star }}}
-\end{equation}
-%%%
-The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
-%%%
-\begin{equation}
-t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
-\end{equation}
-%%%
-In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets.\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}
-
-Using these data, we can now calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
-We consider [A] a Jupiter-twin whose cyclotron frequency is $\sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\sim 300$~MHz (equations (\ref{eq:scalingB}) and (\ref{eq:fcyc})).
-
-Figure \ref{fig:observability} displays the estimated radio intensity (i.e., cyclotron frequency) of Jupiters [A] and [B] around M-type red giants within 100~pc. 
-Jupiters are placed at 1 AU and at 5 AU for reference. 
-The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross). 
-For a hypothetical Jupiter-mass planet at 5 AU, a reasonable number of systems have potential to emit radio wave at the level of $\sim 10 \mu {\rm Jy}$  out to $\sim 100-150$ pc.
-
-%\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
-%I wondered this because if planets at 1 AU would be engulfed anyway it would not be worth discussing here.
-According to e.g.
-Nordhaus and Spiegel (2013) it is the case--however, some planets may migrate inward within 1 AU after evolution.
-So it should be ok.
-In any case this is not the main point of this paper and I would leave it out.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the largest luminosity in a volume limited sample (volume $V$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
+Under these assumptions, the largest luminosity in a volume limited sample (volume $V$, distance $d$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
 The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$. 
@@
 In order to estimate the true luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
-As discussed in Section~3.2,\memoDS{Replace ``3.2'' with the section label.} for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$.
+As discussed in Section \ref{ss:brightness}, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$.
 Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
@@
 Since the confusion limit is on the same order as the signal (Table \ref{tab:sens}), it is crucial to consider the ways to discriminate the signal from these sources. 
-In this section, we discuss time variability and polarization as keys to identify the auroral radio emission from the planets.
+In this section, we discuss two key features to identify the auroral radio emission from the planets.
 
@@
 
-\paragraph{Variability of stellar wind (a few months $\sim $)?}
+\paragraph{Variability of the stellar wind (a few months $\sim $?)}
 If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variabililty of planetary radio emission.
@@
 \paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
-If the planetary orbit is close to the edge-on configuration, the radio emission disappears synchronously to the orbital period, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
+If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
 The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
-The probability of the latter one, secondary eclipse, is $\sim a/R_\star \sim 9$\% (in the case that $a=5~\mathrm{AU}$ and $R_{\star}=100R_{\odot }$). 
+The probability of the latter one, secondary eclipse, is $\sim R_\star/a \sim 9$\% (in the case that $R_{\star}=100R_{\odot }$ and $a=5~\mathrm{AU}$). 
 %
@@
 Therefore, there are some parameter spaces where current radial velocity observations have not been able to survey.
-For this parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
+For such a parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
 
@@
 In turn, we could utilize the time variability to characterize the system.
-For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could also be detectable.
-Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply presence of satellites.
-
-If the spectra are obtained, the upper cut-off frequency of the radio spectra will imply us the magnetic field strengths of the planetary surface.
+For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could be detectable.
+Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply the presence of satellites.
+
+If the spectra are obtained, the upper cut-off frequency of the radio spectra will indicate the magnetic field strengths of the planetary surface.
 Such information would be most useful if we could obtain constraints on planetary mass via e.g.
-radial velocity observations, because once both magnetic field strength and the planetary mass is constrained, the proposed scaling law of planetary dynamo may be contested.
-On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the density of the stellar wind at the planetary orbit.
+radial velocity observations, because once both magnetic field strength and the planetary mass is constrained the proposed scaling law of planetary dynamo may be tested.
+On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the stellar wind property at the planetary orbit.
 
@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike the previous paper, we consider that X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
-Based on such a picture, the massive stellar wind of a red giant or AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
-We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars.
+Unlike the previous paper, we consider that UV/X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral.
+Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
+We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars, and $>100$ times brighter than distant Jupiter-twins around main-sequence stars.
+This implies that they can be searched for 10 times further away, or in 1000 times larger volume.
+This can compensate the rareness of the evolved stars at least partly.
+Thus, RGHJs will serve as  reasonable targets for future search for exoplanetary radio emission.
 
 A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind.
-Due to great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
-The promising targets are massive planetary ($M_p \gtrsim 5M_J$) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
+Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
+The promising targets are massive planetary ($M_p \gtrsim 5M_J$ \memoYF{what shall we say?}) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 
@@
 
-The radio intensity of the RGHJs are intrinsically $>100$ times brighter than the main-sequence counterparts.
-This indicates that they can be observed 10 times further away, or in 1000 times larger volume.
-This can compensate the rareness of the evolved stars at least partly. Thus, RGHJs will be reasonable targets for future search for radio lighthouse from planetary systems.
-
-Radio emission can be follow-up observations of known RGHJs or may also be used as probe to discover them, given the lowered sensitivity of  radial velocity methods in detecting planetary companions. 
-Once the planetary radio emission is detected, it will provide a unique approach to  planetary spin, magnetic field, and presence of satellite, and potentially stellar wind properties.
-
-%Admittedly, uncertainties exist in the relation between radio emission of Jovian planets and the input energy from stellar wind, as well as in the scaling of planetary magnetic field. 
-%Alternatively, once we detect both the gravitational perturbation and radio emission of Jovian planets, these models will be contested.
-%The viability of these scaling relations will be examined in the future.
-
-%The planetary magnetic moment is computed based on the simple scaling relationship given by \citep{christensen2010}. 
-%-about detectability
-%-number of evolved stars within 100pc $\sim 1000$.
+Radio emission can be follow-up observations of known RGHJs or may also be used as a probe to discover them, given the lowered sensitivity of  radial velocity methods in detecting planetary companions.
+Once the planetary radio emission is detected, it will provide a unique approach to the planetary spin, magnetic field, presence of satellites, and potentially stellar wind properties.
 

### 2015-09-22 ms.tex
changed the order of section 2 so that commonly-used framework comes first and original views come later; let me know if you prefer the previous one

@@
 
-Before estimating the frequency of planetary radio emission and its radio spectral intensity, we specify some ingredients. 
-The property of the planetary magnetic field is described in \S\ref{ss:magneticfield}, and the stellar wind of the evolved stars is discussed in \S\ref{ss:stellarwind}.  
-In \S\ref{ss:ionization}, we consider the ionization around the planets because it is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind. 
-Then, we proceed to the framework to estimate the frequency and intensity of planetary radio emission in \S\ref{ss:model_frequency} and \S\ref{ss:model_intensity}, respectively.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Planetary Magnetic Field}
+In this section, we describe our scheme to estimate radio emission from RGHJs. 
+First, we introduce our framework to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
+Then, two ingredients for the framework--the strength of planetary magnetic field and the property of the stellar wind---will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
+In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Frequency of radio emission}
+\label{ss:model_frequency}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
+The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc,\,max}$: 
+%%%%%%%%%% 
+\begin{equation}
+\nu_{\rm cyc,\,max} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
+\end{equation}
+%%%%%%%%%%
+where $B$ is the strength of magnetic field at the planetary surface, $e$ and $m_e$ are the charge and mass of the electron, respectively, and $c$ is the speed of light.
+
+Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$:
+%%%%%%%%%% 
+\begin{equation}
+\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^\oplus \;\;\; \mbox{and} \;\;\; \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}
+\end{equation}
+%%%%%%%%%%
+The plasma frequency may be expressed as
+\begin{eqnarray}
+\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
+ & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
+\label{eq:fplasma}
+\end{eqnarray}
+In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz. 
+On the other hand, the $\nu_{\rm plasma}^{\rm los}$ depends on the density of stellar wind particles around the planet, which will be specified in Section \ref{ss:stellarwind} below.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Flux of radio emission}
+\label{ss:model_intensity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$, can be expressed by:
+%%%
+\begin{equation}
+F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta \nu}
+\label{eq:Fnu}
+\end{equation}
+%%%
+where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.
+
+We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
+The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
+%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
+%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
+%%%
+\begin{eqnarray}
+P_{\rm radio} &\propto & P_{\rm inp} \\
+P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
+P_{\rm inp,\,m} &=& v B_{\star\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
+\end{eqnarray}
+%%%
+where $n$ is the number density of the stellar wind, $v$ is the relative velocity of the stellar wind particles and the planet, $ B_{\star\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point.
+%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
+It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
+In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.
+
+In the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
+In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
+However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
+
+In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
+
+The radius of the magnetic stand-off point, $r_{\rm mag}$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
+%%%
+\begin{equation}
+m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_{\rm mag}}{R_p} \right)^{-6}  \label{eq:stand-off} ,
+\end{equation}
+%%%
+where $m_p$ is the proton mass. Thus, 
+%%%
+\begin{equation}
+r_{\rm mag} \sim R_p \left( 8\pi m_p n \right) ^{-1/6} v^{-1/3} B^{-1/3} \label{eq:stand-off-radius} 
+\end{equation}
+%%%
+The radius obtained for Jupiter from this equality is about half of the actual magnetospheric radius \citep[][]{griesmeier2005}. 
+To estimate $r_{\rm mag}$ for RGHJs, we scale this radius according to the parameter dependence of equation~(\ref{eq:stand-off-radius}).
+
+We assume that the solid angle of the emission, $\Omega $, is same as the Jupiter's one for all of the exoplanets.
+In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
+The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following \citet{griesmeier2007b}.
+
+%We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Assumptions for planetary magnetic field}
 \label{ss:magneticfield}
@@
 
-We estimate the planetary magnetic field of general planets  
-simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
+In order to obtain the frequency and the intensity of the radio emission, we need to compute the strength of the magnetic field at the planetary surface, $B$. 
+We do so simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below. 
 % we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Stellar Wind}
+\subsection{Assumptions for stellar wind}
 \label{ss:stellarwind}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Ionization around the planet}
+\subsection{Ionization of stellar wind particles around the planet}
 \label{ss:ionization}
@@
 
-The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
-%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
-When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
-%%%%%%%%%
-\begin{eqnarray}
-x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
-C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
-%%%%%%%%%
-The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$.
-In the figure, the vertical lines show the magnetic stand-off points obtained by equation (\ref{eq:stand-off-radius}) below.
-While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region. 
-Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The vertical arrows show the Str\"omgren radius estimated simply  by equation (\ref{eq:stromgren}).
-The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius}) below.
+The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$,  obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
 }
@@
 
+The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
+%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
+When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
+%%%%%%%%%
+\begin{eqnarray}
+x[r] &=& \frac{-1 + \sqrt{1+4C[r]}}{2C[r]} \\
+C[r] &\equiv &   \frac{4 \pi n \beta [T_e] r^2}{\dot{N} \sigma_H[E_{\rm photon}]}  \end{eqnarray}
+%%%%%%%%%
+The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$.
+In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
+While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region. 
+Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
+
 The extent of ionized region may also be roughly estimated by Str\"omgren radius of the accretion disk \citep{stromgren1939}: 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Frequency of Radio Emission}
-\label{ss:model_frequency}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Planetary auroral radio wave are emitted at the local cyclotron frequency along the motion of the plasmas.
-The upper limit is around the cyclotron frequency of the planetary surface magnetic field, $\nu_{\rm cyc}$: 
-%%%%%%%%%% 
-\begin{equation}
-\nu_{\rm cyc} = \frac{eB}{2\pi m_e c} \approx 28 {\rm~MHz} \left( \frac{B}{10 \rm~G} \right) \label{eq:fcyc}
-\end{equation}
-%%%%%%%%%%
-where $e$ and $m_e$ are the charge and mass of the electron, respectively.
-
-Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$.
-The plasma frequency may be expressed as
-\begin{eqnarray}
-\nu_{\rm plasma} & = & \sqrt{\frac{n_e e^2}{\pi m_e}} \\
- & = & 8979 {\rm~Hz} \times \left( \frac{n_e}{\rm cm^{-3}} \right)^{1/2} \, .
-\label{eq:fplasma}
-\end{eqnarray}
-In the Earth's ionosphere, the electron number density is less than $10^6$~cm$^{-3}$, which implies that $\nu_{\rm plasma}^\oplus \lsim 10$~MHz.
-At the favorable viewing condition, when the planet is on the near side of its star to the Earth, the maximum plasma frequency along the line of sight corresponds to that in the vicinity of the planet.
-Therefore, combining Eq.~(\ref{eq:n_normalized}) and Eq.~(\ref{eq:fplasma}), we have
-%%%
-\begin{eqnarray}
-\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 
-8979 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
-\label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
- & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
-\end{eqnarray}
-%%%
-%where in Eq.~(\ref{eq:fplasmalos_scaled}) we have taken the solar mass-loss rate $\dot M_\odot$ to be $2.0 \times 10^{-14}~M_\odot$/yr and the typical solar wind velocity $v_{\odot }$ to be 400~km/sec.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Flux of Radio Emission}
-\label{ss:model_intensity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The auroral radio spectral flux of exoplanets observed at the Earth, $F_{\nu}$, can be expressed by:
-%%%
-\begin{equation}
-F_{\nu} = \frac{P_{\rm radio}}{\Omega l^2 \Delta \nu}
-\label{eq:Fnu}
-\end{equation}
-%%%
-where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.
-
-We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
-The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
-%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
-%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
-%%%
-\begin{eqnarray}
-P_{\rm radio} &\propto & P_{\rm inp} \\
-P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
-P_{\rm inp,\,m} &=& v B_{\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
-\end{eqnarray}
-%%%
-where $ B_{\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point. 
-%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
-It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
-In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.
-
-In the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
-In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
-However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
-
-In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
-Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
-
-The radius of the magnetic stand-off point, $r_{\rm mag}$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
-%%%
-\begin{equation}
-m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_{\rm mag}}{R_p} \right)^{-6}  \label{eq:stand-off}
-\end{equation}
-%%%
-The radius obtained for Jupiter from this equality is about half of the actual magnetospheric radius \citep[][]{griesmeier2005}. 
-By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
-%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
-%We estimate $r_{\rm mag}$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
-%%%
-\begin{eqnarray}
-\nonumber r_{\rm mag} 
-%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
-&=& r_{mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
-&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \\
-\nonumber &=& 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
-&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{v}{10^{-1}v_{\odot }} \right)^{-1/6}
- \label{eq:stand-off-radius}
-\end{eqnarray}
-%%%
-
-%Thus, the radio emission, $P_{\rm radio}$, or equivalently the input kinetic energy, $P_{\rm k,\,inp}$, are estimated with $n$, $v$, and $\mathcal{M}$, which should be specified by assuming the properties of the stellar wind and the planetary magnetic field.
-%In the following, we describe our assumptions for these properties.
-
-We assume that the solid angle of the emission, $\Omega $, is same as the Jupiter's one for all of the exoplanets.
-In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
-The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following \citet{griesmeier2007b}.
-
-%We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimate of Planetary Magnetic Field and Maximum Frequency}
+\subsection{Planetary magnetic field and frequency of radio emission}
 \label{ss:Bplanet}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{fig1_linear.pdf}
+\begin{figure}[bhtp]
+   \plotoneh{rho_r_dynamo.pdf}
 %   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
-   \plotoneh{fig2_Christensen.pdf}
+   \plotoneh{qBf_Christensen.pdf}
    \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass.
@@
 Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness. 
-
 %%%%%%%%%% 
@@
 %under this model. 
-Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz ($\sim $ the plasma cut-off frequency of Earth's ionosphere) and 1~GHz. 
+Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz and 1~GHz. 
 In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Estimate of Radio Intensity of RGHJs in comparison with canonical HJs}
+Since $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^\oplus $, the radio emission will not be hindered by Earth's ionosphere cut-off. 
+One the other hand, it may be interfered by the plasma cut-off of the stellar wind particles around the planet. 
+The maximum plasma frequency along the line of sight, $\nu_{\rm plasma}^{\rm los}$, corresponds to that in the vicinity of the planet, if the planet is on the near side of its star to the Earth.
+Therefore, substituting equation~(\ref{eq:n_normalized}) to $n_e$ in equation~(\ref{eq:fplasma}),
+%%%
+\begin{eqnarray}
+\label{eq:fplasmalos} \nu_{\rm plasma}^{\rm los} & \sim & 
+8979 {\rm~kHz} \times \left( \frac{\dot M_\star}{4 \pi a^2 m_p v} \times 1\rm~cm^3 \right)^{1/2} \\
+\label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
+ & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
+\end{eqnarray}
+We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$.
+Therefore, for Jupiter-mass planets, only distant ones at $\sim 5 $ AU or further, will emit the radio waves from the system.
+The detectable parameter space will be presented in more detail in the next section.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Flux of RGHJ radio emission in comparison with canonical HJs}
 \label{ss:brightness}
@@
 
-Based on the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[bp]
+%   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
+%   \plotonesc{radio_emission_Mdot1e-5_constRp_christesnsen.pdf}
+	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
+   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
+The systems are located at 100 pc away.
+The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
+The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
+}
+  \label{fig:radio}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The magnetic stand-off radius (equation (\ref{eq:stand-off-radius})) may be written as follows using the stellar mass-loss rate: 
+%%%
+\begin{eqnarray}
+\nonumber r_{\rm mag} 
+%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
+&=& r_{\rm mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
+&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{v}{v_{\odot }} \right)^{-1/6} \label{eq:stand-off-radius2}
+\end{eqnarray}
+%%%
+The typical value for RGHJs is found by substituting relevant values for stellar wind parameters described in Section \ref{ss:stellarwind}:
+%%%
+\begin{eqnarray}
+\nonumber r_{\rm mag} &\sim & 15 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
+&& \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right)^{-1/6}  \left( \frac{v}{10^{-1}v_{\odot }} \right)^{-1/6}
+ \label{eq:stand-off-radius_RGHJ}
+\end{eqnarray}
+%%%
+
+Substituting equation (\ref{eq:stand-off-radius2}) to equation (\ref{eq:Pinp_kin}), the scaling of the radio emission is expanded as follows:
 %%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bp]
-%   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
-%   \plotonesc{radio_emission_Mdot1e-5_constRp_christesnsen.pdf}
-	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
-   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
-The systems are located at 100 pc away.
-The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
-The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
-}
-  \label{fig:radio}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Combining the expressions above, we find that the radio spectral flux density observed at the Earth is:
@@
 Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
-We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
-%%%
-\begin{equation}
-\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
-\end{equation} 
-%%%
-The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where this criteria is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
+%We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
+%%%
+%\begin{equation}
+%\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
+%\end{equation} 
+%%%
+The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
 In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.
 Instead, it usually exits at lower frequencies.
-Here, we also consider a more conservative criteria, $0.1 f_{\rm cyc} > f_{\rm plasma}^{\rm los}$ as a measure for the observability of the bulk of radio emission.
-In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
+Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission.
+In figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Radio Flux from Nearby M giants}
+\subsection{Radio flux from nearby M giants}
 \label{ss:actualMgiants}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Detectability with Current and Near Future Low Frequency Radio Instrumentation}
+\subsection{Detectability with current and near future low frequency radio instrumentation}
 \label{ss:detectability}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Discriminating the Signal from the Background}
+\subsection{Discriminating the signal from the background}
 \label{ss:timevariability}

### 2015-09-23 ms.tex
Add a few hyphens

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Detectability with current and near future low frequency radio instrumentation}
+\subsection{Detectability with current and near-future low-frequency radio instrumentation}
 \label{ss:detectability}
@@
 
-We consider in this section several current and near future radio observatories that operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum sensitivities less than 1~mJy in a few hours.
+We consider in this section several current and near-future radio observatories that operate at frequencies $\nu \lesssim 350~\rm MHz$ and can reach continuum sensitivities less than 1~mJy in a few hours.
 The results are summarized in Table~\ref{tab:sens}.

### 2015-09-23 ms.tex
minor updates (font, lacking unit)

@@
 In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need models of the internal planetary structure. 
-We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,J}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) converge to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ within 1 Gyr \citep{fortney2007}.
+We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,{\rm J}}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p,{\rm J}} < M_p < 10M_{p, {\rm J}}$ (with core mass less than 10\%) converge to $0.8 R_{p,{\rm J}} < R_p < 1.2R_{p, {\rm J}}$ within 1 Gyr \citep{fortney2007}.
 For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
@@
 \begin{equation}
-%L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
-L_p \sim 6.3\times10^{23} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 
+%L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, 	
+L_p \sim 6.3\times10^{23} \; {\rm erg} \; \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, 
 \label{eq:burrowsLum}
@@
 \begin{equation}
-q_o \sim q_{o, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_{\rm dynamo}}{r_{\rm dynamo,\,J}} \right)^{-2}\, .
+q_o \sim q_{o, {\rm J}} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \left( \frac{r_{\rm dynamo}}{r_{\rm dynamo,\,J}} \right)^{-2}\, .
 \label{eq:burrowsHeatFlux}
@@
 %B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
+B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,{\rm J}}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
 \end{equation}
@@
 Is it at the magnetic standoff point, or at the planetary surface, or somewhere in between?
-At the planet's surface, the infall velocity is 150 km/s for a 10$M_J$ planet, no?}
+At the planet's surface, the infall velocity is 150 km/s for a 10$M_{\rm J}$ planet, no?}
 Here, we simply consider
@@
 L_{\rm acc} \sim &&  10^{25} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{M_J} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
-%
-T_{\rm acc} \sim %&& 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_J} \right) \\
+&& \times \left( \frac{M_p}{M_{\rm J}} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
+%
+T_{\rm acc} \sim %&& 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_{\rm J}} \right) \\
 %\sim 
-&& 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_J} \right). \label{eq:Tacc}
+&& 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_{\rm J}} \right). \label{eq:Tacc}
 \end{eqnarray}
@@
 \begin{equation}
-\tau = \int _{R_J}^r n(1-x) \sigma_H [E_{\rm photon}] dr 
+\tau = \int _{R_{\rm J}}^r n(1-x) \sigma_H [E_{\rm photon}] dr 
 \end{equation}
@@
     \begin{array}{ll}
-      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
-      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
+      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_{\rm J}) \\
+      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_{\rm J})
     \end{array}. 
@@
 %%%%%%%%%
-For a $10 M_J$ planet, $N_i$ is probably approximately in the range 5---10.
+For a $10 M_{\rm J}$ planet, $N_i$ is probably approximately in the range 5---10.
 
@@
 %\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
-When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_J$),  the solution is simply
+When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
 %%%%%%%%%
@@
     \begin{array}{ll}
-      67 ~R_J & \;\;\;(M_p = M_J) \\
-      310 ~R_J & \;\;\;(M_p = 10 M_J)
+      67 ~R_J & \;\;\;(M_p = M_{\rm J}) \\
+      310 ~R_J & \;\;\;(M_p = 10 M_{\rm J})
     \end{array}
@@
 for a planet around a red giants at 5~AU. 
-The Str\"omgren radius for $1M_J $ and for $10M_J$ are also indicated in Figure \ref{fig:ionizationfraction}.
+The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
 Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
@@
 \\
-&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
+&=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:Pkinp}
@@
 %&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
-&\approx &  140 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx &  140 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}{\rm /yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
@@
 %&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
-&\approx & 14000 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 14000 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}{\rm /yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
@@
 %&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
@@
 %& $M_p$ & B & $a$ &  \\ \hline
-%canonical HJ & $M_J$ & $B_J$ & 0.05 AU & 4 days \\
-%RGHJ & $M_J$ & $B_J$ & 5 AU &  0.4 days \\ \hline
+%canonical HJ & $M_{\rm J}$ & $B_J$ & 0.05 AU & 4 days \\
+%RGHJ & $M_{\rm J}$ & $B_J$ & 5 AU &  0.4 days \\ \hline
 %\end{tabular}
@@
 &\approx & 5.2\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{B}{B_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
@@
 &\approx & 0.70 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
@@
 &\approx & 0.70 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}/{\rm yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
@@
 &\approx & 2.4 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
+&&\times \left( \frac{B}{B_{\rm J}} \right)^{-1/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\ 
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
@@
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
-For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_J$. 
+For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_{\rm J}$. 
 On the other hand, for a AGB-star system, only massive planets at distant orbits are marginally detectable.
@@
    \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
-   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_J$ and the host red giants with 100 $R_{\odot }$.
+   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
 The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
@@
 
-Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_J$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
+Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_{\rm J}$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
 Note that the thermal contribution from the accretion disk is negligible in this figure. 
@@
 %   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
-   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_J$ and 10$M_J$ at 1 AU and 5AU.
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ and 10$M_{\rm J}$ at 1~AU and 5~AU.
 Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }
@@
 The low frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
-We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_J$) separately from the full band, which could be used to detect $\sim 30 M_J$ hot Jupiters.
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim 30 M_{\rm J}$ hot Jupiters.
 We again adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ (Equation~\ref{eq:Tsky}), and assume $\Trx \approx 60~\rm K$.
@@
 The noise estimates shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
-On the other hand, for more massive exoplanets ($M_p\sim 10 M_J$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
-LOFAR-HBA has reasonable sensitivity to $M_p =10~M_J$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
-More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_J$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
+LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
+More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.
 
@@
 Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
-The promising targets are massive planetary ($M_p \gtrsim 5M_J$ \memoYF{what shall we say?}) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
+The promising targets are massive planetary ($M_p \gtrsim 5M_{\rm J}$ \memoYF{what shall we say?}) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 
@@
 \begin{eqnarray}
-\mbox{[\#1]} \; P_{\rm rad} &\sim & 4 \times 10^9 \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{0.58} \left( \frac{M_p}{M_J} \right)^{0.98} \left( \frac{a}{a_J} \right)^{-1.17} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.586} \left( \frac{v}{v_{\odot}} \right)^{1.46} \\
-%
-\mbox{[\#2]} \; P_{\rm rad} &\sim & 4 \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{0.79} \left( \frac{M_p}{M_J} \right)^{1.33} \left( \frac{a}{a_J} \right)^{-1.60} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.8} \left( \frac{v}{v_{\odot}} \right)^{2.0} \\
+\mbox{[\#1]} \; P_{\rm rad} &\sim & 4 \times 10^9 \,{\rm W}\,\left( \frac{\omega}{\omega _{\rm J}} \right)^{0.58} \left( \frac{M_p}{M_{\rm J}} \right)^{0.98} \left( \frac{a}{a_{\rm J}} \right)^{-1.17} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.586} \left( \frac{v}{v_{\odot}} \right)^{1.46} \\
+%
+\mbox{[\#2]} \; P_{\rm rad} &\sim & 4 \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _{\rm J}} \right)^{0.79} \left( \frac{M_p}{M_{\rm J}} \right)^{1.33} \left( \frac{a}{a_{\rm J}} \right)^{-1.60} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{0.8} \left( \frac{v}{v_{\odot}} \right)^{2.0} \\
 %
 \mbox{[\#3]} \; P_{\rm rad} &\sim & ?
-\times 10^{11} \,{\rm W}\,\left( \frac{M_p}{M_J} \right)^{2/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-%
-\mbox{[\#4]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
-%
-\mbox{[\#5]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
-%
-\mbox{[\#6]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{1/2} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
-%
-\mbox{[\#7]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _J} \right)^{2/3} \left( \frac{M_p}{M_J} \right)^{1/3} \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+\times 10^{11} \,{\rm W}\,\left( \frac{M_p}{M_{\rm J}} \right)^{2/3} \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+%
+\mbox{[\#4]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _{\rm J}} \right)^{2/3} \left( \frac{M_p}{M_{\rm J}} \right)^{1/3} \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#5]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _{\rm J}} \right)^{1/3} \left( \frac{M_p}{M_{\rm J}} \right)^{1/3} \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#6]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _{\rm J}} \right)^{1/2} \left( \frac{M_p}{M_{\rm J}} \right)^{1/3} \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+%
+\mbox{[\#7]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\,\left( \frac{\omega}{\omega _{\rm J}} \right)^{2/3} \left( \frac{M_p}{M_{\rm J}} \right)^{1/3} \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
 %
 \mbox{[\#8]} \; P_{\rm rad} &\sim & ?
-\times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_J} \right)^{0.69}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.288}  \left( \frac{a}{a_J} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+\times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_{\rm J}} \right)^{0.69}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.288}  \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
 \end{eqnarray}
@@
 \begin{equation}
-L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \tag{\ref{eq:burrowsLum}}
+L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \tag{\ref{eq:burrowsLum}}
 \end{equation} 
@@
 \begin{equation}
-P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{\alpha } \left( \frac{M_p}{M_J} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_J} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
+P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _{\rm J}} \right)^{\alpha } \left( \frac{M_p}{M_{\rm J}} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_{\rm J}} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
 \end{equation} 
@@
 \begin{equation}
-\frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_J} \right)^{2.64} \, .
+\frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_{\rm J}} \right)^{2.64} \, .
 \label{eq:burrowsLum_2}
@@
 %\begin{eqnarray}
-%\nonumber \tau_{\rm conv} & \sim & 3 {\rm~days} \times \left( \frac{M}{M_J} \right)^{1/3} \left( \frac{R}{R_J} \right)^{2/3} \left( \frac{L}{L_\odot} \right)^{-1/3} \\
+%\nonumber \tau_{\rm conv} & \sim & 3 {\rm~days} \times \left( \frac{M}{M_{\rm J}} \right)^{1/3} \left( \frac{R}{R_J} \right)^{2/3} \left( \frac{L}{L_\odot} \right)^{-1/3} \\
 % & = & 
@@
 \nonumber \tau_c & \sim & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{L}{10^{-9} L_\odot} \right)^{1/3}} \\
- & = & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}} \\
+ & = & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_{\rm J}} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}} \\
 \end{eqnarray}
@@
 Ro & = & \frac{\tau_c}{P_{\rm rot}} \\
- & = & \left( \frac{P_{\rm rot}}{3 \rm~hrs} \right)^{-1} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_J} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}}
+ & = & \left( \frac{P_{\rm rot}}{3 \rm~hrs} \right)^{-1} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_{\rm J}} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}}
 \end{eqnarray}
@@
 d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
-  & \sim & 4 R_J \left( \frac{d_0}{R_J}\right) \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
+  & \sim & 4 R_J \left( \frac{d_0}{R_{\rm J}}\right) \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
 \label{eq:Chapman-Ferraro}
@@
  & = & \frac{d_0^2}{8} \left( \frac{\dot{M}_*^2 v^5 B_0^2}{r^4} \right)^{1/3} \\
-\nonumber  & \sim & 2 \times 10^{18} {\rm~W} \left( \frac{d_0}{R_J} \right)^2 \left( \frac{\dot{M}_*}{10^{-5} M_\odot / {\rm yr}} \right)^2 \\
+\nonumber  & \sim & 2 \times 10^{18} {\rm~W} \left( \frac{d_0}{R_{\rm J}} \right)^2 \left( \frac{\dot{M}_*}{10^{-5} M_\odot / {\rm yr}} \right)^2 \\
  & & \times \left( \frac{v}{20 \rm~km/s} \right)^5 \left( \frac{B_0}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^{-4}
@@
 In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
-First, we assume that the planetary radius is constant at $R_p = R_{p,J}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p, J} < M_p < 10M_{p, J}$ (with core mass less than 10\%) are converged to $0.8 R_{p, J} < R_p < 1.2R_{p, J}$ in 1 Gyr \citep{fortney2007}.
+First, we assume that the planetary radius is constant at $R_p = R_{p,\,{\rm J}}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p,\,{\rm J}} < M_p < 10M_{p,\,{\rm J}}$ (with core mass less than 10\%) are converged to $0.8 R_{p,\,{\rm J}} < R_p < 1.2R_{p, \,{\rm J}}$ in 1 Gyr \citep{fortney2007}.
 For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
@@
 \begin{eqnarray}
- \left( \frac{M_p}{M_{p,J}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
+ \left( \frac{M_p}{M_{p,\,{\rm J}}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
  && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}

### 2015-09-23 ms.tex
some thoughts on luminosity function

@@
    \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
-Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $\xi=0.8$.
+Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $N_i=6$.
 The vertical arrows show the Str\"omgren radius estimated simply  by equation (\ref{eq:stromgren}).
@@
 %%%%%%%%%
-The solid lines show the ionization fraction of $\xi=0$ (no additional ionization by electrons) and dashed lines show that of $\xi=0.5$.
+The solid lines show the ionization fraction of $\xi=0 \; (N_i = 1)$ (no additional ionization by electrons) and dashed lines show that of $N_i=6$.
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
@@
 Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission.
-In figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
+In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines.
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
@@
 %; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
-As figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
+As Figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
 For less massive planets (with weaker magnetic fields), the distinction is even clearer, because the peak flux is larger and the peak frequencies are smaller.
@@
 Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
+Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}. Therefore, $\alpha_L \sim -2.7$.
+
 Thus, the criterion $\alpha_L < 3/2$ is satisfied if the slope of the luminosity function of the host stars is shallower than $-1$.
+
+\memoYF{stirring up...}
+
+The number of targets within the shell at radius $r \sim r+\Delta r$, $dN(r)/dr $, is
+%%%
+\begin{eqnarray}
+\frac{dN(r)}{dr} &=& 4 \pi r^2 \int _{L_{\rm min}}^{\infty} \frac{dn(L)}{dL} dL \\
+L_{\rm min} &\propto & r^2 F_{\rm min} 
+\end{eqnarray}
+%%%
+where $F_{\rm min}$ is the detection limit ($=constant$). 
+Assuming $dn(L)/dL \propto L^{-\alpha_L }$, 
+%%%
+\begin{eqnarray}
+\frac{dN(r)}{dr} &\propto & r^2 \left( \frac{L_{\rm min}^{-\alpha_L + 1}}{\alpha_L - 1}  \right)\\
+&\sim & r^2 \left( \frac{r^{2(-\alpha_L + 1)}}{\alpha_L - 1} \right) \\
+&\propto & \frac{r^{-2\alpha_L + 4}}{\alpha_L - 1}
+\end{eqnarray}
+%%%
+($N(r)$ is the number of candidates within volume $V(r) =4\pi r^3/3$.)
+When $\alpha _L=2.7$, 
+\begin{equation}
+\frac{dN(r)}{dr} \propto r^{-1.4}
+\end{equation}
+%Now, using the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996} and $L \sim L_{\star}^{2/3}$, $\alpha_L \sim -2.7$.
+Thus, the number of candidates within volume $V(r)$ increases as $r^{-0.4}$.
+%%%
 

### 2015-09-23 ms.tex
small edits

@@
 It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
-For a red-giant system, the most promising target is massive companions with $M_p \gtrsim 5M_{\rm J}$. 
-On the other hand, for a AGB-star system, only massive planets at distant orbits are marginally detectable.
+For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
+% $M_p \gtrsim 4M_{\rm J}$ is well observable at 5 AU. 
+On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.
 
@@
 Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
-The promising targets are massive planetary ($M_p \gtrsim 5M_{\rm J}$ \memoYF{what shall we say?}) companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
+The most promising targets are massive planetary ($M_p \gtrsim 4 M_{\rm J}$ companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 

### 2015-09-25 ms.tex
note
page break allowed
removed spelling error and disk
Removed accretion disk references and other edits

@@
 %\usepackage[dvipdfmx]{graphicx}
+\allowdisplaybreaks[1]
 
@@
 \def\memoNZ#1{\color{green}$[${\bf #1}$]$ \color{black}}
+
+\def\memoJN#1{\color{purple}$[${\bf #1}$]$ \color{black}}
 
@@
 %
-Mehrdad Mirbabayi\altaffilmark{13}
+Mehrdad Mirbabayi\altaffilmark{12}
 }
@@
 
+\affil{$^{12}$ \memoJN{Need Mehrdad's affiliation here.}}
 \vspace{0.5\baselineskip}
@@
 whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
-Therefore, UV/X-ray radiation ffom accretion disk will create local ionized region around the planet.
+Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
 
@@
    \plotoneh{ionizationfraction.pdf}
-   \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
+   \caption{Profile of ionization fraction due to X-ray from planetary accretion, measured from the surface of the planet.
 Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $N_i=6$.
@@
 
-The extent of ionized region may also be roughly estimated by Str\"omgren radius of the accretion disk \citep{stromgren1939}: 
+The extent of ionized region may also be roughly estimated by Str\"omgren radius \citep{stromgren1939}: 
 %%%%%%%%%
@@
 
-As a whole, we expect for the X-ray emission from the accretion disk to ionize the incoming stellar wind.
+As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
 This implies that the stellar wind particles represented by (equation~(\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_{\rm J}$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from the accretion disk is negligible in this figure. 
+Note that the thermal contribution from the accretion is negligible in this figure. 
 The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
@@
 Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
-Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}. Therefore, $\alpha_L \sim -2.7$.
+Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}.
+Therefore, $\alpha_L \sim -2.7$.
 
@@
 
-\memoYF{stirring up...}
+\memoYF{this is note. this part will be removed later}
 
@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike the previous paper, we consider that UV/X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral.
+Unlike the previous paper, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 

### 2015-09-26 ms.tex
Adds Mehrdad's affiliation
Updated sensitivity values in telescope table.  Changed sensitivity to do inverse-variance weighting (makes ~20% difference for some telescopes).  Changed HERA telescope parameters to match reality.

@@
 We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
-We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and 100 times brighter than equivalent objects around main-sequence stars, which allow us to search them in 1000 times larger volume.
+We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and 100 times brighter than equivalent objects around main-sequence stars, which allow us to search them in a 1000 times larger volume.
 The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array. 
@@
 \startdata
-LOFAR-LBA  &  30-80  & 700   & 120000             & 8.3  & 42 \\ 
-LOFAR-HBA  & 110-200 &  35   &    310             & 3.3  & 1.1 \\  
-HERA       &  30-80  & 870   & 160000             & 1030 & 4.2$\times10^5$\\ 
-GMRT       & 130-190 & 430   &  46000             & 16.5 & 56.9 \\ 
-%LWA       &  30-80  & 58000 &  702127141         & 10.3 & 42.2 \\
-%MWA       &  30-80  & 29000 &  176223211         & 1030 & 4.2$\times10^5$ \\
-SKA-Low (part) & 50-200 & 7.8 &  12.6             & 7.6  & 9.7 \\
-SKA-Low (full) & 50-350 & 2.2 &  1.0              & 4.8  & 1.5 \\
+LOFAR-LBA  &  30-80  & 1100  & 230000             & 10   & 57 \\ 
+LOFAR-HBA  & 110-200 & 180   &   6500             & 4.1  & 1.1 \\  
+HERA       & 50-250  &  76   & 1200               & 410  & 36000\\ 
+GMRT       & 130-190 & 162   &   5400             & 16.5 & 57 \\ 
+%LWA       &  30-80  & 50000 &  702127141         & 10.3 & 42.2 \\
+%MWA       &  30-80  & 24000 &  176223211         & 1030 & 4.2$\times10^5$ \\
+SKA-Low (part) & 50-200 & 5.9 &   7.2             & 7.6  & 9.7 \\
+SKA-Low (full) & 50-350 & 1.8 &  0.7              & 4.8  & 1.5 \\
 %VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
-VLA-LOBO   &  50-350 &  92   &  1800              & 8.6  & 10.4
+VLA-LOBO   &  50-350 &  77   &  1200              & 8.6  & 10.4
 \enddata

### 2015-09-26 code/sensitivity.py

@@ -1,11 +1,23 @@
 #! /usr/bin/env python
-import numpy as np
+import numpy as np, pylab as plt
 
 k_b = 1.380658e-16
 
 def Tsky(nu):
-    return 237 * (nu/.150)**-2.5
+    Tcmb = 2.73
+    return 283.2 * (nu / 150e6)**(-2.47) + Tcmb
 
-def sense(d, N, nu, B=100e6, t=3600):
-    return 2 * 1.22**2 * np.pi / (4 *np.log(2)) *  k_b * Tsky(nu) / (N * d**2 * np.sqrt(B*t) * 1e-23)
-#    return 2 * k_b * Tsky(nu) / (N * d**2 * np.sqrt(B*t) * 1e-23)
+def sense(nu, N=352, B=100e6, t=3600, diam=14., Trx=260):
+    A_eff = 0.7 * np.pi * (diam/2.)**2
+    uJy_scalar = 2 * 1.22**2 * np.pi / (4 *np.log(2)) *  k_b / A_eff * 1e6 # uJy
+    Tsys = Tsky(nu) + Trx
+    nbls = N * (N-1) / 2
+    return uJy_scalar * Tsys / np.sqrt(2 * B * t * nbls)
+
+dnu = 1.
+nu = np.arange(50.,250,dnu)
+noise_uJy = sense(nu,B=dnu)
+wgt = 1./ noise_uJy**2
+print np.sqrt(np.sum((noise_uJy*wgt)**2)) / wgt.sum()
+plt.plot(nu, sense(nu, B=dnu))
+plt.show()

### 2015-09-26 ms.tex
Added HERA paragraph & acknowledgments for AP.

@@
 %
-Mehrdad Mirbabayi\altaffilmark{12}
+Mehrdad Mirbabayi\altaffilmark{4}
 }
@@
 \affil{$^{11}$Astronomy Department, University of Cambridge, UK}
-
-\affil{$^{12}$ \memoJN{Need Mehrdad's affiliation here.}}
 \vspace{0.5\baselineskip}
@@
 
-An additional contribution to the noise is due to source confusion, the imaging noise associated with unresolved interloping radio sources in an observation.
+An additional factor that affects detectability is source confusion, the imaging noise associated with unresolved interloping radio sources in an observation.
 Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
@@
 %%%
+As Table~\ref{tab:sens} illustrates, source confusion is likely to exceed the 2 $\mu$Jy detection limit of a typical hot Jupiter source for most
+telescopes under consideration.  However, source confusion can be mitigated through differencing observations that cancel out background sources.
+Potential axes for such cancellation are polarization and time.
 The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time.
@@
 % HERA
-The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) \ldots \memoYF{write here (Aaron?)}
+The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) is a telescope array under construction
+in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
+Unlike other the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
+of cosmic reionization over wide fields of view.  Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization
+(PAPER; \citealt{parsons_et_al2010}), HERA's dishes are deployed in an extremely compact configuration \citep{parsons_et_al2012} and 
+statically point toward zenith.  While these features make HERA less ideal for targeted observations, HERA's substantial collecting area,
+long observing campaigns, and wide field of view make it a powerful survey instrument.
 
@@
 NM acknowledges support from [???]. 
+AP is grateful for support from NSF grants 1352519 and 1440343.
 YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 

### 2015-09-26 ms.tex
Fixed units of sigma-rms in sensitivity table.

@@
 Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
-           & (MHz) & ($\mu$Jy~hr$^{1/2}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
+           & (MHz) & ($\mu$Jy bm$^{-1}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
 \startdata

### 2015-09-26 ms.tex
minor thing

--- 2015-09-26 ms.tex
@@
 \def\memoNZ#1{\color{green}$[${\bf #1}$]$ \color{black}}
-
-\def\memoJN#1{\color{purple}$[${\bf #1}$]$ \color{black}}
 
@@
 %
-Mehrdad Mirbabayi\altaffilmark{12}
+Mehrdad Mirbabayi\altaffilmark{13}
 }
@@
 
-\affil{$^{12}$ \memoJN{Need Mehrdad's affiliation here.}}
 \vspace{0.5\baselineskip}
@@
 We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
-We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and 100 times brighter than equivalent objects around main-sequence stars, which allow us to search them in a 1000 times larger volume.
+We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.
+%, which allow us to search them in 1000 times larger volume.
 The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array. 
@@
 whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
-Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
+Therefore, UV/X-ray radiation ffom accretion disk will create local ionized region around the planet.
 
@@
    \plotoneh{ionizationfraction.pdf}
-   \caption{Profile of ionization fraction due to X-ray from planetary accretion, measured from the surface of the planet.
+   \caption{Profile of ionization fraction due to X-ray from the planetary accretion disk, measured from the surface of the planet.
 Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $N_i=6$.
@@
 
-The extent of ionized region may also be roughly estimated by Str\"omgren radius \citep{stromgren1939}: 
+The extent of ionized region may also be roughly estimated by Str\"omgren radius of the accretion disk \citep{stromgren1939}: 
 %%%%%%%%%
@@
 
-As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
+As a whole, we expect for the X-ray emission from the accretion disk to ionize the incoming stellar wind.
 This implies that the stellar wind particles represented by (equation~(\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
@@
 Figure \ref{fig:cartoon} is a cartoon for a radio spectrum of a planet with $10~M_{\rm J}$ and that of the host red giant star with 100~$R_{\odot }$, both of which are placed at a distance of 100 pc. 
-Note that the thermal contribution from the accretion is negligible in this figure. 
+Note that the thermal contribution from the accretion disk is negligible in this figure. 
 The spectral shape is modeled by simply scaling the Jovian radio spectrum (e.g. Figure 8 of \cite{zarka_et_al2004}). 
@@
 Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
-Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}.
-Therefore, $\alpha_L \sim -2.7$.
+Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}. Therefore, $\alpha_L \sim -2.7$.
 
@@
 \startdata
-LOFAR-LBA  &  30-80  & 1100  & 230000             & 10   & 57 \\ 
-LOFAR-HBA  & 110-200 & 180   &   6500             & 4.1  & 1.1 \\  
-HERA       & 50-250  &  76   & 1200               & 410  & 36000\\ 
-GMRT       & 130-190 & 162   &   5400             & 16.5 & 57 \\ 
-%LWA       &  30-80  & 50000 &  702127141         & 10.3 & 42.2 \\
-%MWA       &  30-80  & 24000 &  176223211         & 1030 & 4.2$\times10^5$ \\
-SKA-Low (part) & 50-200 & 5.9 &   7.2             & 7.6  & 9.7 \\
-SKA-Low (full) & 50-350 & 1.8 &  0.7              & 4.8  & 1.5 \\
+LOFAR-LBA  &  30-80  & 700   & 120000             & 8.3  & 42 \\ 
+LOFAR-HBA  & 110-200 &  35   &    310             & 3.3  & 1.1 \\  
+HERA       &  30-80  & 870   & 160000             & 1030 & 4.2$\times10^5$\\ 
+GMRT       & 130-190 & 430   &  46000             & 16.5 & 56.9 \\ 
+%LWA       &  30-80  & 58000 &  702127141         & 10.3 & 42.2 \\
+%MWA       &  30-80  & 29000 &  176223211         & 1030 & 4.2$\times10^5$ \\
+SKA-Low (part) & 50-200 & 7.8 &  12.6             & 7.6  & 9.7 \\
+SKA-Low (full) & 50-350 & 2.2 &  1.0              & 4.8  & 1.5 \\
 %VLA 4-Band& 30-80   & 3300  & 2312058            & 28.6 & 330 \\
-VLA-LOBO   &  50-350 &  77   &  1200              & 8.6  & 10.4
+VLA-LOBO   &  50-350 &  92   &  1800              & 8.6  & 10.4
 \enddata
@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike the previous paper, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Unlike the previous paper, we consider that UV/X-ray from the accretion disk around the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral.
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 

### 2015-09-26 ms.tex

@@
 %
-Mehrdad Mirbabayi\altaffilmark{13}
+Mehrdad Mirbabayi\altaffilmark{4}
 }
@@
 \affil{$^{11}$Astronomy Department, University of Cambridge, UK}
-
 \vspace{0.5\baselineskip}

### 2015-09-26 ms.tex
cleaned tex file (removed the parts which have been commented out)

--- 2015-09-26 ms.tex
@@
 \usepackage{natbib}
-%\usepackage{lscape}
 \usepackage{enumerate}
@@
 \hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
-%\usepackage[dvipdfmx]{color}
-%\usepackage[dvipdfmx]{graphicx}
 \allowdisplaybreaks[1]
@@
 \bibliographystyle{apj}
-
-\def\memoYF#1{\color{red}$[${\bf #1}$]$ \color{black}}
-
-\def\memoDS#1{\color{blue}$[${\bf #1}$]$ \color{black}}
-
-\def\memoNZ#1{\color{green}$[${\bf #1}$]$ \color{black}}
-
-\def\memoJN#1{\color{purple}$[${\bf #1}$]$ \color{black}}
 
@@
 
-\newcommand{\cN}[1]{\mathcal{N}}
-\newcommand{\pn}[1]{\mbox{$(#1)$}}
-\newcommand{\spa}{\mbox{ }}
 \def\gsim{\;\rlap{\lower 2.5pt
@@
 \setlength{\voffset}{-0.4in}
-%\setlength{\voffset}{0.3in}
 \parindent 0.2in
@@
 We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
-We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and 100 times brighter than equivalent objects around main-sequence stars, which allow us to search them in a 1000 times larger volume.
+We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
 The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array. 
@@
   stars: AGB and post-AGB}
+
 %]%%% End front material
@@
 In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
-%\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and of the star, which would accelerate electrons and produce radio emission \memoTM{(can we say?) via cyclotron radiation}.
-% I leave this out because this is not based on radiometric bode's law. 
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
@@
 The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
-%Namely, although the detail of the mechanism to generate planetary radio emission is not fully understood so far \memoYF{cite something?}, 
-%observations indicate that the total radio emission, $P_{\rm radio}$ is proportional to the input kinetic energy, $P_{\rm k,\,inp}$, or the input magnetic energy, $P_{\rm m,\,inp}$ \citep[``radio Bode's law''; ][]{desch+kaiser1984}:
 %%%
@@
 where $n$ is the number density of the stellar wind, $v$ is the relative velocity of the stellar wind particles and the planet, $ B_{\star\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point.
-%In the case of the Solar wind, the kinetic energy is dominant input energy over the magnetic one (the former is $\sim 400$ times larger than the latter).  
 It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
@@
 
-%We estimate the radio brightness of RGHJs by simply scaling \memoDS{stray sentence fragment?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We do so simply by scaling the Jovian magnetosphere at the surface $B_J \sim 10$ G according to the planetary mass and age, based on the predicted scaling relation described below.
-% we adopt a simple scaling relation between the magnetic field and macroscopic planetary properties.
 
 So far, several scaling relations for the planetary magnetic field strength  
-have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009} %\memoYF{check!}
-%(see \citet{griesmeier2004} or \citet{christensen2010} for the summary), 
+have been proposed \citep[e.g.][]{russel1978,busse1976,stevenson1979,mizutani1992,sano1993,starchenko2002,christensen2006,christensen_et_al2009}  
 which are summarized and compared with numerical simulations in \citet{christensen2010}. 
@@
 This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
-%\memoYF{describe in more detail}:
-%%%%%%%%%% 
-%\begin{equation}
-%B^2 \propto \rho_c r_c^{4/3} q_c^{2/3}, \label{eq:Bscaling} 
-%\end{equation}
+%%%%%%%%%%
 \begin{equation}
@@
 %%%%%%%%%%
-%where $\rho _c$ and $r_c$ are the density and the radius of the dynamo region, and $q_c$ is the internal convected energy flux in the core region. 
 where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is an efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
@@
 \begin{equation}	
-%L \sim 1.84\times10^{-10} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, 	
 L_p \sim 6.3\times10^{23} \; {\rm erg} \; \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, 
@@
 \begin{equation}
-%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
 B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,{\rm J}}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
@@
 under this model.
-
-%We note that the scaling relation based on \citet{christensen_et_al2009}, or equation (\ref{eq:Bscaling}), has also been adopted in \citet{reiners2010}.
-While the detailed treatment of $\rho _c$ and $q_o$ are different, two estimates of planetary magnetic field strength are fairly close, as shown in \S3 below.
 
@@
 While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$).
-\memoDS{Where is the relevant velocity?
-Is it at the magnetic standoff point, or at the planetary surface, or somewhere in between?
-At the planet's surface, the infall velocity is 150 km/s for a 10$M_{\rm J}$ planet, no?}
 Here, we simply consider
@@
 as a fiducial value for normalization.
-%where $v_{\odot} \sim 4.0 \times 10^2 $ km/sec.
-%, and  (and should be something like the sum in quadrature of these velocities)
 
@@
 %
-T_{\rm acc} \sim %&& 2 \times 10^6 ~\mbox{K} \left( \frac{M_p}{10 M_{\rm J}} \right) \\
-%\sim 
-&& 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_{\rm J}} \right). \label{eq:Tacc}
+T_{\rm acc} \sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_{\rm J}} \right). \label{eq:Tacc}
 \end{eqnarray}
@@
 
-The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
+The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, 
 or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
@@
 %%%%%%%%%
-%With $\xi = 0.8 $, this gives $N_i \sim 5$.  \memoDS{Why 0.8?}
 Alternatively, cascade (\emph{ii}) leads to
@@
 }
-   %\memoDS{This looks great.
-Might be good to also show the locations of the magnetic standoff point and the ``stromgren sphere radius'' on this figure (say, with vertical dashed and dotted lines?), and to move the legend to the lower left corner?
-{\tt plt.legend(loc=3)}}
   \label{fig:ionizationfraction}
@@
 The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
-%\memoDS{We should write the expression ... it's just the quadratic formula, but it would be useful to write.}
 When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
@@
 
-%\citet{drake1983}
-%\citet{}
-%\color{black}
-
-%The temperature of stellar wind of RGs is expected to be 2 orders of magnitude lower than their main sequence counterparts, mainly because the sound speed of hot corona exceeds the escape speed, i.e., hot corona cannot be confined in the stellar atmosphere \citep{suzuki2008}.
-%\begin{equation}
-%\frac{T}{T_{\odot}} \sim 10^{-2}
-%\end{equation}
-%where $T_{\odot } \sim 10^6$ K.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \plotoneh{rho_r_dynamo.pdf}
-%   \caption{Radius and average density of the dynamo region as a function of planetary mass. }
    \plotoneh{qBf_Christensen.pdf}
    \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass.
-Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.} %\memoDS{Can we change density to cgs in this figure?}
+Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.}
   \label{fig:planetaryB}
@@
 Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age.
-%Given that $\rho _c \propto M_p$  at large $M_p$ and $q_c \propto t^{-1.3} M_p^{2.64}/r_c^2$, the magnetic field is roughly:
 Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness. 
-%%%%%%%%%% 
-%\begin{eqnarray}
-%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingB} \\
-%B   &\sim &  10~{\rm G} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingB} \\
-%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.38} \label{eq:scalingfc} 
-%\nu_{\rm cyc} &\sim &  28~{\rm MHz} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \left( \frac{M_p }{M_{p,J}} \right)^{1.04} \label{eq:scalingfc} 
-%\end{eqnarray}
-%%%%%%%%%%
-%under this model. 
 Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz and 1~GHz. 
@@
 \begin{figure*}[bp]
-%   \plotonesc{radio_emission_Mdot1e-8_constRp_christensen.pdf}
-%   \plotonesc{radio_emission_Mdot1e-5_constRp_christesnsen.pdf}
 	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
@@
 \nonumber r_{\rm mag} 
-%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
 &=& r_{\rm mag,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
@@
 \begin{eqnarray}
-P_{\rm k,\,inp} &=& nv^3 r_{\rm mag}^2 %= n v^3 \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/3} R_J^2  \\
-\\
+P_{\rm k,\,inp} &=& nv^3 r_{\rm mag}^2 \\
 &=& P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3}  \notag \\
@@
 We may compare radio emission power of canonical hot Jupiters set at 0.05 AU  and that of RGHJs at 5 AU.
-%Canonical values we adopt for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. 
 Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
@@
 P_{\rm k,\,inp} 
-%&\approx & 227 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-%&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
 &\approx &  140 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-%&\approx & 2.27 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
-%&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
 &\approx & 14000 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for AGB stars' companions)} \notag \\
-%&\approx & 489 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_J} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
-%&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
 &\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
@@
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
-%\memoYF{This is based on theoretical prediction by \citet{griesmeier2004} that the tidally-locked planets have weaker magnetic field due to slow spin rotation. }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}[htp]
-%\caption{Canonical Parameters of 2 types of hot jupiters.}
-%\begin{center}
-%\begin{tabular}{c|cccc} \hline \hline
-%& mass & magnetic field & orbit &  spin period \\ 
-%& $M_p$ & B & $a$ &  \\ \hline
-%canonical HJ & $M_{\rm J}$ & $B_J$ & 0.05 AU & 4 days \\
-%RGHJ & $M_{\rm J}$ & $B_J$ & 5 AU &  0.4 days \\ \hline
-%\end{tabular}
-%\end{center}
-%\label{tab:comp_HJ}
-%\end{table}%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%
-%&\approx & 1.12 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-%&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-%&& \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJ} \\
 &\approx & 0.70 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
@@
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-%%%
-%&\approx & 1.12 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
-%&&\times \left( \frac{B}{B_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\ 
-%&& \times \left( \frac{\dot M_\star}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \label{eq:F_nu_AGB} \\
 &\approx & 0.70 \times 10^{-3} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \notag \\
@@
 %%%
-%Note that, within this framework, the {\it spectral} radio flux has necessarily negative correlation with the planetary magnetic field, as pointed out by \citet{griesmeier2005}. 
-%\memoYF{cite original paper!}. 
 Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
@@
 The target system is located at a distance of 100~pc from the Earth; the flux is scaled by the distance as a quadratic function.
-%The spectral radio emission from RGHJs at around 5-10 AU is found to be $\sim 10^{-6}-10^{-3}$ Jy when observed from 10-100 pc away.
 
 Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
-%We can see emission only from where the cyclotron frequency (equation (\ref{eq:fcyc})) exceeds the plasma frequency along the line of sight:
-%%%
-%\begin{equation}
-%\label{eq:fcyc>fplasma} \nu_{\rm cyc} > \nu_{\rm plasma}^{\rm los}
-%\end{equation} 
-%%%
 The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
@@
 For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
-% $M_p \gtrsim 4M_{\rm J}$ is well observable at 5 AU. 
 On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[bp]
- %\begin{minipage}{0.5\hsize}
-  %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-8_constRp.pdf}
-%   \plotonesc{radio_emission_Mdot1e-8_constRp.eps}
-  %\end{center}
- %\end{minipage}
- %\begin{minipage}{0.5\hsize}
-   %\begin{center}
-   %\includegraphics[width=\hsize]{radio_emission_Mdot1e-5_constRp.pdf}
-%   \plotonesc{radio_emission_Mdot1e-5_constRp.eps}
-  %\end{center} 
- %\end{minipage}
-%   \caption{[{\bf Old version: based on scaling relationship of Sano 1993}] Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc.
-The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere.
-The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion.
-Bottom panel: cyclotron frequency, i.e., the frequency of radio emission.
-}
-%  \label{fig:radio}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Then, we estimate the radio emission of Jupiter-twin around known M giants in Section \ref{ss:actualMgiants}. 
-A general discussion about the luminosity function of planetary radio emission is given in Section \ref{ss:Lfunc}. 
 In Section \ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
@@
 Almost all observations have been carried out 
-%at wavelengths of 6 cm and below, 
 at frequencies $\geq 5~\rm GHz$, 
@@
 Only two published studies describe attempts to detect continuum emission from single (non-binary) red giant stars 
-%at wavelengths above 20 cm 
 at frequencies below 1 GHz ($L$ band); both yielded null results.
@@
 
-Altogether, we lack firm observational constraints on the brightnesses of M giants near %1-m wavelengths.
-30-300 MHz frequencies.
+Altogether, we lack firm observational constraints on the brightnesses of M giants near 30-300 MHz frequencies.
 
 However, assuming thermal Bremsstrahlung emission continues to dominate in this wavelength regime, we can extrapolate down from the reported centimeter flux densities, using the specific spectral index.
-%In this case, for example, extrapolating from the 0.4 mJy flux density of $\alpha$ Ori at 1.46 GHz, and using its spectral index 1.32~\citep{Newell1982}, we arrive at an estimated flux density of 0.04 mJy at 300 MHz.
-% YF: This is consistent with the following equation, so I removed it to avoid redundancy. 
-%
 For example, \citet{OGorman2013} reported $\alpha$~Boo ($R_\star = 25.4 R_{\odot }$, $T=4286$ K, $d=11.26$ pc) at 1~GHz is about 70 $\mu$Jy, and $\alpha$~Tau ($R_\star = 44.2  R_{\odot }$, $T=3910$ K, $d=20.0$ pc) at 3~GHz is about 40 $\mu$Jy.
@@
 The continuum lines from the star in the cases of $\alpha_* =0.8$ and $2.0$ are shown as an extreme case.  
-%; the 0.6 value is the prediction from the constant property wind model \citep{wright1975,panagia1975,olnon1975}.
 As Figure \ref{fig:cartoon} indicates, with a reasonable range of spectral index, the radio emission from the star is smaller by order of magnitude than the expected radio flux from RGHJs at frequencies below 300~MHz.
@@
 \begin{equation}
-%\dot M_\star [M_\odot{\rm /yr}] \sim 4 \times 10^{-13} \eta \left( \frac{R_{\star }}{R_{\odot }} \right)\left( \frac{L_{\star }}{L_{\odot }} \right) \left( \frac{M_\star}{M_\odot} \right)^{-1}
 \dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
@@
 
-%\memoYF{Up to where would the planet be engulfed by evolved stars? References?}
-%I wondered this because if planets at 1 AU would be engulfed anyway it would not be worth discussing here.
-According to e.g.
-Nordhaus and Spiegel (2013) it is the case--however, some planets may migrate inward within 1 AU after evolution.
-So it should be ok.
-In any case this is not the main point of this paper and I would leave it out.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \plotoneh{radio_10Mp.pdf}
-%   \plotoneh{radio_1Mp_5AU.pdf}
-%   \plotoneh{radio_5Mp_5AU.pdf}
-%   \plotoneh{radio_2Mp_4-5Gyr.pdf}
-%   \plotoneh{radio_4Mp_4-5Gyr.pdf}   
    \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ and 10$M_{\rm J}$ at 1~AU and 5~AU.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Luminosity function of planetary radio: 
-nearby faint object v.s. far luminous object}
-\label{ss:Lfunc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In principle, if the expected luminosity function and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
-For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume.
-Under these assumptions, the largest luminosity in a volume limited sample (volume $V$, distance $d$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
-The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$. 
-Therefore,the likelihood of finding the brighter source increases with distance for $\alpha_L < 3/2$. 
-Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
-For example, for an $N[L] \propto L^{-1}$ the apparently brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
-Therefore, if we can estimate the luminosity function of RGHJ emitters, we may estimate their detectability.
-
-Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy.
-In order to estimate the true luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
-As discussed in Section \ref{ss:brightness}, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$.
-Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
-Observations of globular clusters indicates the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996}.
-Therefore, $\alpha_L \sim -2.7$.
-
-Thus, the criterion $\alpha_L < 3/2$ is satisfied if the slope of the luminosity function of the host stars is shallower than $-1$.
-
-\memoYF{this is note. this part will be removed later}
-
-The number of targets within the shell at radius $r \sim r+\Delta r$, $dN(r)/dr $, is
-%%%
-\begin{eqnarray}
-\frac{dN(r)}{dr} &=& 4 \pi r^2 \int _{L_{\rm min}}^{\infty} \frac{dn(L)}{dL} dL \\
-L_{\rm min} &\propto & r^2 F_{\rm min} 
-\end{eqnarray}
-%%%
-where $F_{\rm min}$ is the detection limit ($=constant$). 
-Assuming $dn(L)/dL \propto L^{-\alpha_L }$, 
-%%%
-\begin{eqnarray}
-\frac{dN(r)}{dr} &\propto & r^2 \left( \frac{L_{\rm min}^{-\alpha_L + 1}}{\alpha_L - 1}  \right)\\
-&\sim & r^2 \left( \frac{r^{2(-\alpha_L + 1)}}{\alpha_L - 1} \right) \\
-&\propto & \frac{r^{-2\alpha_L + 4}}{\alpha_L - 1}
-\end{eqnarray}
-%%%
-($N(r)$ is the number of candidates within volume $V(r) =4\pi r^3/3$.)
-When $\alpha _L=2.7$, 
-\begin{equation}
-\frac{dN(r)}{dr} \propto r^{-1.4}
-\end{equation}
-%Now, using the luminosity function of red giants $dn/dL_{\star } \sim L_{\star }^{-1.8}$ \citep{sandquist1996} and $L \sim L_{\star}^{2/3}$, $\alpha_L \sim -2.7$.
-Thus, the number of candidates within volume $V(r)$ increases as $r^{-0.4}$.
-%%%
 
@@
 
-%For now, it is difficult to detect planetary-mass companions around low-mass evolved stars through other means. 
-%The major difficulty in radial velocity measurement is the stellar pulsation (rms of $>30m/s$ for K giants).
-If the orbital period is long enough compared to the period of pulsation, it is possible to average out the pulsation and detect radial velocity of planetary component, but this requires long period monitoring.
-For transit observation Pulsation also contributes to the noise in detecting transit signals \memoYF{?} and besides the transit signals would be as low as 1ppm.
-Due to the great luminosity of the host star, direct imaging is also difficult \memoYF{?}.
-Thus, for the time being, one would have to aim at discovering planetary companions around evolved stars, rather than targeting at known planetary systems.
-
 Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
@@
 where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
-%If the initial velocity is not perpendicular to the magnetic field, $v$ must everywhere be replaced by its perpendicular component.
 
@@
 Therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
-
-%It is interesting to note that, for a plasma of protons and electrons in a stellar wind, the canceling field is clearly dominated by the contribution of protons, though the cyclotron emission is dominated by electrons.
 
@@
 
-%equation (\ref{eq:stand-off-radius})
-%%%
-%\begin{equation}
-%r_{\rm mag} = 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
-%\end{equation}
-%%%
 Aside from this common part, the differences originate mainly from:
@@
 with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$.
+
 \end{document}
-
-\clearpage
-
-\section{Memo}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Brighter Implies Harder to See:\\
-Greater $B$ Produces Lower $F_\nu$}
-\label{ss:counterintuitive}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The cyclotron frequency at radius $r$ is:
-%%%
-\begin{equation}
-\nu_{\rm cyc} = \frac{e B(r)}{2\pi m_e} \propto \frac{B_p}{r^3}
-\end{equation}
-%%
-Therefore, 
-%%%
-\begin{equation}
-\frac{dP}{d\nu_{\rm cyc}} = \frac{dP}{d\nu } \propto -\frac{r^4}{B_p} \frac{dP}{dr}
-\end{equation}
-%%%
-Employing Larmor formula, power emitted from a thin shell at $r\sim r+dr$, $dP/dr$ is 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto 4\pi r^2 N_{\rm plasma}(r) v_{\bot }^2(r) B^2(r) \label{eq:larmor}
-\end{equation}
-%%%
-where $N_{\rm plasma}(r) $ represents the number density of plasma in the planetary magnetosphere at radius $r$.
-
-We assume that $N_{\rm plasma}(r_{\rm mag}) $  is proportional to the squared radius of the magnetic stand-off point:
-%%%
-\begin{equation}
-N_{\rm plasma}(r_{\rm mag}) \propto \pi r_{\rm mag}^2 \;\;(\propto B_p^{2/3}) \label{eq:N0_plasma}
-\end{equation}
-%%%
-Due the the mass flux conservation,
-%%%
-\begin{equation}
-4 \pi r^2 N_{\rm plasma}(r) v_{\|} = const.
-\end{equation}
-%%%
-Combining with equation (\ref{eq:N0_plasma}),
-%%%
-\begin{equation}
-N_{\rm plasma}(r) \propto  \frac{r_{\rm mag}^2 }{v_{\|}(r) r^2} \propto  B_p^{2/3} \cdot \frac{v_{\|}(r)}{r^2}
-\end{equation}
-%%%
-
-Because the magnetic dipole moment
-%%%
-\begin{equation}
-\mu = \frac{mv_{\bot}(r)}{eB(r)}
-\end{equation}
-%%%
-is approximately to be constant while the plasma falls down along the magnetic field, 
-%%%
-\begin{eqnarray}
-v_{\bot }(r) \propto \frac{1}{r^3} \label{eq:v_bot} \\
-B(r) \propto \frac{B_p}{r^3} 
-\end{eqnarray}
-%%%
-On the other hand, conservation of energy ensures that
-%%%
-\begin{equation}
-\mathcal{E} = -\frac{GM_p}{r} + \frac{v_{\bot }^2}{2} + \frac{v_{\|}^2}{2}=const.
-\end{equation}
-%%%
-Assuming that the initial energy (at $r=r_{\rm mag}$) is negligible compared to those near the surface, $\mathcal{E}=0$, 
-%%%
-\begin{equation}
-v_{\|}^2 \sim \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_{\rm mag}} \right)^{-6} \label{eq:v_||}
-\end{equation}
-%%%
-
-Substituting equations (\ref{eq:N0_plasma}),  (\ref{eq:v_bot}) and (\ref{eq:v_||}) into equation (\ref{eq:larmor}) leads to
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{12}} \left( \frac{GM_p}{r} - \frac{v_{\bot ,0}^2}{2} \left( \frac{r}{r_{\rm mag}} \right)^{-6} \right)^{1/2}  
-\end{equation}
-%%%
-The right-hand side has the maximum value $\sqrt{5GM_p/6\tilde r} $ at radius $\tilde r=(6v_{\bot ,0}^2/GM_p)^{1/5}$. 
-At $r>>\tilde r$, 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{25/2}}
-\end{equation}
-%%%
-and
-%%%
-\begin{equation}
-\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{17/2}} \propto \frac{\nu^{17/6}}{B_p^{7/6}}
-\end{equation}
-%%%
-
-At $r<<\tilde r$, 
-%%%
-\begin{equation}
-\frac{dP}{dr} \propto \frac{B_p^{8/3}}{r^{15}}
-\end{equation}
-%%%
-and
-%%%
-\begin{equation}
-\frac{dP}{d\nu } \propto \frac{B_p^{5/3}}{r^{11}} \propto \frac{\nu^{11}}{B_p^{28/3}}
-\end{equation}
-%%%
-
-\newpage
-
-\memoDS{Is this section needed anymore, since this is already in the Griesmeier paper?
-Does the Griesmeier paper make the point explicit enough, or is this still somewhat valuable?
-Also, are we 100\% sure that this section is right?
-A planet with larger surface field achieves an equivalent field to a planet with a smaller surface field at a larger radius, and captures a larger wind flux.
-Should we think more about the spectrum?}
-
-According to Eq.~(\ref{eq:Pkinp}), the total emitted power scales with $B^{2/3}$.
-In detail, it is not obvious how the power spectral density scales with a planet's surface magnetic field, because the emission process involves electrons passing through a wide range of magnetic field conditions (dipolar field strength drops off as $r^{-3}$, and only in an idealized model is a planet a perfect magnetic dipole).
-Nevertheless, a reasonable ansatz is that the radio emission is spread over a range of wavelengths in an approximately scale-independent way.
-In other words, the frequency bandwidth $\Delta \nu$ of Eq.~(\ref{eq:Fnu}) is proportional to $\nu_{\rm cyc}$, as described in Section~\ref{ss:model_intensity} and in \citet{griesmeier2007b}.
-This means that the power spectral density is likely to scale as the total power divided by the cyclotron frequency corresponding to a characteristic field strength where the emission peaks.
-Since $\nu_{\rm cyc}$ scales as $B$ (a higher power of $B$ than the scaling of total power), this implies that the power spectral density in the radio scales as $B^{-1/3}$.
-Planets that are intrinsically brighter, owing to a greater magnetic field strength, probably have their emission spread out over a broader set of frequencies, and therefore have a lower flux density as measured in Janskys!
-\memoDS{Is this pointed out elsewhere in the literature?}
-
-\section{Dave's sketch}
-
-\citep{spiegel2008}
-
-\citep{lecavelier_et_al2013}
-
-\citep{janhunen_et_al2003}
-
-\citep{zarka1992, zarka1998}
-
-\citep{farrell_et_al2004}
-
-\citep{lazio+farrell2007}: likelihood function, tau Boo search
-
-\citep{lecavelier_et_al2009}
-
-\citep{spiegel2012}
-
-\citep{nordhaus+spiegel2013}
-
-\citep{jiang+jin1996}: 12cm radio of Jupiter during Shoemake-Levy-9
-
-\citep{morin2012, morin_et_al2013}
-
-\citep{christensen_et_al2009, christensen2010}
-
-\citep{saar2001}: Inverse rossby number scaling of magnetic field: $B
-\sim 60 {\rm~G} \times Ro^{-1.2}$.  Here, he takes $Ro = \tau_c/P_{\rm
-  rot}$, where $\tau_c$ is the convective turnover time = ?
-\citep{gilliland1986}.  Well, $F \sim \rho v_c^3 \sim \rho
-(H/\tau_c)^3$, so $\tau_c \sim H (\rho / F)^{1/3} = H / (\sigma T_{\rm
-  eff}^4 / \rho)^{1/3}$.  Alternatively, $\tau_{\rm conv} \sim (M R^2
-/ L)^{1/3}$.
-
-On dimensional grounds, the convective turnover time goes as
-$\tau_{\rm conv} \sim (M R^2 / L)^{1/3}$.  According to
-\citet{burrows_et_al2001}, radius $R$ and luminosity scale with time
-as $R \sim R_J$, where $R_J$ is the radius of Jupiter, and
-\begin{equation}
-\frac{L}{10^{-9} L_\odot} \sim \left( \frac{t}{1 \rm~Gyr} \right)^{-1.3} \left( \frac{M}{1~M_{\rm J}} \right)^{2.64} \, .
-\label{eq:burrowsLum_2}
-\end{equation}
-So,
-%\begin{eqnarray}
-%\nonumber \tau_{\rm conv} & \sim & 3 {\rm~days} \times \left( \frac{M}{M_{\rm J}} \right)^{1/3} \left( \frac{R}{R_J} \right)^{2/3} \left( \frac{L}{L_\odot} \right)^{-1/3} \\
-% & = & 
-%\end{eqnarray}
-\begin{eqnarray}
-\nonumber \tau_c & \sim & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{L}{10^{-9} L_\odot} \right)^{1/3}} \\
- & = & 3 {\rm~hrs} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_{\rm J}} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}} \\
-\end{eqnarray}
-So the Rossby number $Ro = \tau_c/P_{\rm rot}$ is
-\begin{eqnarray}
-Ro & = & \frac{\tau_c}{P_{\rm rot}} \\
- & = & \left( \frac{P_{\rm rot}}{3 \rm~hrs} \right)^{-1} \times \frac{\left( \frac{H}{100 \rm~km} \right) \left( \frac{\rho}{10^{-5} \rm~g~cm^{-3}} \right)^{1/3}}{\left( \frac{M}{1 ~M_{\rm J}} \right)^{0.88} \left( \frac{t}{1 \rm~Gyr} \right)^{0.43}}
-\end{eqnarray}
-
-\citep{hallinan_et_al2013}
-
-\citep{desch+kaiser1984} radiometric Bode's law
-
-Noting that
-\begin{equation}
-\dot{M}_* = 4\pi r^2 \rho[r] v \, ,
-\label{eq:mdot}
-\end{equation}
-so $\rho[r] = \dot{M}_*/(4\pi r^2 v)$,
-\begin{eqnarray}
-\frac{\rho v^2}{2} = \frac{B^2}{8\pi} \sim \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-3} \, ,
-\end{eqnarray}
-where $B_0$ is the field strength at a distance $d_0$ from the planet.
-\begin{eqnarray}
-\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
-\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
-\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
-d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
-d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
-  & \sim & 4 R_J \left( \frac{d_0}{R_{\rm J}}\right) \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
-\label{eq:Chapman-Ferraro}
-\end{eqnarray}
-In the above, $d_A$ is the distance from the planet to the Alfven
-point, where the magnetic energy density $u_B = B^2 / 8\pi$ equals the
-kinetic energy density in the stellar wind $u_w = \rho v^2/2$, and
-$B_0$ is the magnetic field strength at distance $d_0$.
-
-The escape speed is
-\begin{equation}
-v_{\rm esc}^* = \sqrt{\frac{2 G M_*}{R_*}} \, ,
-\end{equation}
-so if the stellar wind speed is a factor $C$ times the escape speed, then ...
-
-The power incident on the planet within $d_A$ is
-\begin{eqnarray}
-P_{\rm inc} & = & \frac{\rho v^3}{2} \times \pi d_A^2 \\
-\frac{\rho v^2}{2} & \sim & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
-d_A^6 & = & d_0^6 \frac{B_0^2}{4\pi \rho v^2} \\
-d_A^2 & = & d_0^2 \left( \frac{B_0^2}{4\pi \rho v^2}\right)^{1/3} \\
-\pi d_A^2 \frac{\rho v^3}{2} & = & \frac{d_0^2}{2} \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{4} \right)^{1/3} \\
-P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} 
-%\frac{\dot{M}_* v}{8\pi a^2} & = & \frac{B_0^2}{8\pi} \left( \frac{d}{d_0} \right)^{-6} \\
-%\frac{\dot{M}_* v}{r^2} & = & B_0^2 \left( \frac{d}{d_0} \right)^{-6} \\
-%d^6 & = & \frac{d_0^6 B_0^2 r^2}{\dot{M}_* v} \\
-%d_A & = & d_0 \left( \frac{B_0^2 r^2}{\dot{M}_* v} \right)^{1/6} \\
-%  & \sim & 4 d_0 \left\{ \frac{\left( \frac{B}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^2}{\left( \frac{\dot{M}_*}{10^{-6} M_\odot/\rm yr} \right) \left( \frac{v}{20 \rm~km/s} \right)} \right\}^{1/6}
-\end{eqnarray}
-Note that $\rho v = \dot{M}_*/4\pi r^2$.  Therefore,
-\begin{eqnarray}
-P_{\rm inc} & = & d_0^2 \left( \frac{\pi^2 \rho^2 v^7 B_0^2}{32} \right)^{1/3} \\
- & = & d_0^2 \left( \frac{\dot{M}_*^2 v^5 B_0^2}{512 r^4} \right)^{1/3} \\
- & = & \frac{d_0^2}{8} \left( \frac{\dot{M}_*^2 v^5 B_0^2}{r^4} \right)^{1/3} \\
-\nonumber  & \sim & 2 \times 10^{18} {\rm~W} \left( \frac{d_0}{R_{\rm J}} \right)^2 \left( \frac{\dot{M}_*}{10^{-5} M_\odot / {\rm yr}} \right)^2 \\
- & & \times \left( \frac{v}{20 \rm~km/s} \right)^5 \left( \frac{B_0}{10 \rm~G} \right)^2 \left( \frac{r}{5 \rm~AU} \right)^{-4}
-\end{eqnarray}
-
-The power incident on the planet is
-
-%\citep{lunine_et_al1989} -- error?
-
-% http://kiss.caltech.edu/workshops/magnetic2013/presentations/winterhalter.pdf
-
-%ftp://ftp.iwf.oeaw.ac.at/pub/Scherf/PRE-CD%20V2/pre6/nigl.pdf
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Assumptions for Planetary Magnetic Field}
-%\label{ss:magneticfield}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{It may be better to consider Cristensen's scaling, taking account of the age. But I have not followed the theory yet.}
-
-Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griesmeier2004}:
-%%%%%%%%%% 
-\begin{equation}
-\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
-\end{equation}
-%%%%%%%%%%
-where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively.
-The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$.
-In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}.
-\memoYF{validity?}
-
-Unlike usual hot jupiters, RGHJs are not tidally locked to their host stars, as the stellar tidal field does not change significantly even if the star evolves into a giant.
-Without no physical insights of the typical spin rate, we simply assume that of Jupiter: $\omega = 9.925$ [hr]. 
-\memoYF{Would their spin rate become higher or lower??}
-
-In order to evaluate $\rho _c $ and $r_c$, we need a model of internal structure of gaseous planets. 
-First, we assume that the planetary radius is constant at $R_p = R_{p,\,{\rm J}}$, as the numerical calculations show that the radii of gaseous planets over the range of $0.1 R_{p,\,{\rm J}} < M_p < 10M_{p,\,{\rm J}}$ (with core mass less than 10\%) are converged to $0.8 R_{p,\,{\rm J}} < R_p < 1.2R_{p, \,{\rm J}}$ in 1 Gyr \citep{fortney2007}.
-For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
-%%%%%%%%%% 
-\begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r_2}
-\end{equation}
-%%%%%%%%%%
-We determine the core radius $r_c$ by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_c=700\,\mbox{kg/m}^3$.
-The density of the metallic core, $\rho _c$ is obtained by averaging the density in the core.
-We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.
-
-Equation (\ref{eq:fcyc>fplasma}) can also be rewritten as: 
-%%%
-\begin{eqnarray}
- \left( \frac{B}{10~\mbox{G}} \right) &>& 0.526 \left( \frac{a}{5~\mbox{AU}} \right)^{-1} \\
- && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-1/2} \label{eq:Ba_limit}
-\end{eqnarray}
-%%%
-or, 
-%%%
-\begin{eqnarray}
- \left( \frac{M_p}{M_{p,\,{\rm J}}} \right) &> & 0.627 \left( \frac{a}{5~\mbox{AU}} \right)^{-0.72} \left( \frac{t}{4.5~\mbox{Gyr}} \right)^{0.31} \\
- && \times \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{0.36}  \left( \frac{v}{10^{-1}v_{\odot}} \right)^{-0.36} \label{eq:Ma_limit}
-\end{eqnarray}
-%%%
-In other words, given any orbital distance, there is a lower mass limit for a planet to be able to release the  radio wave out of the system. 
-Substituting equation (\ref{eq:Ba_limit}) into equation (\ref{eq:F_nu_RGHJ}) leads to the maximum spectral radio flux at given orbital period:
-%%%
-\begin{eqnarray}
-F_{\nu} &<& 1.30 \times 10^{-3}~\mbox{Jy} \left( \frac{d}{10~\mbox{pc}} \right)^{-2} \\
-&& \times \left( \frac{a}{5~\mbox{AU}} \right)^{1/3}  \left( \frac{\dot M_\star}{10^6 \dot M_{\odot}} \right)^{1/2} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{13/6}
-\end{eqnarray}
-%%%
-
-\end{document}

### 2015-09-26 ms.tex
LOFAR-HBA is removed from the list of potentially promising instrument

@@
 We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
-The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with current/future instruments such as LOFAR and the Square Kilometer Array. 
+The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array. 
 \end{abstract}
@@
 Estimates for the actual late-type (M type) evolved stars are also included. 
-We find that the Square Kilometer Array(SKA), and perhaps the high band of the LOw Frequency ARray (LOFAR-HBA) as well, will be capable of detecting these signals within a reasonable integration time.
 Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission to characterize the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.
@@
 The noise estimates shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
-On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
-LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
-More promising is the low frequency component of SKA, which will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ and orbital distances $\sim$5~AU around M stars $<$100~pc from Earth.
+%On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
+%LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$5~AU around M stars within $\sim $100~pc from Earth, as well as those around even further stars but orbiting closer to the stars.
+VLA-LOBO could also work for a few nearby systems.
 
@@
 When the particle spirals into the planet, 
-the magnetic pressures increases (by beaming?) by 
+the magnetic pressures increases as 
 %%%
@@
 The radio flux from a system with an exoplanet at 5 AU at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy.
-Such signals would be detectable with SKA within a day or so.
-For a few nearby systems, or for systems with exoplanets in closer orbit, LOFAR-HBA  would also work with a reasonable integration time.
+Such signals would be detectable with SKA within a day. 
+For a few nearby systems, VLA-LOBO would also work with a reasonable integration time.
 In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confused sources in the same resolution element.

### 2015-09-27 ms.tex
typo: other the other

@@
 in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
-Unlike other the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
+Unlike the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
 of cosmic reionization over wide fields of view.  Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization

### 2015-09-28 ms.tex
figure 5 updated including the effect of lower stellar wind and the corresponding part of the text is improved

@@
 
-Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
-%%%%%%%%%% 
-\begin{equation}
-B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,{\rm J}}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
-\end{equation}
-%%%%%%%%%%
-under this model.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age.
+Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
+%%%%%%%%%% 
+\begin{equation}
+B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,{\rm J}}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
+\end{equation}
+%%%%%%%%%%
+under this model. 
 Reasonably, the resultant values agree with \citet{reiners2010}, who adopted the same scaling law for planetary magnetic field; we show this figure just for completeness. 
@@
 where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
-The velocity of the stellar wind is assumed to scale with the escape velocity, hence
-%%%
-\begin{equation}
-v \propto \sqrt{\frac{2GM_\star}{R_{\star }}}
+The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
+%%%
+\begin{equation}
+v \sim \sqrt{\frac{2GM_\star}{4R_{\star }}}
 \end{equation}
@@
 %%%
-In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets.\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}
-
-Using these data, we calculate the maximum frequency and intensity of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
-We consider [A] a Jupiter-twin whose maximum cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 30$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 300$~MHz (equations (\ref{eq:scalingB}) and (\ref{eq:fcyc})).
-
-Figure \ref{fig:observability} displays the estimated radio intensity (i.e., cyclotron frequency) of Jupiters [A] and [B] around M-type red giants within 300~pc. 
+Combining this relation with equations (\ref{eq:fcyc}) and (\ref{eq:scalingB}) results in
+%%%
+\begin{equation}
+\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
+\end{equation}
+%%%
+In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.
+
+Using these data, we calculate the spectral flux of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
+We consider [A] a Jupiter-twin whose maximum cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 20\,(M_{\star }/M_{\odot})$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 200\,(M_{\star }/M_{\odot})$~MHz.
+
+Figure \ref{fig:observability} displays the estimated radio flux from Jupiters [A] and [B] around M-type red giants within 300~pc. 
 Jupiters are placed at 1 AU and at 5 AU for reference. 
-The difference of the symbols indicates whether the radio emission can escape from the system (circle) or not (cross), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$.  
-For a hypothetical Jupiter-mass planet at 5 AU, a reasonable number of systems have potential to emit radio wave at the level of $\sim 10 \mu {\rm Jy}$  out to $\sim 100-150$ pc.
+The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
+Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while the those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
+For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
+$10~M_{\rm J}$ planets at $\sim 1$ AU will be detectable out to $\sim 200$~pc.
 
@@
 \begin{figure}[tbhp]
-   \plotoneh{radio_1Mp.pdf}
-   \plotoneh{radio_10Mp.pdf}
-   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ and 10$M_{\rm J}$ at 1~AU and 5~AU.
+   \plotoneh{radio_M-RG_1Mp.pdf}
+   \plotoneh{radio_M-RG_10Mp.pdf}
+   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ (upper panel) and 10$M_{\rm J}$ (lower panel) at 1~AU (blue) and 5~AU (black).
 Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }

### 2015-09-28 ms.tex
hot jupiters => jupiters where the description is also true for radio emission of any kind

@@
 %%%
-As Table~\ref{tab:sens} illustrates, source confusion is likely to exceed the 2 $\mu$Jy detection limit of a typical hot Jupiter source for most
+As Table~\ref{tab:sens} illustrates, source confusion is likely to exceed the 2 $\mu$Jy detection limit of a typical RGHJ source for most
 telescopes under consideration.  However, source confusion can be mitigated through differencing observations that cancel out background sources.
@@
 The source confusion limit is dominated by active galactic nuclei, which have low polarization fractions $\lesssim2.5\%$ \citep{Stil2014} and slowly vary with time.
-Therefore both the circularly polarized nature of the cyclotron emission from hot jupiters and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing hot jupiters, like other time-variable sources, to be detected below the imaging confusion limit.
-We therefore expect confusion not to be a strong limitation to the detectability of hot jupiters.
+Therefore both the circularly polarized nature of the cyclotron emission from planets and the time variability (discussed in \S\ref{ss:timevariability}) partially mitigate the source confusion limit, allowing planetary radio emission, like other time-variable sources, to be detected below the imaging confusion limit.
+We therefore expect confusion not to be a strong limitation to the detectability of radio emission from RGHJs.
 
@@
 The low frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
-We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim 30 M_{\rm J}$ hot Jupiters.
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim 30 M_{\rm J}$ Jupiters.
 We again adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ (Equation~\ref{eq:Tsky}), and assume $\Trx \approx 60~\rm K$.
@@
 %LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
-On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$5~AU around M stars within $\sim $100~pc from Earth, as well as those around even further stars but orbiting closer to the stars.
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU and at $\sim$5~AU within $\sim $200~pc and $\sim $100~pc from Earth, respectively.
 VLA-LOBO could also work for a few nearby systems.

### 2015-09-28 ms.tex
1 sentence per line.

@@
 % HERA
-The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) is a telescope array under construction
-in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
-Unlike the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements 
-of cosmic reionization over wide fields of view.  Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization
-(PAPER; \citealt{parsons_et_al2010}), HERA's dishes are deployed in an extremely compact configuration \citep{parsons_et_al2012} and 
-statically point toward zenith.  While these features make HERA less ideal for targeted observations, HERA's substantial collecting area,
-long observing campaigns, and wide field of view make it a powerful survey instrument.
+The Hydrogen Epoch of Reionization Array (HERA\footnote{\url{http://reionization.org/}}) is a telescope array under construction in South Africa that will ultimately consist of 352 14-m parabolic dishes, operating from 50 to 250~MHz \citep{pober_et_al2014}.
+Unlike the other telescope observatories considered here, HERA is a dedicated experiment for making power spectral measurements of cosmic reionization over wide fields of view.
+Similar to its progenitor, the Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}), HERA's dishes are deployed in an extremely compact configuration \citep{parsons_et_al2012} and statically point toward zenith.
+While these features make HERA less ideal for targeted observations, HERA's substantial collecting area, long observing campaigns, and wide field of view make it a powerful survey instrument.
 
@@
 % SKA
-The low frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
+The low-frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
 We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim 30 M_{\rm J}$ Jupiters.

### 2015-09-28 ms.tex
proofreading. minor edits

--- 2015-09-28 ms.tex
@@
 While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$).
-Here, we simply consider
+In the next section, we simply consider
 %%%%%%%%%% 
@@
 \paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
-The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep{dessler1983} due to the misalignment between the magnetic axis and the spin axis.
+The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep[e.g.][]{dessler1983} due to the misalignment between the magnetic axis and the spin axis.
 If the time resolution of the observations is high enough, we might detect the periodicity due to planetary spin rotation.
@@
 \paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
-If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse.
+If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse \citep{lecavelier_et_al2013}.
 The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
@@
 
-Once radio emission is detected, it provides some useful information through both time dependence and frequency dependence. 
+Once radio emission is detected, it provides some useful information about the planet itself and the stellar wind through the time dependence and frequency dependence. 
 As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes.
@@
 A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind.
-Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars.
-The most promising targets are massive planetary ($M_p \gtrsim 4 M_{\rm J}$ companions with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
+Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars, making planetary-mass companions to AGB stars unpromising for the search of planetary auroral radio emission.
+The most promising targets are massive planetary companions ($M_p \gtrsim 4 M_{\rm J}$ to red giant stars, with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 

### 2015-09-28 ms.tex
keyword added

@@
   planetary systems --- stars: evolution ---
-  stars: AGB and post-AGB}
+  stars: AGB and post-AGB --- radio continuum: planetary systems}
 

### 2015-09-28 ms.tex
adds rest of Mehrdad's text.

--- 2015-09-28 ms.tex
@@
 This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
-In Appendix \ref{sec:AppendixB}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) is probably more realistic.
+In Appendix \ref{sec:AppendixA}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) -- unequal recoil energies -- is probably more realistic.
 
@@
 \section{Ionization Cascade}
-\label{sec:AppendixB}
+\label{sec:AppendixA}
 
@@
 Of course, $E_{\rm recoil}$ must be larger than $E_{\rm Rydberg}$ for this approximation to be meaningful.
-%This suggests that if the energetic electron ends up ionizing other atoms, it is more likely to put them right at the threshold of
+
+An objection to the above estimate is that the singularity in the $E_{\rm recoil} \rightarrow 0$ limit arises from the long range nature of Coulomb interaction which of course is absent in the real problem.
+Far away, the ionizing electron sees the dipole moment of the neutral atom.
+However, for energy transfer of order a Rydberg $\alpha/2a_0$ we can estimate the transfer momentum and see that it is larger than the inverse of the Bohr radius $a_0$.
+This implies that in this range the above estimate may actually be reliable. The transfer momentum is
+\begin{equation}
+q^2 =\frac{1}{4} m^2 \vrel^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2\vrel^2 \sin^2 \frac{\theta}{2}.
+\end{equation}
+Comparison with (\ref{eq:Erec}) shows
+\begin{equation}
+E_{\rm recoil} = \frac{q^2}{2m}.
+\ee
+Now set $E_{\rm recoil} \sim \alpha/a_0$ to get
+\be
+q \sim \sqrt{\frac{m\alpha}{a_0}}\sim \frac{1}{a_0}
+\ee
+where we used $a_0 = 1/\alpha m$.
 
 \section{Comparison with previous work}
-\label{sec:AppendixA}
+\label{sec:AppendixB}
 

### 2015-09-28 ms.tex
massive -> dense

@@
 When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
-Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a massive stellar wind.
+Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
 Given that magnetized planets interacting with stellar winds emit radio waves, such ``Red-Giant Hot Jupiters'' (RGHJs) may also be candidate radio emitters.

### 2015-09-28 ms.tex
Fixes LaTeX errors in appendix
Remove '(RGB)' from abstract.

@@
 %%%
-When planet-hosting stars evolve off the main sequence and go through the red-giant branch (RGB), the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
+When planet-hosting stars evolve off the main sequence and go through the red-giant branch, the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
 Accordingly, planetary companions around them at orbital distances of a few AU, if they exist, will be heated up to the level of canonical hot Jupiters and also subjected to a dense stellar wind.
@@
 \begin{equation}
-q^2 =\frac{1}{4} m^2 \vrel^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2\vrel^2 \sin^2 \frac{\theta}{2}.
+q^2 =\frac{1}{4} m^2 v_{\rm rel}^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2v_{\rm rel}^2 \sin^2 \frac{\theta}{2}.
 \end{equation}
@@
 E_{\rm recoil} = \frac{q^2}{2m}.
-\ee
+\end{equation}
 Now set $E_{\rm recoil} \sim \alpha/a_0$ to get
-\be
+\begin{equation}
 q \sim \sqrt{\frac{m\alpha}{a_0}}\sim \frac{1}{a_0}
-\ee
+\end{equation}
 where we used $a_0 = 1/\alpha m$.

### 2015-09-28 ms.tex
minor rephrasing in intro

@@
 When stars less than $\sim$8~$M_\sun$ evolve off the main sequence, they evolve through the red-giant branch (RGB) and the asymptotic-giant branch (AGB) phases where their radii and luminosities increase by orders of magnitude.
-Jovian planets in orbit around such stars can migrate inward or outward due to the interplay between tidal torques and mass-loss process on the post-main sequence \citep{nordhaus_et_al2010,nordhaus+spiegel2013}.
+Jovian planets in orbit around such stars can migrate inward or outward due to the interplay between tidal torques and mass-loss process on the post-main sequence \citep{nordhaus_et_al2010, spiegel2012, mustill+villaver2012, nordhaus+spiegel2013}.
 During this time, such planets can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
@@
 
-In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit strong X-rays, thereby ionizing the hydrogen atoms around the planet.
+In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
 The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
-Thus, by extrapolating the ``radiometric Bode's law'', we provide more optimistic estimates for highly evolved stars compared to the previous result.
+Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates for highly evolved stars compared to the previous result.
 We also consider the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 

### 2015-09-28 ms.tex
updates spaces around dashes in section 2

@@
 First, we introduce our framework to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
-Then, two ingredients for the framework--the strength of planetary magnetic field and the property of the stellar wind---will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
+Then, two ingredients for the framework --- the strength of planetary magnetic field and the property of the stellar wind --- will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
 In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind.

### 2015-09-28 ms.tex
property -> properties

--- 2015-09-28 ms.tex
@@
 First, we introduce our framework to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
-Then, two ingredients for the framework--the strength of planetary magnetic field and the property of the stellar wind---will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
+Then, two ingredients for the framework --- the strength of planetary magnetic field and the properties of the stellar wind --- will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
 In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind.

### 2015-09-28 ms.tex
adds word 'the'
adjusts -- to ---

@@
 
-In principle, photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times.
+In principle, photons with energy $E_{\rm photon}$ have the potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times.
 To take this into account, we consider two limiting possibilities:
@@
 This limit leads to a value for $N_i$ that is not dramatically different from that of limit (\emph{ii}).
-In Appendix \ref{sec:AppendixA}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) -- unequal recoil energies -- is probably more realistic.
+In Appendix \ref{sec:AppendixA}, we estimate the Bhabha(/M{\o}ller) scattering cross section and show that cascade (\emph{ii}) --- unequal recoil energies --- is probably more realistic.
 

### 2015-09-28 ms.tex
Adds Greg Novak to acknowledgments
minor changes to cascade section

@@
 
-Scenario (\emph{i}) implies a cascade where an electron with energy $E_{\rm in}$ ionizes an atom producing two electrons (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each.
+Scenario (\emph{i}) implies a cascade where an electron with energy $E_{\rm in}$ ionizes an atom, producing two electrons (an ionizing electron plus the released electron) with energy $ ( E_{\rm in} - E_{\rm Rydberg} ) /2 $ for each.
 For example, in an idealized case with $M_p = 10 M_{\rm J}$, $k_B T_{\rm acc} \sim 172\,{\rm eV} \sim 12 \, E_{\rm Rydberg}$, a photoionization could produce an electron with energy of $(12-1) = 11 E_{\rm Rydberg} $, then a second ionization by that electron would produce two photons with energy of $(11-1)/2 = 5 E_{\rm Rydberg}$, and the third ionization by these two photons would produce four photons with energy of $(5-1)/2 = 2 E_{\rm Rydberg}$, etc.
@@
   \nonumber N_i & = & \frac{1 - \xi^k}{1 - \xi} \\
-  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{\nu - 1} \, ,
+  \label{eq:N_i2}  & = & 1 + \xi + \xi^2 + \cdots + \xi^{k - 1} \, ,
 \end{eqnarray}
@@
 We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.
+We thank Greg Novak for helpful conversations.
 NM acknowledges support from [???]. 

### 2015-09-28 ms.tex
rewritten sentence about \xi=0

@@
 %%%%%%%%%
-The solid lines show the ionization fraction of $\xi=0 \; (N_i = 1)$ (no additional ionization by electrons) and dashed lines show that of $N_i=6$.
+The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0 \; (N_i = 1)$) and dashed lines show that of $N_i=6$.
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.

### 2015-09-28 ms.tex
removes extraneous ()

--- 2015-09-28 ms.tex
@@
 %%%%%%%%%
-The solid lines show the ionization fraction of $\xi=0 \; (N_i = 1)$ (no additional ionization by electrons) and dashed lines show that of $N_i=6$.
+The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and dashed lines show that of $N_i=6$.
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.

### 2015-09-28 ms.tex
'of' -> 'corresponding to'

--- 2015-09-28 ms.tex
@@
 %%%%%%%%%
-The solid lines show the ionization fraction of $\xi=0 \; (N_i = 1)$ (no additional ionization by electrons) and dashed lines show that of $N_i=6$.
+The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and dashed lines show that corresponding to $N_i=6$.
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.

### 2015-09-28 ms.tex
removes extra ()

@@
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
-While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation (\ref{eq:sigma_H})) leads to the decrease in the radius of ionized region.
+While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region.
 Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.

### 2015-09-28 ms.tex
removes extra 'still'
adds ionization limit comment to stromgren section

@@
 While the photon rate is large for larger planets, the strong dependence of cross section on the photon energy (equation \ref{eq:sigma_H}) leads to the decrease in the radius of ionized region.
-Nevertheless, still, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
+Nevertheless, substantial amount of ionized plasmas are expected around the magnetic stand-off radius.
 
@@
 The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
-Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``a'' in equation (13) of \citet{stromgren1939} is not small).
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citet{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
 The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.

### 2015-09-28 ms.tex
citet -> citealt

@@
 The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
-Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citet{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citealt{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
 The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.

### 2015-09-28 ms.tex
adds word 'nearly'

@@
 As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
-This implies that the stellar wind particles represented by (equation~(\ref{eq:n})) are fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
+This implies that the stellar wind particles represented by (equation~\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
 

### 2015-09-28 ms.tex
rewritten sentence about stellar wind opacity
hashed -> hatched

@@
 Since $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^\oplus $, the radio emission will not be hindered by Earth's ionosphere cut-off. 
-One the other hand, it may be interfered by the plasma cut-off of the stellar wind particles around the planet. 
+On the other hand, it may experience opacity due to the plasma of the stellar wind particles around the planet.
 The maximum plasma frequency along the line of sight, $\nu_{\rm plasma}^{\rm los}$, corresponds to that in the vicinity of the planet, if the planet is on the near side of its star to the Earth.
@@
 The systems are located at 100 pc away.
-The doubly hashed regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
-The hashed regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
+The doubly hatched regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
+The hatched regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
 }
@@
 Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
-The doubly hashed regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
+The doubly hatched regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
 In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.

### 2015-09-28 ms.tex
1 sentence per line
criteria -> criterion

@@
 Instead, it usually exits at lower frequencies.
-Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission.
+Here, we also consider one more criterion, $\nu_{\rm cyc,\,max} > 10 \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission.
 In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 

### 2015-09-28 ms.tex
a AGB -> an AGB
adds word 'to'

@@
 For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
-On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.
+On the other hand, for an AGB-star system, only very massive planets at distant orbits are marginally detectable.
 
@@
 In this section, we discuss the observability of the estimated radio emission. 
-An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult identify the planetary contribution.
+An obvious potential obstacle is the intrinsic radio emission from host red-giant stars themselves; if they are bright relative to the radio flux from the planets, it is significantly more difficult to identify the planetary contribution.
 We will see in Section \ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 

### 2015-09-28 ms.tex
moves \geq next to 5

@@
 Almost all observations have been carried out 
-at frequencies $\geq 5~\rm GHz$, 
+at frequencies $\geq$5~GHz, 
 probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.

### 2015-09-28 ms.tex
adds xkcd to acknowledgments
'the previous paper' -> 'Ignace 2010'

@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike the previous paper, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Unlike \citet{ignace2010}, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
@@
 We thank Greg Novak for helpful conversations.
+We thank Jake VanderPlas for developing the XKCD-style plotting package for matplotlib, and acknowledge its use.
 NM acknowledges support from [???]. 

### 2015-09-28 ms.tex
adds word 'photons

@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike \citet{ignace2010}, we consider that UV/X-ray from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 

### 2015-09-28 ms.tex
fixes tense in first paragraph of conclusion

@@
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 
-We found that the intrinsic brightness of radio emission from RGHJs are supposedly comparable to canonical hot Jupiters in close-in orbits around main-sequence stars, and $>100$ times brighter than distant Jupiter-twins around main-sequence stars.
+We find that the intrinsic brightness of radio emission from RGHJs could be comparable to or greater than that of canonical hot Jupiters in close-in orbits around main-sequence stars, and $>100$ times brighter than distant Jupiter-twins around main-sequence stars.
 This implies that they can be searched for 10 times further away, or in 1000 times larger volume.

### 2015-09-28 ms.tex
minor edits in Section 1

@@
 It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
-Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the density of surrounding plasmas, e.g.
+Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
-Observations of radio emission from Solar System planets imply an empirical relation that the radio intensity is proportional to the input solar wind flux going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984}.
+Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}.
 Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
@@
 
-In Section \ref{s:assumptions}, we introduce the framework to obtain the frequency of radio emission and the planetary radio emission, and describe our models for the stellar wind and planetary magnetosphere.
-Section \ref{s:result} presents an estimate of the spectral radio intensity of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
+In Section \ref{s:assumptions}, we introduce the framework to obtain the frequency and the flux of planetary auroral radio emission, and describe our models for the stellar wind and planetary magnetosphere.
+Section \ref{s:result} presents the estimates of the spectral radio flux of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.
 Section \ref{s:observability} gives the prospects for the signal detection with the current/future instruments. 

### 2015-09-28 ms.tex
minor edits in Section 2

@@
 
-In this section, we describe our scheme to estimate radio emission from RGHJs. 
-First, we introduce our framework to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
+In this section, we describe our framework to estimate radio emission from RGHJs. 
+First, we introduce our scheme to compute the frequency and intensity of planetary radio emission in Section \ref{ss:model_frequency} and Section \ref{ss:model_intensity}, respectively. 
 Then, two ingredients for the framework --- the strength of planetary magnetic field and the properties of the stellar wind --- will be presented in Section \ref{ss:magneticfield} and Section \ref{ss:stellarwind}, respectively.
-In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the planetary magnetosphere and the stellar wind.
+In Section \ref{ss:ionization}, we consider the ionization around the planets, which is a crucial factor to determine the efficiency of the interaction between the planetary magnetosphere and the stellar wind.
 
@@
 %%%%%%%%%%
-where $B$ is the strength of magnetic field at the planetary surface, $e$ and $m_e$ are the charge and mass of the electron, respectively, and $c$ is the speed of light.
-
-Radio emission from the planet is observable from ground only when the frequencies of the radio emission are larger than the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$:
+where $B$ is the strength of magnetic field at the planetary surface, $e$ and $m_e$ are the charge and mass of electrons, respectively, and $c$ is the speed of light.
+
+Radio emission from the planet is observable from the ground only when the frequencies of the radio emission are larger than both the plasma frequency of Earth's ionosphere $\nu_{\rm plasma}^\oplus$ and the maximum plasma frequency along the line of sight $\nu_{\rm plasma}^{\rm los}$:
 %%%%%%%%%% 
@@
 %%%
-where $P_{\rm radio}$ is the energy that is deposited as radio emission of considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.
+where $P_{\rm radio}$ is the energy that is deposited as auroral radio emission of the considered frequency range, $\Omega$ is the solid angle of the emission, $l$ is the distance between the target and the Earth, and $\Delta \nu$ is frequency bandwidth.
 
 We estimate the radio emission of exoplanets, $P_{\rm radio}$, simply by scaling the Jovian auroral radio emission, $P_{\rm radio,\,J}$, with the input energy from stellar wind, in the same manner as \citet{griesmeier2005,griesmeier2007a,griesmeier2007b}.
-The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984}, i.e.,
+The scaling is based on the empirical/apparent good correlation between the radio emission intensity of Solar System planets and the input kinetic energy, $P_{\rm inp,\,k}$, or the magnetic energy of the solar wind, $P_{\rm inp,\,m}$, \citep[``radiometric Bode's law''; ][]{desch+kaiser1984,zarka2001}, i.e.,
 %%%
@@
 %%%
-where $n$ is the number density of the stellar wind, $v$ is the relative velocity of the stellar wind particles and the planet, $ B_{\star\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point.
-It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both. 
+where $n$ is the number density of the stellar wind, $v$ is the relative velocity of the stellar wind particles to the planet, $ B_{\star\bot }$ is the interstellar magnetic field perpendicular to the stellar wind flow, and $r_{\rm mag}$ is the radius of the magnetic stand-off point.
+It is not clear from the observations of the Solar System planets which is the fundamental one, the correlation to the input kinetic energy, that to the magnetic energy, or both \citep{zarka2001}. 
 In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$ and consider the possible effects of massive stellar wind.
@@
 \begin{equation}
-r_{\rm mag} \sim R_p \left( 8\pi m_p n \right) ^{-1/6} v^{-1/3} B^{-1/3} \label{eq:stand-off-radius} 
+r_{\rm mag} \sim R_p \left( 8\pi m_p n \right) ^{-1/6} v^{-1/3} B^{1/3} \label{eq:stand-off-radius} 
 \end{equation}
@@
 which are summarized and compared with numerical simulations in \citet{christensen2010}. 
-We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields.
-This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars:
+We employ the scaling law proposed in \citet{christensen_et_al2009}, which has already been used in \citet{reiners2010} to explore the evolution of planetary magnetic fields:
 %%%%%%%%%%
@@
 where $B_{\rm dynamo}$ is the mean magnetic field in the dynamo region, $f_{\rm ohm}$ is the ratio of ohmic dissipation to the total dissipation, $\rho_{\rm dynamo} $ is the mean density in the dynamo region, $F$ is an efficiency factor of order unity, and $q_o$ is the convected flux at the outer boundary of the dynamo region \citep[see][for the comprehensive description]{christensen_et_al2009}.
+This scaling law is based on the assumption that the ohmic dissipation energy is a fraction of the available convected energy and was found to be in good agreement with the numerical experiments over a wide parameter space and with known objects from the Earth to stars.
 Here, $f_{\rm ohm}$ and $F$ are assumed to be constant for the bodies considered in this paper. 
@@
 
-In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need models of the internal planetary structure. 
+In order to evaluate $\rho _{\rm dynamo}$ and $q_o$, we need a model of the internal planetary structure. 
 We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,{\rm J}}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p,{\rm J}} < M_p < 10M_{p, {\rm J}}$ (with core mass less than 10\%) converge to $0.8 R_{p,{\rm J}} < R_p < 1.2R_{p, {\rm J}}$ within 1 Gyr \citep{fortney2007}.
@@
 
-The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the planetary orbital velocity, and the infall velocity (i.e., the velocity due to falling in the planet's gravitional field).
-While $v_{\rm sw}$ is $\sim$30~km/s, the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$), and the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$, depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$).
+The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the infall velocity (i.e., the acceleration due to planet's gravitational field), and the planetary orbital velocity.
+While $v_{\rm sw}$ is $\sim$30~km/s, the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$ depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$), and the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$).
 In the next section, we simply consider
@@
 We suppose a state where the ionization and recombination rates are in equilibrium. 
-Denoting the ionization fraction by $x$, the equilibrium state at a distance $r$ from the planet may be approximately represented by 
+Denoting the ionization fraction by $x$, the equilibrium state at a distance $r$ from the planet may be represented by 
 %%%%%%%%%
@@
 
-For the accretion onto large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity.
+For the accretion onto large planets, however, the characteristic photon energy is so high that the released energetic electrons may also ionize other atoms in the vicinity.
 The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$ \citep{fite1958}, which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
@@
    \plotoneh{ionizationfraction.pdf}
-   \caption{Profile of ionization fraction due to X-ray from planetary accretion, measured from the surface of the planet.
+   \caption{Profile of ionization fraction measured from the surface of the planet, due to UV/X-ray from the accretion of stellar wind onto the planet.
 Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $N_i=6$.
@@
 The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
-Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citealt{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citealt{stromgren1939} is not small) on account of UV/X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
 The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.

### 2015-09-28 ms.tex
minor edits in Section 3

@@
 
-Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core, the estimated strength of planetary magnetic field $B$ and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age.
+Figure \ref{fig:planetaryB} shows the computed radius ($r_c$) and average density ($\rho_c$) of the dynamo region as function of planetary mass, as well as the heat flux at the outer boundary of the core ($q_o$), the estimated strength of planetary magnetic field ($B$) and the corresponding cyclotron frequency ($\nu_{\rm cyc}$) as functions of planetary mass and the age.
 Substituting equation (\ref{eq:burrowsHeatFlux}) into equation (\ref{eq:Bscaling2}) and given that $r_{\rm dynamo} $ does not change significantly, the magnetic field is approximately:
@@
 In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
-LOFAR, HERA, SKA, and potential upgrades to the VLA.
+LOFAR, HERA, SKA, and potential upgrades to the VLA (see Section \ref{ss:detectability}).
 
@@
 \end{eqnarray}
-We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$.
-Therefore, for Jupiter-mass planets, only distant ones at $\sim 5 $ AU or further, will emit the radio waves from the system.
+We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$. Therefore, for Jupiter-mass planets, only distant ones $\gtrsim 5 $  may emit the radio waves from the system. 
 The detectable parameter space will be presented in more detail in the next section.
@@
 %%%
+where we employ $r_{\rm mag,\,J} = 84~R_{\rm J}$ \citep{joy2002}.
 
@@
 
-We may compare radio emission power of canonical hot Jupiters set at 0.05 AU  and that of RGHJs at 5 AU.
+We may compare radio emission power of RGHJs at 5 AU with that of canonical hot Jupiters set at 0.05 AU.
 Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
@@
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for RGB stars' companions)} \notag \\
-&\approx & 14000 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
+&\approx & 14000 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \notag \\
 && \times \left( \frac{\dot M_\star}{10^{-5} M_{\odot}{\rm /yr}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3}  \\
@@
 %%%
-Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, due to the uncertainty of the magnetic field of tidally-locked planets. 
+Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, considering the uncertainty of the magnetic field of tidally-locked planets. 
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
 
-Combining the expressions above, we find that the radio spectral flux density observed at the Earth is:
+Using the expressions above, we find that the radio spectral flux density observed at the Earth is:
 %%%
@@
 Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
-Compared with the distant Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than 2 orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
-This compensates the small population of evolved stars at least partially.
+Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than 2 orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
+This compensates the small population of evolved stars at least partly.
 

### 2015-09-28 ms.tex
description about the comparison with Ignace (2010) is revised

@@
 
-Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$.
-This originates from the different scaling laws for the planetary magnetic field and that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind.
+Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial parameters and full ionization.
+This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
 

### 2015-09-28 ms.tex
slight rephrasing in the first paragraph of Section 4

@@
 
-Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial parameters and full ionization.
+Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
 This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
@@
 We will see in Section \ref{ss:RGradio} that radio flux from the planets will probably be larger in a certain parameter range. 
-Then, we estimate the radio emission of Jupiter-twin around known M giants in Section \ref{ss:actualMgiants}. 
-In Section \ref{ss:detectability}, we estimate the sensitivities and limitations of several current and future
+Then, in Section \ref{ss:actualMgiants}, we estimate the radio flux from hypothetical Jupiter-like planets around known M giants. 
+In Section \ref{ss:detectability}, we examine the sensitivities and limitations of several current and future
 radio instruments at relevant frequencies.

### 2015-09-28 ms.tex
minor edits in section 4.2

@@
 
-In order to examine the potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
+In order to examine the realistic potential to detect radio emission of RGHJs with the current and near-future instruments, we estimate the possible radio emission from known red giants assuming that they have planetary companions.
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature.
-For each red giant, the mass-loss rate is estimated by the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
+For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
 %%%
@@
 %%%
-where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$, $\tilde R = R_{\star }/R_{\odot }$, $\tilde M = M_{\star }/M_{\odot }$, and $g$ is the surface gravity. 
+where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$ is the stellar luminosity, $\tilde R = R_{\star }/R_{\odot }$ is the stellar radius, $\tilde M = M_{\star }/M_{\odot }$ is the stellar mass, and $g$ is the surface gravity.
 The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
-Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while the those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
+Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
 For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
-$10~M_{\rm J}$ planets at $\sim 1$ AU will be detectable out to $\sim 200$~pc.
+$10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
 

### 2015-09-28 ms.tex
minor edits in section 4.3

@@
 
-The noise estimates shown in Table \ref{tab:sens}, together with Figure \ref{fig:observability}, indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
+The noise estimates shown in Table \ref{tab:sens} indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
 %On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
 %LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
-On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within one day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU and at $\sim$5~AU within $\sim $200~pc and $\sim $100~pc from Earth, respectively.
+On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within half a day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU within $\sim $200~pc, or those at $\sim$5~AU within $\sim $100~pc.
 VLA-LOBO could also work for a few nearby systems.

### 2015-09-28 ms.tex
planetary companions => planets

@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planetary companion ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planets ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 

### 2015-09-28 ms.tex
description about the observability in the second last paragraph is modified

@@
 
-The radio flux from a system with an exoplanet at 5 AU at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy.
-Such signals would be detectable with SKA within a day. 
+The radio flux from a system with a Jovian exoplanet at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy.
+Such signals would be detectable with SKA within half a day. 
 For a few nearby systems, VLA-LOBO would also work with a reasonable integration time.

### 2015-09-28 ms.tex
minor edits in Appendix B

@@
 %\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ \nu_{\rm cyc}$ \\ \hline
-\#8 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
- & this work & & \\ \hline
+& \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 
+\#8  & this work & & \\ \hline
 \end{tabular}
@@
 
-If we use the assumptions that $R_p \sim R_J\;\;(const.)$, $\rho _c\sim R_p\sim const.$, and $\sigma = const.$, then the assumptions are reduced to:
+If we adopt the assumptions that $R_p \sim R_J\;\;(const.)$, $\rho _c\sim R_p\sim const.$, and $\sigma = const.$, then the scaling laws of the auroral radio power are reduced to:
 %%%%%%%%%
@@
 %
-\mbox{[\#8]} \; P_{\rm rad} &\sim & ?
-\times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_{\rm J}} \right)^{0.69}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.288}  \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
+\mbox{[\#8]} \; P_{\rm rad} &\sim & 2.1 \times 10^{11} \,{\rm W}\, \left( \frac{M_p}{M_{\rm J}} \right)^{0.70}  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-0.29}  \left( \frac{a}{a_{\rm J}} \right)^{-4/3} \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \, \\
 \end{eqnarray}

### 2015-09-28 ms.tex
caption for figure 2 is revised

@@
    \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass.
-Lower panels: Planetary magnetic field as a function of age for different planetary mass, based on the scaling of magnetic field of \citet{christensen2010} and the evolution of luminosity of \citet{burrows_et_al2001}.}
+Lower panels: evolutions of heat flux at the outer boundary, planetary magnetic field, and maximum cyclotron frequency, for planets with varying masses ($M_{\rm J}$: blue, $5M_{\rm J}$: green, and $10M_{\rm J}$: red).
+}
   \label{fig:planetaryB}

### 2015-09-28 ms.tex
caption for figure 3 is revised

@@
 	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
-   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
+   \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
 The systems are located at 100 pc away.
-The doubly hatched regions show the parameter space where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
-The hatched regions with vertical lines show the parameter space where the frequencies of bulk radio emission, estimated as $\sim 0.1 \nu_{\rm cyc}$, is below $\nu_{\rm plasma}^{\rm los}$, i.e., the large part of the emission would not be able to get out of the system.
-}
+The doubly hatched regions show the parameter spaces where the planetary radio emission would not be observable at all because the maximum frequency of the emission (cyclotron frequency at the planetary surface, $\nu_{\rm cyc}$) is below the plasma frequency cut-off, $\nu_{\rm plasma}^{\rm los}$.
+The regions hatched with vertical lines show the parameter spaces where the frequencies of bulk radio emission is below $\nu_{\rm plasma}^{\rm los}$, i.e., $\nu_{\rm plasma}^{\rm los} > 0.1 \nu_{\rm cyc}$)}
   \label{fig:radio}

### 2015-09-28 ms.tex
caption for figure 4 is revised
caption for figure 5 is revised

@@
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
-The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. figure 8 of \citet{zarka_et_al2004} and figure 2 of \citet{griesmeier2007a}; contribution from Io is not shown here.
+The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; contribution from Io-DAM is not shown here.
 The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
@@
    \plotoneh{radio_M-RG_10Mp.pdf}
-   \caption{Radio emission from existing M-type red giants with a hypothetical planetary companion of 1$M_{\rm J}$ (upper panel) and 10$M_{\rm J}$ (lower panel) at 1~AU (blue) and 5~AU (black).
+   \caption{Radio flux from hypothetical RGHJs of 1$M_{\rm J}$ (upper panel) and 10$M_{\rm J}$ (lower panel) at 1~AU (blue) and 5~AU (black).
 Cross symbols indicate that the radio emission is not observable because cyclotron frequency is less than plasma density around the planet. }

### 2015-09-28 ms.tex
1 sentence per line
UV/X-ray -> X-ray before 'more weakly'

@@
      The vertical arrows show the Str\"omgren radius estimated simply by equation (\ref{eq:stromgren}).
-The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$, obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.
-}
+     The dotted vertical lines indicate the location of the magnetic stand-off radii, $r_{\rm mag}$, obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below. }
   \label{fig:ionizationfraction}
@@
 The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
-Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citealt{stromgren1939} is not small) on account of UV/X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
+Note, however, that unlike the frequently-demonstrated photoionization problem around O/B-type stars, in the situation of our interest, the Str\"omgren radius is not a sharp edge of ionization anymore, due to smaller source rate and smaller cross section (in this case parameter ``$a$'' in equation (13) of \citealt{stromgren1939} is not small) on account of X-ray photons interacting more weakly with neutral hydrogen than UV photons near the ionization limit.
 The Str\"omgren radii are indicated by vertical arrows in Figure \ref{fig:ionizationfraction}.

### 2015-09-28 ms.tex
value -> spectral flux density

@@
 Thus, RGHJs are expected to be intrinsically as bright as the closest hot Jupiters. 
-Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than 2 orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
+Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than two orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
 This compensates the small population of evolved stars at least partly.
 
-Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
-This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
+Equation (\ref{eq:F_nu_RGHJ}) gives a spectral flux density that 1--2 orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
+This is primarly because their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
 

### 2015-09-28 ms.tex
fairly -> mostly

@@
 In this paper, we estimate the radio brightness of distant ``hot Jupiters'' around evolved stars (RGHJ) on the assumption of the simple empirical correlation between planetary radio emission and the input kinetic energy from the stellar wind.
-Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planets ionizes the stellar wind in the vicinity of planets, which would otherwise be fairly neutral. 
+Unlike \citet{ignace2010}, we consider that UV/X-ray photons from accretion onto the planets ionizes the stellar wind in the vicinity of planets, which would otherwise be mostly neutral for a cool star's wind.
 Based on such a picture, the massive stellar wind of a red giant or a AGB star would interact with the planetary magnetic field and input kinetic energy into the magnetosphere of a RGHJ. 

### 2015-09-28 ms.tex
some minor typo corrections

@@
 
-Based on equations (\ref{eq:scale_Mdot}), the number density of the stellar wind (equation (\ref{eq:n})) is normalized as follows:
+Based on equation (\ref{eq:scale_Mdot}), the number density of the stellar wind (equation (\ref{eq:n})) is normalized as follows:
 %%%%%%%%%% 
@@
 \begin{equation}
-\frac{v}{v_{\odot}} \sim 10^{-1} \, . \label{eq:scale_v}
-\end{equation}
-%%%%%%%%%%
-as a fiducial value for normalization.
+\frac{v}{v_{\odot}} \sim 10^{-1} \, \label{eq:scale_v}
+\end{equation}
+%%%%%%%%%%
+a fiducial value for the normalization.
 
@@
 
-As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind are lowered down to order of $\sim 10^{-3}$ \citep{drake1987}.
-Since only charged particles interact with planetary magnetic field, this suggests the inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
-However, at this stage, the velocity of stellar wind becomes slower than the escape velocity of planetary companion and hence the stellar wind particles are expected to accrete onto the planets. 
+As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind is lowered down to order of $\sim 10^{-3}$ \citep{drake1987}.
+Since only charged particles interact with planetary magnetic field, this suggests inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
+However, at this stage, the velocity of the stellar wind becomes slower than the escape velocity of the planetary companion and hence the stellar wind particles are expected to accrete onto the planets.
 \citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ as follows: 
@@
 The accretion onto planets, therefore, leads to emission of UV/X-ray radiation 
-whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of Hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
+whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
 Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
@@
 %%%%%%%%%
-where $\dot N_X$ is the source rate of the photons that can ionize the hydrogen, 
+where $\dot N_X$ is the source rate of the photons that can ionize hydrogen, 
 $\sigma _H$ is the cross section of H atoms for X-ray \citep{verner1996}: 
@@
 
-The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, 
+The source rate is obtained by counting the number of photons with energy exceeding the ionization energy of hydrogen ($E_{\rm Rydberg} = 13.6$~eV, 
 or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
@@
 
-In principle, photons with energy $E_{\rm photon}$ have the potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times.
-To take this into account, we consider two limiting possibilities:
+In principle, photons with energy $E_{\rm photon}$ have the potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ hydrogen atoms.
+To account for this, we consider two limiting possibilities:
 After an ionizing collision, the energy can (\emph{i}) be split evenly between the two electrons, or it can (\emph{ii}) go entirely into the kinetic energy of one electron and not at all into that of the other (of course, any split in between these extremes is possible, too).
@@
 
-In reality, not all released electrons may be able to proceed the next ionization.
-If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}), is
+In reality, not all released electrons result in further ionization interactions.
+If $\xi$ represents the fraction of released electrons that proceed to the next ionization, then the number of ionized atoms $N_i$ released through this cascade (\emph{i}) is
 %%%%%%%%%
@@
 
-The extent of ionized region may also be roughly estimated by Str\"omgren radius \citep{stromgren1939}: 
+The extent of the ionized region may also be roughly estimated as the Str\"omgren radius \citep{stromgren1939}: 
 %%%%%%%%%
@@
 %%%%%%%%%
-for a planet around a red giants at 5~AU. 
+for a planet 5~AU from a red giant host. 
 The Str\"omgren radius for $1M_{\rm J} $ and for $10M_{\rm J}$ are also indicated in Figure \ref{fig:ionizationfraction}.
@@
 As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
-This implies that the stellar wind particles represented by (equation~\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
+This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
 
@@
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
-\end{eqnarray}
-%%%
-Here we normalized the strength of magnetic field of canonical hot jupiters with $B_J$, considering the uncertainty of the magnetic field of tidally-locked planets. 
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot Jupiters)} \notag 
+\end{eqnarray}
+%%%
+Here we normalized the strength of magnetic field of canonical hot Jupiters with $B_J$, considering the uncertainty of the magnetic field of tidally-locked planets. 
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
@@
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu} \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for Jupiter-twin)} \notag \\
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for a Jupiter-twin)} \notag \\
 %%%
@@
 && \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:F_nu_RGHJs} \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot jupiters)} \notag 
+&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot Jupiters)} \notag 
 \end{eqnarray}

### 2015-09-28 ms.tex
word massaging regarding possible LOBO upgrade

@@
 
-The radio flux from a system with a Jovian exoplanet at a distance of 100 pc would be typically on the order of $\sim 10 \mu $Jy.
+The radio flux from a system with a Jovian exoplanet at a distance of 100~pc would typically be on the order of $\sim 10 \mu $Jy.
 Such signals would be detectable with SKA within half a day. 
-For a few nearby systems, VLA-LOBO would also work with a reasonable integration time.
+For a few nearby systems, a possible upgrade to the VLA such as LOBO would also provide reasonable integration times and resolving power.
 In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confused sources in the same resolution element.

### 2015-09-28 ms.tex
not sure how to clarify last paragraph

@@
 This can compensate the rareness of the evolved stars at least partly.
-Thus, RGHJs will serve as reasonable targets for future search for exoplanetary radio emission.
+Thus, RGHJs will serve as reasonable targets in future searches for exoplanetary radio emission.
 
@@
 For a few nearby systems, a possible upgrade to the VLA such as LOBO would also provide reasonable integration times and resolving power.
-In both cases, it is critical to consider polarization and/or time variability of planetary radio flux, in order to separate it from confused sources in the same resolution element.
-
-Radio emission can be follow-up observations of known RGHJs or may also be used as a probe to discover them, given the lowered sensitivity of  radial velocity methods in detecting planetary companions.
-Once the planetary radio emission is detected, it will provide a unique approach to the planetary spin, magnetic field, presence of satellites, and potentially stellar wind properties.
+In both cases, it is critical to consider polarization and/or time variability of the planetary radio flux, in order to separate it from confused sources in the same resolution element.
+
+Finally, we note that this radio emission could studied through follow-up observations of known RGHJs or could be used as a tool for discovery, given the lowered sensitivity of radial velocity methods in detecting planetary companions.
+Once the planetary radio emission is detected, it will provide a unique approach for inferring the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.
 

### 2015-09-28 ms.tex
Edits to concluding paragraph.

@@
 
-Finally, we note that this radio emission could studied through follow-up observations of known RGHJs or could be used as a tool for discovery, given the lowered sensitivity of radial velocity methods in detecting planetary companions.
-Once the planetary radio emission is detected, it will provide a unique approach for inferring the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.
+Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, that traditional exoplanet-discovery methods (e.g., transit or RV) are not very sensitive to planets around RGB or AGB stars.
+Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.
 

### 2015-09-28 ms.tex
Split first paragraph into 2 and made slight edits.

@@
 It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
-Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
+xoplanets could similarly generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
+Excitingly, unlike traditional methods of discovering exoplanets in which the planetary signal is a tiny perturbation on light from the star, low-frequency planetary radio emission might be an arena where planets are vastly brighter than their stars.
+
 Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}.

### 2015-09-28 ms.tex
Slight changes to abstract and first paragraph of intro.

--- 2015-09-28 ms.tex
@@
 We estimate the spectral auroral radio intensity of RGHJs based on the empirical relation with the stellar wind as well as a proposed scaling for planetary magnetic fields. 
-We predict that RGHJs might be intrinsically as bright as canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.  
-The signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array. 
+RGHJs might be intrinsically as bright as or brighter than canonical hot Jupiters, and about 100 times brighter than equivalent objects around main-sequence stars.
+We examine the capabilities of low-frequency radio observatories to detect this emission and find that the signal from a RGHJ may be detectable at distances up to a few hundred parsecs with the Square Kilometer Array.
 \end{abstract}
@@
 It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
-Potentially, exoplanets can also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
+Exoplanets could similarly generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.
+This process could provide an avenue to discover planets that are otherwise extremely difficult to find --- those orbiting highly-evolved stars.
+Unlike traditional methods of discovering exoplanets, in which the planetary signal is a tiny perturbation on light from the star, low-frequency planetary radio emission might be an arena where planets are vastly brighter than their stars.
+This paper is an exploration of the surprisingly diverse range of physical processes that lead to this emission, and the prospects for detecting radio emission from planets around giant stars with current and near-future low-frequency radio observatories.
+
 Observations of radio emission from Solar System planets imply an empirical relation that the auroral radio power is proportional to the input solar wind energy going into each planetary magnetosphere, which is commonly referred to as the ``radiometric Bode's law'' \citep{desch+kaiser1984,zarka2001}.

### 2015-09-28 ms.tex
similarly -> also

@@
 It is well known that Jupiter emits radio waves from its auroral region due to the cyclotron-maser instability \citep[e.g.][]{wu1979,zarka1998}.
-Exoplanets could similarly generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
+Exoplanets could also generate radio emission through similar mechanisms, depending on their intrinsic magnetic fields and the properties of surrounding plasmas, e.g.
 stellar wind particles and particles from Io-like moons.

### 2015-09-28 ms.tex
changed the order of authors
radial velocity observations -> radial-velocity observations

@@
 %
+Mehrdad Mirbabayi\altaffilmark{4}
+%
 Nikku Madhusudhan\altaffilmark{11}
-%
-Mehrdad Mirbabayi\altaffilmark{4}
 }
@@
 Therefore, one possible strategy is to target known planetary systems.  
-One complication of the radial velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30$ [m/s].
-Therefore, there are some parameter spaces where current radial velocity observations have not been able to survey.
+One complication of the radial-velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30$ [m/s].
+Therefore, there are some parameter spaces where current radial-velocity observations have not been able to survey.
 For such a parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
@@
 Such information would be most useful if we could obtain constraints on planetary mass via e.g.
-radial velocity observations, because once both magnetic field strength and the planetary mass is constrained the proposed scaling law of planetary dynamo may be tested.
+radial-velocity observations, because once both magnetic field strength and the planetary mass is constrained the proposed scaling law of planetary dynamo may be tested.
 On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the stellar wind property at the planetary orbit.
@@
 
-Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, that traditional exoplanet-discovery methods (e.g., transit or RV) are not very sensitive to planets around RGB or AGB stars.
+Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
 Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.

### 2015-09-29 ms.tex
adds missing word 'given'

@@
 
-Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
+Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
 Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.

### 2015-09-29 ms.tex
text cleaned up (removed the parts which have been commented out)

@@
 
-\slugcomment{Submitted to ApJ, XX September 2015}
+%\slugcomment{Submitted to ApJ, XX September 2015}
 
@@
 \begin{abstract}
-%%%
 When planet-hosting stars evolve off the main sequence and go through the red-giant branch, the stars become orders of magnitudes more luminous and at the same time lose mass at much higher rates than their main-sequence counterparts.
@@
 \enddata
-%\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.}
 \tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
@@
 While this relation was fit to data taken in the 100-200~MHz range, the authors found it to be consistent with published measurements from 10-408~MHz.
-%The \Trx\ is the receiver noise temperature, which depends on the instruments and is described below.
 
@@
 The noise estimates shown in Table \ref{tab:sens} indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
-%On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, there is hope to detect radio emission from nearby systems with LOFAR-HBA or LOBO.
-%LOFAR-HBA has reasonable sensitivity to $M_p =10~M_{\rm J}$ planets at 5 AU around the few closest systems as well as those around further stars but orbiting closer to the stars. 
 On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within half a day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU within $\sim $200~pc, or those at $\sim$5~AU within $\sim $100~pc.
@@
 \#7 & & & $\mathcal{M} \propto \rho _c^{1/2} \omega r_c^{7/2}$ & & \\ \hline
-%\#8 & \citet{griesmeier2007a,griesmeier2007b} & $P_{\rm radio} \propto P_{\rm sw}$ & same as above & $2.1 \times 10^{11}$ & $ \nu_{\rm cyc}$ \\ \hline
 & \citet{reiners2010} & $P_{\rm radio} \propto P_{\rm sw}$ & $\mathcal{M} \propto M_p^{1/6} L^{1/3} R_p^{25/6}$ \\ 

### 2015-09-29 ms.tex
renamed figure 3

@@
 \begin{figure*}[bp]
-	\plotonesc{radio_emission_ChristensenAubert_multiplecriteria.pdf}
+	\plotonesc{radio_emission_mass_orbit.pdf}
    \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
@@
 
-\newpage
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Auri{\`e}re} {et~al.}(2015){Auri{\`e}re}, {Konstantinova-Antova},
+  {Charbonnel}, {Wade}, {Tsvetkova}, {Petit}, {Dintrans}, {Drake}, {Decressin},
+  {Lagarde}, {Donati}, {Roudier}, {Ligni{\`e}res}, {Schr{\"o}der},
+  {Landstreet}, {L{\`e}bre}, {Weiss}, \& {Zahn}}]{auriere2015}
+{Auri{\`e}re}, M., {Konstantinova-Antova}, R., {Charbonnel}, C., {et~al.} 2015,
+  \aap, 574, A90
+
+\bibitem[{{Bastian}(1990)}]{Bastian1990}
+{Bastian}, T.~S. 1990, \solphys, 130, 265
+
+\bibitem[{{Bastian} {et~al.}(2000){Bastian}, {Dulk}, \&
+  {Leblanc}}]{bastian2000}
+{Bastian}, T.~S., {Dulk}, G.~A., \& {Leblanc}, Y. 2000, \apj, 545, 1058
+
+\bibitem[{{Beasley} {et~al.}(1992){Beasley}, {Stewart}, \&
+  {Carter}}]{Beasley1992}
+{Beasley}, A.~J., {Stewart}, R.~T., \& {Carter}, B.~D. 1992, \mnras, 254, 1
+
+\bibitem[{{Burrows} {et~al.}(2001){Burrows}, {Hubbard}, {Lunine}, \&
+  {Liebert}}]{burrows_et_al2001}
+{Burrows}, A., {Hubbard}, W.~B., {Lunine}, J.~I., \& {Liebert}, J. 2001,
+  Reviews of Modern Physics, 73, 719
+
+\bibitem[{{Busse}(1976)}]{busse1976}
+{Busse}, F.~H. 1976, Physics of the Earth and Planetary Interiors, 12, 350
+
+\bibitem[{{Christensen}(2010)}]{christensen2010}
+{Christensen}, U.~R. 2010, \ssr, 152, 565
+
+\bibitem[{{Christensen} \& {Aubert}(2006)}]{christensen2006}
+{Christensen}, U.~R., \& {Aubert}, J. 2006, Geophysical Journal International,
+  166, 97
+
+\bibitem[{{Christensen} {et~al.}(2009){Christensen}, {Holzwarth}, \&
+  {Reiners}}]{christensen_et_al2009}
+{Christensen}, U.~R., {Holzwarth}, V., \& {Reiners}, A. 2009, \nat, 457, 167
+
+\bibitem[{{Condon}(1974)}]{Condon1974}
+{Condon}, J.~J. 1974, \apj, 188, 279
+
+\bibitem[{{Condon} \& {Ransom}(2016)}]{condon+ransom2016}
+{Condon}, J.~J., \& {Ransom}, S.~M. 2016, {Essential Radio Astronomy (Princeton
+  Series in Modern Observational Astronomy)} (Princeton Series in Modern
+  Observational Astronomy, Princeton University Press, 2016)
+
+\bibitem[{{Condon} {et~al.}(2012){Condon}, {Cotton}, {Fomalont}, {Kellermann},
+  {Miller}, {Perley}, {Scott}, {Vernstrom}, \& {Wall}}]{Condon2012}
+{Condon}, J.~J., {Cotton}, W.~D., {Fomalont}, E.~B., {et~al.} 2012, \apj, 758,
+  23
+
+\bibitem[{{Desch} \& {Kaiser}(1984)}]{desch+kaiser1984}
+{Desch}, M.~D., \& {Kaiser}, M.~L. 1984, \nat, 310, 755
+
+\bibitem[{{Dessler}(1983)}]{dessler1983}
+{Dessler}, A.~J. 1983, {Physics of the Jovian magnetosphere}
+
+\bibitem[{{Drake} \& {Linsky}(1986)}]{drake1986}
+{Drake}, S.~A., \& {Linsky}, J.~L. 1986, \aj, 91, 602
+
+\bibitem[{{Drake} {et~al.}(1987){Drake}, {Linsky}, \& {Elitzur}}]{drake1987}
+{Drake}, S.~A., {Linsky}, J.~L., \& {Elitzur}, M. 1987, \aj, 94, 1280
+
+\bibitem[{{Dumm} \& {Schild}(1998)}]{dumm1998}
+{Dumm}, T., \& {Schild}, H. 1998, New Astronomy, 3, 137
+
+\bibitem[{{Farrell} {et~al.}(1999){Farrell}, {Desch}, \& {Zarka}}]{farrell1999}
+{Farrell}, W.~M., {Desch}, M.~D., \& {Zarka}, P. 1999, \jgr, 104, 14025
+
+\bibitem[{{Fite} \& {Brackmann}(1958)}]{fite1958}
+{Fite}, W.~L., \& {Brackmann}, R.~T. 1958, Physical Review, 112, 1141
+
+\bibitem[{{Fix} \& {Spangler}(1976)}]{Fix1976}
+{Fix}, J.~D., \& {Spangler}, S.~R. 1976, \apj, 209, 503
+
+\bibitem[{{Fortney} {et~al.}(2007){Fortney}, {Marley}, \&
+  {Barnes}}]{fortney2007}
+{Fortney}, F.~J., {Marley}, M.~S., \& {Barnes}, J.~W. 2007, \apj, 659, 1661
+
+\bibitem[{{George} \& {Stevens}(2007)}]{george2007}
+{George}, S.~J., \& {Stevens}, I.~R. 2007, \mnras, 382, 455
+
+\bibitem[{{Grie{\ss}meier} {et~al.}(2005){Grie{\ss}meier}, {Motschmann},
+  {Mann}, \& {Rucker}}]{griesmeier2005}
+{Grie{\ss}meier}, J.-M., {Motschmann}, U., {Mann}, G., \& {Rucker}, H.~O. 2005,
+  \aap, 437, 717
+
+\bibitem[{{Grie{\ss}meier} {et~al.}(2007{\natexlab{a}}){Grie{\ss}meier},
+  {Preusse}, {Khodachenko}, {Motschmann}, {Mann}, \&
+  {Rucker}}]{griesmeier2007a}
+{Grie{\ss}meier}, J.-M., {Preusse}, S., {Khodachenko}, M., {et~al.}
+  2007{\natexlab{a}}, \planss, 55, 618
+
+\bibitem[{{Grie{\ss}meier} {et~al.}(2007{\natexlab{b}}){Grie{\ss}meier},
+  {Zarka}, \& {Spreeuw}}]{griesmeier2007b}
+{Grie{\ss}meier}, J.-M., {Zarka}, P., \& {Spreeuw}, H. 2007{\natexlab{b}},
+  \aap, 475, 359
+
+\bibitem[{{Grie{\ss}meier} {et~al.}(2004){Grie{\ss}meier}, {Stadelmann},
+  {Penz}, {Lammer}, {Selsis}, {Ribas}, {Guinan}, {Motschmann}, {Biernat}, \&
+  {Weiss}}]{griesmeier2004}
+{Grie{\ss}meier}, J.-M., {Stadelmann}, A., {Penz}, T., {et~al.} 2004, \aap,
+  425, 753
+
+\bibitem[{{Hallinan} {et~al.}(2013){Hallinan}, {Sirothia}, {Antonova},
+  {Ishwara-Chandra}, {Bourke}, {Doyle}, {Hartman}, \& {Golden}}]{hallinan2013}
+{Hallinan}, G., {Sirothia}, S.~K., {Antonova}, A., {et~al.} 2013, \apj, 762, 34
+
+\bibitem[{{Hicks} {et~al.}(2012){Hicks}, {Paravastu-Dalal}, {Stewart},
+  {Erickson}, {Ray}, {Kassim}, {Burns}, {Clarke}, {Schmitt}, {Craig},
+  {Hartman}, \& {Weiler}}]{Hicks2012}
+{Hicks}, B.~C., {Paravastu-Dalal}, N., {Stewart}, K.~P., {et~al.} 2012, \pasp,
+  124, 1090
+
+\bibitem[{{Hundhausen}(1997)}]{hundhausen1997}
+{Hundhausen}, A.~J. 1997, in Cosmic Winds and the Heliosphere, ed. J.~R.
+  {Jokipii}, C.~P. {Sonett}, \& M.~S. {Giampapa}, 259
+
+\bibitem[{{Ignace} {et~al.}(2010){Ignace}, {Giroux}, \&
+  {Luttermoser}}]{ignace2010}
+{Ignace}, R., {Giroux}, M.~L., \& {Luttermoser}, D.~G. 2010, \mnras, 402, 2609
+
+\bibitem[{{Joy} {et~al.}(2002){Joy}, {Kivelson}, {Walker}, {Khurana},
+  {Russell}, \& {Ogino}}]{joy2002}
+{Joy}, S.~P., {Kivelson}, M.~G., {Walker}, R.~J., {et~al.} 2002, Journal of
+  Geophysical Research (Space Physics), 107, 1309
+
+\bibitem[{{Kassim} {et~al.}(2015){Kassim}, {Clarke}, {Helmboldt}, {Ray},
+  {Lane}, {Polisensky}, {Mroczkowski}, {Deneva}, {Hicks}, {Hyman}, {Brisken},
+  {Perley}, {Owen}, \& {Intema}}]{Kassim2015IAU}
+{Kassim}, N.~E., {Clarke}, T., {Helmboldt}, J., {et~al.} 2015, IAU General
+  Assembly, 22, 53643
+
+\bibitem[{{Kiss} {et~al.}(1999){Kiss}, {Szatm{\'a}ry}, {Cadmus}, \&
+  {Mattei}}]{Kiss:1999aa}
+{Kiss}, L.~L., {Szatm{\'a}ry}, K., {Cadmus}, Jr., R.~R., \& {Mattei}, J.~A.
+  1999, \aap, 346, 542
+
+\bibitem[{{Knapp} {et~al.}(1995){Knapp}, {Bowers}, {Young}, \&
+  {Phillips}}]{Knapp1995}
+{Knapp}, G.~R., {Bowers}, P.~F., {Young}, K., \& {Phillips}, T.~G. 1995, \apj,
+  455, 293
+
+\bibitem[{{Konstantinova-Antova} {et~al.}(2010){Konstantinova-Antova},
+  {Auri{\`e}re}, {Charbonnel}, {Drake}, {Schr{\"o}der}, {Stateva}, {Alecian},
+  {Petit}, \& {Cabanac}}]{konstantinova2010}
+{Konstantinova-Antova}, R., {Auri{\`e}re}, M., {Charbonnel}, C., {et~al.} 2010,
+  \aap, 524, A57
+
+\bibitem[{{Konstantinova-Antova} {et~al.}(2013){Konstantinova-Antova},
+  {Aur{\'{\i}}ere}, {Charbonnel}, {Wade}, {Kolev}, {Antov}, {Tsvetkova},
+  {Schr{\"o}der}, {Drake}, {Petit}, {de Medeiros}, {L{\'e}bre}, {Zhilyaev},
+  {Verlyuk}, {Svyatogorov}, {Gershberg}, {Lovkaya}, {Bogdanovski}, {Stateva},
+  {Cabanac}, {Avgoloupis}, {Contadakis}, \& {Seiradakis}}]{konstantinova2013}
+{Konstantinova-Antova}, R., {Aur{\'{\i}}ere}, M., {Charbonnel}, C., {et~al.}
+  2013, Bulgarian Astronomical Journal, 19, 14
+
+\bibitem[{{Lazio} {et~al.}(2004){Lazio}, {Farrell}, {Dietrick}, {Greenlees},
+  {Hogan}, {Jones}, \& {Hennig}}]{lazio2004}
+{Lazio}, W., T.~J., {Farrell}, W.~M., {Dietrick}, J., {et~al.} 2004, \apj, 612,
+  511
+
+\bibitem[{{Lecavelier des Etangs} {et~al.}(2013){Lecavelier des Etangs},
+  {Sirothia}, {Gopal-Krishna}, \& {Zarka}}]{lecavelier_et_al2013}
+{Lecavelier des Etangs}, A., {Sirothia}, S.~K., {Gopal-Krishna}, \& {Zarka}, P.
+  2013, \aap, 552, A65
+
+\bibitem[{{Lim} {et~al.}(1998){Lim}, {Carilli}, {White}, {Beasley}, \&
+  {Marson}}]{Lim1998}
+{Lim}, J., {Carilli}, C.~L., {White}, S.~M., {Beasley}, A.~J., \& {Marson},
+  R.~G. 1998, \nat, 392, 575
+
+\bibitem[{{Marley} {et~al.}(2007){Marley}, {Fortney}, {Hubickyj},
+  {Bodenheimer}, \& {Lissauer}}]{marley2007}
+{Marley}, M.~S., {Fortney}, J.~J., {Hubickyj}, O., {Bodenheimer}, P., \&
+  {Lissauer}, J.~J. 2007, \apj, 655, 541
+
+\bibitem[{{Mizutani} {et~al.}(1992){Mizutani}, {Yamamoto}, \&
+  {Fujimura}}]{mizutani1992}
+{Mizutani}, H., {Yamamoto}, T., \& {Fujimura}, A. 1992, Advances in Space
+  Research, 12, 265
+
+\bibitem[{{Murphy} {et~al.}(2015){Murphy}, {Bell}, {Kaplan}, {Gaensler},
+  {Offringa}, {Lenc}, {Hurley-Walker}, {Bernardi}, {Bowman}, {Briggs},
+  {Cappallo}, {Corey}, {Deshpande}, {Emrich}, {Goeke}, {Greenhill}, {Hazelton},
+  {Hewitt}, {Johnston-Hollitt}, {Kasper}, {Kratzenberg}, {Lonsdale}, {Lynch},
+  {McWhirter}, {Mitchell}, {Morales}, {Morgan}, {Oberoi}, {Ord}, {Prabu},
+  {Rogers}, {Roshi}, {Shankar}, {Srivani}, {Subrahmanyan}, {Tingay},
+  {Waterson}, {Wayth}, {Webster}, {Whitney}, {Williams}, \&
+  {Williams}}]{murphy2015}
+{Murphy}, T., {Bell}, M.~E., {Kaplan}, D.~L., {et~al.} 2015, \mnras, 446, 2560
+
+\bibitem[{{Mustill} \& {Villaver}(2012)}]{mustill+villaver2012}
+{Mustill}, A.~J., \& {Villaver}, E. 2012, ArXiv e-prints, arXiv:1210.0328
+
+\bibitem[{{Newell} \& {Hjellming}(1982)}]{Newell1982}
+{Newell}, R.~T., \& {Hjellming}, R.~M. 1982, \apjl, 263, L85
+
+\bibitem[{{Nordhaus} \& {Spiegel}(2013)}]{nordhaus+spiegel2013}
+{Nordhaus}, J., \& {Spiegel}, D.~S. 2013, \mnras, 432, 500
+
+\bibitem[{{Nordhaus} {et~al.}(2010){Nordhaus}, {Spiegel}, {Ibgui}, {Goodman},
+  \& {Burrows}}]{nordhaus_et_al2010}
+{Nordhaus}, J., {Spiegel}, D.~S., {Ibgui}, L., {Goodman}, J., \& {Burrows}, A.
+  2010, \mnras, 1164
+
+\bibitem[{{Noyola} {et~al.}(2014){Noyola}, {Satyal}, \&
+  {Musielak}}]{noyola2014}
+{Noyola}, J.~P., {Satyal}, S., \& {Musielak}, Z.~E. 2014, \apj, 791, 25
+
+\bibitem[{{O'Gorman} {et~al.}(2013){O'Gorman}, {Harper}, {Brown}, {Drake}, \&
+  {Richards}}]{OGorman2013}
+{O'Gorman}, E., {Harper}, G.~M., {Brown}, A., {Drake}, S., \& {Richards},
+  A.~M.~S. 2013, \aj, 146, 98
+
+\bibitem[{{Parsons} {et~al.}(2012){Parsons}, {Pober}, {McQuinn}, {Jacobs}, \&
+  {Aguirre}}]{parsons_et_al2012}
+{Parsons}, A., {Pober}, J., {McQuinn}, M., {Jacobs}, D., \& {Aguirre}, J. 2012,
+  \apj, 753, 81
+
+\bibitem[{{Parsons} {et~al.}(2010){Parsons}, {Backer}, {Foster}, {Wright},
+  {Bradley}, {Gugliucci}, {Parashare}, {Benoit}, {Aguirre}, {Jacobs},
+  {Carilli}, {Herne}, {Lynch}, {Manley}, \& {Werthimer}}]{parsons_et_al2010}
+{Parsons}, A.~R., {Backer}, D.~C., {Foster}, G.~S., {et~al.} 2010, \aj, 139,
+  1468
+
+\bibitem[{{Pequignot} {et~al.}(1991){Pequignot}, {Petitjean}, \&
+  {Boisson}}]{pequignot1991}
+{Pequignot}, D., {Petitjean}, P., \& {Boisson}, C. 1991, \aap, 251, 680
+
+\bibitem[{{Petit} {et~al.}(2013){Petit}, {Auri{\`e}re}, {Konstantinova-Antova},
+  {Morgenthaler}, {Perrin}, {Roudier}, \& {Donati}}]{petit2013}
+{Petit}, P., {Auri{\`e}re}, M., {Konstantinova-Antova}, R., {et~al.} 2013, in
+  Lecture Notes in Physics, Berlin Springer Verlag, Vol. 857, Lecture Notes in
+  Physics, Berlin Springer Verlag, ed. J.-P. {Rozelot} \& C.~. {Neiner}, 231
+
+\bibitem[{{Pober} {et~al.}(2014){Pober}, {Liu}, {Dillon}, {Aguirre}, {Bowman},
+  {Bradley}, {Carilli}, {DeBoer}, {Hewitt}, {Jacobs}, {McQuinn}, {Morales},
+  {Parsons}, {Tegmark}, \& {Werthimer}}]{pober_et_al2014}
+{Pober}, J.~C., {Liu}, A., {Dillon}, J.~S., {et~al.} 2014, \apj, 782, 66
+
+\bibitem[{{Queloz} {et~al.}(2006){Queloz}, {Udry}, {Mayor}, {Benz}, {Cassen},
+  {Guillot}, \& {Quirrenbach}}]{exoplanets2006}
+{Queloz}, D., {Udry}, S., {Mayor}, M., {et~al.}, eds. 2006, {Extrasolar
+  planets}
+
+\bibitem[{{Reimers}(1975)}]{reimers1975}
+{Reimers}, D. 1975, Memoires of the Societe Royale des Sciences de Liege, 8,
+  369
+
+\bibitem[{{Reiners} \& {Christensen}(2010)}]{reiners2010}
+{Reiners}, A., \& {Christensen}, U.~R. 2010, \aap, 522, A13
+
+\bibitem[{{Rogers} \& {Bowman}(2008)}]{Rogers+Bowman2008}
+{Rogers}, A.~E.~E., \& {Bowman}, J.~D. 2008, \aj, 136, 641
+
+\bibitem[{{Russell}(1978)}]{russel1978}
+{Russell}, C.~T. 1978, \nat, 272, 147
+
+\bibitem[{{Sano}(1993)}]{sano1993}
+{Sano}, Y. 1993, Journal of geomagnetism and geoelectricity, 45, 65
+
+\bibitem[{{Schild}(1989)}]{schild1989}
+{Schild}, H. 1989, \mnras, 240, 63
+
+\bibitem[{{Sch{\"o}ier} \& {Olofsson}(2001)}]{schoier2001}
+{Sch{\"o}ier}, F.~L., \& {Olofsson}, H. 2001, \aap, 368, 969
+
+\bibitem[{{Schr{\"o}der} \& {Cuntz}(2005)}]{schroder2005}
+{Schr{\"o}der}, K.-P., \& {Cuntz}, M. 2005, \apjl, 630, L73
+
+\bibitem[{{Schr{\"o}der} \& {Cuntz}(2007)}]{schroder2007}
+---. 2007, \aap, 465, 593
+
+\bibitem[{{Sirothia} {et~al.}(2014){Sirothia}, {Lecavelier des Etangs},
+  {Gopal-Krishna}, {Kantharia}, \& {Ishwar-Chandra}}]{sirothia2014}
+{Sirothia}, S.~K., {Lecavelier des Etangs}, A., {Gopal-Krishna}, {Kantharia},
+  N.~G., \& {Ishwar-Chandra}, C.~H. 2014, \aap, 562, A108
+
+\bibitem[{{Skinner} {et~al.}(1997){Skinner}, {Dougherty}, {Meixner}, {Bode},
+  {Davis}, {Drake}, {Arens}, \& {Jernigan}}]{Skinner1997}
+{Skinner}, C.~J., {Dougherty}, S.~M., {Meixner}, M., {et~al.} 1997, \mnras,
+  288, 295
+
+\bibitem[{{Spiegel}(2012)}]{spiegel2012}
+{Spiegel}, D.~S. 2012, ArXiv e-prints
+
+\bibitem[{{Spiegel} \& {Madhusudhan}(2012)}]{spiegel+madhusudhan2012}
+{Spiegel}, D.~S., \& {Madhusudhan}, N. 2012, \apj, 756, 132
+
+\bibitem[{{Starchenko} \& {Jones}(2002)}]{starchenko2002}
+{Starchenko}, S.~V., \& {Jones}, C.~A. 2002, Icarus, 157, 426
+
+\bibitem[{{Stevens}(2005)}]{stevens2005}
+{Stevens}, I.~R. 2005, \mnras, 356, 1053
+
+\bibitem[{{Stevenson}(1979)}]{stevenson1979}
+{Stevenson}, D.~J. 1979, Geophysical and Astrophysical Fluid Dynamics, 12, 139
+
+\bibitem[{{Stil} {et~al.}(2014){Stil}, {Keller}, {George}, \&
+  {Taylor}}]{Stil2014}
+{Stil}, J.~M., {Keller}, B.~W., {George}, S.~J., \& {Taylor}, A.~R. 2014, \apj,
+  787, 99
+
+\bibitem[{{Stroe} {et~al.}(2012){Stroe}, {Snellen}, \&
+  {R{\"o}ttgering}}]{stroe2012}
+{Stroe}, A., {Snellen}, I.~A.~G., \& {R{\"o}ttgering}, H.~J.~A. 2012, \aap,
+  546, A116
+
+\bibitem[{{Str{\"o}mgren}(1939)}]{stromgren1939}
+{Str{\"o}mgren}, B. 1939, \apj, 89, 526
+
+\bibitem[{{Suzuki}(2007)}]{suzuki2007}
+{Suzuki}, T.~K. 2007, \apj, 659, 1592
+
+\bibitem[{{Trifonov} {et~al.}(2015){Trifonov}, {Reffert}, {Zechmeister},
+  {Reiners}, \& {Quirrenbach}}]{trifonov2015}
+{Trifonov}, T., {Reffert}, S., {Zechmeister}, M., {Reiners}, A., \&
+  {Quirrenbach}, A. 2015, ArXiv e-prints, arXiv:1508.04769
+
+\bibitem[{{Tsvetkova} {et~al.}(2013){Tsvetkova}, {Petit}, {Auri{\`e}re},
+  {Konstantinova-Antova}, {Wade}, {Charbonnel}, {Decressin}, \&
+  {Bogdanovski}}]{tsvetkova2013}
+{Tsvetkova}, S., {Petit}, P., {Auri{\`e}re}, M., {et~al.} 2013, \aap, 556, A43
+
+\bibitem[{{van den Oord} \& {de Bruyn}(1994)}]{vandenOord1994}
+{van den Oord}, G.~H.~J., \& {de Bruyn}, A.~G. 1994, \aap, 286, 181
+
+\bibitem[{{van Haarlem} {et~al.}(2013){van Haarlem}, {Wise}, {Gunst}, {Heald},
+  {McKean}, {Hessels}, {de Bruyn}, {Nijboer}, {Swinbank}, {Fallows},
+  {Brentjens}, {Nelles}, {Beck}, {Falcke}, {Fender}, {H{\"o}randel},
+  {Koopmans}, {Mann}, {Miley}, {R{\"o}ttgering}, {Stappers}, {Wijers},
+  {Zaroubi}, {van den Akker}, {Alexov}, {Anderson}, {Anderson}, {van Ardenne},
+  {Arts}, {Asgekar}, {Avruch}, {Batejat}, {B{\"a}hren}, {Bell}, {Bell}, {van
+  Bemmel}, {Bennema}, {Bentum}, {Bernardi}, {Best}, {B{\^\i}rzan}, {Bonafede},
+  {Boonstra}, {Braun}, {Bregman}, {Breitling}, {van de Brink}, {Broderick},
+  {Broekema}, {Brouw}, {Br{\"u}ggen}, {Butcher}, {van Cappellen}, {Ciardi},
+  {Coenen}, {Conway}, {Coolen}, {Corstanje}, {Damstra}, {Davies}, {Deller},
+  {Dettmar}, {van Diepen}, {Dijkstra}, {Donker}, {Doorduin}, {Dromer}, {Drost},
+  {van Duin}, {Eisl{\"o}ffel}, {van Enst}, {Ferrari}, {Frieswijk}, {Gankema},
+  {Garrett}, {de Gasperin}, {Gerbers}, {de Geus}, {Grie{\ss}meier}, {Grit},
+  {Gruppen}, {Hamaker}, {Hassall}, {Hoeft}, {Holties}, {Horneffer}, {van der
+  Horst}, {van Houwelingen}, {Huijgen}, {Iacobelli}, {Intema}, {Jackson},
+  {Jelic}, {de Jong}, {Juette}, {Kant}, {Karastergiou}, {Koers}, {Kollen},
+  {Kondratiev}, {Kooistra}, {Koopman}, {Koster}, {Kuniyoshi}, {Kramer},
+  {Kuper}, {Lambropoulos}, {Law}, {van Leeuwen}, {Lemaitre}, {Loose}, {Maat},
+  {Macario}, {Markoff}, {Masters}, {McFadden}, {McKay-Bukowski}, {Meijering},
+  {Meulman}, {Mevius}, {Middelberg}, {Millenaar}, {Miller-Jones}, {Mohan},
+  {Mol}, {Morawietz}, {Morganti}, {Mulcahy}, {Mulder}, {Munk}, {Nieuwenhuis},
+  {van Nieuwpoort}, {Noordam}, {Norden}, {Noutsos}, {Offringa}, {Olofsson},
+  {Omar}, {Orr{\'u}}, {Overeem}, {Paas}, {Pandey-Pommier}, {Pandey}, {Pizzo},
+  {Polatidis}, {Rafferty}, {Rawlings}, {Reich}, {de Reijer}, {Reitsma},
+  {Renting}, {Riemers}, {Rol}, {Romein}, {Roosjen}, {Ruiter}, {Scaife}, {van
+  der Schaaf}, {Scheers}, {Schellart}, {Schoenmakers}, {Schoonderbeek},
+  {Serylak}, {Shulevski}, {Sluman}, {Smirnov}, {Sobey}, {Spreeuw}, {Steinmetz},
+  {Sterks}, {Stiepel}, {Stuurwold}, {Tagger}, {Tang}, {Tasse}, {Thomas},
+  {Thoudam}, {Toribio}, {van der Tol}, {Usov}, {van Veelen}, {van der Veen},
+  {ter Veen}, {Verbiest}, {Vermeulen}, {Vermaas}, {Vocks}, {Vogt}, {de Vos},
+  {van der Wal}, {van Weeren}, {Weggemans}, {Weltevrede}, {White}, {Wijnholds},
+  {Wilhelmsson}, {Wucknitz}, {Yatawatta}, {Zarka}, {Zensus}, \& {van
+  Zwieten}}]{vanHaarlem2013}
+{van Haarlem}, M.~P., {Wise}, M.~W., {Gunst}, A.~W., {et~al.} 2013, \aap, 556,
+  A2
+
+\bibitem[{{van Loon} {et~al.}(2005){van Loon}, {Cioni}, {Zijlstra}, \&
+  {Loup}}]{vanloon2005}
+{van Loon}, J.~T., {Cioni}, M.-R.~L., {Zijlstra}, A.~A., \& {Loup}, C. 2005,
+  \aap, 438, 273
+
+\bibitem[{{Vassiliadis} \& {Wood}(1993)}]{vassiliadis1993}
+{Vassiliadis}, E., \& {Wood}, P.~R. 1993, \apj, 413, 641
+
+\bibitem[{{Verner} {et~al.}(1996){Verner}, {Ferland}, {Korista}, \&
+  {Yakovlev}}]{verner1996}
+{Verner}, D.~A., {Ferland}, G.~J., {Korista}, K.~T., \& {Yakovlev}, D.~G. 1996,
+  \apj, 465, 487
+
+\bibitem[{{Wu} \& {Lee}(1979)}]{wu1979}
+{Wu}, C.~S., \& {Lee}, L.~C. 1979, \apj, 230, 621
+
+\bibitem[{{Zarka}(1998)}]{zarka1998}
+{Zarka}, P. 1998, \jgr, 103, 20159
+
+\bibitem[{{Zarka} {et~al.}(2004){Zarka}, {Cecconi}, \&
+  {Kurth}}]{zarka_et_al2004}
+{Zarka}, P., {Cecconi}, B., \& {Kurth}, W.~S. 2004, Journal of Geophysical
+  Research (Space Physics), 109, 9
+
+\bibitem[{{Zarka} {et~al.}(2001){Zarka}, {Treumann}, {Ryabov}, \&
+  {Ryabov}}]{zarka2001}
+{Zarka}, P., {Treumann}, R.~A., {Ryabov}, B.~P., \& {Ryabov}, V.~B. 2001,
+  \apss, 277, 293
+
+\end{thebibliography}
 

### 2015-10-20 luminosity.tex
thinking about discussion on luminosity function

%\documentclass[12pt,preprint]{aastex}
\documentclass[12pt]{emulateapj} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amstext}
%\usepackage{apjfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{url}
%------------------------------------------
% User-defined macros.
\usepackage{color}

\definecolor{myColor}{rgb}{0.9,0.9,0.9}  
%------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\renewcommand\bottomfraction{.9}
\newcommand{\PD}[2]{\frac{\partial {#1}}{\partial {#2}}}

\title{Luminosity function of RGHJs}
\author{Yuka Fujii\altaffilmark{1}}
\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}

\begin{abstract}
N/A
\end{abstract}

\keywords{planetary systems --- planets and satellites: general}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Luminosity Function Note \#1} 
\label{sec:luminosity function}

Assume:
%%%
\begin{displaymath}
\frac{dn}{dL} = \left\{
\begin{array}{ll}
C' L^{-\alpha } & (L_{\rm min} < L < L_{\rm max}) \\
0 & (\mbox{elsewhere})
\end{array}
\right.
\end{displaymath}
%%%
where $C' $ is the proportional coefficient.

%%%
\begin{equation}
\frac{d^2n}{dL dr} dL dr =  4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr
\end{equation}
%%%

The relationship between flux $F$ and Luminosity $L$ is:
%%%
\begin{equation}
F = \frac{L}{r^2}
\end{equation}
%%%
where $r$ is the distance to the target.

The number of the targets within distance $R$ which have flux at $F \sim F+dF$ is
%%%
\begin{eqnarray}
\frac{dn}{dF} dF &=& \int dr \int dL \; \Psi (L, r) \\
&=& \int _0^{R} dr \int _{F}^{F+dF} dF \; \Psi (F r^2, r)\; det(J) 
\end{eqnarray}
%%%
where
%%%
\begin{equation}
det(J) = \left| \PD{r}{r}\PD{L}{F} - \PD{r}{F}\PD{L}{r} \right| = r^2
\end{equation}
%%%
Therefore, 
%%%
\begin{eqnarray}
\frac{dn}{dF} dF &=& \left[ 4 \pi \int _0 ^{R} dr \; r^4 \Phi (F, r) \right] dF\\
\Phi (F, r) &=& \left\{
\begin{array}{ll}
C (F r^2)^{-\alpha } & (\sqrt{L_{\rm min}/F} < r < \sqrt{L_{\rm max}/F}) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{eqnarray}
%%%
Therefore, 
%%%
\begin{eqnarray}
&& \frac{dn}{dF} dF \\
&=& 0 \;\;\;\; (R < \sqrt{L_{\rm min}/F}) \\
&=& \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;  (\sqrt{L_{\rm min}/F} < R < \sqrt{L_{\rm max}/F} ) \\
&=& \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] \\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\; (\sqrt{L_{\rm max}/F} < R) 
\end{eqnarray}
%%%

\vspace{2\baselineskip}

\end{document}

The probability to have the maximum luminosity of $F \sim F + dF$, $\mathcal{P} (F_{\rm max})$, with $N$ samples is
% $expected value of the maximum luminosity $L_{\rm max}$ is
%%%
\begin{eqnarray}
\mathcal{P}(F_{\rm max}) &\cdot & F_{\rm max} \\
&=& N \cdot p (F_{\rm max}) \cdot P^{N-1}(<F_{\rm max}) \cdot dF_{\rm max}\end{eqnarray}
%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Luminosity Function Note \#2} 
\label{sec:luminosity function}

Assume 
%%%
\begin{equation}
\frac{dn}{dL} = L^{-\alpha }
\end{equation}
%%%
Probability for a star to have luminosity $L\sim L+dL$ is 
%%%
\begin{equation}
p (L) dL = C L^{-\alpha }
\end{equation}
%%%

Probability for a star to have luminosity larger than $L$ is 
%%%
\begin{equation}
P(>L) = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
\end{equation}
%%%

Probability for a star to have luminosity less than $L$ is 
%%%
\begin{equation}
P(<L) = 1 -P (>L) \end{equation}
%%%

The probability to have the maximum luminosity of $L \sim L + dL$, $\mathcal{P(L_{\rm max}})$, with $N$ samples is
% $expected value of the maximum luminosity $L_{\rm max}$ is
%%%
\begin{eqnarray}
\mathcal{P}(L_{\rm max}) &\cdot & dL_{\rm max} \\
&=& N \cdot p (L_{\rm max}) \cdot P^{N-1}(<L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C L_{\rm max}^{-\alpha } \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1}
\end{eqnarray}
%%%
Thus, the expected value for the maximum luminosity is
%%%
\begin{eqnarray}
< L_{\rm max} > (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1} \\
&\equiv & N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max})
\end{eqnarray}
%%%

%Thus, the expected value for the maximum flux from the spherical shell at $l \sim l+dl$, $f_{\rm max} (l)$, is:
%%%
%\begin{equation}
%f_{\rm max} (l) = < L_{\rm max} > (4\pi l^2 dl) / l^2
%\end{equation}
%%%

As we observer further (i.e. while the distance $l$ increases by d$l$), the maximum luminosity increases
%%%
\begin{eqnarray}
&& \frac{d < L_{\rm max} >}{dl} = \frac{dN}{dl} \frac{d < L_{\rm max} >}{dN} \\
&\propto & l^{2} \left[ \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max}) \right. \\
&&\left. + N (N-1) \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-2}(L_{\rm max}) \right]
\end{eqnarray}
%%%

Let us compute the expected value for the maximum flux $F_{\rm max}$ as a function of distance $d$ of the sample. 
%%%
\begin{equation}
aiu
\end{equation}
%%%

\vspace{2in}

\begin{thebibliography}{}
\bibitem[Schroder(2007)]{Schroder2007} Schr\"{o}der , K.-P. \& Cuntz, M. 2005, ApJ, 630,  L73 
\bibitem[Schroder(2007)]{Schroder2007} Schr\"{o}der , K.-P. \& Cuntz, M. 2007, A\&A, 465, 593 
\end{thebibliography}

\end{document}

### 2015-11-06 reply2referee.txt
writing draft of reply to referee

Dear Editor,

The main topic of our paper is the re-evaluation of radio emission from planets around evolved stars. 
While the possibility of their strong radio emission has been addressed in Ignace et al. (2011), there are important updates in this paper in the following regards:

- taking account of the scaling of planetary magnetosphere. As a result, our estimate of radio emission is order-of-magnitude off of their estimate.  
- pointing out the presence of ionizing radition from accretion and quantitative evaluation of their ionizing effects. The mechanism to ionize otherwise neutral stellar wind has been briefly introduced in Ignace et al. (2011), but the mechanism we introduce is different one.  
- taking account of the plasma frequency of stellar wind, which severely affects the detectability of radio signal.

In the revised manuscript, we tried to make these point clearer. <<<to do>>>

Previously, we covered some topics that have already been addressed by previous papers, with the intention of making the paper self-contained and easy to follow. According to referee's suggestion that this is rather lengthy, we reduced the amount of the contents and removed the appendix B.

We hope the manuscript has been improved well and can now be recognized as qualified for publication.

Sincerely, 
Yuka Fujii

--------------------------------------------------------------------------------------
Comparison with previous work:

The nature of radio emission from red giant Hot Jupiters has already been addressed by Ignace et al (2010). The main difference in this new paper is that the authors explicitely allow for the area presented to the stellar wind by the exoplanetary magnetosphere, rather than simply the area presented by the bow shock around an unmagnetised planet. This provides around two orders of magnitude increase in the input kinetic power intercepted by the exoplanet.

This approach requires that the authors make some estimate of the magnetic field strength of the planet, for which they use published expressions for the field strength as a function of the exoplanet's mass and age. As a smaller point, in the present paper, the authors also explicitely consider the ionisation of the plasma around the exoplanet due to simple Bondi-Hoyle accretion. In the Ignace paper this mechanism was also introduced, but not explored in detail as the ionisation was provided by the presence of the bow shock that forms around the exoplanet.

The role of the size of the exoplanetary magnetosphere has been addressed by many other authors, including many of the papers by Zarka and Griessmeier cited by the authors. The novel aspect is the application to red giants. Most of the other parts of the paper involve applying published results. The most interesting of these is the use of the published expressions for the drop in the planet's convective heat flux with time as a means of estimating the decay with time of the planetary field strength and hence the emission frequency.
--------------------------------------------------------------------------------------

"the area presented by the bow shock around an unmagnetised planet. " ...??

--------------------------------------------------------------------------------------
Recommendation:

My main concern with this paper is that it is much too long for its original scientific content. The amendment to the Ignace (2010) result is interesting, as is the decay with time of the emission frequency, but much of the rest is unnecessary. For example, Appendix B covers almost two pages, but is not referred to or used in the paper. I have outlined below detailed comments on each section, but my recommendation is that the authors reduce the main paper by a factor of four by focussing on only the new and relevant results.
--------------------------------------------------------------------------------------

Previously, we reiterated some topics that have already been addressed by previous papers with the intention of making the paper self-contained and easy to follow. According to your suggestion, we revised the manuscript in the following points:
- 
- 
- removed Appendix B

--------------------------------------------------------------------------------------
Detailed comments:

Introduction: The authors should cite Jardine & Cameron (2008) who provide a model for the radio emission that does not rely on scaling of the solar system, and Smith et al 2009 for a search for a secondary eclipse.
--------------------------------------------------------------------------------------

Thank you for

--------------------------------------------------------------------------------------
Section 2.2

Eqns 6-8 seem to be missing a factor of 4pi.
--------------------------------------------------------------------------------------

Thank you for pointing this out.

--------------------------------------------------------------------------------------
Section 2.3

This section is only needed to calculate the decay with time of the field strength of the planet. For the radio emission, the authors simply scale to a field strength of 10G (which is perfectly acceptable as most of the parameters used in section 2.4 are unknown). This section simply quotes results from other papers and could be moved to an appendix.
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 2.4

The same comment applies here...the authors ultimately only use a wind velocity that is 1/10 that of the solar wind, so much of this section is unnecessary.
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 2.5

This section is new, but not necessary, as Ignace (2010) have already addressed the issue of the ionisation of the exoplanetary exosphere. 
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 3.2

Given that the authors dismiss the AGB stars because their cutoff frequencies are too high (which could have been demonstrated very briefly) it seems unnecessary to include these at every step. More significantly, the comparison with the "classical" hot Jupiters is not valid, either in eqns 43 or 48, as in this case the orbital velocity of the planet cannot be neglected when considering the relative velocity of the stellar wind particles to the planet (equation 7). The stellar rotational velocity is probably small and so can be neglected however. The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere. 
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Fig 3: the numbers on the RHS have no units...they are probably fluxes, but they should be shown. 
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 4:

Much of this section could be cut, saving perhaps section 4.2. Predictions for observations with different facilities have been made many times before.
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 5 and Appendix B:

Could be cut.
--------------------------------------------------------------------------------------

--------------------------------------------------------------------------------------
Section 6:

The authors note the rareness of evolved stars - it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider.
--------------------------------------------------------------------------------------

In summary, this paper contains some interesting results that would make much more impact if they were clearly presented in a much shorter paper.

### 2015-11-06 ms.tex
unnecesary bibliography part removed
defined tex command for revised parts

--- 2015-09-29 ms.tex
@@
 \def\memoTM#1{\color{DarkGreen}$[${\bf #1}$]$ \color{black}}
+
+\def\revise#1{\color{blue}$[${\bf #1}$]$ \color{blue}}
 
@@
 P_{\rm radio} &\propto & P_{\rm inp} \\
-P_{\rm inp,\,k} &=& n v^3 r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
-P_{\rm inp,\,m} &=& v B_{\star\bot }^2 r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
+P_{\rm inp,\,k} &=& n v^3 \cdot \pi r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
+P_{\rm inp,\,m} &=& \pi v B_{\star\bot }^2 \cdot \pi r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
 \end{eqnarray}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{s:discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Implication for discovery and characterization of exoplanets}
-\label{ss:implication}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-So far, more than 60 exoplanets are found around evolved stars \citep[e.g.][and references therein]{trifonov2015}. 
-Therefore, one possible strategy is to target known planetary systems.  
-One complication of the radial-velocity observations of evolved stars is the high degree of jitter due to chromospheric activities and stellar pulsations, which typically produces RV errors of $\sim 30$ [m/s].
-Therefore, there are some parameter spaces where current radial-velocity observations have not been able to survey.
-For such a parameter space, radio emission would work as a  probe to discover the possible sub-stellar companions.
-
-Once radio emission is detected, it provides some useful information about the planet itself and the stellar wind through the time dependence and frequency dependence. 
-As mentioned in \S\ref{ss:timevariability}, auroral radio flux significantly varies in time in association with several physical processes.
-In turn, we could utilize the time variability to characterize the system.
-For example, if the time resolution of the observation is sufficiently high (with full SKA, for instance), the time variation associated with planetary spin rotation could be detectable.
-Long term monitoring could reveal the time variability corresponding to orbital period if the system is near edge-on. Modulation on timescale of a few days may imply the presence of satellites.
-
-If the spectra are obtained, the upper cut-off frequency of the radio spectra will indicate the magnetic field strengths of the planetary surface.
-Such information would be most useful if we could obtain constraints on planetary mass via e.g.
-radial-velocity observations, because once both magnetic field strength and the planetary mass is constrained the proposed scaling law of planetary dynamo may be tested.
-On the other hand, the lower cut-off frequency indicates the plasma frequency in the vicinity of the planets, which might be used as a probe of the stellar wind property at the planetary orbit.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Back-reaction of a plasma flowing into a magnetic field}
-\label{ss:offset}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-One might expect that plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field.
-To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field.
-A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
-%%%
-\begin{equation}
-r=\frac{mv_\bot }{eB}.
-\end{equation}
-%%%
-which creates a magnetic dipole
-%%%
-\begin{equation}
-\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B}.
-\end{equation}
-%%%
-The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
-%%%
-\begin{equation}
-\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
-\end{equation}
-%%%
-
-Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
-%%%
-\begin{equation}
-\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B},
-\end{equation}
-%%%
-where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
-
-Just inside the stand-off point, 
-%%%
-\begin{equation}
-m_p n[r_{\rm mag}] v^2 < \frac{B[r_{\rm mag}]^2}{2\pi }
-\end{equation}
-%%%
-and thus $\rho_K/\rho _B < 1$. 
-When the particle spirals into the planet, 
-the magnetic pressures increases as 
-%%%
-\begin{equation}
-\frac{B^2}{8\pi } \propto \frac{1}{r^6}
-\end{equation}
-%%%
-On the other hand, the kinetic energy of the moment increases
-%%%
-\begin{equation}
-\frac{mv^2}{2} \propto \frac{1}{r}
-%\rho _K \propto \frac{1}{r}
-\end{equation}
-%%%
-Therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We thank Jake VanderPlas for developing the XKCD-style plotting package for matplotlib, and acknowledge its use. 
-NM acknowledges support from [???]. 
 AP is grateful for support from NSF grants 1352519 and 1440343.
@@
 
-\newpage
-
 \appendix
@@
 where we used $a_0 = 1/\alpha m$.
+
+\end{document}
 

### 2015-11-07 luminosity.tex
expected value for maximum flux as a function of distance r?

@@
 \usepackage{color}
+
+\allowdisplaybreaks[1]
 
@@
 
+%In principle, if the expected luminosity function and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys.
+For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume.
+%Under these assumptions, the largest luminosity in a volume limited sample (volume $V$, distance $d$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
+%The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$. 
+%Therefore,the likelihood of finding the brighter source increases with distance for $\alpha_L < 3/2$. 
+%Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
+%For example, for an $N[L] \propto L^{-1}$ the apparently brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
+%Therefore, if we can estimate the luminosity function of RGHJ emitters, we may estimate their detectability.
+
+%Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy. 
+In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
+For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
+Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
+Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
+. Therefore, $\alpha_L \sim -2.7$.
+
+\vspace{2\baselineskip}
+
 Assume:
@@
 \begin{array}{ll}
-C' L^{-\alpha } & (L_{\rm min} < L < L_{\rm max}) \\
+C L^{-\alpha } & (L_{\rm min} < L < L_{\rm max}) \\
 0 & (\mbox{elsewhere})
@@
 %%%
-where $C' $ is the proportional coefficient.
-
+where $C $ is the proportional coefficient. 
 %%%
@@
 %%%
+
 Therefore, 
@@
 && \frac{dn}{dF} dF \\
-&=& 0 \;\;\;\; (R < \sqrt{L_{\rm min}/F}) \\
-&=& \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;  (\sqrt{L_{\rm min}/F} < R < \sqrt{L_{\rm max}/F} ) \\
-&=& \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] \\
-&& \;\;\;\;\;\;\;\;\;\;\;\;\;\; (\sqrt{L_{\rm max}/F} < R) 
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
+\end{array}
+\right.
 \end{eqnarray}
+%%%
+
+The maximum flux of volume $4\pi R^3/3$ is likely to occur (?) at $F_{\rm max}$ such that
+%%%
+\begin{equation}
+\int _{F_0}^{\infty} \frac{dn}{dF} dF = 1
+\end{equation}
 %%%
@@
 \end{document}
+
+%%%
+\begin{eqnarray}
+&&<F> = \int F \frac{dn}{dF} dF \\
+%
+&&= \frac{4 \pi C}{5 - 2 \alpha } \\
+&& \times \left[ \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
+&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right] dF \\
+%
+&&= \frac{4 \pi C}{5 - 2 \alpha } \\
+&& \times \left\{ \left[ \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
+&&\left. + \left[ \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
+&&\propto R 
+%
+\end{eqnarray}
+%%%
+
+Therefore, 
+%%%
+\begin{eqnarray}
+&& \frac{dn}{dF} dF \\
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; (R < \sqrt{L_{\rm min}/F}) \\
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  (\sqrt{L_{\rm min}/F} < R < \sqrt{L_{\rm max}/F} ) \\
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; (\sqrt{L_{\rm max}/F} < R) 
+\end{array}
+\right.
+\end{eqnarray}
+%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-11-07 reply2referee.txt
Initial response to Comparison with previous work

@@
 --------------------------------------------------------------------------------------
+
+We thank the referee for pointing out that we were not as clear as we
+would like to have been regarding the many differences from and
+advances upon the seminal paper of Ignace (2010) in our original
+submission.  In this resubmission, we have taken the referee's
+comments to heart and have endeavored to trim literature review where
+it is unnecessary, and to highlight the new aspects of our work.
 

### 2015-11-10 reply2referee.txt
responding to referee's comments. reply2referee.txt includes to-do list with three items

--- 2015-11-06 reply2referee.txt
@@
-Dear Editor,
+***** TO DO LIST *****
 
-The main topic of our paper is the re-evaluation of radio emission from planets around evolved stars. 
-While the possibility of their strong radio emission has been addressed in Ignace et al. (2011), there are important updates in this paper in the following regards:
+1) response to ``The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere. ''
 
-- taking account of the scaling of planetary magnetosphere. As a result, our estimate of radio emission is order-of-magnitude off of their estimate.  
-- pointing out the presence of ionizing radition from accretion and quantitative evaluation of their ionizing effects.
-The mechanism to ionize otherwise neutral stellar wind has been briefly introduced in Ignace et al.
-(2011), but the mechanism we introduce is different one.
-- taking account of the plasma frequency of stellar wind, which severely affects the detectability of radio signal.
+2) argue the necesity of ``Observability`` section, in particular S4.3 and S4.4.
 
-In the revised manuscript, we tried to make these point clearer. <<<to do>>>
+3) response to ``it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider. ''
 
-Previously, we covered some topics that have already been addressed by previous papers, with the intention of making the paper self-contained and easy to follow.
-According to referee's suggestion that this is rather lengthy, we reduced the amount of the contents and removed the appendix B.
-
-We hope the manuscript has been improved well and can now be recognized as qualified for publication.
-
-Sincerely, 
-Yuka Fujii
+**********************
 
@@
 
-"the area presented by the bow shock around an unmagnetised planet. " ...??
+We thank referee's pointing this out, which made us realize that we previously failed to put our work into the context. 
+As referee understands, the main topic of our paper is the re-evaluation of radio emission from planets around evolved stars.
+While the possibility of their strong radio emission has been addressed in Ignace et al.
+(2011), there are important updates in this paper, in particular:
 
---------------------------------------------------------------------------------------
-Recommendation:
+- taking account of the shrinking of planetary magnetosphere. As a result, our estimate of radio emission is order-of-magnitude off of their estimate.  
+- pointing out the presence of ionizing radition from accretion and quantitative evaluation of their ionizing effects.
+A mechanism to ionize otherwise neutral stellar wind has been briefly introduced in Ignace et al.
+(2011), but it is different from the mechanism we introduce.
+- taking account of the plasma frequency of stellar wind, which severely affects the detectability of radio signal.
 
-My main concern with this paper is that it is much too long for its original scientific content.
-The amendment to the Ignace (2010) result is interesting, as is the decay with time of the emission frequency, but much of the rest is unnecessary.
-For example, Appendix B covers almost two pages, but is not referred to or used in the paper.
-I have outlined below detailed comments on each section, but my recommendation is that the authors reduce the main paper by a factor of four by focussing on only the new and relevant results.
---------------------------------------------------------------------------------------
+In the revised manuscript, we tried to make these point clearer in Introduction section. The revised parts are marked in bold font.
 
-Previously, we reiterated some topics that have already been addressed by previous papers with the intention of making the paper self-contained and easy to follow.
-According to your suggestion, we revised the manuscript in the following points:
-- 
-- 
-- removed Appendix B
+Previously, we covered some topics that have already been addressed by previous papers, with an intention of making the paper self-contained and easy to follow.
+According to referee's suggestion, we attempted to reduce the materials as much as we think reasonable <<<grammatically wrong?>>>.
+There are some arguments which we still think are worth part of the paper. We describe them in the following, in reponse to each of referee's detailed comments.
 
@@
 
-Thank you for
+We now included there papers in this section.
 
@@
 
-Thank you for pointing this out.
+We thank the referee for pointing this out.
+We think we missed pi for equations 7-8 instead of 4pi, since we are interested in the cross-sectional area of the stellar wind energy input.
+We believe eqn 6 does not need 4pi.
 
@@
 
+The model of planetary magnetic field descibed in Section 2.3 is necessary to discuss the planetary parameter space, especially in terms of planetary mass and orbit, shown in Figure 3.
+Therefore, we would like to retain the description in the main manuscript.
+On the other hand, it is true that the scaling of planetary magnetic field is not a novel point of this paper (as explicitly mentioned in the manuscript), so we removed some panels from figure 2.
+
 --------------------------------------------------------------------------------------
@@
 
+It is true that some of the points discussed here are not new points.
+Nevertheless, we think it is our responsibility to clarify our assumptions and that readers would be rather benefited from these descriptions because these properties are not common sense in the field of exoplanets.
+It is necessary to quantitatively evaluate not only the velocity but also significant mass-loss rate.
+Also, the typical values of stellar wind density is helpful and necessary step to discuss plasma frequency.
+
 --------------------------------------------------------------------------------------
@@
 --------------------------------------------------------------------------------------
+
+In Ignace et al.
+(2010) paper, post-shock ionization was introduced.
+The mechanism we newly propose in this paper provides a different view, and this allows us to adopt the same scaling law of radio emission as that of Solar-System planets.
+Therefore we think this is an important part of our work and we will not remove this from the paper.
 
@@
 
+As for the AGB stars, we believe it is important to discuss not only potentially detectable signals but also the limitation of our ability of detection.
+In addition, there are some parameter range where AGB companions could be detected.
+Therefore, we think it is worth including the discussion of AGB stars.
+
+As for the comparison with "classical" hot Jupiters, we appreciate referee's comments.
+We estimated the orbital velocity of our ``canonical hot Jupiter'' at 0.05 AU to be ~130 km/sec, which can contribute 5% increase in the relative velocity.
+We mentioned in the paragraph following equation (43).
+
+<<< ram pressure ??? >>>
+
 --------------------------------------------------------------------------------------
@@
 --------------------------------------------------------------------------------------
+
+We appreciate this feedback. We have indicated the unit in the title of Figure 3.
 
@@
 
+We would like to retain Section 4.1; indeed, when we talked about this work with people, they often ask me about it. 
+We also think Section 4.3 and 4.4 are useful. <<< To Tony, please describe how difficult (or not straight-forward) it is to obtain these number >>>
+
 --------------------------------------------------------------------------------------
@@
 --------------------------------------------------------------------------------------
+
+Following the referee's comment, we cut Section 5.1, while some part of it are merged with the last section (shown in bold font). 
+The intention of Section 5 was to answer a potential concern about the canceling field of far more massive stellar wind than sollar wind. We have clarified this motivation and moved it to Appendix. 
+Previously we thought Appendix B might be useful for future workers (since we often got confused when reading previous papers), but we decided to cut it for the sake of brevity, as the referee suggested.
 
@@
 
-In summary, this paper contains some interesting results that would make much more impact if they were clearly presented in a much shorter paper.
+As far as we understand the referee's feedback, Figure 5 partly answers this suggestion, where the expected flux from the known system is estimated.
+We now improved the discussion by including the effects of occurrence rate of Jupiter-like planets.
+<<< to do >>>

### 2015-11-10 ms.tex
responding to referee's comments. reply2referee.txt includes to-do list with three items

@@
 \usepackage{url}
+\usepackage{ulem}
 \usepackage{hyperref}
@@
 \definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
-\def\memoTM#1{\color{DarkGreen}$[${\bf #1}$]$ \color{black}}
-
-\def\revise#1{\color{blue}$[${\bf #1}$]$ \color{blue}}
+\def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}
+
+\def\revise#1#2{\color{blue}\sout{#1} {\bf #2} \color{black}}
 
@@
 In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
-Although observational searches for these radio signatures are underway, no clear detection has been claimed \citep{bastian2000,george2007,stroe2012,hallinan2013,murphy2015}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
+We note that \revise{}{\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates which is not based on the ``radiometric Bode's law''.
+}
+Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{}{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 Based on this speculation, \citet{ignace2010} examined radio emission from known substellar-mass companions around cool evolved stars.
-They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission, probably below the detection limit.
-
-In this paper, we argue that the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
+They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission. 
+\revise{}{In addition, they considered the scenario where the post-bow shock heating could produce ionized hydrogen atoms.
+This indicates a configuration of radio wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit.
+}
+
+In this paper, we \revise{argue that}{consider another plausible scenario where} the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
 The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
 Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates for highly evolved stars compared to the previous result. 
-We also consider the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
-Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
+\revise{}{Additional two major updates from \citet{ignace2010} are the following. } 
+\revise{We also consider}{Firstly, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
+\revise{Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
 Instead, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
+}{Secondly, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.
+}
 
@@
 \begin{figure*}[bp]
-	\plotonesc{radio_emission_mass_orbit.pdf}
+	\plotonesc{radio_emission_mass_orbit_ver2.pdf}
    \caption{Radio flux in unit of Jy from a planetary companion to a red giant with mass loss rate $10^{-8} M_{\odot }/\mbox{yr}$ (top) and that to an AGB star with mass loss rate $10^{-5} M_{\odot }/\mbox{yr}$ (bottom).
@@
 &\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{B}{B_{\rm J}} \right)^{2/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \notag \\
-&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
+&& \times \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \label{eq:P_HJ} \\
 && \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; \mbox{(for canonical hot Jupiters)} \notag 
@@
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
+\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at $0.05 {\rm AU}$ around a Solar-mass star is $\sim 130 {\rm km/sec}$, which could contribute to only $\sim $5\% increase of the velocity.
+}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Back-reaction of a plasma flowing into a magnetic field}
+\label{ss:offset}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\revise{One might expect}{Given that the density of stellar wind of evolved stars is fairly high, one might anticipate }
+that \revise{}{massive} plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field.
+To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field.
+A single charged particle moving perpendicular to the magnetic field moves in a circular orbit of radius 
+%%%
+\begin{equation}
+r=\frac{mv_\bot }{eB}.
+\end{equation}
+%%%
+which creates a magnetic dipole
+%%%
+\begin{equation}
+\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B}.
+\end{equation}
+%%%
+The volume integral of the canceling magnetic field $B_c$ generated by a single dipole $\mu$ is
+%%%
+\begin{equation}
+\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
+\end{equation}
+%%%
+
+Hence, for a number density $n$ of these charged particles, the fraction of canceling field to the background magnetic field is
+%%%
+\begin{equation}
+\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B},
+\end{equation}
+%%%
+where $\rho_K$ and $\rho_B$ are the kinetic energy density and the magnetic energy density, respectively.
+
+Just inside the stand-off point, 
+%%%
+\begin{equation}
+m_p n[r_{\rm mag}] v^2 < \frac{B[r_{\rm mag}]^2}{2\pi }
+\end{equation}
+%%%
+and thus $\rho_K/\rho _B < 1$. 
+When the particle spirals into the planet, 
+the magnetic pressures increases as 
+%%%
+\begin{equation}
+\frac{B^2}{8\pi } \propto \frac{1}{r^6}
+\end{equation}
+%%%
+On the other hand, the kinetic energy of the moment increases
+%%%
+\begin{equation}
+\frac{mv^2}{2} \propto \frac{1}{r}
+%\rho _K \propto \frac{1}{r}
+\end{equation}
+%%%
+Therefore, unless the density increases more drastically than $1/r^5$, the ratio $B_c/B$ is significantly less than unity.
+
 \end{document}

### 2015-11-10 reply2referee.txt

@@
 The most interesting of these is the use of the published expressions for the drop in the planet's convective heat flux with time as a means of estimating the decay with time of the planetary field strength and hence the emission frequency.
+--------------------------------------------------------------------------------------
+
+We thank the referee for pointing out that we were not as clear as we
+would like to have been regarding the many differences from and
+advances upon the seminal paper of Ignace (2010) in our original
+submission.  In this resubmission, we have taken the referee's
+comments to heart and have endeavored to trim literature review where
+it is unnecessary, and to highlight the new aspects of our work.
+
+--------------------------------------------------------------------------------------
+Recommendation:
+
+My main concern with this paper is that it is much too long for its original scientific content.
+The amendment to the Ignace (2010) result is interesting, as is the decay with time of the emission frequency, but much of the rest is unnecessary.
+For example, Appendix B covers almost two pages, but is not referred to or used in the paper.
+I have outlined below detailed comments on each section, but my recommendation is that the authors reduce the main paper by a factor of four by focussing on only the new and relevant results.
 --------------------------------------------------------------------------------------

### 2015-11-11 reply2referee.txt
Reformat response file; some minor wording changes; add cover letter to editor.

--- 2015-11-10 reply2referee.txt
@@
 
---------------------------------------------------------------------------------------
-Comparison with previous work:
+                                                10 November 2015
 
-The nature of radio emission from red giant Hot Jupiters has already been addressed by Ignace et al (2010).
-The main difference in this new paper is that the authors explicitely allow for the area presented to the stellar wind by the exoplanetary magnetosphere, rather than simply the area presented by the bow shock around an unmagnetised planet.
-This provides around two orders of magnitude increase in the input kinetic power intercepted by the exoplanet.
+Dear Dr. Burton,
 
-This approach requires that the authors make some estimate of the magnetic field strength of the planet, for which they use published expressions for the field strength as a function of the exoplanet's mass and age.
-As a smaller point, in the present paper, the authors also explicitely consider the ionisation of the plasma around the exoplanet due to simple Bondi-Hoyle accretion.
-In the Ignace paper this mechanism was also introduced, but not explored in detail as the ionisation was provided by the presence of the bow shock that forms around the exoplanet.
+  We now resubmit our paper titled "Radio Emission from Red Giant Hot
+Jupiters" by Yuka Fujii and collaborators, having addressed the
+referee's points.  In so doing we have provided additional explanatory
+text and updated the references, both in ways suggested by the referee
+and on our own initiative.  Below is our point-by-point response to
+the referee.  In our response, we present the referee's comments
+preceded by "## ", and our own comments indented in the space that
+follows.
 
-The role of the size of the exoplanetary magnetosphere has been addressed by many other authors, including many of the papers by Zarka and Griessmeier cited by the authors.
-The novel aspect is the application to red giants.
-Most of the other parts of the paper involve applying published results.
-The most interesting of these is the use of the published expressions for the drop in the planet's convective heat flux with time as a means of estimating the decay with time of the planetary field strength and hence the emission frequency.
+  We realized upon reading the referee's report that we should have
+done a better job of motivating some of the sections in our paper.
+For instance, the section about the canceling field potentially
+generated by stellar-wind electrons spiraling down field lines as they
+accrete onto the planet is precisely in order to allay a reader's
+possible concerns that the planetary magnetic field would be
+significantly attenuated by the canceling field generated by the
+massive stellar wind from an AGB star, a possibility that we wrestled
+with for probably 100 hours.  We hope to save our readers from having
+to repeat the same thought process we went through by laying out the
+logic clearly.  However, it seems that we didn't explain well enough
+why we put this section in the paper; in this resubmission, we have
+tried to better motivate the parts that the referee thought were less
+germane.
+
+  In addition, it appears that the referee and we have somewhat
+different philosophies regarding the purpose of a paper.  For example,
+the referee suggests that we eliminate the section "Assumptions for
+planetary magnetic field" and instead simply state that we assume a
+magnetic field of 10G.  In our view, this would significantly weaken
+our manuscipt.  Our aim is not merely to explain the assumptions that
+go into making each figure and table but also to walk the reader
+through the physics of the processes under discussion.
+
+  Finally, we point out that this comment from the report was
+surprising:
+----
+  "Section 2.5 This section is new, but not necessary, as Ignace
+   (2010) have already addressed the issue of the ionisation of the
+   exoplanetary exosphere."
+----
+Our manuscript presents a more detailed and accurate description of
+the ionisation profile around a planet accreting stellar wind than
+that in Ignace et al.'s paper.  It is unusual, in our experience, for
+a referee to say that a description in a paper that is new, correct,
+and more detailed than another description in the literature, is
+unnecessary.
+
+  Should you have any further questions, please feel free to get in
+touch with the corresponding author, Yuka Fujii.
+
+All the very best,
+  Yuka Fujii (for the authors)
+
 --------------------------------------------------------------------------------------
 
-We thank referee's pointing this out, which made us realize that we previously failed to put our work into the context. 
-As referee understands, the main topic of our paper is the re-evaluation of radio emission from planets around evolved stars.
-While the possibility of their strong radio emission has been addressed in Ignace et al.
-(2011), there are important updates in this paper, in particular:
+## Reviewer's Comments:
+##
+## This paper addresses the possibility of observing radio emission from
+## planets orbiting around red giants. This emission is powered by the
+## interaction of the stellar wind with the exoplanet, in a manner
+## similar to that observed from many solar-system planets including
+## Jupiter and the Earth. The winds of red giants are much cooler and
+## slower than the solar wind, but they have a much higher mass
+## density. Their kinetic energy fluxes therefore may be large enough to
+## power observable radio fluxes. There are currently many planned and
+## ongoing searches for radio emission from exoplanets, so this is a
+## timely topic to address.
+## 
+##
+## Comparison with previous work: 
+##
+## The nature of radio emission from red giant Hot Jupiters has already
+## been addressed by Ignace et al (2010). The main difference in this new
+## paper is that the authors explicitely allow for the area presented to
+## the stellar wind by the exoplanetary magnetosphere, rather than simply
+## the area presented by the bow shock around an unmagnetised
+## planet. This provides around two orders of magnitude increase in the
+## input kinetic power intercepted by the exoplanet.
+##
+## This approach requires that the authors make some estimate of the
+## magnetic field strength of the planet, for which they use published
+## expressions for the field strength as a function of the exoplanet's
+## mass and age. As a smaller point, in the present paper, the authors
+## also explicitely consider the ionisation of the plasma around the
+## exoplanet due to simple Bondi-Hoyle accretion. In the Ignace paper
+## this mechanism was also introduced, but not explored in detail as the
+## ionisation was provided by the presence of the bow shock that forms
+## around the exoplanet.
+##
+## The role of the size of the exoplanetary magnetosphere has been
+## addressed by many other authors, including many of the papers by Zarka
+## and Griessmeier cited by the authors. The novel aspect is the
+## application to red giants. Most of the other parts of the paper
+## involve applying published results. The most interesting of these is
+## the use of the published expressions for the drop in the planet's
+## convective heat flux with time as a means of estimating the decay with
+## time of the planetary field strength and hence the emission frequency.
 
-- taking account of the shrinking of planetary magnetosphere. As a result, our estimate of radio emission is order-of-magnitude off of their estimate.  
-- pointing out the presence of ionizing radition from accretion and quantitative evaluation of their ionizing effects.
-A mechanism to ionize otherwise neutral stellar wind has been briefly introduced in Ignace et al.
-(2011), but it is different from the mechanism we introduce.
-- taking account of the plasma frequency of stellar wind, which severely affects the detectability of radio signal.
+  We thank the referee for pointing out that we were not as clear as
+  we would like to have been regarding the many differences from and
+  advances upon the seminal paper of Ignace (2010) in our original
+  submission.  In this resubmission, we have taken the referee's
+  comments to heart and have endeavored to trim literature review
+  where it is unnecessary, and to highlight the new aspects of our
+  work.
 
-In the revised manuscript, we tried to make these point clearer in Introduction section. The revised parts are marked in bold font.
+## Recommendation:
+## 
+## My main concern with this paper is that it is much too long for its
+## original scientific content. The amendment to the Ignace (2010) result
+## is interesting, as is the decay with time of the emission frequency,
+## but much of the rest is unnecessary. For example, Appendix B covers
+## almost two pages, but is not referred to or used in the paper. I have
+## outlined below detailed comments on each section, but my
+## recommendation is that the authors reduce the main paper by a factor
+## of four by focussing on only the new and relevant results.
 
-Previously, we covered some topics that have already been addressed by previous papers, with an intention of making the paper self-contained and easy to follow.
-According to referee's suggestion, we attempted to reduce the materials as much as we think reasonable <<<grammatically wrong?>>>.
-There are some arguments which we still think are worth part of the paper. We describe them in the following, in reponse to each of referee's detailed comments.
+  We thank referee for this comment.  We now realize that we had
+  previously failed to put our work into proper context.  [DSS: strike
+  the following: As referee understands,] the main topic of our paper
+  is the re-evaluation of radio emission from planets around evolved
+  stars. While the possibility of their strong radio emission has been
+  addressed in Ignace et al. (2011) [DSS: don't we mean 2010?], there
+  are important updates in this paper, in particular:
 
---------------------------------------------------------------------------------------
-Detailed comments:
+  - taking account of the shrinking of planetary magnetosphere. As a
+    result, our estimate of radio emission is order-of-magnitude off
+    of their estimate.
+  - pointing out the presence of ionizing radition from accretion and
+    quantitative evaluation of their ionizing effects. A mechanism to
+    ionize otherwise neutral stellar wind has been briefly introduced
+    in Ignace et al. (2011), but it is different from the mechanism we
+    introduce.
+  - taking account of the plasma frequency of stellar wind, which
+    severely affects the detectability of radio signal.
 
-Introduction: The authors should cite Jardine & Cameron (2008) who provide a model for the radio emission that does not rely on scaling of the solar system, and Smith et al 2009 for a search for a secondary eclipse.
---------------------------------------------------------------------------------------
+  In the revised manuscript, we tried to make these point clearer in
+  Introduction section. The revised parts are marked in bold font.
 
-We now included there papers in this section.
+  Previously, we covered some topics that have already been addressed
+  by previous papers, with an intention of making the paper
+  self-contained and easy to follow. According to referee's
+  suggestion, we attempted to reduce the materials as much as we think
+  reasonable <<<grammatically wrong?>>>.  There are some arguments
+  which we still think are worth part of the paper. We describe them
+  in the following, in reponse to each of referee's detailed comments.
 
---------------------------------------------------------------------------------------
-Section 2.2
+## Detailed comments:
+## 
+## Introduction: The authors should cite Jardine & Cameron (2008) who
+## provide a model for the radio emission that does not rely on scaling
+## of the solar system, and Smith et al 2009 for a search for a secondary
+## eclipse.
 
-Eqns 6-8 seem to be missing a factor of 4pi.
---------------------------------------------------------------------------------------
+  We now included their papers in this section.
 
-We thank the referee for pointing this out.
-We think we missed pi for equations 7-8 instead of 4pi, since we are interested in the cross-sectional area of the stellar wind energy input.
-We believe eqn 6 does not need 4pi.
+## Section 2.2
+## 
+## Eqns 6-8 seem to be missing a factor of 4pi.
 
---------------------------------------------------------------------------------------
-Section 2.3
+  This is a good catch by the referee!  It looks like we missed a
+  factor of pi in equations 7-8 instead of 4pi, since we are
+  interested in the cross-sectional area of the stellar wind energy
+  input.  Equation 6 looks like it's okay since it's a
+  proportionality, not equality.
 
-This section is only needed to calculate the decay with time of the field strength of the planet.
-For the radio emission, the authors simply scale to a field strength of 10G (which is perfectly acceptable as most of the parameters used in section 2.4 are unknown).
-This section simply quotes results from other papers and could be moved to an appendix.
---------------------------------------------------------------------------------------
+## Section 2.3
+## 
+## This section is only needed to calculate the decay with time of the
+## field strength of the planet. For the radio emission, the authors
+## simply scale to a field strength of 10G (which is perfectly acceptable
+## as most of the parameters used in section 2.4 are unknown). This
+## section simply quotes results from other papers and could be moved to
+## an appendix.
 
-The model of planetary magnetic field descibed in Section 2.3 is necessary to discuss the planetary parameter space, especially in terms of planetary mass and orbit, shown in Figure 3.
-Therefore, we would like to retain the description in the main manuscript.
-On the other hand, it is true that the scaling of planetary magnetic field is not a novel point of this paper (as explicitly mentioned in the manuscript), so we removed some panels from figure 2.
+  The model of planetary magnetic field descibed in Section 2.3 is
+  necessary to discuss the planetary parameter space, especially in
+  terms of planetary mass and orbit, shown in Figure 3. Therefore, we
+  would like to retain the description in the main manuscript.  On the
+  other hand, it is true that the scaling of planetary magnetic field
+  is not a novel point of this paper (as explicitly mentioned in the
+  manuscript), so we removed some panels from figure 2.
 
---------------------------------------------------------------------------------------
-Section 2.4
+## Section 2.4
+## 
+## The same comment applies here...the authors ultimately only use a wind
+## velocity that is 1/10 that of the solar wind, so much of this section
+## is unnecessary.
 
-The same comment applies here...the authors ultimately only use a wind velocity that is 1/10 that of the solar wind, so much of this section is unnecessary.
---------------------------------------------------------------------------------------
+  It is true that some of the points discussed here are not new
+  points. Nevertheless, we think it is our responsibility to clarify
+  our assumptions and that readers would be rather benefited from
+  these descriptions because these properties are not common sense in
+  the field of exoplanets.  It is necessary to quantitatively evaluate
+  not only the velocity but also significant mass-loss rate. Also, the
+  typical values of stellar wind density is helpful and necessary step
+  to discuss plasma frequency.
 
-It is true that some of the points discussed here are not new points.
-Nevertheless, we think it is our responsibility to clarify our assumptions and that readers would be rather benefited from these descriptions because these properties are not common sense in the field of exoplanets.
-It is necessary to quantitatively evaluate not only the velocity but also significant mass-loss rate.
-Also, the typical values of stellar wind density is helpful and necessary step to discuss plasma frequency.
+## Section 2.5
+## 
+## This section is new, but not necessary, as Ignace (2010) have
+## already addressed the issue of the ionisation of the exoplanetary
+## exosphere.
 
---------------------------------------------------------------------------------------
-Section 2.5
+  In the Ignace et al. (2010) paper, post-shock ionization was
+  introduced. The mechanism we newly propose in this paper provides a
+  different view, and this allows us to adopt the same scaling law of
+  radio emission as that of Solar-System planets. Therefore we think
+  this is an important part of our work and we will not remove this
+  from the paper.
 
-This section is new, but not necessary, as Ignace (2010) have already addressed the issue of the ionisation of the exoplanetary exosphere. 
---------------------------------------------------------------------------------------
+## Section 3.2
+## 
+## Given that the authors dismiss the AGB stars because their cutoff
+## frequencies are too high (which could have been demonstrated very
+## briefly) it seems unnecessary to include these at every step. More
+## significantly, the comparison with the "classical" hot Jupiters is not
+## valid, either in eqns 43 or 48, as in this case the orbital velocity
+## of the planet cannot be neglected when considering the relative
+## velocity of the stellar wind particles to the planet (equation 7). The
+## stellar rotational velocity is probably small and so can be neglected
+## however. The authors should demonstrate that the ram pressure of any
+## exoplanetary outflow induced by heating can also be neglected in
+## determining the size of the magnetosphere.
 
-In Ignace et al.
-(2010) paper, post-shock ionization was introduced.
-The mechanism we newly propose in this paper provides a different view, and this allows us to adopt the same scaling law of radio emission as that of Solar-System planets.
-Therefore we think this is an important part of our work and we will not remove this from the paper.
+  As for the AGB stars, we believe it is important to discuss not only
+  potentially detectable signals but also the limitation of our
+  ability of detection. In addition, there are some parameter range
+  where AGB companions could be detected. Therefore, we think it is
+  worth including the discussion of AGB stars.
 
---------------------------------------------------------------------------------------
-Section 3.2
-
-Given that the authors dismiss the AGB stars because their cutoff frequencies are too high (which could have been demonstrated very briefly) it seems unnecessary to include these at every step.
-More significantly, the comparison with the "classical" hot Jupiters is not valid, either in eqns 43 or 48, as in this case the orbital velocity of the planet cannot be neglected when considering the relative velocity of the stellar wind particles to the planet (equation 7).
-The stellar rotational velocity is probably small and so can be neglected however.
-The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere.
---------------------------------------------------------------------------------------
-
-As for the AGB stars, we believe it is important to discuss not only potentially detectable signals but also the limitation of our ability of detection.
-In addition, there are some parameter range where AGB companions could be detected.
-Therefore, we think it is worth including the discussion of AGB stars.
-
-As for the comparison with "classical" hot Jupiters, we appreciate referee's comments.
-We estimated the orbital velocity of our ``canonical hot Jupiter'' at 0.05 AU to be ~130 km/sec, which can contribute 5% increase in the relative velocity.
-We mentioned in the paragraph following equation (43).
+  As for the comparison with "classical" hot Jupiters, we appreciate
+  referee's comments. We estimated the orbital velocity of our
+  ``canonical hot Jupiter'' at 0.05 AU to be ~130 km/sec, which can
+  contribute 5% increase in the relative velocity. We mentioned in the
+  paragraph following equation (43).
 
@@
 
---------------------------------------------------------------------------------------
-Fig 3: the numbers on the RHS have no units...they are probably fluxes, but they should be shown. 
---------------------------------------------------------------------------------------
+## Fig 3: the numbers on the RHS have no units...they are probably
+## fluxes, but they should be shown.
 
-We appreciate this feedback. We have indicated the unit in the title of Figure 3.
+  We appreciate this feedback. We have indicated the unit in the title
+  of Figure 3.
 
---------------------------------------------------------------------------------------
-Section 4:
+## Section 4:
+## 
+## Much of this section could be cut, saving perhaps section
+## 4.2. Predictions for observations with different facilities have been
+## made many times before.
 
-Much of this section could be cut, saving perhaps section 4.2. Predictions for observations with different facilities have been made many times before.
---------------------------------------------------------------------------------------
+  We would like to retain Section 4.1; indeed, when we talked about
+  this work with people, they often ask me about it.  We are unaware
+  of any predictions in the literature that make it easy for the
+  reader to estimate the required duration of the observations
+  describe in our manuscript.  We also think Section 4.3 and 4.4 are
+  useful. <<< To Tony, please describe how difficult (or not
+  straight-forward) it is to obtain these number >>>
 
-We would like to retain Section 4.1; indeed, when we talked about this work with people, they often ask me about it. 
-We also think Section 4.3 and 4.4 are useful. <<< To Tony, please describe how difficult (or not straight-forward) it is to obtain these number >>>
+## Section 5 and Appendix B:
+## 
+## Could be cut.
 
---------------------------------------------------------------------------------------
-Section 5 and Appendix B:
+  Following the referee's comment, we cut Section 5.1, while some part
+  of it are merged with the last section (shown in bold font).  The
+  intention of Section 5 was to answer a potential concern about the
+  canceling field of far more massive stellar wind than sollar
+  wind. We have clarified this motivation and moved it to Appendix.
+  Previously we thought Appendix B might be useful for future workers
+  (since we often got confused when reading previous papers), but we
+  decided to cut it for the sake of brevity, as the referee suggested.
 
-Could be cut.
---------------------------------------------------------------------------------------
+  [DSS: I don't think it should be moved to the Appendix.]
 
-Following the referee's comment, we cut Section 5.1, while some part of it are merged with the last section (shown in bold font). 
-The intention of Section 5 was to answer a potential concern about the canceling field of far more massive stellar wind than sollar wind. We have clarified this motivation and moved it to Appendix. 
-Previously we thought Appendix B might be useful for future workers (since we often got confused when reading previous papers), but we decided to cut it for the sake of brevity, as the referee suggested.
+## Section 6:
+## 
+## The authors note the rareness of evolved stars - it would be useful if
+## they included a brief calculation or statement of how many might be
+## expected, particularly in the age ranges they consider.
 
---------------------------------------------------------------------------------------
-Section 6:
-
-The authors note the rareness of evolved stars - it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider.
---------------------------------------------------------------------------------------
-
-As far as we understand the referee's feedback, Figure 5 partly answers this suggestion, where the expected flux from the known system is estimated.
-We now improved the discussion by including the effects of occurrence rate of Jupiter-like planets.
-<<< to do >>>
+  As far as we understand the referee's feedback, Figure 5 partly
+  answers this suggestion, where the expected flux from the known
+  system is estimated. We now improved the discussion by including the
+  effects of occurrence rate of Jupiter-like planets. <<< to do >>>

### 2015-11-11 reply2referee.txt
Ignace et al. 2011 -> 2010
1. arXiv number in reference is updated. 2. Discussion in previous Section 5.1 is merged to current conclusion section. 3. minor updates in reply2referee.txt

@@
 preceded by "## ", and our own comments indented in the space that
-follows.
+follows. We also revised the reference list to match the journal's
+nomenclature.
 
@@
   We thank referee for this comment.  We now realize that we had
-  previously failed to put our work into proper context.  [DSS: strike
-  the following: As referee understands,] the main topic of our paper
-  is the re-evaluation of radio emission from planets around evolved
-  stars. While the possibility of their strong radio emission has been
-  addressed in Ignace et al. (2011) [DSS: don't we mean 2010?], there
-  are important updates in this paper, in particular:
+  previously failed to put our work into proper context.  The main topic
+  of our paper is the re-evaluation of radio emission from planets around
+  evolved stars. While the possibility of their strong radio emission has
+  been addressed in Ignace et al. (2010), there are important updates in 
+  this paper, in particular:
 
@@
     ionize otherwise neutral stellar wind has been briefly introduced
-    in Ignace et al. (2011), but it is different from the mechanism we
+    in Ignace et al. (2010), but it is different from the mechanism we
     introduce.

### 2015-11-11 ms.tex
1. arXiv number in reference is updated. 2. Discussion in previous Section 5.1 is merged to current conclusion section. 3. minor updates in reply2referee.txt

@@
-\documentclass[iop,numberedappendix,apj]{emulateapj}
+\documentclass[iop,numberedappendix,apj,]{emulateapj}
 
@@
 Estimates for the actual late-type (M type) evolved stars are also included. 
-Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission to characterize the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.
+\revise{Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission to characterize the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.}
 Finally, Section \ref{s:conc} concludes the paper with a brief summary.
@@
 
-In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, $3.2\times 10^{10}$ W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, \revise{$3.2\times 10^{10}$}{$8.2\times 10^{10}$} W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
 Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
@@
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
-\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at $0.05 {\rm AU}$ around a Solar-mass star is $\sim 130 {\rm km/sec}$, which could contribute to only $\sim $5\% increase of the velocity.
+\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at $0.05 {\rm AU}$ around a Solar-mass star is $\sim 130~{\rm km/sec}$, which contributes to only $\sim $5\% increase of the velocity.
 }
@@
 
+\revise{%
 Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
-Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.
+Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.%
+}{%
+Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property.
+As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites.
+If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g.
+radial-velocity observations, tests  the proposed scaling law of planetary dynamo.
+A extra fruit from observations of RGHJs in particular is that the lower cut-off frequency, which presumably corresponds to in situ plasma frequency, could probe of the stellar wind property at the planetary orbit.
+In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
+%
+We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
+%
+}
 

### 2015-11-12 reply2referee.txt
justifications for 4.3 and 4.4

@@
   describe in our manuscript.  We also think Section 4.3 and 4.4 are
-  useful. <<< To Tony, please describe how difficult (or not
-  straight-forward) it is to obtain these number >>>
+  useful.  To our knowledge, we know of no such comparison for state of
+  the art facilities that is up to date for late 2015, nor do we know
+  of any consolidation of this information in one publication.
+  Predictions for future facilities become rapidly out of date as
+  projects are descoped (or "rebaselined" in the case of the SKA), and
+  many sensitivity predictions for existing instruments were made
+  before the instrument was built.  Including the latest measured 
+  performance or design specifications is crucial to assess observing 
+  feasibility.
+  In section 4.4, we discuss the important point that one can exploit 
+  the unique time variability of these signatures for detection.  
+  We think this is a crucial point to consider, as direct imaging 
+  would be impossible in the face of confusion from both Galactic and
+  extragalactic sources (which are brighter but will not vary on the same
+  time scale).
 

### 2015-11-12 ms.tex
argument about the expected number of detection, in response to referee's last comment

@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
-Assuming Jupiter-mass planets which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, a reasonable number of systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
+Assuming Jupiter-mass planets \revise{}{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{a reasonable number of}{148 (44)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
 For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
 $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
+
+\revise{}{Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. %
+Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 15 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.5\% \citep{cumming2008}.
+%
+Therefore, given that 148 (44) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10 \mu {\rm Jy}$, about 2-5 would actually be emitting the radio wave of our interest. %
+For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10\mu {\rm Jy}$ is 21 (5).
+Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity 10$\mu {\rm Jy}$.
+%
+}
 

### 2015-11-12 reply2referee.txt
one more action item
Minor changes to cover letter; updates to response on Section 4.

@@
 3) response to ``it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider. ''
+
+4) literature survey if 4.3 and 4.4 have been discussed already in previous papers
 
@@
 done a better job of motivating some of the sections in our paper.
-For instance, the section about the canceling field potentially
-generated by stellar-wind electrons spiraling down field lines as they
-accrete onto the planet is precisely in order to allay a reader's
-possible concerns that the planetary magnetic field would be
-significantly attenuated by the canceling field generated by the
-massive stellar wind from an AGB star, a possibility that we wrestled
-with for probably 100 hours.  We hope to save our readers from having
-to repeat the same thought process we went through by laying out the
-logic clearly.  However, it seems that we didn't explain well enough
-why we put this section in the paper; in this resubmission, we have
-tried to better motivate the parts that the referee thought were less
-germane.
+For instance, we wrote the section about the canceling field generated
+by stellar-wind electrons, as they spiral down field lines in
+accreting onto the planet, in order to allay the reader's possible
+concerns that the planetary magnetic field would be significantly
+attenuated by the canceling field generated by the massive stellar
+wind from an AGB star -- a possibility that we wrestled with for
+probably 100 hours.  We hope to save our readers from having to repeat
+the same thought process we went through by laying out the logic
+clearly.  However, it seems that we didn't explain well enough why we
+put this section in the paper; in this resubmission, we have tried to
+better motivate the parts that the referee thought were less germane.
 
@@
 that in Ignace et al.'s paper.  It is unusual, in our experience, for
-a referee to say that a description in a paper that is new, correct,
-and more detailed than another description in the literature, is
-unnecessary.
+a referee to say that a description that is new, correct, and more
+detailed than another description in the literature, is unnecessary.
 
@@
 
-  We would like to retain Section 4.1; indeed, when we talked about
-  this work with people, they often ask me about it.  We are unaware
-  of any predictions in the literature that make it easy for the
-  reader to estimate the required duration of the observations
-  describe in our manuscript.  We also think Section 4.3 and 4.4 are
-  useful.  To our knowledge, we know of no such comparison for state of
-  the art facilities that is up to date for late 2015, nor do we know
-  of any consolidation of this information in one publication.
+  We believe that Section 4.1 (regarding intrinsic radio emission from
+  red giant stars) enhances the paper.  For instance, when we discuss
+  this work with people, they often ask us about this topic.  It's a
+  natural consideration, since a key component of observability is
+  SNR, and the star obviously contributes some of the Noise (indeed,
+  in most exoplanet contexts, the signal from the planet is competing
+  against a much brighter star).  To devote 1 page to what the reader
+  is likely to be concerned is the strongest source of Noise in the
+  observations does not seem unreasonable to us.
+
+  We also think Section 4.3 and 4.4 are useful.  We are unaware of any
+  predictions in the literature that make it easy for the reader to
+  estimate the required duration of the observations describe in our
+  manuscript.  Specifically, we know of no such comparison for state
+  of the art facilities that is up to date for late 2015, nor do we
+  know of any consolidation of this information in one publication.
   Predictions for future facilities become rapidly out of date as
@@
   performance or design specifications is crucial to assess observing
-  feasibility.
-  In section 4.4, we discuss the important point that one can exploit 
-  the unique time variability of these signatures for detection.  
-  We think this is a crucial point to consider, as direct imaging 
-  would be impossible in the face of confusion from both Galactic and
-  extragalactic sources (which are brighter but will not vary on the same
-  time scale).
+  feasibility.  In section 4.4, we discuss the important point that
+  one can exploit the unique time variability of these signatures for
+  detection.  We think this is a crucial point to consider, as direct
+  imaging would be impossible in the face of confusion from both
+  Galactic and extragalactic sources (which are brighter but will not
+  vary on the same time scale).
 

### 2015-11-12 ms_20150929submittedtoapj.tex
writing draft of reply to referee
adding theta = resolution to 4.3

--- 2015-09-29 ms.tex
@@
 \tablehead{
-Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & Resolution & $\sigma_c$\tablenotemark{c}\\
+Instrument & Band  & \sigRMS\tablenotemark{a} & $\tau$\tablenotemark{b}  & $\theta$\tablenotemark{c}  & $\sigma_c$\tablenotemark{d}\\
            & (MHz) & ($\mu$Jy bm$^{-1}$)         &  (hr)                    & (\arcsec)  & ($\mu$Jy bm$^{-1}$)} 
@@
 of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
-\tablenotetext{c}{Source confusion RMS contribution.}
+\tablenotetext{c}{Resolution of the instrument.}
+\tablenotetext{d}{Source confusion RMS contribution.}
 \end{deluxetable*}
@@
 An additional factor that affects detectability is source confusion, the imaging noise associated with unresolved interloping radio sources in an observation.
-Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an image due to one or more unresolved sources in the beam solid angle (for a review, see \cite{Condon1974,Condon2012}).
+Source confusion is characterized by the standard deviation $\sigma_c$ in the surface brightness of an image due to one or more unresolved sources in the beam solid angle, or resolution element, $\theta$ (for a review, see \cite{Condon1974,Condon2012}).
 To estimate $\sigma_c$, reported in Table~\ref{tab:sens}, we use the relations provided by \cite{condon+ransom2016}, reproduced below:
@@
 \bibliography{biblio.bib}
-
-\newpage
 

### 2015-11-13 luminosity.tex
considering luminosity function

@@
 For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
-Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
+Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
+Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
 Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
-. Therefore, $\alpha_L \sim -2.7$.
+. Therefore, $\alpha_L \sim -3.1$.
 
@@
 \frac{dn}{dF} dF &=& \int dr \int dL \; \Psi (L, r) \\
-&=& \int _0^{R} dr \int _{F}^{F+dF} dF \; \Psi (F r^2, r)\; det(J) 
+&=& \int _{F}^{F+dF} dF \int _0^{R} dr \; \Psi (F r^2, r)\; det(J) 
 \end{eqnarray}
@@
 
-Therefore, 
+Thus,  
+%%%
+\begin{eqnarray}
+&& \frac{dn}{dF} dF \\
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
+\\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
+\end{array}
+\right. \\
+%%%
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
+\\
+\displaystyle \frac{4\pi C }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
+\\
+\displaystyle \frac{4\pi C F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
+\end{array}
+\right. 
+\end{eqnarray}
+%%%
+
+The maximum flux of volume $4\pi R^3/3$ is likely to occur (?) at $F_{\rm max}$ such that
+%%%
+\begin{equation}
+\int _{F_0}^{\infty} \frac{dn}{dF} dF = 1
+\end{equation}
+%%%
+
+Solar luminosity becomes 2 times brighter than current value when it evolves off the main-sequence stage.
+Correspondingly, the radio wave from Jupiter will becomes $2.1 \cdot 10^{11} \times 2^{7/12} = 3.1 \cdot 10^{11}~{\rm W} = 2.5 \cdot 10^{11} ~{\rm W/str}$ .
+
+\vspace{2\baselineskip}
+
+\begin{itemize}
+\item $L_{\rm min} = 2.5 \times 10^{11} ~{\rm W/str}$
+\item $L_{\rm max} = $
+\end{itemize}
+
+\vspace{2\baselineskip}
+
+\vspace{2\baselineskip}
+
+\end{document}
+
 %%%
@@
 %%%
-
-The maximum flux of volume $4\pi R^3/3$ is likely to occur (?) at $F_{\rm max}$ such that
-%%%
-\begin{equation}
-\int _{F_0}^{\infty} \frac{dn}{dF} dF = 1
-\end{equation}
-%%%
-
-\vspace{2\baselineskip}
-
-\end{document}
 

### 2015-11-16 luminosity.tex
flux distribution...??

@@
 \author{Yuka Fujii\altaffilmark{1}}
-\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}
+%\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}
 
@@
 %Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy.
-In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
-For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
-Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
-Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
-. Therefore, $\alpha_L \sim -3.1$.
 
-\vspace{2\baselineskip}
+We consider the number density of observed flux from targets within the distance $R$. 
+Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
+\vspace{1\baselineskip}
 
-Assume:
+Let us denote the number density of evolved stars per unit volume by $n$ and assume that the luminosity function can be written as follows. 
 %%%
-\begin{displaymath}
+\begin{equation}
 \frac{dn}{dL} = \left\{
@@
 \right. 
-\end{displaymath}
+\end{equation}
 %%%
-where $C $ is the proportional coefficient. 
+Here, $C $ is the proportional coefficient.
+
+Then, let us denote the (expected) total number of evolved stars in a sphere of radius $R$ by $N$.
+Consider a spherical shell at radius $r$ ($r<R$) with thickness $dr$.
+The number of evolved stars in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
 %%%
 \begin{equation}
-\frac{d^2n}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr 
+\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
 \end{equation}
@@
 
-The relationship between flux $F$ and Luminosity $L$ is:
+The relationship between flux $F$ and luminosity $L$ is, as usual,
 %%%
 \begin{equation}
-F = \frac{L}{r^2}
+F = \frac{L}{4\pi r^2} 
 \end{equation}
@@
 
-The number of the targets within distance $R$ which have flux at $F \sim F+dF$ is
+Now, we want to get the number of targets with flux between $F$ and $F+dF$. 
+To do so, we want to integrate equation (\ref{eq:d2N/dLdr}) over the parameter space $\mathcal{S}$ satisfying
+%%%
+\begin{equation}
+F < \left( \frac{L}{4\pi r^2} \right) < F+dF 
+\end{equation}
+%%%
+To do so, we change the set of variables from $\{ L,\,r \}$ to $\{ F,\,r \}$. 
+Thus,
 %%%
 \begin{eqnarray}
-\frac{dn}{dF} dF &=& \int dr \int dL \; \Psi (L, r) \\
-&=& \int _{F}^{F+dF} dF \int _0^{R} dr \; \Psi (F r^2, r)\; det(J) 
+\frac{dN}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
+&=& \int _0^{R} dr \int _{F}^{F+dF} dF' \;\; \Psi (4\pi r^2F', r)\; det(J) 
 \end{eqnarray}
@@
 \begin{equation}
-det(J) = \left| \PD{r}{r}\PD{L}{F} - \PD{r}{F}\PD{L}{r} \right| = r^2
+det(J) = \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
 \end{equation}
@@
 \begin{eqnarray}
-\frac{dn}{dF} dF &=& \left[ 4 \pi \int _0 ^{R} dr \; r^4 \Phi (F, r) \right] dF\\
+\frac{dN}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
 \Phi (F, r) &=& \left\{
 \begin{array}{ll}
-C (F r^2)^{-\alpha } & (\sqrt{L_{\rm min}/F} < r < \sqrt{L_{\rm max}/F}) \\
+C' F^{-\alpha } r^{4-2\alpha} & (\sqrt{L_{\rm min}/4 \pi F} < r < \sqrt{L_{\rm max}/4 \pi F}) \\
 0 & (\mbox{elsewhere})
 \end{array}
-\right. 
+\right. \\
+C' &\equiv & C ( 4 \pi )^{2-\alpha }
 \end{eqnarray}
@@
 \begin{eqnarray}
-&& \frac{dn}{dF} dF \\
+&& \frac{dN}{dF} dF \\
 && = \left\{
 \begin{array}{l}
-0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] dF \\
 \\
-\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] dF \\
 \\
-\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
 \end{array}
@@
 \begin{array}{l}
-0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
 \\
-\displaystyle \frac{4\pi C }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\displaystyle \frac{C' }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
 \\
-\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
 \\
-\displaystyle \frac{4\pi C F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\displaystyle \frac{C' F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
 \\
-\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
 \end{array}
@@
 %%%
+
+\vspace{1\baselineskip}
+
+For now, let us suppose
+%%%
+\begin{itemize}
+\item range of luminosity of ``evolved stars'':\\$L_{\odot }-10,000 L_{\odot }$
+\item $\Rightarrow$ minimum radio luminosity of ``RGHJs''\\%
+$L_{\rm min} = 2,1\times 10^{11}/30 {\rm MHz} = 7000 {\rm W/Hz}$
+\item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13} {\rm W}$
+\end{itemize}
+%%%
+We also assume $\alpha = -3.1$; see next subsection.
+
+\subsection{Actual luminosity function (?)}
+
+In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
+For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
+Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
+Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
+. Therefore, $\alpha \sim -3.1$.
+
+\end{document}
 

### 2015-11-23 ms.tex
add one sentence
discussion about ram pressure

@@
 %%%
-where $m_p$ is the proton mass. Thus, 
+where $m_p$ is the proton mass. 
+\revise{Thus, }{In equation (\ref{eq:stand-off}), we ignore the ram pressure of the particles from the planets. %
+}
 %%%
@@
 However, at this stage, the velocity of the stellar wind becomes slower than the escape velocity of the planetary companion and hence the stellar wind particles are expected to accrete onto the planets.
-\citet{spiegel+madhusudhan2012} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ as follows: 
+\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi–Hoyle accretion and} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ as follows: 
 %%%%%%%%%
@@
 Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
+
+\revise{}{Note that in this case the accretion radius is}
+%%%%%%%%%
+\begin{eqnarray}
+R_{\rm acc} = \frac{2GM_p}{v_{\rm rel}^2} \sim 
+\end{eqnarray}
+%%%%%%%%%
 
@@
 
+\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant.
+Therefore, what we could envision is...}
+
 As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
+\revise{}{We note that in this range }
 For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
@@
 Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 15 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.5\% \citep{cumming2008}.
-%
-Therefore, given that 148 (44) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10 \mu {\rm Jy}$, about 2-5 would actually be emitting the radio wave of our interest. %
+We could assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage.
+%
+Then, given that 148 (44) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10 \mu {\rm Jy}$, about 2-5 would actually be emitting the radio wave of our interest. %
 For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10\mu {\rm Jy}$ is 21 (5).
@@
 
+\color{blue}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Effect of ram pressure due to planetary outflow}
+
+At the red giant stage, the atmospheric temperature of planets increases to $> 1000 {\rm K}$. At this point, one might anticipate that planetary atmosphere starts to escape. 
+Also, the UV/X-ray produced from accretion may input energy for atmospheric molecules to escape. In this section, we briefly estimate these effects on the circumplanetary configuration.
+
+The escape parameter of RGHJs is:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{equation}
+\lambda _c = \frac{G M_p m_{\rm p}}{k T_c r_c} = 214 \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{T_c}{1000 {\rm K}} \right)^{-1} \left( \frac{r_c}{R_{\rm J}} \right)^{-1}
+\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+where $m_{\rm p}$ is mass of a hydrogen atom, $r_c$ is the radius of exobase. Therefore in most of the case the escape is safely assumed to be Jeans escape. 
+Escape rate of Jeans escape is: 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{equation}
+%\dot M = 4 \pi \rho_0 a r^2 \left( \frac{v_{\rm esc}(r_0)}{2a} \right)^2 \exp \left( - \frac{v_{\rm esc}^2 (r_0) }{2 a^2} + \frac{3}{2} \right)
+%\end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{eqnarray}
+%\Phi _{\rm Jeans} &=& 4 \pi r_c^2 \cdot \frac{n_c}{2 \sqrt{\pi}} B \sqrt{\frac{2 k_B T_c }{m}} ( 1 + \lambda _c ) e^{-\lambda _c} \\
+\Phi _{\rm Jeans} (r_c) &=& \frac{1}{\sigma } \sqrt{ \frac{2 G \bar \rho }{3} } \left( \lambda _c + 1 \right) \sqrt{ \lambda _c } e^{-\lambda _c} \\
+%&=& 1/(pi*(0.529e-10)**2)*sqrt(2*6.674e-11*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) 
+%&=& 1/(pi*(0.529)**2)*sqrt(2*66.74*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) * 1e14
+\end{eqnarray}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+and the ram pressure at distance $r$ due to such an outflow is
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{eqnarray}
+P_{\rm ram} (r) &=& m_{\rm p} \Phi _{\rm Jeans} (r_c) \left( \frac{r}{R_p} \right)^{-2} v_{\rm esc} \\
+% 1.674e-27 * 5.3e18 / 100.0 * 59.5e3 
+%&=& 5.27 \times 10^{-6} ~{\rm Pa} \; \left( \frac{r}{10~R_p} \right)^{-2} \left( \frac{M_p}{M_{\rm J}} \right)^{1/2}
+\end{eqnarray}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-12} ~{\rm Pa} $. 
+This implies that the ram pressure of the planetary outflow would be negligible when $\lambda _c > 15$. [NEED TO CHECK]
+
+\color{black}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Ionization Cascade}
 \label{sec:AppendixA}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-11-23 ms.tex
math corrected, minor edits

@@
-\documentclass[iop,numberedappendix,apj,]{emulateapj}
+\documentclass[iop,numberedappendix,apj,twocolappendix,]{emulateapj}
 
@@
 where $m_p$ is the proton mass. 
-\revise{Thus, }{In equation (\ref{eq:stand-off}), we ignore the ram pressure of the particles from the planets. %
+\revise{}{We note that the outflow from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
 }
+Thus, 
 %%%
@@
 However, at this stage, the velocity of the stellar wind becomes slower than the escape velocity of the planetary companion and hence the stellar wind particles are expected to accrete onto the planets.
-\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi–Hoyle accretion and} computed the accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ as follows: 
+\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi--Hoyle accretion where the accretion disk is}
+%%%%%%%%%
+\begin{eqnarray}
+R_{\rm acc} &=& \frac{2GM_p}{v_{\rm rel}^2} \\
+&\sim & 4.0~R_{\rm J} \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{v_{\rm rel}}{30 ~{\rm km~s^{-1}}} \right)^{-2}
+\end{eqnarray}
+%%%%%%%%%
+\revise{}{The accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are}
 %%%%%%%%%
@@
 Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
-
-\revise{}{Note that in this case the accretion radius is}
-%%%%%%%%%
-\begin{eqnarray}
-R_{\rm acc} = \frac{2GM_p}{v_{\rm rel}^2} \sim 
-\end{eqnarray}
-%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Effect of ram pressure due to planetary outflow}
-
-At the red giant stage, the atmospheric temperature of planets increases to $> 1000 {\rm K}$. At this point, one might anticipate that planetary atmosphere starts to escape. 
-Also, the UV/X-ray produced from accretion may input energy for atmospheric molecules to escape. In this section, we briefly estimate these effects on the circumplanetary configuration.
-
-The escape parameter of RGHJs is:
+\section{Planetary outflow}
+\label{ap:outflow}
+
+One might anticipate that, at the red giant stage, planetary atmosphere start to escape due to both the increased temperature due to stellar irradiation (typically $> 1000 {\rm K}$) and the UV/X-ray radiation produced by accretion from stellar wind.
+In this section, we briefly estimate these effects on the circumplanetary configuration.
+
+%One might anticipate that these factors increase the escape of planetary atmospheres, which could affect the pressure balance represented by equation (\ref{eq:stand-off}).
+
+The conventional escape parameter is computed for RGHJs as follows
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{equation}
-\lambda _c = \frac{G M_p m_{\rm p}}{k T_c r_c} = 214 \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{T_c}{1000 {\rm K}} \right)^{-1} \left( \frac{r_c}{R_{\rm J}} \right)^{-1}
+\lambda _c = \frac{G M_p m_{\rm p}}{k T_c r_c} = 218 \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{T_c}{1000 {\rm K}} \right)^{-1} \left( \frac{r_c}{R_{\rm J}} \right)^{-1}
 \end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-where $m_{\rm p}$ is mass of a hydrogen atom, $r_c$ is the radius of exobase. Therefore in most of the case the escape is safely assumed to be Jeans escape. 
-Escape rate of Jeans escape is: 
+where $T_c$ and $r_c$ are the radius and temperature at exobase. In most of the cases we consider, therefore, the escape is safely assumed to be Jeans escape. 
+The rate of Jeans escape is 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\Phi _{\rm Jeans} &=& 4 \pi r_c^2 \cdot \frac{n_c}{2 \sqrt{\pi}} B \sqrt{\frac{2 k_B T_c }{m}} ( 1 + \lambda _c ) e^{-\lambda _c} \\
-\Phi _{\rm Jeans} (r_c) &=& \frac{1}{\sigma } \sqrt{ \frac{2 G \bar \rho }{3} } \left( \lambda _c + 1 \right) \sqrt{ \lambda _c } e^{-\lambda _c} \\
+\Phi _{\rm Jeans} (r_c) &=& \frac{1}{\sigma } \sqrt{ \frac{G M_p}{2 R_p^3} } \left( \lambda _c + 1 \right) \sqrt{ \lambda _c } e^{-\lambda _c} \\
 %&=& 1/(pi*(0.529e-10)**2)*sqrt(2*6.674e-11*1330./3.0) * (20+1.0)*sqrt(20.)*exp(-20.0) 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-and the ram pressure at distance $r$ due to such an outflow is
+where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here [[OK??]]. 
+The ram pressure at distance $r$ due to such an outflow is
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{eqnarray}
-P_{\rm ram} (r) &=& m_{\rm p} \Phi _{\rm Jeans} (r_c) \left( \frac{r}{R_p} \right)^{-2} v_{\rm esc} \\
+P_{\rm ram} (r) &=& m_{\rm p} \Phi _{\rm Jeans} (r_c) \left( \frac{r}{R_p} \right)^{-2} v_{\rm esc} 
 % 1.674e-27 * 5.3e18 / 100.0 * 59.5e3 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-12} ~{\rm Pa} $. 
-This implies that the ram pressure of the planetary outflow would be negligible when $\lambda _c > 15$. [NEED TO CHECK]
+which indicates $3.6\times 10^{-7}~{\rm barye}$ even when $\lambda _c = 1$. 
+On the other hand, the ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-5} ~{\rm barye}$. 
+This implies that the ram pressure of the planetary outflow would be negligible.
 

### 2015-11-27 ms.tex
wrong number corrected

@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
-Assuming Jupiter-mass planets \revise{}{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{a reasonable number of}{148 (44)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
+Assuming Jupiter-mass planets \revise{}{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{a reasonable number of}{148 (12)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
 For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
@@
 \revise{}{Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. %
-Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 15 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.5\% \citep{cumming2008}.
-We could assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage.
-%
-Then, given that 148 (44) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10 \mu {\rm Jy}$, about 2-5 would actually be emitting the radio wave of our interest. %
-For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10\mu {\rm Jy}$ is 21 (5).
-Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity 10$\mu {\rm Jy}$.
+Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.9\% \citep{cumming2008}.
+%
+%(Here we assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage. ) %
+Given that 148 (12) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10~\mu {\rm Jy}$, about 2-6 would actually be emitting the radio wave of our interest at the level of $>10~\mu {\rm Jy}$.
+%
+For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$.
 %

### 2015-11-30 luminosity.tex
update luminosity function

@@
 %\usepackage{apjfonts}
-\usepackage{graphicx}
+%\usepackage{graphicx}
 \usepackage{epstopdf}
@@
 \usepackage{color}
+\def\plotoneh#1{\centering \leavevmode
+\includegraphics[clip=, width=.95\columnwidth]{#1}}
 
@@
 \newcommand{\PD}[2]{\frac{\partial {#1}}{\partial {#2}}}
+\newcommand{\memoYF}[1]{\color{red} #1 \color{black}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Luminosity Function Note \#1} 
+\section{Distribution of observed flux} 
 \label{sec:luminosity function}
@@
 
-Then, let us denote the (expected) total number of evolved stars in a sphere of radius $R$ by $N$.
+Then, let us denote the (expected) total number of evolved stars in a sphere of radius $R$ by $N_R$.
 Consider a spherical shell at radius $r$ ($r<R$) with thickness $dr$.
@@
 \begin{equation}
-\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
+\frac{d^2N_R}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
 \end{equation}
@@
 \begin{eqnarray}
-\frac{dN}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
+\frac{dN_R}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
 &=& \int _0^{R} dr \int _{F}^{F+dF} dF' \;\; \Psi (4\pi r^2F', r)\; det(J) 
@@
 \begin{eqnarray}
-\frac{dN}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
+\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
 \Phi (F, r) &=& \left\{
@@
 
-Thus,  
+Thus, when $\alpha \not = 2.5$,
 %%%
 \begin{eqnarray}
-&& \frac{dN}{dF} dF \\
+&& \frac{dN_R}{dF} dF \\
 && = \left\{
@@
 \\
-\displaystyle \frac{C' }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
 \\
@@
 
-\vspace{1\baselineskip}
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{dndF_alpha31.pdf}
+   \plotoneh{dndF_alpha15.pdf}
+   \caption{Number density of observed flux in $\mu {\rm Jy}$.}
+  \label{fig:dndF}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%
-We also assume $\alpha = -3.1$; see next subsection.
+With these assumptions, number density of observed flux is shown in Figure \ref{fig:dndF}. We consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ for demonstration.
 
-\subsection{Actual luminosity function (?)}
+\vspace{2\baselineskip}
+
+\section{Expected value for the highest flux within radius $R$}
+
+Let us consider that the probability of finding an object with flux in the range between $F$ and $F + dF$ is
+%%%
+\begin{equation}
+P (F) dF = \frac{1}{N_R} \frac{dN_R}{dF}
+\end{equation}
+%%%
+Note that $N_R$ is the {\it expected} total number of targets within radius $R$. \memoYF{not sure how to deal with the fact that this is expected number.}
+
+Then, the probability to find one object with flux higher than $\tilde F$ is
+%%%
+\begin{equation}
+P (> \tilde F) = \int _{\tilde F} ^{\infty}  P (F) \; dF 
+\end{equation}
+%%%
+In turn, the probability to find an object with flux lower than $\tilde F$ s
+%%%
+\begin{equation}
+P (< \tilde F) = 1 - P (> \tilde F)
+\end{equation}
+%%%
+Thus, the probability to find the maximum flux between $\tilde F \sim \tilde F + d\tilde F$, $\mathcal{P} (\tilde F) d\tilde F$ is
+%%%
+\begin{eqnarray}
+\mathcal{P} (\tilde F) d\tilde F &=& N P(\tilde F) d\tilde F \cdot \left[ P (< \tilde F) \right]^{N-1} \\
+&=& N P(\tilde F) d\tilde F \cdot \left[ 1 - P (> \tilde F) \right]^{N-1} \\
+&\sim & N P(\tilde F) d\tilde F \cdot \left[ 1 - ( N -1 ) P (> \tilde F) \right]
+\end{eqnarray}
+%%%
+
+So the expected value for the maximum flux, $<F_{\rm max}>$ is:
+%%%
+\begin{eqnarray}
+<F_{\rm max}> &=& \int \tilde F \mathcal{P} (\tilde F) \; d\tilde F \\
+&=& ...
+\end{eqnarray}
+%%%
+
+\memoYF{Not sure if the argument above is right}
+
+\vspace{2\baselineskip}
+
+\section{Power index of luminosity function (?)}
 

### 2015-12-02 ms.tex
added discussion about the electromagnetic structure around RGHJs and noted the list of M stars include AGB stars

@@
 However, at this stage, the velocity of the stellar wind becomes slower than the escape velocity of the planetary companion and hence the stellar wind particles are expected to accrete onto the planets.
-\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi--Hoyle accretion where the accretion disk is}
+\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi--Hoyle accretion where the accretion radius is}
 %%%%%%%%%
@@
 L_{\rm acc} \sim &&  10^{25} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{M_{\rm J}} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \\
+&& \times \left( \frac{M_p}{M_{\rm J}} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \label{eq:Lacc}\\
 %
@@
 \revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
-Therefore, what we could envision is...}
+The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
+Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. ??
+%While interacting with magnetic field, the ionized portion could lose their energy 
+%Therefore, some part of the incoming wind particles are what we could envision is the 
+%Considering other uncertainties of radio wave generation, we 
+The detailed electromagnetic structure around RGHJs therefore requires an elaborate numerical simulations, which is beyond the scope of this paper.
+Noting that all other uncertainties including the radio wave generation, in this paper we simply aim at giving an order-of-magnitude estimate.
+}
 
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{}{We note that in this range }
+\revise{}{We note that there data do not unambiguously distinguish RG from early AGB stars and thus the list likely includes about 40\% of early AGB stars. }
 For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:

### 2015-12-02 ms.tex
minor edits

@@
 
+As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind. 
+\revise{This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.}{}
+
 \revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
@@
 
-As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
-This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Estimates}
 \label{s:result}
@@
 $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
-
-\revise{}{Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. %
-Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.9\% \citep{cumming2008}.
-%
-%(Here we assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage. ) %
-Given that 148 (12) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10~\mu {\rm Jy}$, about 2-6 would actually be emitting the radio wave of our interest at the level of $>10~\mu {\rm Jy}$.
-%
-For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$.
-%
-}
 

### 2015-12-02 ms.tex
discussion about the expected number of detection

@@
 \label{eq:fplasmalos_scaled} &=& 12 {\rm~MHz} \times \left( \frac{a}{5~\mbox{AU}}\right)^{-1} \left(\frac{v}{30~\mbox{km/s}}  \right)^{-1/2} \notag \\
- & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \, .
+ & & \times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}}\right)^{1/2} \label{eq:fplasma_RG} \, .
 \end{eqnarray}
@@
 
+%YFYFYFYFYFYFYFYF
+
+\color{blue}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Expected number}
+\label{ss:detectability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. 
+For this purpose, we consider an empirical power-law planet occurrence rate described as
+%%%
+\begin{eqnarray}
+f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
+&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
+\end{eqnarray}
+%%%
+where they find $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
+Using this equation, the possibility of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
+%%%
+\begin{equation}
+\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
+\end{equation}
+%%%
+where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux.
+For the former, combining equations (\ref{eq:fcyc}) and (\ref{eq:fplasma_RG}) leads to
+%%%
+\begin{eqnarray}
+a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
+&&\times \left( \frac{\dot M}{10^{-8} M_{\odot}/{\rm yr}} \right)^{1/2} 
+\end{eqnarray}
+%%%
+while for the latter, equations (\ref{eq:scalingB}) and (\ref
+{eq:F_nu_RGHJ}) indicate
+%%%
+\begin{eqnarray}
+a_{\rm max} (M_p) &=& 3.80~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
+{-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
+&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
+&& \times \left( \frac{M_{\star }}{10^{-8}~M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
+\end{eqnarray}
+%%%
+They are translated into the orbital period via Kepler's law, $P_{\{{\rm min,max}\}} = 2\pi \sqrt{a^3_{\{{\rm min,max}\}} / GM_{\star } }$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{cumlative_expected_value.pdf}
+   \caption{}
+  \label{fig:expected_values}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Using equation (\ref{eq:detect_prob}), the expected number for $M_p > >M_{p0}$ planet with detectable radio emission is $\sum _i \mathcal{P} _i(>M_{p0})$, where $\mathcal{P}_i(>M_{p0})$ is the probability for the $i$-th target.
+
+Figure \ref{fig:expected_values} show the expected number of detection as a function of threshold planetary mass $M_{p0}$.
+This figure indicates that, if all of the target in Figure \ref{fig:observability} are red giant stars, %
+the total number of detections would be about 4 (7), provided that the sensitivity of the radio instruments $F_{\rm min}$ is $10~\mu {\rm Jy}$ ($5~\mu {\rm Jy}$). 
+However, such high sensitivity of the instrument will not be achieved at low frequency, which makes us consider massive planets as candidates. 
+Roughly assuming that $\nu _{\rm cyc} > 200~{\rm MHz} $ (i.e. $M_p > 7 M_{\rm J}$) is needed, then the expected values of detections would be reduced to 1-2.
+
+\color{black}
+
 \end{document}
+
+Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.9\% \citep{cumming2008}.
+%
+%(Here we assume the rate does not change significantly in red giant stage, while admitting the likely orbital evolution at this stage. ) %
+Given that 148 (12) systems with 1$M_{\rm J}$ planets at 1 AU (5 AU) have potential to emit $>10~\mu {\rm Jy}$, about 2-6 would actually be emitting the radio wave of our interest at the level of $>10~\mu {\rm Jy}$.
+%
+For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$.
 

### 2015-12-03 luminosity.tex
luminosity function memo updated

@@
 %\documentclass[12pt,preprint]{aastex}
-\documentclass[12pt]{emulateapj} 
+\documentclass[iop,numberedappendix,apj,twocolappendix,]{emulateapj} 
 \usepackage{amsmath}
@@
 \usepackage{amstext}
+\usepackage{natbib}
 %\usepackage{apjfonts}
 %\usepackage{graphicx}
+\usepackage{appendix}
 \usepackage{epstopdf}
@@
 \usepackage{url}
+
+\bibliographystyle{apj}
+
 %------------------------------------------
@@
 \title{Luminosity function of RGHJs}
-\author{Yuka Fujii\altaffilmark{1}}
+\author{%
+Yuka Fujii\altaffilmark{1}, %
+David S. Spiegel\altaffilmark{2,3,4}%
+}
+
+\affil{$^1$Earth-Life Science Institute, Tokyo Institute of Technology, 
+  Tokyo, JAPAN, 152-8550}
+
+\affil{$^2$Analytics \& Algorithms, Stitch Fix,
+  San Francisco, CA  94103}
+
+\affil{$^3$Research \& Development, Sum Labs,
+  New York, NY  10001}
+
 %\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}
@@
 \begin{abstract}
-N/A
+We examine how the highest observed flux evolves as we observe further. 
+Given a luminosity function characterized by a power law with lower and upper limits of luminosity, firstly we consider the distribution of observed flux from a sphere within distance $R$ of a given luminosity function ("flux function").
+The flux function composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
+Then, we compute the expected value of the highest flux from a spherical shell at distance $R\sim R+dR$. within a volume with radius $R$. 
 \end{abstract}
@@
 
-We consider the number density of observed flux from targets within the distance $R$. 
-Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
+In this section, we consider the number density of observed flux of the targets at spherical shell at distance $r$.
+
+In the following, Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
 \vspace{1\baselineskip}
@@
 
-Then, let us denote the (expected) total number of evolved stars in a sphere of radius $R$ by $N_R$.
-Consider a spherical shell at radius $r$ ($r<R$) with thickness $dr$.
+Then, let us denote the (expected) total number of evolved stars by $N$.
+Consider a spherical shell at radius $r$ with thickness $dr$.
 The number of evolved stars in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
@@
 \begin{equation}
-\frac{d^2N_R}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
+\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
 \end{equation}
@@
 
+Now, we want to change variables from $\{L,\,r\}$ to $\{F,\,r\}$. 
 The relationship between flux $F$ and luminosity $L$ is, as usual,
@@
 where $r$ is the distance to the target. 
-
-Now, we want to get the number of targets with flux between $F$ and $F+dF$. 
-To do so, we want to integrate equation (\ref{eq:d2N/dLdr}) over the parameter space $\mathcal{S}$ satisfying
+As changing the set of variables needs to employ Jacobian,
+%%%
+\begin{eqnarray}
+\frac{d^2 N}{dL dr} &=& \Psi (4\pi r^2F', r)\; det(J) \\
+det(J) &=& \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
+\end{eqnarray}
+%%%
+Therefore, the number density of the flux coming from the spherical shell is
 %%%
 \begin{equation}
-F < \left( \frac{L}{4\pi r^2} \right) < F+dF 
+\frac{d^2 N}{dF dr} = \left\{
+\begin{array}{ll}
+C' F^{-\alpha} r^{4-2\alpha } & (L_{\rm min} < F/4\pi r^2 < L_{\rm max}) \label{eq:dNdFdr} \\
+0 & (\mbox{elsewhere})
+\end{array}
+\right. 
 \end{equation}
 %%%
-To do so, we change the set of variables from $\{ L,\,r \}$ to $\{ F,\,r \}$. 
-Thus,
+where $C' \equiv (4 \pi )^{2-\alpha}$.
+
+%Therefore, 
+%%%
+%\begin{eqnarray}
+%\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
+%\Phi (F, r) &=& \left\{
+%\begin{array}{ll}
+%C' F^{-\alpha } r^{4-2\alpha} & (\sqrt{L_{\rm min}/4 \pi F} < r < \sqrt{L_{\rm max}/4 \pi F}) \\
+%0 & (\mbox{elsewhere})
+%\end{array}
+%\right. \\
+%C' &\equiv & C ( 4 \pi )^{2-\alpha }
+%\end{eqnarray}
+%%%
+
+The flux distribution of targets within radius $R$ can be obtained by integrating equation (\ref{eq:dNdFdr}) from $0$ to $R$. When $\alpha \not = 2.5$,
 %%%
 \begin{eqnarray}
-\frac{dN_R}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
-&=& \int _0^{R} dr \int _{F}^{F+dF} dF' \;\; \Psi (4\pi r^2F', r)\; det(J) 
-\end{eqnarray}
-%%%
-where
-%%%
-\begin{equation}
-det(J) = \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
-\end{equation}
-%%%
-
-Therefore, 
-%%%
-\begin{eqnarray}
-\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
-\Phi (F, r) &=& \left\{
-\begin{array}{ll}
-C' F^{-\alpha } r^{4-2\alpha} & (\sqrt{L_{\rm min}/4 \pi F} < r < \sqrt{L_{\rm max}/4 \pi F}) \\
-0 & (\mbox{elsewhere})
-\end{array}
-\right. \\
-C' &\equiv & C ( 4 \pi )^{2-\alpha }
-\end{eqnarray}
-%%%
-
-Thus, when $\alpha \not = 2.5$,
-%%%
-\begin{eqnarray}
-&& \frac{dN_R}{dF} dF \\
+&& \frac{dN_R}{dF} \\
 && = \left\{
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] dF \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] dF \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] \\
 \\
@@
 
-\newpage
+%\newpage
 
@@
 
-For now, let us suppose
+Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
+For demonstration, we consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ with $L_{\rm min } = 7000 {\rm W/Hz}$, $L_{\rm max} = 4.5\times 10^{13} {\rm W/Hz}$.
+The flux distribution from a spherical shell composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
+
+\newpage
+
+\section{Expected value for the highest flux from spherical shell at distance $r$}
+
+Let us consider a flux distribution of the targets from spherical shell at distance $r$.
+
+The probability of a star to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution:
+%%%
+\begin{equation}
+P(F) dF = \frac{dN_r}{dF} = C' F^{\alpha } r^{4-2\alpha }
+\end{equation}
+%%%
+where
+%%%
+\begin{equation}
+N_r = \frac{dN}{dr} 
+\end{equation}
+%%%
+Note that $N_r$ is the {\it expected} number. \memoYF{not sure how to deal with the fact that this is expected number.}
+
+Then, the probability to find one object with flux lower than $F'$ is
+%%%
+\begin{equation}
+P (<F') = \int _{-\infty} ^{F'}  P (F) \; dF 
+\end{equation}
+%%%
+
+The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux.
+Noting that we have $N_r$ ways to select the target with the highest flux, such a probability is:
+%%%
+\begin{equation}
+\mathcal{P} (F_{\rm max}) dF_{\rm max} = N_R P (< F_{\rm max})^{N_R-1}  P(F_{\rm max}) dF_{\rm max} %\\
+%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
+%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
+\end{equation}
+%%%
+
+The expected value for the maximum flux, $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
+%%%
+\begin{eqnarray}
+<F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
+&=& N_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{N_r-1}  P(F_{\rm max})
+\end{eqnarray}
+%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{Prob_alpha15.pdf}
+   \plotoneh{Prob_alpha31.pdf}
+   \caption{Flux distribution of targets in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+  \label{fig:prob}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{expectedFmax_alpha31.pdf}
+   \plotoneh{expectedFmax_alpha15.pdf}
+   \caption{Expected value for the maximum flux in $\mu {\rm Jy}$ from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+  \label{fig:dnrdF}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dnrdF}.
+For demonstration, we consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ with $L_{\rm min } = 7000 {\rm W/Hz}$, $L_{\rm max} = 4.5\times 10^{13} {\rm W/Hz}$.
+The flux distribution from a spherical shell composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
+
+\newpage
+
+\appendix
+
+\section{Luminosity function of Red Giant Hot Jupiters}
+
+In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
+For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+The improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
+%%%
+\begin{equation}
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
+\end{equation}
+%%%
+implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
+Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
+Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
+. Therefore, $\alpha \sim -3.1$.
+
+The upper and lower limits are tentatively assumed as follows. 
 %%%
@@
 %%%
-With these assumptions, number density of observed flux is shown in Figure \ref{fig:dndF}. We consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ for demonstration.
 
-\vspace{2\baselineskip}
-
-\section{Expected value for the highest flux within radius $R$}
-
-Let us consider that the probability of finding an object with flux in the range between $F$ and $F + dF$ is
-%%%
-\begin{equation}
-P (F) dF = \frac{1}{N_R} \frac{dN_R}{dF}
-\end{equation}
-%%%
-Note that $N_R$ is the {\it expected} total number of targets within radius $R$. \memoYF{not sure how to deal with the fact that this is expected number.}
-
-Then, the probability to find one object with flux higher than $\tilde F$ is
-%%%
-\begin{equation}
-P (> \tilde F) = \int _{\tilde F} ^{\infty}  P (F) \; dF 
-\end{equation}
-%%%
-In turn, the probability to find an object with flux lower than $\tilde F$ s
-%%%
-\begin{equation}
-P (< \tilde F) = 1 - P (> \tilde F)
-\end{equation}
-%%%
-Thus, the probability to find the maximum flux between $\tilde F \sim \tilde F + d\tilde F$, $\mathcal{P} (\tilde F) d\tilde F$ is
-%%%
-\begin{eqnarray}
-\mathcal{P} (\tilde F) d\tilde F &=& N P(\tilde F) d\tilde F \cdot \left[ P (< \tilde F) \right]^{N-1} \\
-&=& N P(\tilde F) d\tilde F \cdot \left[ 1 - P (> \tilde F) \right]^{N-1} \\
-&\sim & N P(\tilde F) d\tilde F \cdot \left[ 1 - ( N -1 ) P (> \tilde F) \right]
-\end{eqnarray}
-%%%
-
-So the expected value for the maximum flux, $<F_{\rm max}>$ is:
-%%%
-\begin{eqnarray}
-<F_{\rm max}> &=& \int \tilde F \mathcal{P} (\tilde F) \; d\tilde F \\
-&=& ...
-\end{eqnarray}
-%%%
-
-\memoYF{Not sure if the argument above is right}
-
-\vspace{2\baselineskip}
-
-\section{Power index of luminosity function (?)}
-
-In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
-For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
-Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
-Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
-. Therefore, $\alpha \sim -3.1$.
+\bibliography{biblio.bib}
 
@@
 
+Now, we want to get the number of targets with flux between $F$ and $F+dF$. 
+To do so, we want to integrate equation (\ref{eq:d2N/dLdr}) over the parameter space $\mathcal{S}$ satisfying
+%%%
+\begin{equation}
+F < \left( \frac{L}{4\pi r^2} \right) < F+dF 
+\end{equation}
+%%%
+To do so, we change the set of variables from $\{ L,\,r \}$ to $\{ F,\,r \}$. 
+Thus,
+%%%
+\begin{eqnarray}
+\frac{dN_R}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
+&=& \int _0^{R} dr \int _{F}^{F+dF} dF' \;\; \Psi (4\pi r^2F', r)\; det(J) 
+\end{eqnarray}
+%%%
+where
+%%%
+\begin{equation}
+det(J) = \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
+\end{equation}
+%%%
+
+Therefore, 
+%%%
+\begin{eqnarray}
+\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
+\Phi (F, r) &=& \left\{
+\begin{array}{ll}
+C' F^{-\alpha } r^{4-2\alpha} & (\sqrt{L_{\rm min}/4 \pi F} < r < \sqrt{L_{\rm max}/4 \pi F}) \\
+0 & (\mbox{elsewhere})
+\end{array}
+\right. \\
+C' &\equiv & C ( 4 \pi )^{2-\alpha }
+\end{eqnarray}
+%%%
+
+Thus, when $\alpha \not = 2.5$,
+%%%
+\begin{eqnarray}
+&& \frac{dN_R}{dF} \\
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
+\\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
+\\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
+\end{array}
+\right. \\
+%%%
+&& = \left\{
+\begin{array}{l}
+0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
+\\
+\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } }  \\
+\displaystyle \times \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
+\\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\\
+\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
+\end{array}
+\right. 
+\end{eqnarray}
+%%%
+
+\vspace{2\baselineskip}
+
+\newpage
+
+\section{Expected value for the highest flux within radius $R$}
+
+In order to estimate the expected value for the highest flux, we need to get the probability function for the highest flux.
+
+We may assume \memoYF{???} that the probability of finding an object with flux in the range between $F$ and $F + dF$ is proportional to the distribution of the observed flux. 
+%%%
+\begin{equation}
+P (F) dF = \frac{1}{N_R} \frac{dN_R}{dF}
+\end{equation}
+%%%
+Note that $N_R$ is the {\it expected} total number of targets within radius $R$. \memoYF{not sure how to deal with the fact that this is expected number.}
+
+Then, the probability to find one object with flux lower than $F'$ is
+%%%
+\begin{equation}
+P (<F') = \int _{-\infty} ^{F'}  P (F) \; dF 
+\end{equation}
+%%%
+So the probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is
+%%%
+\begin{equation}
+\mathcal{P} (F_{\rm max}) dF_{\rm max} = N_R P (< F_{\rm max})^{N_R-1}  P(F_{\rm max}) dF_{\rm max} %\\
+%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
+%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
+\end{equation}
+%%%
+Then, the expected value for the maximum flux, $<F_{\rm max}>$ is:
+%%%
+\begin{eqnarray}
+<F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
+&=& \int dF_{\rm max} F_{\rm max} N_R P (< F_{\rm max})^{N_R-1}  P(F_{\rm max})
+\end{eqnarray}
+%%%
+
 \end{document}

### 2015-12-04 luminosity.tex
minor updates
Update title & affil
text edit

@@
 
-\title{Luminosity function of RGHJs}
+\title{Luminosity function and flux function}
 \author{%
@@
 We examine how the highest observed flux evolves as we observe further. 
-Given a luminosity function characterized by a power law with lower and upper limits of luminosity, firstly we consider the distribution of observed flux from a sphere within distance $R$ of a given luminosity function ("flux function").
+This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further.
+%
+To answer this question, we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere.
+In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity, %
+We find the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away. 
+%we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
+%firstly we consider the distribution of observed flux from a sphere within distance $R$ of a given luminosity function ("flux function").
 The flux function composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
-Then, we compute the expected value of the highest flux from a spherical shell at distance $R\sim R+dR$. within a volume with radius $R$. 
+%Then, we compute the expected value of the highest flux from a spherical shell at distance $R\sim R+dR$. within a volume with radius $R$. 
 \end{abstract}
 
-\keywords{planetary systems --- planets and satellites: general}
+%\keywords{planetary systems --- planets and satellites: general}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Distribution of observed flux} 
+\section{Distribution of observed flux from a spherical shell} 
 \label{sec:luminosity function}
@@
 In this section, we consider the number density of observed flux of the targets at spherical shell at distance $r$. 
-
 In the following, Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
@@
 \begin{array}{ll}
-C' F^{-\alpha} r^{4-2\alpha } & (L_{\rm min} < F/4\pi r^2 < L_{\rm max}) \label{eq:dNdFdr} \\
+C' F^{-\alpha} r^{4-2\alpha } & (L_{\rm min} < 4\pi r^2 F < L_{\rm max}) \\
 0 & (\mbox{elsewhere})
 \end{array}
-\right. 
+\right. \label{eq:dNdFdr}
 \end{equation}
@@
 where $C' \equiv (4 \pi )^{2-\alpha}$.
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htbp]
+   \plotoneh{Prob_alpha15.pdf}
+   \plotoneh{Prob_alpha31.pdf}
+   \caption{Flux distribution of targets in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+  \label{fig:prob}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+\section{Distribution of observed flux within a sphere}
 
@@
 
-%\newpage
+\vspace{1\baselineskip}
+
+Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
+For demonstration, we consider $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$ for some reasons (Appendix).
+The flux distribution from a sphere composes of three regimes: in the order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
+
+\newpage
 
@@
    \plotoneh{dndF_alpha15.pdf}
-   \caption{Number density of observed flux in $\mu {\rm Jy}$.}
+   \caption{Flux distribution of targets within radius $R$ with varying power-law index and $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$.
+The $y$-axis is arbitrary.
+}
   \label{fig:dndF}
@@
 
-Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
-For demonstration, we consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ with $L_{\rm min } = 7000 {\rm W/Hz}$, $L_{\rm max} = 4.5\times 10^{13} {\rm W/Hz}$.
-The flux distribution from a spherical shell composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
-
 \newpage
 
-\section{Expected value for the highest flux from spherical shell at distance $r$}
+\section{Expected value for the highest flux from a spherical shell at distance $r$}
 
-Let us consider a flux distribution of the targets from spherical shell at distance $r$.
-
-The probability of a star to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution:
+Let us consider a flux distribution of the targets from a spherical shell at distance $r$ with thickness $dr$. 
+The ({\it expected}) total number of the target within that spherical shell is
 %%%
 \begin{equation}
-P(F) dF = \frac{dN_r}{dF} = C' F^{\alpha } r^{4-2\alpha }
+4 \pi r^2 dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \equiv n_r. 
+\end{equation}
+%%%
+\memoYF{not sure how to deal with the fact that this is expected number.}
+
+The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
+%%%
+\begin{equation}
+P(F) dF = C' F^{\alpha } r^{4-2\alpha }
 \end{equation}
@@
 \begin{equation}
-N_r = \frac{dN}{dr} 
+C' = n_r \left[ \int _0 ^{\infty}P(F)~dF~\right]^{-1}
 \end{equation}
 %%%
-Note that $N_r$ is the {\it expected} number. \memoYF{not sure how to deal with the fact that this is expected number.}
 
-Then, the probability to find one object with flux lower than $F'$ is
+The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux.
+The probability to find one object with flux lower than $F'$ is
 %%%
@@
 %%%
-
-The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux.
-Noting that we have $N_r$ ways to select the target with the highest flux, such a probability is:
+Noting that we have $n_r$ ways to select the target with the highest flux, such a probability is:
 %%%
 \begin{equation}
-\mathcal{P} (F_{\rm max}) dF_{\rm max} = N_R P (< F_{\rm max})^{N_R-1}  P(F_{\rm max}) dF_{\rm max} %\\
+\mathcal{P} (F_{\rm max}) dF_{\rm max} = n_r P (< F_{\rm max})^{n_r-1}  P(F_{\rm max}) dF_{\rm max} %\\
 %&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
@@
 
-The expected value for the maximum flux, $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
+The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
 %%%
@@
 <F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
-&=& N_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{N_r-1}  P(F_{\rm max})
+&=& n_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{n_r-1}  P(F_{\rm max})
 \end{eqnarray}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htbp]
-   \plotoneh{Prob_alpha15.pdf}
-   \plotoneh{Prob_alpha31.pdf}
-   \caption{Flux distribution of targets in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
-  \label{fig:prob}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Figure \ref{fig:expectedFmax} shows $<F_{\rm max}>$ as a function of distance $r$ with varying number density of the targets. 
+Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
+It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}
+
+\newpage
 
@@
    \caption{Expected value for the maximum flux in $\mu {\rm Jy}$ from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
-  \label{fig:dnrdF}
+  \label{fig:expectedFmax}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dnrdF}.
-For demonstration, we consider $\alpha = 3.1$ (see the last section) and $\alpha = 1.5$ with $L_{\rm min } = 7000 {\rm W/Hz}$, $L_{\rm max} = 4.5\times 10^{13} {\rm W/Hz}$.
-The flux distribution from a spherical shell composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
 
@@
 For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
-The improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
+The improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007} says:
 %%%
 \begin{equation}
-\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right), \label{eq:mass-loss}
 \end{equation}
 %%%
-implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
+which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$. 
+By crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
 Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
@@
 \item $\Rightarrow$ minimum radio luminosity of ``RGHJs''\\%
-$L_{\rm min} = 2,1\times 10^{11}/30 {\rm MHz} = 7000 {\rm W/Hz}$
-\item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13} {\rm W}$
+$L_{\rm min} = 2.1\times 10^{11} W/30\,{\rm MHz} = 7.0 \times 10^3\,{\rm W/Hz}$
+\item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13}{\rm W}/30\,{\rm MHz} = 1.5 \times 10^{6}\,{\rm W/Hz}$
 \end{itemize}

### 2015-12-04 ms.tex
minor edits

@@
 %%%
-where they find $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
-Using this equation, the possibility of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
+where \citet{cumming2008} found $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
+Using this equation, the probability of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
 %%%
@@
 a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
-&&\times \left( \frac{\dot M}{10^{-8} M_{\odot}/{\rm yr}} \right)^{1/2} 
+&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
 \end{eqnarray}
@@
 && \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
-&& \times \left( \frac{M_{\star }}{10^{-8}~M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
+&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
 \end{eqnarray}

### 2015-12-05 reply2referee.txt
add one note
response to referee is updated

@@
 
-1) response to ``The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere. ''
+1) response to ``The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere. '' => done
 
@@
 
-3) response to ``it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider. ''
+3) response to ``it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider. '' => done
 
@@
 
+5) revise Figure 4 (?)
+
 **********************
 
-                                                10 November 2015
+                                                12 December 2015
 
@@
 
-  - taking account of the shrinking of planetary magnetosphere. As a
-    result, our estimate of radio emission is order-of-magnitude off
-    of their estimate.
   - pointing out the presence of ionizing radition from accretion and
@@
     introduce.
+  - taking account of the shrinking of planetary magnetosphere. As a
+    result, our estimate of radio emission is order-of-magnitude off
+    of their scaling (eq. 20 of their paper).
   - taking account of the plasma frequency of stellar wind, which
@@
   suggestion, we attempted to reduce the materials as much as we think
-  reasonable <<<grammatically wrong?>>>.  There are some arguments
-  which we still think are worth part of the paper. We describe them
-  in the following, in reponse to each of referee's detailed comments.
+  reasonable.  There are some arguments which we still think are worth
+  part of the paper. We describe them in the following, in reponse to
+  each of referee's detailed comments.
 
@@
 
-  <<< ram pressure ??? >>>
+  We now added the discussion about the effect of planetary outflow in 
+  Appendix A.
 
@@
   answers this suggestion, where the expected flux from the known
-  system is estimated. We now improved the discussion by including the
-  effects of occurrence rate of Jupiter-like planets. <<< to do >>>
+  system is estimated. We now added explicitly mention the number of
+  potential targets above the detection limit. 
+  Another way to answer this question we think of is to convolute the 
+  planet occurrence rate, noting that not all of these targets are likely
+  to harbor a planet. Thus, we also addressed the expected value of
+  detection, based on the previously estimated occurrence rate of
+  Jupiter-size planets. The method to estimate that number is detailed in
+  Appendix D and the main text quotes them.

### 2015-12-06 ms.tex
minor edits

@@
 \begin{equation}
-B   \sim   10~{\rm G} \left( \frac{M_p }{M_{p,{\rm J}}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
+B   \sim   10~{\rm G} \left( \frac{M_p }{M_{\rm J}} \right)^{1.04} \left( \frac{t}{4.5~\rm{Gyr}} \right)^{-0.43} \label{eq:scalingB}
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbp]
-   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
+\begin{figure}[tbp]
+   \plotoneh{cartoon2_5Mj_100pc_smooth.pdf}
+%\begin{figure*}[tbp]
+%   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
    \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
 The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; contribution from Io-DAM is not shown here.
-The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law. }
+The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
+\revise{}{The shadowed region represents the frequency below the plasma frequency of the stellar wind.}}
   \label{fig:cartoon}
-\end{figure*}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
+
+\revise{}{A more relistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
+Observations of main-sequence stars implies that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
+Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be order of unity.  
+A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. 
+The analysis indicates that if the detection limit is 10$\mu {\rm Jy}$ the total expected value is about 3. }
+%However, as we see in the next subsection, the . and the expected value for massive planets ($M_p>5M_{\rm J}$) which supposedly have relatively high cyclotron frequency is about 1-2.
 
@@
 
+%\revise{}{The expected values for these targets are }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 radial-velocity observations, tests  the proposed scaling law of planetary dynamo.
-A extra fruit from observations of RGHJs in particular is that the lower cut-off frequency, which presumably corresponds to in situ plasma frequency, could probe of the stellar wind property at the planetary orbit.
+A extra fruit from observations of RGHJs in particular is that the lower cut-off frequency, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit.
 In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Expected number}
-\label{ss:detectability}
+\section{Expected Number of Detection Taking Account of Planet Occurrence Rate}
+\label{s:expectedvalue}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{figure}[htbp]
-   \plotoneh{cumlative_expected_value.pdf}
-   \caption{}
+   \plotoneh{cumulative_expected_value.pdf}
+   \caption{The expected number of radio detection of Jovian exoplanets above the given threshold mass. }
   \label{fig:expected_values}

### 2015-12-08 luminosity.tex
change formatting
Rephrase abstract; function () -> []

@@
 
-\title{Luminosity function and flux function}
+\title{Luminosity function and flux function\\
+or\\
+How far to the brightest beacon?}
 \author{%
 Yuka Fujii\altaffilmark{1}, %
-David S. Spiegel\altaffilmark{2,3,4}%
+David S. Spiegel\altaffilmark{2}%
 }
@@
 
-\affil{$^3$Research \& Development, Sum Labs,
-  New York, NY  10001}
-
 %\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}
@@
 \begin{abstract}
-We examine how the highest observed flux evolves as we observe further. 
-This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further.
+%We examine how the highest observed flux evolves as we observe further. 
+%This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further.
+Within a sphere centered on an observer, is the apparently-brightest source likely to be near the center of the sphere or near the periphery?
+The answer is not obvious because near the center (near the observer), brightness is increased by the inverse square law; however, far from the observer, there is much more volume available.
 %
 To answer this question, we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere.
-In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity, %
+In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity.
 We find the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away. 
@@
 
-In this section, we consider the number density of observed flux of the targets at spherical shell at distance $r$. 
-In the following, Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
+In this section, we consider the number density of observed flux of the targets in a spherical shell of radius $r$. 
+In the following, luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
 \vspace{1\baselineskip}
 
-Let us denote the number density of evolved stars per unit volume by $n$ and assume that the luminosity function can be written as follows. 
+Let us denote the number density of sources of a particular class (quasars, stars, ...) per unit volume by $n$ and assume that the luminosity function can be written as follows. 
 %%%
@@
 %%%
-Here, $C $ is the proportional coefficient.
+Here, $C $ is the coefficient of proportionality.
 
-Then, let us denote the (expected) total number of evolved stars by $N$.
+Then, let us denote the (expected) total number of sources by $N$.
 Consider a spherical shell at radius $r$ with thickness $dr$. 
-The number of evolved stars in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
+The number of sources in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
 %%%
 \begin{equation}
-\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
+\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi [L, r] dL dr \label{eq:d2N/dLdr}
 \end{equation}
@@
 \begin{eqnarray}
-\frac{d^2 N}{dL dr} &=& \Psi (4\pi r^2F', r)\; det(J) \\
-det(J) &=& \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
+\frac{d^2 N}{dL dr} &=& \Psi [4\pi r^2F', r]\; \det[J] \\
+\det[J] &=& \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
 \end{eqnarray}
@@
 where $C' \equiv (4 \pi )^{2-\alpha}$.
-
-\newpage
 
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right) \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right) \\
 \\
@@
 \\
-\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] \\
+\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right) \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right) \\
 \\
@@
 \begin{equation}
-C' = n_r \left[ \int _0 ^{\infty}P(F)~dF~\right]^{-1}
+C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
 \end{equation}
@@
 \begin{equation}
-P (<F') = \int _{-\infty} ^{F'}  P (F) \; dF 
+P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
 \end{equation}
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right) dF \\
 \\
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right) dF \\
 \\
@@
 &&= \frac{4 \pi C}{5 - 2 \alpha } \\
-&& \times \left[ \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
-&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right] dF \\
+&& \times \left( \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
+&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right) dF \\
 %
 &&= \frac{4 \pi C}{5 - 2 \alpha } \\
-&& \times \left\{ \left[ \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
-&&\left. + \left[ \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
+&& \times \left\{ \left( \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
+&&\left. + \left( \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
 &&\propto R 
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right) \\
 \\
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right) \\
 \\
@@
 &=& N \cdot p (L_{\rm max}) \cdot P^{N-1}(<L_{\rm max}) \cdot dL_{\rm max} \\
-&=& N C L_{\rm max}^{-\alpha } \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1}
+&=& N C L_{\rm max}^{-\alpha } \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1}
 \end{eqnarray}
@@
 < L_{\rm max} > (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
-&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1} \\
+&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1} \\
 &\equiv & N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max})
@@
 && \frac{d < L_{\rm max} >}{dl} = \frac{dN}{dl} \frac{d < L_{\rm max} >}{dN} \\
-&\propto & l^{2} \left[ \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max}) \right. \\
+&\propto & l^{2} \left( \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max}) \right. \\
 &&\left. + N (N-1) \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-2}(L_{\rm max}) \right]
@@
 \begin{eqnarray}
-\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
+\frac{dN_R}{dF} dF &=& \left( \int _0 ^{R} dr \; \Phi [F, r] \right) dF\\
 \Phi (F, r) &=& \left\{
@@
 \displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } }  \\
-\displaystyle \times \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
+\displaystyle \times \left( R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right) dF \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right) dF \\
 \\

### 2015-12-08 luminosity.tex
minor phrasing changes; more function () -> []; <> -> \langle \rangle

@@
 
-The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
+The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
 %%%
 \begin{equation}
-P(F) dF = C' F^{\alpha } r^{4-2\alpha }
+P[F] dF = C' F^{\alpha } r^{4-2\alpha }
 \end{equation}
@@
 
-The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux.
-The probability to find one object with flux lower than $F'$ is
+The probability that the maximum flux lies in the range between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$, denoted $\mathcal{P} [F_{\rm max}] dF_{\rm max}$, is the joint probability that one of the targets has flux between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$ and that all others have smaller flux.
+The probability that one object has flux lower than $F'$ is
 %%%
@@
 \begin{equation}
-\mathcal{P} (F_{\rm max}) dF_{\rm max} = n_r P (< F_{\rm max})^{n_r-1}  P(F_{\rm max}) dF_{\rm max} %\\
+\mathcal{P} [F_{\rm max}] dF_{\rm max} = n_r P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}] dF_{\rm max} %\\
 %&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
@@
 
-The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
+The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
 %%%
 \begin{eqnarray}
-<F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
-&=& n_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{n_r-1}  P(F_{\rm max})
+\langle F_{\rm max} \rangle &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} [F_{\rm max}] \\
+&=& n_r \int dF_{\rm max} F_{\rm max} P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}]
 \end{eqnarray}
@@
 
-Figure \ref{fig:expectedFmax} shows $<F_{\rm max}>$ as a function of distance $r$ with varying number density of the targets. 
+Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the targets. 
 Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
@@
 \begin{eqnarray}
-&&<F> = \int F \frac{dn}{dF} dF \\
+&&\langle F \rangle = \int F \frac{dn}{dF} dF \\
 %
@@
 \begin{equation}
-P(>L) = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
+P[>L] = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
 \end{equation}
@@
 \begin{equation}
-P(<L) = 1 -P (>L) \end{equation}
+P[<L] = 1 -P [>L] \end{equation}
 %%%
@@
 \begin{eqnarray}
-< L_{\rm max} > (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
+\langle L_{\rm max} \rangle (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
 &=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1} \\

### 2015-12-14 luminosity.tex
Minor changes (some 'target' -> 'source'; some 'for' -> 'of')

@@
 
-In this section, we consider the number density of observed flux of the targets in a spherical shell of radius $r$. 
+In this section, we consider the number density of observed flux of sources in a spherical shell of radius $r$.
 In the following, luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
@@
    \plotoneh{Prob_alpha31.pdf}
-   \caption{Flux distribution of targets in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+   \caption{Flux distribution of sources in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
   \label{fig:prob}
@@
 
-The flux distribution of targets within radius $R$ can be obtained by integrating equation (\ref{eq:dNdFdr}) from $0$ to $R$. When $\alpha \not = 2.5$,
+The flux distribution of sources within radius $R$ can be obtained by integrating equation (\ref{eq:dNdFdr}) from $0$ to $R$. When $\alpha \not = 2.5$,
 %%%
@@
    \plotoneh{dndF_alpha15.pdf}
-   \caption{Flux distribution of targets within radius $R$ with varying power-law index and $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$.
+   \caption{Flux distribution of sources within radius $R$ with varying power-law index and $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$.
 The $y$-axis is arbitrary.
@@
 
-\section{Expected value for the highest flux from a spherical shell at distance $r$}
+\section{Expected value of the highest flux from a spherical shell at distance $r$}
 
-Let us consider a flux distribution of the targets from a spherical shell at distance $r$ with thickness $dr$. 
-The ({\it expected}) total number of the target within that spherical shell is
+Let us consider the distribution of fluxes from sources from a spherical shell at distance $r$ with thickness $dr$.
+The ({\it expected}) total number of the sources within that spherical shell is
 %%%
@@
 
-The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
+The probability that a source within the spherical shell has a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
 %%%
@@
 
-The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
+The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
 %%%
@@
 
-Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the targets. 
+Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the sources. 
 Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 

### 2015-12-14 luminosity.tex
Switch order of n_r equation
didn't I push the revision I made last time...?

@@
 In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity.
-We find the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away.
+We find that \memoYF{...}
+%the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away. 
 %we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
@@
 \begin{figure}[htbp]
-   \plotoneh{Prob_alpha15.pdf}
-   \plotoneh{Prob_alpha31.pdf}
+   \plotoneh{Prob_alpha10.pdf}
+   \plotoneh{Prob_alpha30.pdf}
    \caption{Flux distribution of sources in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
@@
 \begin{equation}
-4 \pi r^2 dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \equiv n_r. 
+n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \, . 
 \end{equation}
@@
 \begin{equation}
-P[F] dF = C' F^{\alpha } r^{4-2\alpha }
+P[F] dF = \left\{
+\begin{array}{ll}
+C' F^{\alpha } r^{4-2\alpha } dF & (F_{\rm min}(r) < F < F_{\rm max}(r)) \\
+0 & (\mbox{elsewhere})
+\end{array}
+\right. 
 \end{equation}
@@
 %%%
-\begin{equation}
-C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
-\end{equation}
+\begin{eqnarray}
+C' &=& n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1} \\
+F_{\rm min}(r) &=& L_{\rm max} / 4 \pi r^2 \\
+F_{\rm max}(r) &=& L_{\rm max} / 4 \pi r^2
+\end{eqnarray}
 %%%
 
-The probability that the maximum flux lies in the range between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$, denoted $\mathcal{P} [F_{\rm max}] dF_{\rm max}$, is the joint probability that one of the targets has flux between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$ and that all others have smaller flux.
+The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
 The probability that one object has flux lower than $F'$ is
@@
 %%%
-Noting that we have $n_r$ ways to select the target with the highest flux, such a probability is:
+Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
 %%%
 \begin{equation}
-\mathcal{P} [F_{\rm max}] dF_{\rm max} = n_r P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}] dF_{\rm max} %\\
+\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
 %&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
@@
 
-The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
+The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the flowing integral. 
 %%%
 \begin{eqnarray}
-\langle F_{\rm max} \rangle &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} [F_{\rm max}] \\
-&=& n_r \int dF_{\rm max} F_{\rm max} P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}]
+\langle F_{\rm bright} \rangle &=& \int dF_{\rm bright} \, F_{\rm bright} \mathcal{P} [F_{\rm bright}] \\
+&=& n_r \int dF_{\rm bright} F_{\rm bright} P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}]
 \end{eqnarray}
@@
 
-Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the sources. 
-Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
-It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}
+Figure \ref{fig:expectedFmax} shows $\langle F_{\rm bright} \rangle$ as a function of distance $r$ with varying number density of the sources. 
+%It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}
 
@@
 \begin{figure}[htbp]
-   \plotoneh{expectedFmax_alpha31.pdf}
-   \plotoneh{expectedFmax_alpha15.pdf}
-   \caption{Expected value for the maximum flux in $\mu {\rm Jy}$ from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+   \plotoneh{expectedvalues_alpha-1_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
+   \plotoneh{expectedvalues_alpha-15_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
+   \plotoneh{expectedvalues_alpha-3_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
+   \caption{Expected value for the maximum flux from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) in the case of the number density of the objects is $10^{-3}\,{\rm pc^{-3}}$.
+Blue and red dashed lines show $F_{\rm max} = L_{\rm max}/4\pi r^2$ and $F_{\rm min} = L_{\rm min}/4\pi r^2$, respectively.
+Something is wrong with $\alpha=1.0$ case at $3000<F$.}
   \label{fig:expectedFmax}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{document}
 
@@
 \bibliography{biblio.bib}
-
-\end{document}
 

### 2015-12-14 luminosity.tex
figures updated
Eliminate appendix

--- 2015-12-08 luminosity.tex
@@
 \begin{abstract}
-%We examine how the highest observed flux evolves as we observe further. 
-%This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further.
-Within a sphere centered on an observer, is the apparently-brightest source likely to be near the center of the sphere or near the periphery?
-The answer is not obvious because near the center (near the observer), brightness is increased by the inverse square law; however, far from the observer, there is much more volume available.
+We examine how the highest observed flux evolves as we observe further. 
+This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further.
 %
 To answer this question, we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere.
-In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity.
+In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity, %
 We find the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away. 
@@
 
-In this section, we consider the number density of observed flux of the targets in a spherical shell of radius $r$. 
-In the following, luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
+In this section, we consider the number density of observed flux of the targets at spherical shell at distance $r$. 
+In the following, Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
 \vspace{1\baselineskip}
 
-Let us denote the number density of sources of a particular class (quasars, stars, ...) per unit volume by $n$ and assume that the luminosity function can be written as follows. 
+Let us denote the number density of evolved stars per unit volume by $n$ and assume that the luminosity function can be written as follows. 
 %%%
@@
 %%%
-Here, $C $ is the coefficient of proportionality.
+Here, $C $ is the proportional coefficient.
 
-Then, let us denote the (expected) total number of sources by $N$.
+Then, let us denote the (expected) total number of evolved stars by $N$.
 Consider a spherical shell at radius $r$ with thickness $dr$.
-The number of sources in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
+The number of evolved stars in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
 %%%
 \begin{equation}
-\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi [L, r] dL dr \label{eq:d2N/dLdr}
+\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
 \end{equation}
@@
 \begin{eqnarray}
-\frac{d^2 N}{dL dr} &=& \Psi [4\pi r^2F', r]\; \det[J] \\
-\det[J] &=& \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
+\frac{d^2 N}{dL dr} &=& \Psi (4\pi r^2F', r)\; det(J) \\
+det(J) &=& \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
 \end{eqnarray}
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right) \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right) \\
+\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right) \\
+\displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right) \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] \\
 \\
@@
 Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
-For demonstration, we consider $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$ for some reasons (Appendix).
+For demonstration, we consider $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$. 
 The flux distribution from a sphere composes of three regimes: in the order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
@@
 
-The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
+The probability for a star within the spherical shell to have a flux between $F\sim F+dF$, $P(F)dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
 %%%
 \begin{equation}
-P[F] dF = C' F^{\alpha } r^{4-2\alpha }
+P(F) dF = C' F^{\alpha } r^{4-2\alpha }
 \end{equation}
@@
 \begin{equation}
-C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
+C' = n_r \left[ \int _0 ^{\infty}P(F)~dF~\right]^{-1}
 \end{equation}
@@
 
-The probability that the maximum flux lies in the range between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$, denoted $\mathcal{P} [F_{\rm max}] dF_{\rm max}$, is the joint probability that one of the targets has flux between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$ and that all others have smaller flux.
-The probability that one object has flux lower than $F'$ is
+The probability to find the maximum flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$, $\mathcal{P} (F_{\rm max}) dF_{\rm max}$ is the joint probability where one of the targets has flux between $F_{\rm max} \sim F_{\rm max} + dF_{\rm max}$ and all others have smaller flux.
+The probability to find one object with flux lower than $F'$ is
 %%%
 \begin{equation}
-P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
+P (<F') = \int _{-\infty} ^{F'}  P (F) \; dF 
 \end{equation}
@@
 \begin{equation}
-\mathcal{P} [F_{\rm max}] dF_{\rm max} = n_r P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}] dF_{\rm max} %\\
+\mathcal{P} (F_{\rm max}) dF_{\rm max} = n_r P (< F_{\rm max})^{n_r-1}  P(F_{\rm max}) dF_{\rm max} %\\
 %&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
@@
 
-The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
+The expected value for the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $<F_{\rm max}>$, is obtained by calculating the flowing integral. 
 %%%
 \begin{eqnarray}
-\langle F_{\rm max} \rangle &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} [F_{\rm max}] \\
-&=& n_r \int dF_{\rm max} F_{\rm max} P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}]
+<F_{\rm max}> &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} (F_{\rm max}) \\
+&=& n_r \int dF_{\rm max} F_{\rm max} P (< F_{\rm max})^{n_r-1}  P(F_{\rm max})
 \end{eqnarray}
@@
 
-Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the targets. 
+Figure \ref{fig:expectedFmax} shows $<F_{\rm max}>$ as a function of distance $r$ with varying number density of the targets. 
 Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
@@
 
-\appendix
+%% \appendix
 
-\section{Luminosity function of Red Giant Hot Jupiters}
+%% \section{Luminosity function of Red Giant Hot Jupiters}
 
-In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
-For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
-The improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007} says:
-%%%
-\begin{equation}
-\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right), \label{eq:mass-loss}
-\end{equation}
-%%%
-which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$. 
-By crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
-Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
-Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
-. Therefore, $\alpha \sim -3.1$.
+%% In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
+%% For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
+%% The improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007} says:
+%% %%%
+%% \begin{equation}
+%% \dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right), \label{eq:mass-loss}
+%% \end{equation}
+%% %%%
+%% which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$. 
+%% By crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$.
+%% Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$.
+%% Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
+%% . Therefore, $\alpha \sim -3.1$.
 
-The upper and lower limits are tentatively assumed as follows. 
-%%%
-\begin{itemize}
-\item range of luminosity of ``evolved stars'':\\$L_{\odot }-10,000 L_{\odot }$
-\item $\Rightarrow$ minimum radio luminosity of ``RGHJs''\\%
-$L_{\rm min} = 2.1\times 10^{11} W/30\,{\rm MHz} = 7.0 \times 10^3\,{\rm W/Hz}$
-\item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13}{\rm W}/30\,{\rm MHz} = 1.5 \times 10^{6}\,{\rm W/Hz}$
-\end{itemize}
-%%%
+%% The upper and lower limits are tentatively assumed as follows. 
+%% %%%
+%% \begin{itemize}
+%% \item range of luminosity of ``evolved stars'':\\$L_{\odot }-10,000 L_{\odot }$
+%% \item $\Rightarrow$ minimum radio luminosity of ``RGHJs''\\%
+%% $L_{\rm min} = 2.1\times 10^{11} W/30\,{\rm MHz} = 7.0 \times 10^3\,{\rm W/Hz}$
+%% \item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13}{\rm W}/30\,{\rm MHz} = 1.5 \times 10^{6}\,{\rm W/Hz}$
+%% \end{itemize}
+%% %%%
 
-\bibliography{biblio.bib}
+%% \bibliography{biblio.bib}
 
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right) dF \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
 \\
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right) dF \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
 \\
@@
 \begin{eqnarray}
-&&\langle F \rangle = \int F \frac{dn}{dF} dF \\
+&&<F> = \int F \frac{dn}{dF} dF \\
 %
 &&= \frac{4 \pi C}{5 - 2 \alpha } \\
-&& \times \left( \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
-&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right) dF \\
+&& \times \left[ \int _{F_{\rm l}} ^{F_{u}} F^{1-\alpha } \left\{ R^{5-2\alpha } - \left( \frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right. dF \\
+&&+ \left. \int _{F_{u}} ^{\infty } F^{1-\alpha } \left\{ \left( \frac{L_{\rm max}}{F} \right)^{2.5-\alpha} - \left(\frac{L_{\rm min}}{F} \right)^{2.5-\alpha} \right\} \right] dF \\
 %
 &&= \frac{4 \pi C}{5 - 2 \alpha } \\
-&& \times \left\{ \left( \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
-&&\left. + \left( \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
+&& \times \left\{ \left[ \frac{F^{2-\alpha } R^{5-2\alpha }}{2-\alpha } - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right. \\
+&&\left. + \left[ \frac{F^{-0.5}L_{\rm max}^{2.5-\alpha} }{-0.5} - \frac{F^{-0.5}L_{\rm min}^{2.5-\alpha} }{-0.5} \right]_{F_l} ^{F_u} \right\} \\
 &&\propto R 
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right) \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] \\
 \\
@@
 \\
-\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left( \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right) \\
+\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] \\
 \\
@@
 \begin{equation}
-P[>L] = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
+P(>L) = \int _L^{\infty} C L^{-\alpha } dL = C \frac{L^{-\alpha +1}}{-\alpha + 1}
 \end{equation}
@@
 \begin{equation}
-P[<L] = 1 -P [>L] \end{equation}
+P(<L) = 1 -P (>L) \end{equation}
 %%%
@@
 &=& N \cdot p (L_{\rm max}) \cdot P^{N-1}(<L_{\rm max}) \cdot dL_{\rm max} \\
-&=& N C L_{\rm max}^{-\alpha } \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1}
+&=& N C L_{\rm max}^{-\alpha } \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\langle L_{\rm max} \rangle (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
-&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left( 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right)^{N-1} \\
+< L_{\rm max} > (N) &=& \int L_{\rm max} \cdot \mathcal{P_{\rm max}}(L_{\rm max}) \cdot dL_{\rm max} \\
+&=& N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} \left[ 1 - \left( \frac{CL_{\rm max}^{-\alpha+1}}{-\alpha+1} \right) \right]^{N-1} \\
 &\equiv & N C \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max})
@@
 && \frac{d < L_{\rm max} >}{dl} = \frac{dN}{dl} \frac{d < L_{\rm max} >}{dN} \\
-&\propto & l^{2} \left( \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max}) \right. \\
+&\propto & l^{2} \left[ \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-1}(L_{\rm max}) \right. \\
 &&\left. + N (N-1) \int dL_{\rm max} \cdot L_{\rm max}^{-\alpha +1} K^{N-2}(L_{\rm max}) \right]
@@
 \begin{eqnarray}
-\frac{dN_R}{dF} dF &=& \left( \int _0 ^{R} dr \; \Phi [F, r] \right) dF\\
+\frac{dN_R}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
 \Phi (F, r) &=& \left\{
@@
 \displaystyle \frac{C' }{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } }  \\
-\displaystyle \times \left( R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right) dF \\
+\displaystyle \times \left[ R^{5 - 2\alpha}F^{-\alpha }  (4 \pi )^{2.5-\alpha }  -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
 \\
@@
 \\
-\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left( L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right) dF \\
+\displaystyle \frac{C' F^{-2.5 }}{(5 - 2\alpha) (4 \pi )^{2.5-\alpha } } \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
 \\

### 2015-12-14 luminosity.tex

--- 2015-12-14 luminosity.tex
@@
    \plotoneh{Prob_alpha30.pdf}
-   \caption{Flux distribution of sources in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
+   \caption{Flux distribution of sources in a spherical shell at distance $r$ when $L_{\rm min}=1$ and $L_{\rm max}=10^6$.}
   \label{fig:prob}

### 2015-12-15 luminosity.tex
example figures for flux distirbution within radius R (fig.2) are now corresponding to fig.1.

@@
 
+Examples with $\alpha = 1.0$ and $\alpha = 3.0$ are shown in Figure \ref{fig:prob}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
    \plotoneh{Prob_alpha30.pdf}
-   \caption{Flux distribution of sources in a spherical shell at distance $r$ when $L_{\rm min}=1$ and $L_{\rm max}=10^6$.}
+   \caption{Flux distribution of sources in a spherical shell at distance $r$ when $L_{\rm min}=1$ and $L_{\rm max}=10^6$. Number density of the sources is assumed to be $10^{-3}~{\rm pc}^{-3}$.}
   \label{fig:prob}
@@
 
-Examples with $\alpha = 3.1$ and $\alpha = 1.5$ are shown in Figure \ref{fig:dndF}.
-For demonstration, we consider $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$. 
+Examples with $\alpha = 1.0$ and $\alpha = 3.0$ are shown in Figure \ref{fig:dndF}.
+For demonstration, we consider $L_{\rm min } = 1$, $L_{\rm max} = 10^6$. 
 The flux distribution from a sphere composes of three regimes: in the order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5.
@@
 \begin{figure}[htbp]
-   \plotoneh{dndF_alpha31.pdf}
-   \plotoneh{dndF_alpha15.pdf}
-   \caption{Flux distribution of sources within radius $R$ with varying power-law index and $L_{\rm min } = 7\times 10^3~{\rm W/Hz}$, $L_{\rm max} = 1.5\times 10^6~{\rm W/Hz}$.
-The $y$-axis is arbitrary.
-}
+   \plotoneh{dN_dF_alpha1.pdf}
+   \plotoneh{dN_dF_alpha3.pdf}
+   \caption{Flux distribution of sources within radius $R$ with varying power-law index and $L_{\rm min } = 1$, $L_{\rm max} = 10^6$.
+Number density of the sources is assumed to be $10^{-3}~{\rm pc}^{-3}$.}
   \label{fig:dndF}

### 2015-12-15 luminosity.tex
explanation about the fact that n_r is an expected value

@@
 \begin{equation}
-n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \, . 
+n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \label{eq:n_r}\, . 
 \end{equation}
 %%%
-\memoYF{not sure how to deal with the fact that this is expected number.}
+Note that the result of the right hand side is actually the {\it expected} number and, in reality, the source count should be an integer with some occurrence probability around this expected number.
 
@@
 \begin{eqnarray}
-C' &=& n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1} \\
+C' &=& \left( \int _{F_{\rm max}} ^{F_{\rm min}} F^{\alpha } r^{4-2\alpha } dF~dF~\right)^{-1} \\
 F_{\rm min}(r) &=& L_{\rm max} / 4 \pi r^2 \\
@@
 %%%
+Here, the right thing to do would be to take an infinite sum over integer values of $n_r$ with occurrence probability function, but for the sake of simplicity, here we simply assume $n_r$ computed by equation (\ref{eq:n_r}) is a good proxy.
 

### 2015-12-15 luminosity.tex
Adjustment to n_r sentence; flowing -> following

@@
 %%%
-Here, the right thing to do would be to take an infinite sum over integer values of $n_r$ with occurrence probability function, but for the sake of simplicity, here we simply assume $n_r$ computed by equation (\ref{eq:n_r}) is a good proxy.
+Strictly speaking, the mathematically correct thing to do here would be to take an infinite sum over integer values of $n_r$, weighted by the occurrence probability of that value of $n_r$.
+However, it is a reasonable proxy (and considerably simpler) to simply use the expected value of $n_r$, as given by equation (\ref{eq:n_r}).
 
-The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the flowing integral. 
+The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the following integral. 
 %%%

### 2015-12-19 reply2referee.txt
minor edits

@@
-***** TO DO LIST *****
-
-1) response to ``The authors should demonstrate that the ram pressure of any exoplanetary outflow induced by heating can also be neglected in determining the size of the magnetosphere. '' => done
-
-2) argue the necesity of ``Observability`` section, in particular S4.3 and S4.4.
-
-3) response to ``it would be useful if they included a brief calculation or statement of how many might be expected, particularly in the age ranges they consider. '' => done
-
-4) literature survey if 4.3 and 4.4 have been discussed already in previous papers
-
-5) revise Figure 4 (?)
-
-**********************
-
                                                 12 December 2015
@@
   In the revised manuscript, we tried to make these point clearer in
-  Introduction section. The revised parts are marked in bold font.
+  Introduction section. The revised parts are marked in bold and blue 
+  font.
 
@@
   terms of planetary mass and orbit, shown in Figure 3. Therefore, we
-  would like to retain the description in the main manuscript.  On the
-  other hand, it is true that the scaling of planetary magnetic field
-  is not a novel point of this paper (as explicitly mentioned in the
-  manuscript), so we removed some panels from figure 2.
+  would like to retain the description in the main manuscript.
 

### 2015-12-19 ms.tex
minor edits

@@
 The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
-Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. ??
+Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
 %While interacting with magnetic field, the ionized portion could lose their energy 
@@
 %Considering other uncertainties of radio wave generation, we 
-The detailed electromagnetic structure around RGHJs therefore requires an elaborate numerical simulations, which is beyond the scope of this paper.
-Noting that all other uncertainties including the radio wave generation, in this paper we simply aim at giving an order-of-magnitude estimate.
+The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper.
+Noting that all other uncertainties, in this paper we simply aim at giving an order-of-magnitude estimate.
 }

### 2015-12-20 ms.tex
a couple typo fixes

@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{}{We note that there data do not unambiguously distinguish RG from early AGB stars and thus the list likely includes about 40\% of early AGB stars. }
+\revise{}{We note that these data do not unambiguously distinguish RG from early AGB stars and thus the list likely includes about 40\% of early AGB stars. }
 For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
@@
 
-\revise{}{A more relistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
+\revise{}{A more realistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
 Observations of main-sequence stars implies that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
@@
 LOFAR-LBA's most sensitive band is centered at 60~MHz, and LOFAR-HBA's is at 150~MHz.
-Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the reciever noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, to obtain the sensitivity and imaging parameters in Table~\ref{tab:sens}.
+Given the strong frequency dependence of the effective aperture of a dipole antenna, and that the receiver noise temperature for LOFAR $\Trx \sim \Tsky$, we use the LOFAR Image Noise calculator\footnote{Heald; \url{http://www.astron.nl/~heald/test/sens.php}}, which is based on {\it SKA Memo 113}\footnote{Nijboer, Pandey-Pommier, \& de Bruyn; \url{http://www.skatelescope.org/uploaded/59513\_113\_Memo\_Nijboer.pdf}}, to obtain the sensitivity and imaging parameters in Table~\ref{tab:sens}.
 
@@
 \paragraph{Variability of the stellar wind (a few months $\sim $?)}
-If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variabililty of planetary radio emission.
+If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variability of planetary radio emission.
 Such variability might be expected to occur on timescales of several months to half-a-year as many M giants have semi-regular periodicities on the order of a few hundred days \citep{Kiss:1999aa}.

### 2015-12-20 ms.tex
minor revisions for grammar etc.

--- 2015-12-19 ms.tex
@@
 Note that in these papers, the scaling relation of planetary magnetic fields differ from paper to paper.
-In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic field based on \citet{christensen_et_al2009}. 
-We note that \revise{}{\citet{jardine2008} modeled the reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates which is not based on the ``radiometric Bode's law''.
-}
+In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic fields based on \citet{christensen_et_al2009}.
+We note that \revise{}{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{}{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
@@
 Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates for highly evolved stars compared to the previous result. 
-\revise{}{Additional two major updates from \citet{ignace2010} are the following. } 
-\revise{We also consider}{Firstly, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
+\revise{}{In addition, two major updates from \citet{ignace2010} are the following.}
+\revise{We also consider}{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
 \revise{Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
 Instead, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
-}{Secondly, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.
-}
+}{Second, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}
 
@@
 where $m_p$ is the proton mass. 
-\revise{}{We note that the outflow from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
+\revise{}{We note that the outflow ram pressures from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
 }
@@
 %%%%%%%%%
-\revise{}{The accretion luminosity $L_{\rm acc}$ and the temperature $T_{\rm acc}$ are}
+\revise{}{The accretion luminosity $L_{\rm acc}$ and temperature $T_{\rm acc}$ are}
 %%%%%%%%%

### 2015-12-20 reply2referee.txt
Edits to reply2referee.txt for flow.

@@
 preceded by "## ", and our own comments indented in the space that
-follows. We also revised the reference list to match the journal's
-nomenclature.
+follows.  We have also revised the reference list to match the
+journal's nomenclature.
 
@@
 done a better job of motivating some of the sections in our paper.
-For instance, we wrote the section about the canceling field generated
-by stellar-wind electrons, as they spiral down field lines in
-accreting onto the planet, in order to allay the reader's possible
+For instance, we wrote the section about the "canceling field"
+generated by stellar-wind electrons, as they spiral down field lines
+in accreting onto the planet, in order to allay the reader's possible
 concerns that the planetary magnetic field would be significantly
-attenuated by the canceling field generated by the massive stellar
-wind from an AGB star -- a possibility that we wrestled with for
-probably 100 hours.  We hope to save our readers from having to repeat
-the same thought process we went through by laying out the logic
-clearly.  However, it seems that we didn't explain well enough why we
-put this section in the paper; in this resubmission, we have tried to
-better motivate the parts that the referee thought were less germane.
+attenuated by the canceling field that would be generated by the
+massive stellar wind from an AGB star -- a possibility that we
+wrestled with for probably 100 hours.  We hope to save our readers
+from having to repeat the same thought process we went through by
+laying out the logic clearly.  However, it seems that we didn't
+explain well enough why we put this section in the paper; in this
+resubmission, we have tried to better motivate the parts that the
+referee thought were less germane.
 
@@
 Our manuscript presents a more detailed and accurate description of
-the ionisation profile around a planet accreting stellar wind than
+the ionization profile around a planet accreting stellar wind than
 that in Ignace et al.'s paper.  It is unusual, in our experience, for
@@
 
-  - pointing out the presence of ionizing radition from accretion and
-    quantitative evaluation of their ionizing effects. A mechanism to
+  - pointing out the presence of ionizing radiation from accretion and
+    quantitatively evaluating the ionizing effects. A mechanism to
     ionize otherwise neutral stellar wind has been briefly introduced
@@
     introduce.
-  - taking account of the shrinking of planetary magnetosphere. As a
-    result, our estimate of radio emission is order-of-magnitude off
-    of their scaling (eq. 20 of their paper).
+
+  - taking account of the shrinking of the planetary magnetosphere. As
+    a result, our estimate of radio emission is an order-of-magnitude
+    off of their scaling (eq. 20 of their paper).
+
   - taking account of the plasma frequency of stellar wind, which
@@
 
-  In the revised manuscript, we tried to make these point clearer in
-  Introduction section. The revised parts are marked in bold and blue 
-  font.
+  In the revised manuscript, we tried to make these points clearer in
+  the Introduction section.  The revised parts are marked in bold and
+  blue font.
 
@@
   by previous papers, with an intention of making the paper
-  self-contained and easy to follow. According to referee's
-  suggestion, we attempted to reduce the materials as much as we think
-  reasonable.  There are some arguments which we still think are worth
-  part of the paper. We describe them in the following, in reponse to
-  each of referee's detailed comments.
+  self-contained and easy to follow.  Based on the referee's
+  suggestions, we attempted to reduce the amount of background
+  material as much as we think reasonable.  There are some arguments
+  from the literature that we still think are worth being part of the
+  paper.  We describe them below, in reponse to the relevant parts of
+  the referee's detailed comments.
 
@@
 
-  We now included their papers in this section.
+  Good suggestion.  We now include their papers in this section.
 
@@
 
-  It is true that some of the points discussed here are not new
-  points. Nevertheless, we think it is our responsibility to clarify
-  our assumptions and that readers would be rather benefited from
-  these descriptions because these properties are not common sense in
-  the field of exoplanets.  It is necessary to quantitatively evaluate
-  not only the velocity but also significant mass-loss rate. Also, the
-  typical values of stellar wind density is helpful and necessary step
-  to discuss plasma frequency.
+  It is true that some of the text in this section is discussion of
+  the physics, and not new points/results.  Nevertheless, we think it
+  is our responsibility to clarify our assumptions and that readers
+  would benefit from these descriptions because these properties are
+  not common sense in the field of exoplanets.  It is necessary to
+  quantitatively evaluate not only the velocity but also the
+  significant mass-loss rate.  Also, knowing the typical values of
+  stellar wind density is helpful, and indeed a necessary step to
+  discuss plasma frequency.
 
@@
   radio emission as that of Solar-System planets.  Therefore we think
-  this is an important part of our work and we will not remove this
-  from the paper.
+  this is an important part of our work, and we believe that our
+  manuscript is not improved by removing it.
 
@@
 
-  As for the AGB stars, we believe it is important to discuss not only
-  potentially detectable signals but also the limitation of our
-  ability of detection. In addition, there are some parameter range
-  where AGB companions could be detected. Therefore, we think it is
-  worth including the discussion of AGB stars.
+  Regarding whether to include a discussion of AGB stars, we believe
+  it is important to discuss not only potentially detectable signals
+  but also the limitations of our ability to detect radio-emitting
+  planets.  In addition, there are some parameter ranges where AGB
+  companions could be detected.  Therefore, we think it is worth
+  including the discussion of AGB stars.
 
-  As for the comparison with "classical" hot Jupiters, we appreciate
-  referee's comments. We estimated the orbital velocity of our
+  Regarding the comparison with "classical" hot Jupiters, we
+  appreciate referee's comments.  The orbital velocity of our
   ``canonical hot Jupiter'' at 0.05 AU to be ~130 km/sec, which can
-  contribute 5% increase in the relative velocity. We mentioned in the
-  paragraph following equation (43).
+  contribute 5% increase in the relative velocity.  We now add the
+  following text in the paragraph following equation (43):
 
-  We now added the discussion about the effect of planetary outflow in 
+    "We also note that the orbital velocity of the canonical hot
+    Jupiters has been ignored in equation (45); the orbital velocity
+    at 0.05~AU around a Solar-mass star is $\sim$130~km~sec$^{-1}$,
+    which leads to only a $\sim$5\% increase of the relative velocity
+    between planet and wind particles."
+
+  We now add discussion about the effect of planetary outflow in
   Appendix A.
@@
 
-  We appreciate this feedback. We have indicated the unit in the title
-  of Figure 3.
+  We appreciate this feedback.  We have indicated the units in the
+  title of Figure 3.
 
@@
   in most exoplanet contexts, the signal from the planet is competing
-  against a much brighter star).  To devote 1 page to what the reader
-  is likely to be concerned is the strongest source of Noise in the
-  observations does not seem unreasonable to us.
+  against a much brighter star!).  To devote 1 page to what a reader
+  might be likely to be concerned is the strongest source of Noise in
+  the observations does not seem unreasonable to us.
 
-  We also think Section 4.3 and 4.4 are useful.  We are unaware of any
-  predictions in the literature that make it easy for the reader to
-  estimate the required duration of the observations describe in our
-  manuscript.  Specifically, we know of no such comparison for state
-  of the art facilities that is up to date for late 2015, nor do we
-  know of any consolidation of this information in one publication.
-  Predictions for future facilities become rapidly out of date as
+  We also think Sections 4.3 and 4.4 are useful.  We are unaware of
+  any predictions in the literature that make it easy for the reader
+  to estimate the required duration of the observations describe in
+  our manuscript.  Specifically, we know of no such comparison for
+  state-of-the-art facilities that is up to date for late 2015, nor do
+  we know of any consolidation of this information in one publication.
+  Predictions for future facilities rapidly become out of date as
   projects are descoped (or "rebaselined" in the case of the SKA), and
@@
   one can exploit the unique time variability of these signatures for
-  detection.  We think this is a crucial point to consider, as direct
+  detection.  We think this is a vital point to consider, as direct
   imaging would be impossible in the face of confusion from both
@@
 
-  Following the referee's comment, we cut Section 5.1, while some part
-  of it are merged with the last section (shown in bold font).  The
-  intention of Section 5 was to answer a potential concern about the
-  canceling field of far more massive stellar wind than sollar
-  wind. We have clarified this motivation and moved it to Appendix.
-  Previously we thought Appendix B might be useful for future workers
-  (since we often got confused when reading previous papers), but we
-  decided to cut it for the sake of brevity, as the referee suggested.
-
-  [DSS: I don't think it should be moved to the Appendix.]
+  Following the referee's comment, we have cut Section 5.1, moving
+  some parts of it to last section (shown in bold font) and other
+  parts to the Appendix.  The intention of Section 5 was to answer a
+  potential concern about the canceling field that would result from a
+  stellar wind that is much denser than that of the Sun.  In preparing
+  our original submission, we thought that the former Appendix B might
+  be useful for future workers (since we often got confused when
+  reading previous papers), but we decided to cut it for the sake of
+  brevity, as the referee suggests.
 
@@
 
-  As far as we understand the referee's feedback, Figure 5 partly
-  answers this suggestion, where the expected flux from the known
-  system is estimated. We now added explicitly mention the number of
-  potential targets above the detection limit. 
-  Another way to answer this question we think of is to convolute the 
-  planet occurrence rate, noting that not all of these targets are likely
-  to harbor a planet. Thus, we also addressed the expected value of
-  detection, based on the previously estimated occurrence rate of
-  Jupiter-size planets. The method to estimate that number is detailed in
-  Appendix D and the main text quotes them.
+  Figure 5 partly answers this question, where the expected flux from
+  the known system is estimated.  We have added a section to the
+  Appendix (and quoted results from it in the main text) that
+  explicitly addresses the referee's question in more detail by
+  estimating how many potential targets are likely to be brighter than
+  the detection limit.  In making this estimate, we take into account
+  the fact that not all of stellar targets are likely to harbor the
+  right kind of planet in the right orbital regime.

### 2015-12-20 ms.tex
Edits to reply2referee.txt for flow.

@@
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
-\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at $0.05 {\rm AU}$ around a Solar-mass star is $\sim 130~{\rm km/sec}$, which contributes to only $\sim $5\% increase of the velocity.
-}
+\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at 0.05~AU around a Solar-mass star is $\sim$130~km~sec$^{-1}$, which contributes to only $\sim$5\% increase of the velocity.}
 

### 2015-12-22 reply2referee.txt
elaborating the difference from Ignace's paper in the letter to the editor

@@
 ----
+Ignace considered ionization purely due to shock heating as the stellar
+wind flows past the exoplanet.  The physical picture we propose is 
+different, namely that significant ionization can occur as wind material
+is accreted onto the exoplanets surface.  We quantify this result as a
+function of distance from the planet and planetary mass while 
+considering the effect of secondary ionization by ionized electrons.  
+These results suggest substantial ionization to large radii.  As the 
+referee states that this section is new and as we can find no evidence
+of this scenario in Ignace 2010, we prefer to keep this section in the 
+manuscript.
+
+[YF: I added the section above to include Jason's feedback. Will we 
+remove the following part instead?]
 Our manuscript presents a more detailed and accurate description of

### 2015-12-22 reply2referee.txt
Significant rewrite of letter to editors: add paragraph setting context for our pushback

@@
-                                                12 December 2015
+                                                22 December 2015
 
@@
 
-  We realized upon reading the referee's report that we should have
-done a better job of motivating some of the sections in our paper.
-For instance, we wrote the section about the "canceling field"
-generated by stellar-wind electrons, as they spiral down field lines
-in accreting onto the planet, in order to allay the reader's possible
+  We were surprised to see that the referee's report suggests
+that our manuscript is an "amendment to the Ignace (2010) result" and
+that the manuscript's length could be reduced by a factor of four.
+Much of what the referee thinks is not new or original is either
+entirely new or pulls literature results together in new ways.  In
+this prefatory note to you, we'd like to point out a few examples of
+parts that the referee thought should be cut where we think the
+referee's judgment is misguided.
+
+  For instance, this comment from the report was surprising:
+----
+  "Section 2.5 This section is new, but not necessary, as Ignace
+   (2010) have already addressed the issue of the ionisation of the
+   exoplanetary exosphere."
+----
+Ignace considered ionization purely due to shock heating as the
+stellar wind flows past the exoplanet.  The physical picture we
+propose is different, namely that significant ionization can occur as
+wind material is accreted onto the exoplanets surface.  We quantify
+this result as a function of distance from the planet and planetary
+mass while considering the effect of secondary ionization by ionized
+electrons.  These results suggest substantial ionization to large
+radii.  Since the referee states that this section is new and as we
+can find no evidence of this scenario in Ignace (2010), we prefer to
+keep this section in the manuscript.  We note that it is unusual, in
+our experience, for a referee to say that a description that is new,
+correct, and more detailed than another description in the literature,
+is unnecessary.
+
+  Another example is the referee's comment about the section on radio
+observability: "Much of this section could be cut, saving perhaps
+section 4.2. Predictions for observations with different facilities
+have been made many times before."  We strongly disagree with the
+referee's judgment here; in fact, the section on radio observability
+could have been a separate short paper on its own.  Our reply to the
+referee below addresses this point, but we here hope to underscore
+that we believe there is no paper in the literature where one can find
+predictions for the observability of this class of object with
+state-of-the-art facilities in 2015-2016 and beyond; certainly, if
+such predictions exist in the literature, the referee did not point
+out where.
+
+  The referee's report did help us to realize where we could have done
+a better job motivating some of the sections in our paper.  For
+instance, we wrote the section about the "canceling field" generated
+by stellar-wind electrons, as they spiral down field lines in
+accreting onto the planet, in order to allay the reader's possible
 concerns that the planetary magnetic field would be significantly
@@
 
-  In addition, it appears that the referee and we have somewhat
-different philosophies regarding the purpose of a paper.  For example,
-the referee suggests that we eliminate the section "Assumptions for
+  Finally, it appears that the referee and we have somewhat different
+philosophies regarding the purpose of a paper.  For example, the
+referee suggests that we eliminate the section "Assumptions for
 planetary magnetic field" and instead simply state that we assume a
@@
 through the physics of the processes under discussion.
-
-  Finally, we point out that this comment from the report was
-surprising:
-----
-  "Section 2.5 This section is new, but not necessary, as Ignace
-   (2010) have already addressed the issue of the ionisation of the
-   exoplanetary exosphere."
-----
-Ignace considered ionization purely due to shock heating as the stellar
-wind flows past the exoplanet.  The physical picture we propose is 
-different, namely that significant ionization can occur as wind material
-is accreted onto the exoplanets surface.  We quantify this result as a
-function of distance from the planet and planetary mass while 
-considering the effect of secondary ionization by ionized electrons.  
-These results suggest substantial ionization to large radii.  As the 
-referee states that this section is new and as we can find no evidence
-of this scenario in Ignace 2010, we prefer to keep this section in the 
-manuscript.
-
-[YF: I added the section above to include Jason's feedback. Will we 
-remove the following part instead?]
-Our manuscript presents a more detailed and accurate description of
-the ionization profile around a planet accreting stellar wind than
-that in Ignace et al.'s paper.  It is unusual, in our experience, for
-a referee to say that a description that is new, correct, and more
-detailed than another description in the literature, is unnecessary.
 

### 2015-12-24 ms.tex
including Neil's comment

@@
 \allowdisplaybreaks[1]
-
 \bibliographystyle{apj}
@@
 \definecolor{DarkGreen}{rgb}{0.0, 0.6, 0.0}
+
+\def\revise#1#2{\color{blue}\sout{#1} {\bf #2} \color{black}}
+
+%%%%%%% this part is to be removed eventually %%%%%%%
 \def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}
-
-\def\revise#1#2{\color{blue}\sout{#1} {\bf #2} \color{black}}
+\def\memoYF#1{\color{red}$\leftarrow${\bf #1} \color{black}}
 
@@
 The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper.
-Noting that all other uncertainties, in this paper we simply aim at giving an order-of-magnitude estimate.
+Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate.
 }
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{}{We note that these data do not unambiguously distinguish RG from early AGB stars and thus the list likely includes about 40\% of early AGB stars. }
+\revise{}{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars.
+}\memoYF{Doesn't ``consists of'' sound like ``A is made of B''?}
 For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
@@
 \revise{}{A more realistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
-Observations of main-sequence stars implies that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
-Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be order of unity.  
+Observations of main-sequence stars imply that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
+Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be of order unity.  
 A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. 
@@
 radial-velocity observations, tests  the proposed scaling law of planetary dynamo.
-A extra fruit from observations of RGHJs in particular is that the lower cut-off frequency, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit.
+Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit.
 In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here [[OK??]]. 
+where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here \memoYF{OK??}. 
 The ram pressure at distance $r$ due to such an outflow is

### 2015-12-24 ms.tex
minor edits

@@
 
+%%% \sout will be removed before submission %%%
 \def\revise#1#2{\color{blue}\sout{#1} {\bf #2} \color{black}}
 
-%%%%%%% this part is to be removed eventually %%%%%%%
+%%% this part is to be removed eventually %%%
 \def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}
@@
 We note that \revise{}{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
-Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{}{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, though there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
+Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{}{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
-Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates for highly evolved stars compared to the previous result. 
+Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates \revise{for highly evolved stars}{} compared to the previous result. 
 \revise{}{In addition, two major updates from \citet{ignace2010} are the following.}
@@
 P_{\rm inp,\,k} &=& n v^3 \cdot \pi r_{\rm mag} ^2 \label{eq:Pinp_kin}, \\
-P_{\rm inp,\,m} &=& \pi v B_{\star\bot }^2 \cdot \pi r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
+P_{\rm inp,\,m} &=& (B_{\star\bot }^2/2\mu _0) \, v \cdot \pi r_{\rm mag} ^2 \label{eq:Pinp_mag} \, ,
 \end{eqnarray}
@@
 We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,{\rm J}}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p,{\rm J}} < M_p < 10M_{p, {\rm J}}$ (with core mass less than 10\%) converge to $0.8 R_{p,{\rm J}} < R_p < 1.2R_{p, {\rm J}}$ within 1 Gyr \citep{fortney2007}.
-For the density profile, we assume a polytrope gas sphere with index $n=1$, which results in:
+For the density profile, we \revise{}{follow \citet{griesmeier2007b} and} assume a polytrope gas sphere with index $n=1$, which results in:
 %%%%%%%%%% 
@@
 The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
-Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
+%Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
 %While interacting with magnetic field, the ionized portion could lose their energy 
@@
 \end{eqnarray}
-We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$. Therefore, for Jupiter-mass planets, only distant ones $\gtrsim 5 $  may emit the radio waves from the system. 
+We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$. 
+\revise{Therefore, for Jupiter-mass planets, only distant ones $\gtrsim 5 $  may emit the radio waves from the system. }{}
 The detectable parameter space will be presented in more detail in the next section.
@@
 Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
-The doubly hatched regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth.
+The doubly hatched regions in Figure \ref{fig:radio} indicate the parameter spaces where 
+%the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and 
+\revise{}{$\nu_{\rm cyc,\,max} < \nu_{\rm plasma}^{\rm los}$ and there is no hope to observe from Earth.}
+thus the radio emission from the planet cannot be observed from the Earth. 
 In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.
@@
 \revise{}{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars.
-}\memoYF{Doesn't ``consists of'' sound like ``A is made of B''?}
+}\memoYF{grammatical question: doesn't ``consists of'' sound like ``A is made of B''?}
 For each red giant, the mass-loss rate is estimated using the improved Reimers' equation \citep{reimers1975} given by \citet{schroder2005,schroder2007}:
@@
 
-\revise{}{A more realistic expected number of detection can be also evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
+\revise{}{A more realistic expected number of detection may be evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
 Observations of main-sequence stars imply that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
 Assuming the same population for RG systems, the expected number of actual detection from RGHJs would be of order unity. 
-A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. 
-The analysis indicates that if the detection limit is 10$\mu {\rm Jy}$ the total expected value is about 3. }
+A more detailed examination using the empirical planet mass function by \citet{cumming2008} is given in Appendix \ref{s:expectedvalue}. }
 %However, as we see in the next subsection, the . and the expected value for massive planets ($M_p>5M_{\rm J}$) which supposedly have relatively high cyclotron frequency is about 1-2.

### 2015-12-24 reply2referee.txt
Remove several ---'s
Remove word from 1 sentence of reply

@@
 
-  We were surprised to see that the referee's report suggests
-that our manuscript is an "amendment to the Ignace (2010) result" and
-that the manuscript's length could be reduced by a factor of four.
-Much of what the referee thinks is not new or original is either
-entirely new or pulls literature results together in new ways.  In
-this prefatory note to you, we'd like to point out a few examples of
-parts that the referee thought should be cut where we think the
-referee's judgment is misguided.
+  We were surprised to see the referee's report suggest that our
+manuscript is an "amendment to the Ignace (2010) result" and that the
+manuscript's length could be reduced by a factor of four.  Much of
+what the referee thinks is not new or original is either entirely new
+or pulls literature results together in new ways.  In this prefatory
+note to you, we'd like to point out a few examples of parts that the
+referee thought should be cut where we think the referee's judgment is
+misguided.
 
@@
 
---------------------------------------------------------------------------------------
+-----------------------------------------------------------------------------
 

### 2015-12-27 ms.tex
Rephrase Bohr radius sentence, and remove memo
strikethrough lines are removed

@@
 
-%%% \sout will be removed before submission %%%
-\def\revise#1#2{\color{blue}\sout{#1} {\bf #2} \color{black}}
+\def\revise#1{\color{blue}{\bf #2} \color{black}}
 
 %%% this part is to be removed eventually %%%
-\def\memoTM#1{\color{DarkGreen}${\bf #1}$ \color{black}}
 \def\memoYF#1{\color{red}$\leftarrow${\bf #1} \color{black}}
@@
 In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic fields based on \citet{christensen_et_al2009}.
-We note that \revise{}{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
-Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{}{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
+We note that \revise{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
+Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
 
@@
 They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission. 
-\revise{}{In addition, they considered the scenario where the post-bow shock heating could produce ionized hydrogen atoms.
+\revise{In addition, they considered the scenario where the post-bow shock heating could produce ionized hydrogen atoms.
 This indicates a configuration of radio wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit.
@@
 
-In this paper, we \revise{argue that}{consider another plausible scenario where} the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
+In this paper, we \revise{consider another plausible scenario where} the accretion of the massive stellar wind onto the planet would emit UV and X-ray photons that ionize the stellar wind in the vicinity of the planet.
 The ionized stellar wind particles would then interact with the planetary magnetic field in the same way as Solar System planets do.
-Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates \revise{for highly evolved stars}{} compared to the previous result. 
-\revise{}{In addition, two major updates from \citet{ignace2010} are the following.}
-\revise{We also consider}{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
-\revise{Given that the survey of exoplanets around highly evolved stars is not complete, we do not constrain ourselves to the systems known to have sub-stellar companions.
-Instead, we investigate the parameter space where we can search for radio emission and examine the possibility to detect them with current and future instruments.
-}{Second, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}
+Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates compared to the previous result. 
+\revise{In addition, two major updates from \citet{ignace2010} are the following.}
+\revise{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
+\revise{Second, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}
 
@@
 Estimates for the actual late-type (M type) evolved stars are also included. 
-\revise{Section \ref{s:discussion} is devoted to additional discussions, one for the usefulness of the radio emission to characterize the system and the other for the effects of canceling magnetic field which results from the plasmas spiraling in the planetary magnetosphere.}
 Finally, Section \ref{s:conc} concludes the paper with a brief summary.
@@
 
-In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, \revise{$3.2\times 10^{10}$}{$8.2\times 10^{10}$} W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
+In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, \revise{$8.2\times 10^{10}$} W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
 Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
@@
 where $m_p$ is the proton mass. 
-\revise{}{We note that the outflow ram pressures from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
+\revise{We note that the outflow ram pressures from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
 }
@@
 We consider Jupiter-like gaseous planets and assume that the planetary radius is constant at $R_p = R_{p,{\rm J}}$, as numerical calculations show that the radii of gaseous planets over the range of $0.1 M_{p,{\rm J}} < M_p < 10M_{p, {\rm J}}$ (with core mass less than 10\%) converge to $0.8 R_{p,{\rm J}} < R_p < 1.2R_{p, {\rm J}}$ within 1 Gyr \citep{fortney2007}.
-For the density profile, we \revise{}{follow \citet{griesmeier2007b} and} assume a polytrope gas sphere with index $n=1$, which results in:
+For the density profile, we \revise{follow \citet{griesmeier2007b} and} assume a polytrope gas sphere with index $n=1$, which results in:
 %%%%%%%%%% 
@@
 However, at this stage, the velocity of the stellar wind becomes slower than the escape velocity of the planetary companion and hence the stellar wind particles are expected to accrete onto the planets.
-\citet{spiegel+madhusudhan2012} \revise{}{considered Bondi--Hoyle accretion where the accretion radius is}
+\citet{spiegel+madhusudhan2012} \revise{considered Bondi--Hoyle accretion where the accretion radius is}
 %%%%%%%%%
@@
 %%%%%%%%%
-\revise{}{The accretion luminosity $L_{\rm acc}$ and temperature $T_{\rm acc}$ are}
+\revise{The accretion luminosity $L_{\rm acc}$ and temperature $T_{\rm acc}$ are}
 %%%%%%%%%
@@
 As a whole, we expect for the X-ray emission from the accretion onto the planet to ionize the incoming stellar wind.
-\revise{This implies that the stellar wind particles represented by equation (\ref{eq:n}) are nearly fully ionized plasmas like Solar wind, and that the stellar wind can interact with the planetary magnetic fields in a rather similar way to the case of Solar System planets.}{}
-
-\revise{}{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
+
+\revise{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
 The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
@@
 We can see emission only from where $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$. 
-\revise{Therefore, for Jupiter-mass planets, only distant ones $\gtrsim 5 $  may emit the radio waves from the system. }{}
 The detectable parameter space will be presented in more detail in the next section.
@@
 Depending on the modeling of magnetic field strength, there is also speculation that the tidally-locked planets may have weaker magnetic fields due to slow rotation \citep[e.g.][]{griesmeier2004}; in that case the radio emission would be weaker.
-\revise{}{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at 0.05~AU around a Solar-mass star is $\sim$130~km~sec$^{-1}$, which contributes to only $\sim$5\% increase of the velocity.}
+\revise{We also note that the orbital velocity of the canonical hot Jupiters has been ignored in equation (\ref{eq:P_HJ}); the orbital velocity at 0.05~AU around a Solar-mass star is $\sim$130~km~sec$^{-1}$, which contributes to only $\sim$5\% increase of the velocity.}
 
@@
 %the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and 
-\revise{}{$\nu_{\rm cyc,\,max} < \nu_{\rm plasma}^{\rm los}$ and there is no hope to observe from Earth.}
+\revise{$\nu_{\rm cyc,\,max} < \nu_{\rm plasma}^{\rm los}$ and there is no hope to observe from Earth.}
 thus the radio emission from the planet cannot be observed from the Earth. 
@@
 The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
-\revise{}{The shadowed region represents the frequency below the plasma frequency of the stellar wind.}}
+\revise{The shadowed region represents the frequency below the plasma frequency of the stellar wind.}}
   \label{fig:cartoon}
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{}{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars.
+\revise{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars.
 }\memoYF{grammatical question: doesn't ``consists of'' sound like ``A is made of B''?}
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
-Assuming Jupiter-mass planets \revise{}{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{a reasonable number of}{148 (12)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
+Assuming Jupiter-mass planets \revise{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{148 (12)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
 For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
@@
 
-\revise{}{A more realistic expected number of detection may be evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
+\revise{A more realistic expected number of detection may be evaluated by combining these results with the probability for a star to have a planet with certain mass and orbit,  %
 Observations of main-sequence stars imply that the number of Jovian planets is about a few to ten percent of the number of stars \citep[e.g.][]{cumming2008,cassan2012}. %
@@
 
-%\revise{}{The expected values for these targets are }
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \revise{%
-Finally, we note that the radio emission considered in this paper can either be an avenue to learn more about known RGHJs or a tool for discovering new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
-Once planetary radio emission is detected, it will provide a unique approach for learning about the planetary spin, magnetic field, presence of satellites, and potentially the stellar wind properties.%
-}{%
 Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-where $\sigma $ is the cross section of hydrogen atoms, assumed to be equal to Bohr radius here \memoYF{OK??}. 
+where $\sigma $ is the cross section hydrogen, here taken to be the geometric cross section associated with the Bohr radius.
 The ram pressure at distance $r$ due to such an outflow is
@@
 
-\revise{One might expect}{Given that the density of stellar wind of evolved stars is fairly high, one might anticipate }
-that \revise{}{massive} plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field.
+\revise{Given that the density of stellar wind of evolved stars is fairly high, one might anticipate }
+that \revise{massive} plasma flowing into a region permeated by a magnetic field would, by spiraling around the field lines, generate an opposing magnetic field that partially cancels the intrinsic planetary magnetic field.
 To estimate the strength of this effect, consider a uniform flow of particles of charge $e$, mass $m$, and velocity $v$ into a region of magnetic field $B$, spiraling along the initial magnetic field.

### 2015-12-27 ms.tex
affiliation revised

@@
 
-\def\revise#1{\color{blue}{\bf #2} \color{black}}
+\def\revise#1{\color{blue}{\bf #1} \color{black}}
 
@@
 %
-Yuka Fujii\altaffilmark{1} 
-%
-David S. Spiegel\altaffilmark{2,3,4}
-%
-Tony Mroczkowski\altaffilmark{5,6}
-%
-Jason Nordhaus\altaffilmark{7,8}\\
-%
-Neil T. Zimmerman\altaffilmark{9}
-%
-Aaron Parsons\altaffilmark{10}
-%
-Mehrdad Mirbabayi\altaffilmark{4}
-%
-Nikku Madhusudhan\altaffilmark{11}
+Yuka Fujii\altaffilmark{1,2} 
+%
+David S. Spiegel\altaffilmark{3,4,5}
+%
+Tony Mroczkowski\altaffilmark{6,7}
+%
+Jason Nordhaus\altaffilmark{8,9}\\
+%
+Neil T. Zimmerman\altaffilmark{10}
+%
+Aaron Parsons\altaffilmark{11}
+%
+Mehrdad Mirbabayi\altaffilmark{5}
+%
+Nikku Madhusudhan\altaffilmark{12}
 }
@@
 
-\affil{$^2$Analytics \& Algorithms, Stitch Fix,
+\affil{$^2$NASA Goddard Institute for Space Studies, 
+  New York, NY 10025}
+
+\affil{$^3$Analytics \& Algorithms, Stitch Fix,
   San Francisco, CA  94103}
 
-\affil{$^3$Research \& Development, Sum Labs,
+\affil{$^4$Research \& Development, Sum Labs,
   New York, NY 10001}
 
-\affil{$^4$Astrophysics Department, Institute for Advanced Study,
+\affil{$^5$Astrophysics Department, Institute for Advanced Study,
   Princeton, NJ 08540}
 
-\affil{$^5$National Research Council Fellow}
-
-\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
-
-\affil{$^7$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^8$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}
-
-\affil{$^9$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
-
-\affil{$^{10}$Astronomy Department, University of California Berkeley}
-
-\affil{$^{11}$Astronomy Department, University of Cambridge, UK}
+\affil{$^6$National Research Council Fellow}
+
+\affil{$^7$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}
+
+\affil{$^8$Department of Science and Mathematics, National Technical Institute for the Deaf, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^9$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}
+
+\affil{$^10$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218}
+
+\affil{$^{11}$Astronomy Department, University of California Berkeley}
+
+\affil{$^{12}$Astronomy Department, University of Cambridge, UK}
 \vspace{0.5\baselineskip}

### 2015-12-27 ms.tex
likely => probably

@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list likely consists of about 40\% early AGB stars.
+\revise{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list probably consists of about 40\% early AGB stars.
 }\memoYF{grammatical question: doesn't ``consists of'' sound like ``A is made of B''?}
@@
 
-YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
+YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science and from an appointment to the NASA Postdoctoral
+Program at NASA Ames Research Center, administered by Oak Ridge Affiliated Universities. 
 DSS gratefully acknowledges support from a fellowship from the AMIAS group. JN acknowledges support from NASA grant HST AR-12146.04-A and NSF grant AST-1102738.

### 2015-12-28 ms.tex
Minor change -- put sentence on its own line.
revision of the last part of section 2, plus minor edits

@@
 
-\revise{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
-The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
-%Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
-%While interacting with magnetic field, the ionized portion could lose their energy 
-%Therefore, some part of the incoming wind particles are what we could envision is the 
-%Considering other uncertainties of radio wave generation, we 
+\revise{In reality, the temperature and luminosity based on the Bondi-Hoyle accretion (Eq.
+(\ref{eq:Lacc} and (\ref{eq:Tacc}) describes the situation only approximately.
+Precisely, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field, and the ionized portion would lose some energy at the bow shock before it accretes.
+On the other hand, the ionized plasmas interacting with magnetic field could have a cross section larger than the Bondi–Hoyle accretion radius.
 The detailed electromagnetic structure around RGHJs therefore requires elaborate numerical simulations, which is beyond the scope of this paper.
@@
 \revise{%
-Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property.
+Once planetary radio emission is detected, it provides a unique approach for learning the planetary property.
 As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites.
@@
 radial-velocity observations, tests  the proposed scaling law of planetary dynamo.
-Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit.
-In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
+Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, probes the stellar wind properties at the planetary orbit.
+In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
 %

### 2015-12-28 ms.tex
couple corrections

@@
 
-\revise{In reality, the temperature and luminosity based on the Bondi-Hoyle accretion (Eq.
-(\ref{eq:Lacc} and (\ref{eq:Tacc}) describes the situation only approximately.
+\revise{In reality, the temperature and luminosity based on the Bondi--Hoyle accretion (equations (\ref{eq:Lacc} and (\ref{eq:Tacc})) describes the situation only approximately.
 Precisely, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field, and the ionized portion would lose some energy at the bow shock before it accretes.
-On the other hand, the ionized plasmas interacting with magnetic field could have a cross section larger than the Bondi–Hoyle accretion radius.
+On the other hand, the ionized plasmas interacting with magnetic field could have a cross section larger than the Bondi--Hoyle accretion radius.
 The detailed electromagnetic structure around RGHJs therefore requires elaborate numerical simulations, which is beyond the scope of this paper.
@@
 %the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and 
-\revise{$\nu_{\rm cyc,\,max} < \nu_{\rm plasma}^{\rm los}$ and there is no hope to observe from Earth.}
-thus the radio emission from the planet cannot be observed from the Earth. 
+\revise{$\nu_{\rm cyc,\,max} < \nu_{\rm plasma}^{\rm los}$ and there is no hope to observe it from below the ionosphere.}
+%thus the radio emission from the planet cannot be observed from the Earth. 
 In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.

### 2015-12-29 ms.tex
fudge factor 6 for a 1M_J planet is strange and thus removed.

@@
 \begin{figure}[htbp]
-   \plotoneh{ionizationfraction.pdf}
+   \plotoneh{ionizationfraction2.pdf}
    \caption{Profile of ionization fraction measured from the surface of the planet, due to UV/X-ray from the accretion of stellar wind onto the planet.
-     Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, while the dashed lines show the solutions which take the correction into account with efficiency factor $N_i=6$.
+     Solid lines show the solutions without the correction for the secondary ionization by ionized electrons, and the dashed line shows the solution for a  10$M_{\rm J}$ planet taking the correction into account with efficiency factor $N_i=6$.
      The vertical arrows show the Str\"omgren radius estimated simply by equation (\ref{eq:stromgren}).
@@
 %%%%%%%%%
-The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and dashed lines show that corresponding to $N_i=6$.
+The solid lines show the ionization fraction corresponding to no additional ionization by electrons (i.e., $\xi=0$, or $N_i = 1$) and \revise{the dashed line shows the solution with $N_i=6$ for a $10 M_{\rm J}$ planet}.
 In the figure, the vertical lines show the magnetic stand-off radius obtained by equation (\ref{eq:stand-off-radius_RGHJ}) below.

### 2015-12-29 ms.tex
typo corrected

@@
 where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux.
-For the former, combining equations (\ref{eq:fcyc}) and (\ref{eq:fplasma_RG}) leads to
-%%%
-\begin{eqnarray}
-a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
+For the former, combining equations (\ref{eq:fcyc}), (\ref{eq:scalingB}), and (\ref{eq:fplasma_RG}) leads to
+%%%
+\begin{eqnarray}
+a_{\rm min} (M_p) &=& 2.1~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
 &&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
@@
 \begin{eqnarray}
-a_{\rm max} (M_p) &=& 3.80~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
+a_{\rm max} (M_p) &=& 3.8~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
 {-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
-&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
+&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43/4} \\
 && \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
@@
 
-Using equation (\ref{eq:detect_prob}), the expected number for $M_p > >M_{p0}$ planet with detectable radio emission is $\sum _i \mathcal{P} _i(>M_{p0})$, where $\mathcal{P}_i(>M_{p0})$ is the probability for the $i$-th target.
+Using equation (\ref{eq:detect_prob}), the expected number for planets more massive than $M_{p0}$ with detectable radio emission is $\sum _i \mathcal{P} _i(>M_{p0})$, where $\mathcal{P}_i(>M_{p0})$ is the probability for the $i$-th target.
 

### 2015-12-29 ms.tex
Minor changes:  - 1 sentence per line  - connect \sim from numbers  - a few very minor word changes  - add punctuation and spaces to equation mode equations

@@
 In the case that the correlation with input magnetic energy is fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars are not well constrained for highly evolved stars; most of observations only set an upper limit \citep[e.g.,][]{konstantinova2010,petit2013,tsvetkova2013,konstantinova2013,auriere2015}.
-In the case of M-type giant EK boo, surface magnetic field $\sim 0.1-10 $G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
+In the case of M-type giant EK boo, surface magnetic field $\sim$0.1-10~G has been measured; In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus may also increase the planetary radio emission.
 However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.
 
-In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$ W for the average, \revise{$8.2\times 10^{10}$} W for the average of highly active time, and $4.5 \times 10^{11}$ W for the peak activity \citep{zarka_et_al2004}.
-Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
+In reality, the total power of Jovian auroral emission varies greatly over time: $1.3\times 10^{10}$~W for the average, \revise{$8.2\times 10^{10}$}~W for the average of highly active time, and $4.5 \times 10^{11}$~W for the peak activity \citep{zarka_et_al2004}.
+Here we employ $P_{\rm radio,\,J}=2.1\times 10^{11}$~W as a canonical value, following \citet{griesmeier2005,griesmeier2007b}.
 
@@
 where $m_p$ is the proton mass. 
-\revise{We note that the outflow ram pressures from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}. %
+\revise{We note that the outflow ram pressures from heated planets are negligible compared to these pressures, as discussed in Appendix \ref{ap:outflow}.
 }
@@
 We assume that the solid angle of the emission, $\Omega $, is same as the Jupiter's one for all of the exoplanets.
-In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim 1.6$, $\sim $6.3, and $\sim $3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
+In reality, the solid angles of auroral radio emission from  Jupiter, Saturn, and Earth are $\sim$1.6, $\sim$6.3, and $\sim$3.5, respectively \citep{desch+kaiser1984}, which are on the same order and will not significantly affect our order-of-magnitude estimate of radio emission.
 The bandwidth, $\Delta \nu$, is assumed to be proportional to the representative frequency of the emission, which is the cyclotron frequency, following \citet{griesmeier2007b}.
@@
 \begin{equation}
-B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3.  \label{eq:Bscaling2}
+B \propto B_{\rm dynamo} \left( \frac{r_{\rm dynamo}}{R_p} \right)^3 \, .  \label{eq:Bscaling2}
 \end{equation}
@@
 \begin{equation}
-\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)}. \label{eq:rho_r}
-\end{equation}
-%%%%%%%%%%
-We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit}=0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
+\rho [r] = \left( \frac{\pi M_p}{4 R_p^3} \right) \frac{\sin \left[ \pi \frac{r}{R_p} \right]}{\left( \pi \frac{r}{R_p} \right)} \, . \label{eq:rho_r}
+\end{equation}
+%%%%%%%%%%
+We determine the radius of outer boundary of the dynamo region, $r_{\rm dynamo}$, by assuming that the hydrogen becomes metallic when $\rho (r)$ exceeds the critical density $\rho_{\rm crit} = 0.7\,\mbox{g/cm}^3$ \citep{exoplanets2006, griesmeier2007b}.
 The density of the metallic core, $\rho _{\rm dynamo}$ is obtained by averaging the density in the core. 
@@
 \begin{equation}	
-L_p \sim 6.3\times10^{23} \; {\rm erg} \; \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, 
+L_p \sim 6.3\times10^{23} \; {\rm erg} \; \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_{\rm J}} \right)^{2.64} \, .
 \label{eq:burrowsLum}
@@
 \begin{equation}
-n = \frac{\dot M_\star}{4\pi a^2 m_p v_{\rm sw}}
+n = \frac{\dot M_\star}{4\pi a^2 m_p v_{\rm sw}} \, ,
 \label{eq:n}
@@
 n &=& 1.8 \times 10^6 \; {\rm cm^{-3}} \times \left( \frac{a}{5 \; {\rm AU}} \right)^{-2} \notag \\
-&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v_{\rm sw}}{30~\mbox{km/s}} \right)^{-1}. \label{eq:n_normalized}
+&&\times \left( \frac{\dot M_\star}{10^{-8} M_{\odot }{\rm /yr}} \right) \left( \frac{v_{\rm sw}}{30~\mbox{km/s}} \right)^{-1} \, . \label{eq:n_normalized}
 \end{eqnarray}
@@
 R_{\rm acc} &=& \frac{2GM_p}{v_{\rm rel}^2} \\
-&\sim & 4.0~R_{\rm J} \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{v_{\rm rel}}{30 ~{\rm km~s^{-1}}} \right)^{-2}
+&\sim & 4.0~R_{\rm J} \left( \frac{M_p}{M_{\rm J}} \right) \left( \frac{v_{\rm rel}}{30 ~{\rm km~s^{-1}}} \right)^{-2} \, .
 \end{eqnarray}
@@
 L_{\rm acc} \sim &&  10^{25} \; {\rm erg\;s}^{-1} \left( \frac{\dot M_*}{10^{-8} M_{\odot }/{\rm yr}} \right)  \notag \\
-&& \times \left( \frac{M_p}{M_{\rm J}} \right)^3 \left( \frac{M_*}{M_{\odot }} \right). \label{eq:Lacc}\\
-%
-T_{\rm acc} \sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_{\rm J}} \right). \label{eq:Tacc}
-\end{eqnarray}
-%%%%%%%%%
-The accretion onto planets, therefore, leads to emission of UV/X-ray radiation 
-whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$. 
+&& \times \left( \frac{M_p}{M_{\rm J}} \right)^3 \left( \frac{M_*}{M_{\odot }} \right) \, . \label{eq:Lacc}\\
+%
+T_{\rm acc} \sim && 2 \times 10^5 ~\mbox{K} \left( \frac{M_p}{M_{\rm J}} \right) \, . \label{eq:Tacc}
+\end{eqnarray}
+%%%%%%%%%
+The accretion onto planets, therefore, leads to emission of UV/X-ray radiation whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$.
 Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
@@
 %%%%%%%%%
-where $E_{\rm photon}$ is the energy per photon, 
-and $\beta [T_e]$ is the ``class B'' recombination coefficient which is 
-$ \beta \sim 2.6 \times 10^{-13}\;{\rm cm^3/sec} $ \citep{pequignot1991} 
-at electron temperature of stellar wind of evolved stars, $T_e \sim 10^4 $K \citep{suzuki2007}.
-
-The source rate is obtained by counting the number of photons with energy exceeding the ionization energy of hydrogen ($E_{\rm Rydberg} = 13.6$~eV, 
-or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
+where $E_{\rm photon}$ is the energy per photon, and $\beta [T_e]$ is the ``class B'' recombination coefficient which is $\beta \sim 2.6 \times 10^{-13}\;{\rm cm^3/sec} $ \citep{pequignot1991} at the electron temperature of the stellar wind of evolved stars, $T_e \sim 10^4$~K \citep{suzuki2007}.
+
+The source rate is obtained by counting the number of photons with energy exceeding the ionization energy of hydrogen ($E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
 %%%%%%%%%
@@
       3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_{\rm J})
-    \end{array}. 
+    \end{array} \, .
   \right.
@@
 The detailed electromagnetic structure around RGHJs therefore requires elaborate numerical simulations, which is beyond the scope of this paper.
-Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate.
-}
+Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate.}
 
@@
    \caption{Upper panels: Radius and average density of the dynamo region as a function of planetary mass.
-Lower panels: evolutions of heat flux at the outer boundary, planetary magnetic field, and maximum cyclotron frequency, for planets with varying masses ($M_{\rm J}$: blue, $5M_{\rm J}$: green, and $10M_{\rm J}$: red).
-}
+     Lower panels: evolutions of heat flux at the outer boundary, planetary magnetic field, and maximum cyclotron frequency, for planets with varying masses ($M_{\rm J}$: blue, $5M_{\rm J}$: green, and $10M_{\rm J}$: red).}
   \label{fig:planetaryB}
@@
 Note that the cyclotron frequency of Jovian planets typically falls between 10~MHz and 1~GHz. 
-In this regime, there are a number of current and near-future radio wave detectors including GMRT, 
-LOFAR, HERA, SKA, and potential upgrades to the VLA (see Section \ref{ss:detectability}).
+In this regime, there are a number of current and near-future radio wave detectors including GMRT, LOFAR, HERA, SKA, and potential upgrades to the VLA (see Section \ref{ss:detectability}).
 
@@
 We may compare radio emission power of RGHJs at 5 AU with that of canonical hot Jupiters set at 0.05 AU.
-Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows.
+Then, equation (\ref{eq:Pkinp}) can be re-normalized as follows:
 %%%
@@
 Compared with the equivalent Jupiter-like planets around main sequence stars, the massive stellar wind of late red giants can increase the radio emission from planetary companions by more than two orders of magnitude, which allow us to explore 10 times more distant system, i.e., 1000 times more volume.
-This compensates the small population of evolved stars at least partly.
-
-Equation (\ref{eq:F_nu_RGHJ}) gives a spectral flux density that 1--2 orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
+This at least partially compensates for the small population of evolved stars.
+
+Equation (\ref{eq:F_nu_RGHJ}) gives a spectral flux density that 1---2 orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial values and full ionization.
 This is primarly because their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
@@
 Over the last four decades there have been numerous radio continuum observations of nearby red giants, many with the aim of understanding the extended atmospheres and mass-loss mechanisms of K- and M-type giants~\citep[e.g.,][]{Newell1982, Knapp1995, Skinner1997, Lim1998, OGorman2013}.
-Almost all observations have been carried out 
-at frequencies $\geq$5~GHz, 
-probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
+Almost all observations have been carried out at frequencies $\geq$5~GHz, probing thermal Bremsstrahlung emission from the large, partially ionized envelopes surrounding the giant stars~\citep{drake1986}.
 The spectral index of this emission is of order unity, with a range of reported values for various sources between 0.8 and 1.6~\citep{OGorman2013}.
@@
 For this purpose, we obtained the list of M-type red giants from Table 4 of \citet{dumm1998} with the data of mass, radius, and effective temperature. 
-\revise{We note that their data do not unambiguously distinguish RG from early AGB stars and thus the list probably consists of about 40\% early AGB stars.
+\revise{We note that their data do not unambiguously distinguish RG from early AGB stars and so about 40\% of the list probably consists of early AGB stars.
 }\memoYF{grammatical question: doesn't ``consists of'' sound like ``A is made of B''?}
@@
 \begin{equation}
-\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \label{eq:mass-loss}
+\dot M_\star [M_\odot{\rm /yr}] \sim 8 \times 10^{-14} \frac{\tilde L \tilde R}{\tilde M} \left( \frac{T_{\rm eff}}{4000} \right)^{3.5} \left( 1 + \frac{g_{\odot }}{4300 g_{\star}} \right) \, , \label{eq:mass-loss}
 \end{equation}
@@
 %%%
-The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass. We simply assume:
-%%%
-\begin{equation}
-t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5}
+The age of the system is assumed to be roughly the same as the lifetime of the main-sequence stage, which depends on the stellar mass.
+We simply assume:
+%%%
+\begin{equation}
+t \sim 10\,{\rm Gyr}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{-2.5} \, .
 \end{equation}
@@
 \begin{equation}
-\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} 
-\end{equation}
-%%%
-In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{http://www.rssd.esa.int/index.php?project=HIPPARCOS}.
+\nu_{\rm cyc,\,max} \sim 20 \,{\rm MHz}\, \left( \frac{M_{\star}}{M_{\odot }} \right)^{1.075} \left( \frac{M_p}{M_{p,\,{\rm J}}} \right)^{1.04} \, .
+\end{equation}
+%%%
+In addition, the distance to the system is obtained based on the parallax data from Hipparcos datasets\footnote{\url{http://www.rssd.esa.int/index.php?project=HIPPARCOS}}.
 
@@
 For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
-$10~M_{\rm J}$ planets at $\sim 1$ AU may be detectable out to $\sim 200$~pc.
+$10~M_{\rm J}$ planets at $\sim$1~AU may be detectable out to $\sim$200~pc.
 
@@
 \enddata
-\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported 
-in this table (Equation~\ref{eq:rms_sens}).}
-\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection
-of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
+\tablenotetext{a}{RMS noise in a 1-hour observation, computed for imaging of the full band reported in this table (Equation~\ref{eq:rms_sens}).}
+\tablenotetext{b}{The integration time in hours required to reach an RMS of 2~$\mu$Jy (i.e.\ 5-$\sigma$ detection of a typical source at 100~pc with 10~$\mu$Jy bm$^{-1}$ average flux).}
 \tablenotetext{c}{Source confusion RMS contribution.}
@@
 \sigRMS = \frac{2 k \Tsys}{A_{\rm eff} \, \sqrt{\Delta \nu \, \tau N (N-1)}} 
-\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right).
+\left(\frac{\rm 10^{26} Jy}{\rm W m^{-2} Hz^{-1}}\right) \, .
 \label{eq:rms_sens}
@@
 %%%
-As Table~\ref{tab:sens} illustrates, source confusion is likely to exceed the 2 $\mu$Jy detection limit of a typical RGHJ source for most
-telescopes under consideration.  However, source confusion can be mitigated through differencing observations that cancel out background sources.
+As Table~\ref{tab:sens} illustrates, source confusion is likely to exceed the 2 $\mu$Jy detection limit of a typical RGHJ source for most telescopes under consideration.
+However, source confusion can be mitigated through differencing observations that cancel out background sources.
 Potential axes for such cancellation are polarization and time.
@@
 In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
-%
 We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
-%
 }
@@
 
-YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science and from an appointment to the NASA Postdoctoral
-Program at NASA Ames Research Center, administered by Oak Ridge Affiliated Universities. 
-DSS gratefully acknowledges support from a fellowship from the AMIAS group. JN acknowledges support from NASA grant HST AR-12146.04-A and NSF grant AST-1102738.
+YF is supported from the Grant-in-Aid No.
+25887024 by the Japan Society for the Promotion of Science and from an appointment to the NASA Postdoctoral Program at NASA Ames Research Center, administered by Oak Ridge Affiliated Universities.
+DSS gratefully acknowledges support from a fellowship from the AMIAS group.
+JN acknowledges support from NASA grant HST AR-12146.04-A and NSF grant AST-1102738.
 We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.
@@
 YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
-The portion of this research for which TM is responsible was performed under a National Research 
-Council Research Associateship Award at the Naval Research Laboratory (NRL).
+The portion of this research for which TM is responsible was performed under a National Research Council Research Associateship Award at the Naval Research Laboratory (NRL).
 Basic research in radio astronomy at NRL is supported by 6.1 Base funding.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-where $T_c$ and $r_c$ are the radius and temperature at exobase. In most of the cases we consider, therefore, the escape is safely assumed to be Jeans escape. 
+where $T_c$ and $r_c$ are the radius and temperature at exobase.
+In most of the cases we consider, therefore, the escape is safely assumed to be Jeans escape. 
 The rate of Jeans escape is 
@@
 However, for energy transfer of order a Rydberg $\alpha/2a_0$ we can estimate the transfer momentum and see that it is larger than the inverse of the Bohr radius $a_0$.
-This implies that in this range the above estimate may actually be reliable. The transfer momentum is
-\begin{equation}
-q^2 =\frac{1}{4} m^2 v_{\rm rel}^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2v_{\rm rel}^2 \sin^2 \frac{\theta}{2}.
+This implies that in this range the above estimate may actually be reliable.
+The transfer momentum is
+\begin{equation}
+q^2 =\frac{1}{4} m^2 v_{\rm rel}^2 (\sin^2\theta +(1-\cos \theta)^2)= m^2v_{\rm rel}^2 \sin^2 \frac{\theta}{2} \, .
 \end{equation}
@@
 \begin{equation}
-E_{\rm recoil} = \frac{q^2}{2m}.
+E_{\rm recoil} = \frac{q^2}{2m} \, .
 \end{equation}
@@
 \begin{equation}
-r=\frac{mv_\bot }{eB}.
+r=\frac{mv_\bot }{eB} \, .
 \end{equation}
@@
 \begin{equation}
-\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B}.
+\mu = \frac{e}{2\pi r/v_\bot} \pi r^2 = \frac{1}{2} e r v_\bot = \frac{mv_\bot^2}{2B} \, .
 \end{equation}
@@
 \begin{equation}
-\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu.
+\int d^3{\boldsymbol r} B_c = \frac{8\pi}{3} \mu \, .
 \end{equation}
@@
 \begin{equation}
-\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B},
+\frac{B_c}{B} = \frac{n(mv_\bot^2/2)}{3 B^2/8\pi} < \frac{\rho_K}{3\rho_B} \, ,
 \end{equation}
@@
 and thus $\rho_K/\rho _B < 1$. 
-When the particle spirals into the planet, 
-the magnetic pressures increases as 
-%%%
-\begin{equation}
-\frac{B^2}{8\pi } \propto \frac{1}{r^6}
+When the particle spirals into the planet, the magnetic pressures increases as 
+%%%
+\begin{equation}
+\frac{B^2}{8\pi } \propto \frac{1}{r^6} \, .
 \end{equation}
@@
 f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
-&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
+&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta } \, ,
 \end{eqnarray}
@@
 \begin{equation}
-\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
+\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \, , \label{eq:detect_prob}
 \end{equation}
@@
 a_{\rm min} (M_p) &=& 2.1~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
-&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
-\end{eqnarray}
-%%%
-while for the latter, equations (\ref{eq:scalingB}) and (\ref
-{eq:F_nu_RGHJ}) indicate
+&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} \, ,
+\end{eqnarray}
+%%%
+while for the latter, equations (\ref{eq:scalingB}) and (\ref {eq:F_nu_RGHJ}) indicate
 %%%
@@
 && \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43/4} \\
-&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
+&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} \, .
 \end{eqnarray}
@@
 Figure \ref{fig:expected_values} show the expected number of detection as a function of threshold planetary mass $M_{p0}$.
-This figure indicates that, if all of the target in Figure \ref{fig:observability} are red giant stars, %
-the total number of detections would be about 4 (7), provided that the sensitivity of the radio instruments $F_{\rm min}$ is $10~\mu {\rm Jy}$ ($5~\mu {\rm Jy}$). 
+This figure indicates that, if all of the target in Figure \ref{fig:observability} are red giant stars, the total number of detections would be about 4 (7), provided that the sensitivity of the radio instruments $F_{\rm min}$ is $10~\mu {\rm Jy}$ ($5~\mu {\rm Jy}$).
 However, such high sensitivity of the instrument will not be achieved at low frequency, which makes us consider massive planets as candidates. 
-Roughly assuming that $\nu _{\rm cyc} > 200~{\rm MHz} $ (i.e. $M_p > 7 M_{\rm J}$) is needed, then the expected values of detections would be reduced to 1-2.
+Roughly assuming that $\nu _{\rm cyc} > 200~{\rm MHz} $ (i.e. $M_p > 7 M_{\rm J}$) is needed, then the expected values of detections would be reduced to 1---2.
 

### 2015-12-29 ms.tex
More minor edits:  - replace unit barye with dyne~cm^{-2}  - put $\sim$ next to value when not in an equation  - slight rewrite of a few sentences

@@
 Extrapolating this scaling to exoplanets, radio emission from exoplanetary systems has been examined. 
-\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim $1 mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
+\citet{farrell1999,zarka2001,lazio2004} estimated that a few of the known exoplanetary systems may have radio flux of $\sim$1~mJy level, due to the small orbital distance of the planet and/or the larger planetary mass.
 \citet{stevens2005} gave improved estimates of the stellar mass-loss rate based on X-ray flux and re-evaluated the radio flux of known exoplanetary systems. 
@@
 During this time, such planets can be transiently heated to hot-Jupiter temperatures ($\gtrsim$1000~K) at distances out to tens of AU, depending on the star's mass; such planets are termed ``Red Giant Hot Jupiters'' (RGHJs), though the term can refer to planets orbiting either RGB and AGB stars \citep{spiegel+madhusudhan2012}.
-Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim 10^{-8} M_\odot$/yr to $\sim  10^{-5} M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}.
+Such planets are also subject to interactions with a massive (but slow) stellar wind, as the mass-loss rate of evolved stars is significant, ranging from $\sim$10$^{-8}$~$M_\odot$/yr to $\sim$10$^{-5}$~$M_\odot$/yr with the highest values for AGB stars \citep[e.g.,][]{reimers1975, schild1989, vassiliadis1993, schoier2001, vanloon2005}.
 On the assumption that the radio emission is correlated with the stellar wind, planetary companions around evolved stars could also generate bright radio emission.
@@
 The stellar wind velocity, $v_{\rm sw}$, becomes smaller as the star evolves.
-The wind velocity is typically of order the escape velocity at a distance of several stellar radius \citep{suzuki2007}, i.e., $\sim \sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star}$.
+The wind velocity is typically of order the escape velocity at a distance of several stellar radius \citep{suzuki2007}, i.e., $\sim$$\sqrt{2GM_{\star}/R'_{\star}}$ where $R'_{\star} \sim (4-5) R_{\star}$.
 For a star with radius $R_{\star }=100~R_{\odot }$, this results in $v_{\rm sw}\sim 30~{\rm km/s}$.
@@
 The contributions for the velocity term in equation (\ref{eq:Pinp_kin}), which should be the relative velocity between the planet and the solar wind, are given by the stellar wind velocity, the infall velocity (i.e., the acceleration due to planet's gravitational field), and the planetary orbital velocity.
-While $v_{\rm sw}$ is $\sim$30~km/s, the infall velocity from the planetary gravity is $\sim 10-25~{\rm km/s}$ depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$), and the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$).
+While $v_{\rm sw}$ is $\sim$30~km/s, the infall velocity from the planetary gravity is $\sim$10-25~km/s depending on the planetary mass (ranging from $1 M_{\rm J}-10 M_{\rm J}$), and the orbital velocity is $10-30~{\rm km/s}$ depending on the orbital distance (ranging from $1-5~{\rm AU}$).
 In the next section, we simply consider
@@
 
-As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind is lowered down to order of $\sim 10^{-3}$ \citep{drake1987}.
+As discussed in \citet{ignace2010}, as the stars evolve, the ionization fraction of the stellar wind diminishes to of order $\sim$10$^{-3}$ \citep{drake1987}.
 Since only charged particles interact with planetary magnetic field, this suggests inefficient interaction with planetary magnetosphere and hence low input energy for radio emission.
@@
 %%%%%%%%%
-The accretion onto planets, therefore, leads to emission of UV/X-ray radiation whose characteristic energy $\sim k_B T_{\rm acc} $ exceeds the ionization energy of hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$.
+The accretion onto planets, therefore, leads to emission of UV/X-ray radiation whose characteristic energy $\sim$$k_B T_{\rm acc}$ exceeds the ionization energy of hydrogen, $E_{\rm Rydberg} = 13.6$~eV, or $\lambda = 91.2\rm~nm$.
 Therefore, UV/X-ray radiation from accretion will create local ionized region around the planet.
@@
 For the accretion onto large planets, however, the characteristic photon energy is so high that the released energetic electrons may also ionize other atoms in the vicinity.
-The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$ \citep{fite1958}, which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
+The cross section\footnote{This is close to the geometric cross section of the Bohr radius.} of hydrogen for electrons is $\sim$4$\times$10$^{-17}$~cm$^2$ \citep{fite1958}, which implies a mean free path for ionized electrons of $\sim$2$R_J$ in the surrounding medium.
 As a result, nearly 2/3 of released energetic electrons will ionize a hydrogen atom within $\sim$2$R_J$, and more than 99\% will ionize a hydrogen atom within $\sim$10$R_J$.
@@
 The ionization fraction $x$ as a solution of equation (\ref{eq:equilibrium}) is shown in Figure \ref{fig:ionizationfraction}. 
-When, $\tau \sim n \sigma _H r$ is much smaller than unity and thus $e^{-\tau }$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
+When, $\tau \sim n \sigma_H r$ is much smaller than unity and thus $e^{-\tau}$ term can be ignored (that is the case for $M_p = 10 M_{\rm J}$),  the solution is simply
 %%%%%%%%%
@@
 \begin{eqnarray}
-\nonumber F_{\star}(\nu ) &\sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
+\nonumber F_{\star}(\nu ) & \sim & (0.4-1.4) \times 10^{-5} ~\mbox{Jy} \times \\
 && \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \!\! \left( \frac{R_{\star }}{100~R_{\odot}} \right)^2 \!\! \left( \frac{\nu}{1~\mbox{GHz}} \right)^{\alpha_* } 
@@
 where $\tilde L = L_{\star }/L_{\odot }(=4\pi R_{\star }^2 T_{\star }^4)$ is the stellar luminosity, $\tilde R = R_{\star }/R_{\odot }$ is the stellar radius, $\tilde M = M_{\star }/M_{\odot }$ is the stellar mass, and $g$ is the surface gravity.
-The velocity of the stellar wind is assumed to be the escape velocity at $\sim 4 R_{\star }$:
+The velocity of the stellar wind is assumed to be the escape velocity at $\sim$$4 R_{\star}$:
 %%%
@@
 Using these data, we calculate the spectral flux of radio emission by specifying planetary mass and orbital distance of a hypothetical planetary companion. 
-We consider [A] a Jupiter-twin whose maximum cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 20\,(M_{\star }/M_{\odot})$~MHz, and [B] a larger Jovian planet with $M_p\sim 10M_p$ whose cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 200\,(M_{\star }/M_{\odot})$~MHz.
+We consider [A] a Jupiter-twin whose maximum cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 20\,(M_{\star }/M_{\odot})$~MHz, and [B] a larger Jovian planet with $M_p \sim 10M_p$ whose cyclotron frequency is $\nu _{\rm cyc,\,max} \sim 200\,(M_{\star }/M_{\odot})$~MHz.
 
@@
 The difference of the symbols indicates whether the radio emission can escape from the system (circle), i.e., $\nu _{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$,  or not (cross). 
-Assuming Jupiter-mass planets \revise{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{148 (12)} systems have potential to emit radio wave at the level above $\sim 10~\mu {\rm Jy}$  out to $\sim 100-300$ pc, while those with the highest mass-loss rate would suffer from the plasma cut-off of the stellar wind.
-For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
+Assuming Jupiter-mass planets \revise{at 1 AU (5 AU)} which typically have the maximum cyclotron frequency at $10-100$~MHz depending on the age, \revise{148 (12)} systems have potential to emit radio waves at the level above $\sim$10$~\mu$Jy out to $\sim$100-300~pc, while those with the highest mass-loss rates would suffer from the plasma cut-off of the stellar wind.
+For more massive planets with the maximum cyclotron frequency at around $100-1000$~MHz, the radio flux density is lowered due to its dependence on $B^{-1/3}$ (equation (\ref{eq:F_nu})), but more likely to get to the Earth.
 $10~M_{\rm J}$ planets at $\sim$1~AU may be detectable out to $\sim$200~pc.
@@
 The low-frequency component of the Square Kilometer Array (SKA), recently rebaselined to have 0.4~km$^2$ collecting area in 130,000 elements with baselines extending to 65~km, will operate from 50-350~MHz.\footnote{\url{https://www.skatelescope.org/news/worlds-largest-radio-telescope-near-construction/}}
-We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim 30 M_{\rm J}$ Jupiters.
+We estimate the noise in the lower half of the band ($\nu<200~\rm MHz$), appropriate for lower mass ($\lesssim 10 M_{\rm J}$) separately from the full band, which could be used to detect $\sim$$30 M_{\rm J}$ Jupiters.
 We again adopt the \cite{Rogers+Bowman2008} relation for \Tsys\ (Equation~\ref{eq:Tsky}), and assume $\Trx \approx 60~\rm K$.
@@
 The noise estimates shown in Table \ref{tab:sens} indicate that, at the frequencies relevant for the detection of radio emission from Jupiter-size planets, current instrument sensitivities are generally too low.
-On the other hand, for more massive exoplanets ($M_p\sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within half a day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU within $\sim $200~pc, or those at $\sim$5~AU within $\sim $100~pc.
+On the other hand, for more massive exoplanets ($M_p \sim 10 M_{\rm J}$) where the bulk of the radio emission would exist above 50~MHz, low frequency component of SKA will be able to detect the signal within half a day from planets with $M_p \sim 10~M_{\rm J}$ at $\sim$1~AU within $\sim$200~pc, or those at $\sim$5~AU within $\sim$100~pc.
 VLA-LOBO could also work for a few nearby systems.
@@
 
-\paragraph{Modulation due to planetary spin rotation (a few hours $\sim $)}
+\paragraph{Modulation due to planetary spin rotation (a few hours $\sim$)}
 The probability of the occurrence of the Jovian radio burst is correlated with the spin rotation phase \citep[e.g.][]{dessler1983} due to the misalignment between the magnetic axis and the spin axis.
@@
 %
-\paragraph{Modulation due to the presence of satellites (a few days $\sim $)}
+\paragraph{Modulation due to the presence of satellites (a few days $\sim$)}
 The occurrence probability of Jovian radio burst is affected by the location of Io as well \citep{dessler1983}, because Io disturbs the surrounding electromagnetic field. 
@@
 
-\paragraph{Variability of the stellar wind (a few months $\sim $?)}
+\paragraph{Variability of the stellar wind (a few months $\sim$?)}
 If the stellar wind passing the planet is variable, any modulation of the plasma density would also lead to time variability of planetary radio emission.
@@
 %
-\paragraph{Modulation due to orbital motion of the planet (a few years $\sim $)}
+\paragraph{Modulation due to orbital motion of the planet (a few years $\sim$)}
 If the planetary orbit is close to the edge-on configuration, the radio emission disappears concurrently with the planetary orbital motion, due to the increased plasma cut-off frequency along the path and/or secondary eclipse \citep{lecavelier_et_al2013}.
 The former is because when the planet is behind the star the path of the radio emission toward the Earth comes through the vicinity of the star where the plasma density is high.
-The probability of the latter one, secondary eclipse, is $\sim R_\star/a \sim 9$\% (in the case that $R_{\star}=100R_{\odot }$ and $a=5~\mathrm{AU}$). 
+The probability of the latter one, secondary eclipse, is $\sim$$R_\star/a \sim 9$\% (in the case that $R_{\star}=100R_{\odot }$ and $a=5~\mathrm{AU}$). 
 %
@@
 A major obstacle to observe this radio emission is the plasma cut-off frequency of the (ionized) stellar wind.
-Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim 12$ MHz for typical red giants and $\sim$ 400 MHz for typical AGB stars, making planetary-mass companions to AGB stars unpromising for the search of planetary auroral radio emission.
+Due to the great density of the stellar wind, the cut-off frequency is as high as $\sim$12~MHz for typical red giants and $\sim$400~MHz for typical AGB stars, making planetary-mass companions to AGB stars unpromising for the search of planetary auroral radio emission.
 The most promising targets are massive planetary companions ($M_p \gtrsim 4 M_{\rm J}$ to red giant stars, with magnetic field stronger than Jupiter (i.e., higher cyclotron frequency).
 
-The radio flux from a system with a Jovian exoplanet at a distance of 100~pc would typically be on the order of $\sim 10 \mu $Jy.
+The radio flux from a system with a Jovian exoplanet at a distance of 100~pc would typically be on the order of $\sim$10~$\mu$Jy.
 Such signals would be detectable with SKA within half a day. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-which indicates $3.6\times 10^{-7}~{\rm barye}$ even when $\lambda _c = 1$. 
-On the other hand, the ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim 2.7 \times 10^{-5} ~{\rm barye}$. 
+which indicates $3.6\times 10^{-7} {\rm~dyne~cm^{-2}}$ even when $\lambda _c = 1$. % DSS: barye is a unit that no one uses
+On the other hand, the ram pressure of the stellar wind or planetary magnetic pressure (either hand of equation (\ref{eq:stand-off})) is $\sim$2.7$\times$10$^{-5} {\rm~dyne~cm^{-2}}$. 
 This implies that the ram pressure of the planetary outflow would be negligible.
@@
 
-Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim $ 3.9\% \citep{cumming2008}.
+Observations suggest that the occurrence rate of planets with masses $M_{\rm J} < M_p \sin i < 2 M_{\rm J}$ in orbits $1 {\rm AU} < a < 5 {\rm AU}$ around F, G, or K stars is $\sim$3.9\% \citep{cumming2008}.
 %
@@
 %
-For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim 3.1\%$ \citep{cumming2008}, one could expect additional $\sim 1$ radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$.
+For larger planets ($M_p>2M_{\rm J}$), the number of potentially detectable systems are less, due to both the $B^{-1/3}$ dependence of the spectral flux: the number of systems where a 10 $M_{\rm J}$ planet at 1 AU (5 AU) emit $>10~\mu {\rm Jy}$ is 98 (5): Since the occurrence rate of such larger planets in the same orbital region is $\sim$3.1\% \citep{cumming2008}, one could expect additional $\sim$1 radio source detection from larger planets with sensitivity $10~\mu {\rm Jy}$.
 

### 2015-12-29 ms.tex
Edits to Introduction

@@
 In \citet{reiners2010}, the authors adopted a new scaling relation of planetary magnetic fields based on \citet{christensen_et_al2009}.
-We note that \revise{\citet{jardine2008} modeled reconnection between the magnetic fields of close-in planets and that of the star to obtain estimates that are not based on the ``radiometric Bode's law''.}
+\revise{\citet{jardine2008} modeled reconnection between the magnetic field of a close-in planet and that of the host star to obtain estimates that are not based on the ``radiometric Bode's law''.}
 Although observational searches for these radio signatures are underway, no clear detection has been claimed \revise{\citep{bastian2000,george2007,smith2009,stroe2012,hallinan2013,murphy2015}}, while there are some promising initial results \citep{lecavelier_et_al2013,sirothia2014}.
@@
 They found that the low ionization fraction of the stellar wind of evolved stars suppresses their radio emission and leads to weak radio emission. 
-\revise{In addition, they considered the scenario where the post-bow shock heating could produce ionized hydrogen atoms.
-This indicates a configuration of radio wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit.
-}
+\revise{In addition, they considered a scenario in which post-bow shock heating could produce ionized hydrogen atoms.
+This indicates a configuration of radio-wave generation very different from that of Solar System, and the lower-limit estimate, at least, is well below the detection limit.}
 
@@
 Thus, by extrapolating the ``radiometric Bode's law,'' we provide more optimistic estimates compared to the previous result. 
-\revise{In addition, two major updates from \citet{ignace2010} are the following.}
-\revise{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detect radio emission from RGHJs. 
-\revise{Second, we discuss the planetary parameter space to  search for radio emission, employing the scaling law of planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}
-
-In Section \ref{s:assumptions}, we introduce the framework to obtain the frequency and the flux of planetary auroral radio emission, and describe our models for the stellar wind and planetary magnetosphere.
+\revise{In addition, we introduce two major advances beyond the work of \citet{ignace2010} that are related to the observability of radio emission from RGHJs.}  % I don't like referring to our work as "updates" from Ignace
+\revise{First, we estimate} the plasma frequency cut-off of the stellar wind, which turns out to be one of the major obstacles to detecting radio emission from RGHJs.
+\revise{Second, we discuss the planetary parameter space to search for radio emission, employing scaling laws for the planetary magnetic field, noting that the survey of exoplanets around highly evolved stars is not complete.}
+
+In Section \ref{s:assumptions}, we present the framework to obtain the frequency and the flux of planetary auroral radio emission, and describe our models for the stellar wind and planetary magnetosphere.
 Section \ref{s:result} presents the estimates of the spectral radio flux of RGHJs and compares the predictions with what might be expected from canonical hot Jupiters as well as those from Jupiter-twins.

### 2015-12-29 ms.tex
a few final touches, mainly wording changes. --tony

@@
 %   \plotonesc{cartoon_10Mj_100pc_smooth.pdf}
-   \caption{A cartoon of radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
-     The spectrum of RGHJ is modeled after Jovian radio spectra, e.g. Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; contribution from Io-DAM is not shown here.
+   \caption{A cartoon of the radio emission spectra of a RGHJ with 10$M_{\rm J}$ and the host red giants with 100 $R_{\odot }$.
+     The spectrum of the RGHJ is modeled after Jovian radio spectra, e.g.\ Figure 8 of \citet{zarka_et_al2004} and Figure 2 of \citet{griesmeier2007a}; the contribution from Io-DAM is not shown here.
      The spectra of the host red giant are modeled simply by extrapolating observed radio spectra above 1~GHz with power law.
-     \revise{The shadowed region represents the frequency below the plasma frequency of the stellar wind.}}
+     \revise{The shaded region represents the portion of the spectrum below the plasma frequency of the stellar wind.}}
   \label{fig:cartoon}
@@
 \revise{%
-Once planetary radio emission is detected, it provides a unique approach for learning the planetary property.
-As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites.
-If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g.
-radial-velocity observations, tests  the proposed scaling law of planetary dynamo.
+Once planetary radio emission is detected, it provides a unique approach for studying the planet's property.
+As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to infer the planetary spin rotation period or the presence of satellites.
+If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength at the planetary surface, which, when combined with constraints on the planetary mass via e.g.\ radial-velocity observations, tests the proposed scaling law of planetary dynamo.
 Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, probes the stellar wind properties at the planetary orbit.
 In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''.
-We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
+We also note that the radio emission of RGHJs may be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars.
 }
